### 2019-10-22 text/suppl_methods.Rmd
first commit

---
author: "N.S."
date: "15 October 2019"
output: html_document
---

# Supplementary methods
## Species selection
-> bigger than 7cm 
-> Family for which we had cnp body content data
-> omit extreme rare species (X%)

## 1. Parameter estimates

### 1. Growth parameters

#### Data compilation
We used the parameter kmax see renato paper

We extracted the data from @Morais2019 and filtered out only the species of our species list. As the Lenth-Frequency method consistently overestimates kmax, we omitted the kmax estimates coming from this method. In total this selection process resulted in xx observations of kmax for different species and temperatures.

Further, we used the otolith data provided by Morat et al. and fitted vbgc's to all species at each loction for which there were at least 3 individuals. We fitted the model using bayesian regression models as provided by fishflux. kmax was obtained using similar methods as described in @Morais2019. 
In total we retrieved 57 kmax observations for xx species and xx locations of varying sst's.

After combining the two data sources, we obtained a database of 496 observations and 181 number of species. 
kmax is mostly determined by body size and temperature. 
Morais and bellwood account for phylogeny, but don't actually include it for predictions. Here we try to include phylogeny directly.

#### Statistical analysis

\noindent We applied a hierarchical model to predict the growth rate of fishes in function of body size, temperature and phylogeny:

\begin{equation}
	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}size +  \beta_\textrm{2} sst + \epsilon,
	\label{kmax}
\end{equation}

where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, \gamma_\textrm{0phy} is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.

\noindent

Phylogenetic re
Thephylogenetic heritability (equivalent to Pagel’\lambda (29,30)), was estimated asthe proportion of total variance, conditioned on the fixed effects, attributable to the random effect of phylogeny (i.e.s2[lng0phy]=(s2[lng0phy]+s2[lng0spp]+s2[lne]))

We use the R package brms to fit a bayesian phylogenetic regression model We predict log(kmax) in function of log(sizemax), sst with varying intercept per species. The intercept per species is structured by the covariance matrix.

 Family: gaussian 
  Links: mu = identity; sigma = identity 
Formula: log(kmax) ~ log(sizemax) + sstmean + (1 | phylo) 
   Data: oto (Number of observations: 496) 
Samples: 4 chains, each with iter = 2000; warmup = 1000; thin = 1;
         total post-warmup samples = 4000

Group-Level Effects: 
~phylo (Number of levels: 181) 
              Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00

Population-Level Effects: 
           Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
Intercept      0.66      0.58    -0.48     1.81       1498 1.00
logsizemax    -0.76      0.10    -0.96    -0.57       1281 1.00
sstmean        0.02      0.01    -0.00     0.05       4071 1.00

Family Specific Parameters: 
      Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
sigma     0.46      0.02     0.43     0.50       1991 1.00

Samples were drawn using sampling(NUTS). For each parameter, Eff.Sample 
is a crude measure of effective sample size, and Rhat is the potential 
scale reduction factor on split chains (at convergence, Rhat = 1).

phylogenetic signal is 0.76 (0.65, 0.84). 
bayes R2 is 0.73759 (0.702, 0.769).

For extrapolation we use:
phyestimate from package picante which uses brownian motion 
with this we extrapolate the phylogenetic effect for each iteration. We only use one chain in order to keep computational time reasonable.

For each draw, we extrapolate the phylogenetic effect for 100 trees and then take the average effect of these 100 trees. 
This is done for each draw. To take into account the temperature variation in which species can occur, we predict the kmax for each temperature (rounded 1 °C) where a species occurs in the global uvc database. This results in kmax predictions for 4712 cases and 1110 species. (extra table?) To predict kmax per draw we used the respective estimates of intercept and slopes. 
Finally, we summarised all kmax predictions per sst per species by taking the mean and standard deviation across all draws.

### 2. Diet

### 3. Body stoichiometry
#### 3.1 Data collection

#### 3.2 Data analysis

only species with nrep >= 3

Stoichiometry is well conserved within taxonomic entities. Through a database of 1633 individuals, 108 species, locations: Moorea, Palmyra, Carribean

25 families
 [1] "Acanthuridae"   "Balistidae"     "Bothidae"       "Chaetodontidae" "Cirrhitidae"    "Fistulariidae" 
 [7] "Haemulidae"     "Holocentridae"  "Kyphosidae"     "Labridae"       "Lethrinidae"    "Lutjanidae"    
[13] "Monacanthidae"  "Mugilidae"      "Mullidae"       "Ostraciidae"    "Pempheridae"    "Pomacanthidae" 
[19] "Pomacentridae"  "Sciaenidae"     "Scorpaenidae"   "Serranidae"     "Siganidae"      "Tetraodontidae"
[25] "Zanclidae"

multivariate model

extrapolation

phylopars from rphylopars
for each iteration of 1 chain, for each tree of 100 trees

### 2019-10-22 R/functions_wrangling.R

@@ -1,0 +1,196 @@
+
+## combine parameters ##
+
+load("data/fishtree_glob.RData")
+
+
+##### sptl #####
+get_sptl <- function(x){
+  sptl <- read.csv("data/species_list_tl.csv")
+  sptl$Species <- gsub("_", " ", sptl$species)
+  tax <- rfishbase::load_taxa()
+  sptl <- right_join(dplyr::select(tax, Species, Family), sptl)
+  sptl[sptl$species == "Rhinesomus_triqueter", "Family"] <- "Ostraciidae"
+  sptl[sptl$species == "Abudefduf_luridus", "Family"] <- "Pomacentridae"
+  sptl[sptl$Family == "Scaridae", "Family"] <- "Labridae"
+  return(sptl)
+}
+
+##### metabolic parameters #####
+get_metpar <- function(kmax, sptl){
+  metpar <- read.csv("data/metpar_fam_smr.csv")
+  B0_mean <- mean(metpar$B0)
+  B0_sd <- sd(metpar$B0)
+  alpha_mean <- mean(metpar$alpha)
+  alpha_sd <- sd(metpar$alpha)
+  theta_mean <- mean(metpar$theta)
+  
+  metpar <- metpar %>% full_join(unique(select(sptl, Family)))
+  metpar[is.na(metpar$alpha), "alpha"] <- alpha_mean
+  metpar[is.na(metpar$alpha_sd), "alpha_sd"] <- alpha_sd
+  metpar[is.na(metpar$B0), "B0"] <- B0_mean
+  metpar[is.na(metpar$B0_sd), "B0_sd"] <- B0_sd
+  metpar[is.na(metpar$theta), "theta"] <- theta_mean
+  
+  spt <- unique(dplyr::select(kmax, sst))
+  spt <-  expand.grid(spt$sst, unique(sptl$Family))
+  colnames(spt) <- c("sst", "Family")
+  
+  param <- left_join(spt, metpar)
+  param$B0_adj <- 
+    param$B0 * exp(0.59 / 8.62e-5 * (1 / (28 + 273.15) - 1 / (param$sst + 273.15)))
+  metpar <- dplyr::select(param, Family, sst,
+                   alpha_m = alpha, alpha_sd,
+                   f0_m = B0_adj, f0_sd = B0_sd, theta_m = theta)
+  
+  return(metpar)
+}
+
+
+##### cnp #####
+get_cnp <- function(){
[…]

### 2019-10-22 R/packages.R

@@ -1,0 +1,10 @@
+library(purrr)
+library(tidybayes)
+library(ggplot2)
+library(fishflux)
+require(Rphylopars)
+library(dplyr)
+library(tidyr)
+library(drake)
+
+library(utils)

### 2019-10-22 R/plan.R

@@ -1,0 +1,23 @@
+
+plan <- drake_plan(
+  sptl = get_sptl(),
+  kmax = get_kmax(),
+  lw = get_lw(sptl),
+  cnp = get_cnp(),
+  cnpdiet = get_cnpdiet(),
+  metpar = get_metpar(kmax, sptl),
+  artr = get_artr(),
+  params = combine_params(sptl, kmax, lw, cnp, cnpdiet, metpar, artr),
+  output_params = write.csv(params, "params_sst_glob.csv", row.names = FALSE),
+  tfish_unique = get_tfish_unique(),
+  cnpflux = run_fishflux(tfish_unique, params),
+  output_cnpflux = write.csv(cnpflux, "flux_results.csv", row.names = FALSE)
+)
+
+#make(plan)
+
+small_config <- drake_config(plan)
+vis_drake_graph(small_config, targets_only = TRUE)
+
+make(plan)
+

### 2019-10-22 make.R

@@ -1,0 +1,9 @@
+source("R/packages.R")  # loads packages
+source("R/functions_wrangling.R") # defines the create_plot() function
+source("R/plan.R")      # creates the drake plan
+# options(clustermq.scheduler = "multicore") # optional parallel computing. Also needs parallelism = "clustermq"
+
+make(
+  plan, # defined in R/plan.R
+  verbose = 2
+)

### 2019-10-22 R/plan.R
test

@@ -21,3 +21,4 @@ vis_drake_graph(small_config, targets_only = TRUE)
 
 make(plan)
 
+#hello

### 2019-10-24 R/functions_wrangling.R
flux and contributions

@@ -99,14 +99,21 @@ lwl2 <- lapply(lwl, function(x){
 
 get_artr <- function(sptl){
  ar <- map(as.list(sptl$Species), possibly(fishflux::aspect_ratio, otherwise =  NA_real_))
- ar2 <- lapply(ar, function(x){x$aspect_ratio}) %>% unlist()
+ ar2 <- lapply(ar, function(x){
+   if(is.data.frame(x)){
+     return(x$aspect_ratio)
+   } else{return(NA)}
+   }) %>% unlist()
  tr <- map(as.list(sptl$Species), possibly(fishflux::trophic_level, otherwise =  NA_real_))
- tr2 <- lapply(tr, function(x){x$trophic_level}) %>% unlist()
-
+ tr2 <- lapply(tr, function(x){
+   if(is.data.frame(x)){
+     return(x$trophic_level)
+   } else{return(NA)}
+ }) %>% unlist()
  res <- sptl %>% mutate(h_m = tr2, r_m = ar2)
 
  # Family level average for missing
- ar_fam <- group_by(red, Family) %>% 
+ ar_fam <- group_by(res, Family) %>% 
    summarize(ar_fam = mean(r_m, na.rm = TRUE), tr_fam = mean(h_m, na.rm = TRUE))
  res <- left_join(res, ar_fam)
 
@@ -123,14 +130,17 @@ get_artr <- function(sptl){
 }
 
 ##### combine all so far #####
+
 combine_params <- function(sptl, kmax, lw, cnp, cnpdiet, metpar, artr){
-  params <- dplyr::full_join(sptl, kmax) %>% 
+  params <- dplyr::full_join(select(sptl, Family, Species, species), kmax) %>% 
     dplyr::left_join(cnp) %>% 
-    dplyr::left_join(cnpdiet) %>% 
+    dplyr::left_join(select(cnpdiet, -Family)) %>% 
     dplyr::left_join(metpar) %>%
     dplyr::left_join(lw) %>% 
     dplyr::left_join(artr) %>%
-    mutate(v_m = sst) %>% select(-sst)
+    mutate(v_m = sst, linf_m = sizemax) %>% select(-sst, -sizemax, -diet_cat) %>% 
+    mutate( F0nz_m = 0.0037, F0nz_sd = 0.0046, F0pz_m = 0.00037, F0pz_sd = 0.00051,
+            ac_m = 0.8, an_m = 0.8, ap_m = 0.7)
[…]

### 2019-10-24 R/packages.R

@@ -6,5 +6,7 @@ require(Rphylopars)
 library(dplyr)
 library(tidyr)
 library(drake)
-
+library(e1071)
+library(brms)
 library(utils)
+Sys.setlocale("LC_MESSAGES", "en_US.utf8")

### 2019-10-24 R/plan.R

@@ -6,19 +6,22 @@ plan <- drake_plan(
   cnp = get_cnp(),
   cnpdiet = get_cnpdiet(),
   metpar = get_metpar(kmax, sptl),
-  artr = get_artr(),
+  artr = get_artr(sptl),
   params = combine_params(sptl, kmax, lw, cnp, cnpdiet, metpar, artr),
-  output_params = write.csv(params, "params_sst_glob.csv", row.names = FALSE),
+  output_params = write.csv(params, "output/data/params_sst_glob.csv", row.names = FALSE),
   tfish_unique = get_tfish_unique(),
   cnpflux = run_fishflux(tfish_unique, params),
-  output_cnpflux = write.csv(cnpflux, "flux_results.csv", row.names = FALSE)
+  output_cnpflux = write.csv(cnpflux, "output/data/flux_results.csv", row.names = FALSE),
+  
+  tfish = read.csv("data/tfish_corr.csv"),
+  
+  summary_transect = summarise_pertransect(tfish, cnpflux, params),
+  output_fluxsum = write.csv(summary_transect, "output/data/flux_summary_transect.csv", row.names = FALSE),
+  
+  contributions = get_contributions(tfish, cnpflux, params, summary_transect),
+  
+  models_contributions_Fp = fit_contribution_Fp(contributions)
 )
 
-#make(plan)
-
-small_config <- drake_config(plan)
-vis_drake_graph(small_config, targets_only = TRUE)
-
-make(plan)
 
 #hello

### 2019-10-24 make.R

@@ -5,5 +5,9 @@ source("R/plan.R")      # creates the drake plan
 
 make(
   plan, # defined in R/plan.R
-  verbose = 2
+  verbose = 2, lock_envir = FALSE
 )
+
+
+#config <- drake_config(plan)
+#vis_drake_graph(config, targets_only = TRUE)

### 2019-11-07 text/suppl_methods.Rmd
update drake plan

@@
 # Supplementary methods
-## Species selection
--> bigger than 7cm 
--> Family for which we had cnp body content data
--> omit extreme rare species (X%)
+## 1. Underwater visual census database
+\noindent We used a published global database of field data collection of belt transects [@Barneche2019].
+This database encompasses transect data across 585 sites in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Figure).
+This database only includes sites with a hard reef bottom are at the outer reef slope and were carried out at a constant depth, parallel to the reef crest.
+We splected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all sites.
+The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
 
-## 1. Parameter estimates
+## Phylogeny
 
-### 1. Growth parameters
+## 2. Parameter estimates
+
+### 2.1. Growth parameters
 
 #### Data compilation
-We used the parameter kmax see renato paper
+We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF).
+For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e.
+$k_{max}$, @Morais2019].
+$t0$ was kept constant at 0 for all species.
 
-We extracted the data from @Morais2019 and filtered out only the species of our species list.
-As the Lenth-Frequency method consistently overestimates kmax, we omitted the kmax estimates coming from this method.
-In total this selection process resulted in xx observations of kmax for different species and temperatures.
+We extracted the data for $k_{max}$ from @Morais2019 and filtered out only the species of our species list.
+As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method.
+In total, this selection process resulted in 439 observations of kmax for different species and temperatures.
 
-Further, we used the otolith data provided by Morat et al.
-and fitted vbgc's to all species at each loction for which there were at least 3 individuals.
-We fitted the model using bayesian regression models as provided by fishflux.
-kmax was obtained using similar methods as described in @Morais2019.
-In total we retrieved 57 kmax observations for xx species and xx locations of varying sst's.
+Further, we used the otolith data provided by Morat et al., including measurements of fishes from five Polynesian islands and fitted the Von Bertalanffy growth models to all species at each location for which there were at least 3 individuals.
+We fitted the model using Bayesian regression models as provided by fishflux.
 
-After combining the two data sources, we obtained a database of 496 observations and 181 number of species. 
-kmax is mostly determined by body size and temperature. 
-Morais and bellwood account for phylogeny, but don't actually include it for predictions. Here we try to include phylogeny directly.
+After combining the two data sources, we obtained a database of 496 observations and 181 species.
 
-#### Statistical analysis
+#### Statistical analysis and extrapolation
 
-\noindent We applied a hierarchical model to predict the growth rate of fishes in function of body size, temperature and phylogeny:
+\noindent Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2019].
+
+We applied a Bayesian hierarchical model to predict the growth rate of fishes in function of body size, temperature and phylogeny:
 
@@
 
-where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, \gamma_\textrm{0phy} is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
-
-\noindent
-
-Phylogenetic re
-Thephylogenetic heritability (equivalent to Pagel’\lambda (29,30)), was estimated asthe proportion of total variance, conditioned on the fixed effects, attributable to the random effect of phylogeny (i.e.s2[lng0phy]=(s2[lng0phy]+s2[lng0spp]+s2[lne]))
+\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
+\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
+\noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature.
+The Bayesian R2 of the model was 0.73759 (95%CI: 0.702-0.769).
+\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$ (REF)) was estimated as the proportion of total variance, conditioned on the effects, attributable to the  phylogeny(i.e.
+$\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2  / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)$).
+This calculation resulted in a phylogenetic signal of 0.74 (95% CI: 0.70 - 0.77).
 
@@
 
-phylogenetic signal is 0.76 (0.65, 0.84). 
-bayes R2 is 0.73759 (0.702, 0.769).
+\noindent We extrapolated $\kappa$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
+There is currently no streamlined method to make predictions to new species from a phylogenetic regression model.
+We circumvent the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model.
+We subsequently predicted these phylogenetic effects for missing species with the help of the function phyEstimate in the picante package for R [@Kembel2010].
+This function uses phylogenetic ancestral state estimation to infer trait values for new species on a phylogenetic tree by rerooting the tree to the parent edge for the node to be predicted [@Kembel2012].
+We repeated this for all 100 trees and 1000 draws.
+Per draw, we averaged the extrapolated values per species for the hundred trees.
+Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa$ for each species.
+We only use one chain in order to keep computational time reasonable.
+Finally, we summarised all $\kappa$ predictions per sst per species by taking the mean and standard deviation across the 1000 draws.
 
-For extrapolation we use:
-phyestimate from package picante which uses brownian motion 
-with this we extrapolate the phylogenetic effect for each iteration. We only use one chain in order to keep computational time reasonable.
-
-For each draw, we extrapolate the phylogenetic effect for 100 trees and then take the average effect of these 100 trees. 
-This is done for each draw.
-To take into account the temperature variation in which species can occur, we predict the kmax for each temperature (rounded 1 °C) where a species occurs in the global uvc database.
-This results in kmax predictions for 4712 cases and 1110 species.
-(extra table?) To predict kmax per draw we used the respective estimates of intercept and slopes.
-Finally, we summarised all kmax predictions per sst per species by taking the mean and standard deviation across all draws.
-
-### 2. Diet
-
-### 3. Body stoichiometry
+### 2. Body stoichiometry
 #### 3.1 Data collection
@@
 for each iteration of 1 chain, for each tree of 100 trees
+
+### 3. Diet

### 2019-11-07 R/functions_wrangling.R

@@ -388,35 +388,166 @@ tfss <- left_join(tfs, select(summary_transect, transect_id, nspec, bioregion)) 
 return(tfss)
 }
 
+
 ##### fit contribution models #####
-fit_contribution_Fp <- function(contributions){
+fit_contribution_Fp <- function(contributions, sp_loc){
   
   ## compile model once 
-  subsp <- filter(contributions, species == "Variola_louti")
-  subsp$bioregion <- as.factor(as.character(subsp$bioregion))
-  fit <- brm("Fp_p ~ (0 + bioregion) + (0 + 1|locality)", chains = 1, family = "beta", data = subsp)
-  
-  spp <- unique(contributions$species)
+  subsp <- filter(contributions, bioregion == "c_indopacific", species == "Acanthurus_leucocheilus")
+  fit <- brm("Fp_p ~ 1 + (1|locality) + (1|sites)", chains = 1, family = "beta", data = subsp)
   
   # run same model on all species
-  list <- parallel::mclapply(spp[1:2], function(x){
+  list <- parallel::mclapply(1:nrow(sp_loc), function(x){
     print(x)
-    subsp <- filter(contributions, species == x)
-    subsp$bioregion <- as.factor(as.character(subsp$bioregion))
-    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 2, control = list(adapt_delta = 0.95))
+    subsp <- filter(contributions, bioregion == sp_loc$bioregion[x], species == sp_loc$species[x])
+    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 2, control = list(adapt_delta = 0.99))
     return(fit_new)
-  }, mc.cores = 7)
+  }, mc.cores = 6)
   
   return(list)
 }
 
-# l2 <- parallel::mclapply(list, function(x){
+fit_contribution_Fn <- function(contributions, sp_loc){
+  
+  ## compile model once 
+  subsp <- filter(contributions, bioregion == "c_indopacific", species == "Acanthurus_leucocheilus")
+  fit <- brm("Fn_p ~ 1 + (1|locality) + (1|sites)", chains = 1, family = "beta", data = subsp)
+  
+  # run same model on all species
+  list <- parallel::mclapply(1:nrow(sp_loc), function(x){
+    print(x)
[…]

### 2019-11-07 R/plan.R

@@ -19,8 +19,16 @@ plan <- drake_plan(
   output_fluxsum = write.csv(summary_transect, "output/data/flux_summary_transect.csv", row.names = FALSE),
   
   contributions = get_contributions(tfish, cnpflux, params, summary_transect),
+  sp_loc = unique(select(ungroup(contributions), bioregion, species)),
   
-  models_contributions_Fp = fit_contribution_Fp(contributions)
+  models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
+  models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
+  models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
+  models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
+  models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
+  models_contributions_Wp = fit_contribution_Wp(contributions, sp_loc),
+  models_contributions_Wn = fit_contribution_Wn(contributions, sp_loc),
+  models_contributions_Wc = fit_contribution_Wc(contributions, sp_loc)
 )
 
 

### 2019-11-07 make.R

@@ -8,6 +8,7 @@ make(
   verbose = 2, lock_envir = FALSE
 )
 
+make(plan, targets = c("models_contributions_Wc", "models_contributions_Wn", "models_contributions_Wp"))
 
 #config <- drake_config(plan)
 #vis_drake_graph(config, targets_only = TRUE)

### 2020-01-03 R/functions_wrangling.R
update contribution models, adding piscivory, herbivory

@@ -55,7 +55,11 @@ get_cnp <- function(){
 
 ##### cnpdiet #####
 get_cnpdiet <- function(){
-  cnpdiet <- read.csv("data/cnpdiet_glob.csv")
+  cnpdiet <- read.csv("data/cnpdiet_glob.csv") 
+  cnpdiet[,3:8] <- cnpdiet[,3:8] * 100
+  colnames(cnpdiet) <-
+    c("family", "species", "Dc_m", "Dc_sd", 
+      "Dn_m", "Dn_sd", "Dp_m", "Dp_sd", "diet_cat")
   return(cnpdiet)
 }
 
@@ -134,11 +138,11 @@ get_artr <- function(sptl){
 combine_params <- function(sptl, kmax, lw, cnp, cnpdiet, metpar, artr){
   params <- dplyr::full_join(select(sptl, Family, Species, species), kmax) %>% 
     dplyr::left_join(cnp) %>% 
-    dplyr::left_join(select(cnpdiet, -Family)) %>% 
+    dplyr::left_join(select(cnpdiet, -family)) %>% 
     dplyr::left_join(metpar) %>%
     dplyr::left_join(lw) %>% 
     dplyr::left_join(artr) %>%
-    mutate(v_m = sst, linf_m = sizemax) %>% select(-sst, -sizemax, -diet_cat) %>% 
+    mutate(v_m = sst, linf_m = sizemax) %>% select(-sst, -sizemax) %>% 
     mutate( F0nz_m = 0.0037, F0nz_sd = 0.0046, F0pz_m = 0.00037, F0pz_sd = 0.00051,
             ac_m = 0.8, an_m = 0.8, ap_m = 0.7)
   return(params)
@@ -159,16 +163,15 @@ run_fishflux <- function(tfish_unique, params){
   
   data <- left_join(select(tfish_unique, species, size_cm, v_m), params)
   
-  cnpflux <- parallel::mclapply(1:nrow(data), function(x){
+  cnpflux <- parallel::mclapply(1:nrow(tfish_unique), function(x){
     print(x)
     
     dt <- data[x,] 
-    par <- dt %>% select(-species, - Family, - size_cm, -Species) %>% as.list()
+    par <- dt %>% select(-species, - Family, - size_cm, -Species, -diet_cat) %>% as.list()
     mod <- fishflux::cnp_model_mcmc(TL = dt$size_cm,
                                     param = par, iter = 2000)
     
-    mod$summary
[…]

### 2020-01-03 R/plan.R

@@ -1,5 +1,6 @@
 
 plan <- drake_plan(
+  # load all parameters
   sptl = get_sptl(),
   kmax = get_kmax(),
   lw = get_lw(sptl),
@@ -7,28 +8,45 @@ plan <- drake_plan(
   cnpdiet = get_cnpdiet(),
   metpar = get_metpar(kmax, sptl),
   artr = get_artr(sptl),
+  
+  # combine parameters
   params = combine_params(sptl, kmax, lw, cnp, cnpdiet, metpar, artr),
   output_params = write.csv(params, "output/data/params_sst_glob.csv", row.names = FALSE),
   tfish_unique = get_tfish_unique(),
+  
+  # Run fishflux bioenergetic model
   cnpflux = run_fishflux(tfish_unique, params),
   output_cnpflux = write.csv(cnpflux, "output/data/flux_results.csv", row.names = FALSE),
   
+  # load all transect data
   tfish = read.csv("data/tfish_corr.csv"),
   
+  # summarize results per transect
   summary_transect = summarise_pertransect(tfish, cnpflux, params),
   output_fluxsum = write.csv(summary_transect, "output/data/flux_summary_transect.csv", row.names = FALSE),
   
   contributions = get_contributions(tfish, cnpflux, params, summary_transect),
   sp_loc = unique(select(ungroup(contributions), bioregion, species)),
   
+  # run models to get relative contribution of each ecosystem process
   models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
   models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
   models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
   models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
+  models_contributions_In = fit_contribution_In(contributions, sp_loc),
+  models_contributions_Ip = fit_contribution_Ip(contributions, sp_loc),
   models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
+  models_contributions_Gn = fit_contribution_Gn(contributions, sp_loc),
+  models_contributions_Gp = fit_contribution_Gp(contributions, sp_loc),
   models_contributions_Wp = fit_contribution_Wp(contributions, sp_loc),
   models_contributions_Wn = fit_contribution_Wn(contributions, sp_loc),
-  models_contributions_Wc = fit_contribution_Wc(contributions, sp_loc)
[…]

### 2020-01-03 make.R

@@ -8,7 +8,10 @@ make(
   verbose = 2, lock_envir = FALSE
 )
 
-make(plan, targets = c("models_contributions_Wc", "models_contributions_Wn", "models_contributions_Wp"))
+#make(plan, targets = c("models_contributions_Wc", "models_contributions_Wn", "models_contributions_Wp"))
 
-#config <- drake_config(plan)
-#vis_drake_graph(config, targets_only = TRUE)
+config <- drake_config(plan)
+vis_drake_graph(config, targets_only = TRUE)
+
+drake::clean("cnpflux")
+make(plan, targets = "herb_pisc", lock_envir = FALSE)

### 2020-01-03 R/functions_wrangling.R
add seeds for reproducibility

@@ -388,7 +388,7 @@ fit_contribution_Fp <- function(contributions, sp_loc){
   list <- parallel::mclapply(1:nrow(sp_loc), function(x){
     print(x)
     subsp <- filter(contributions, bioregion == sp_loc$bioregion[x], species == sp_loc$species[x])
-    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99))
+    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99), seed = x)
     return(fit_new)
   }, mc.cores = 8)
   
@@ -405,7 +405,7 @@ fit_contribution_Fn <- function(contributions, sp_loc){
   list <- parallel::mclapply(1:nrow(sp_loc), function(x){
     print(x)
     subsp <- filter(contributions, bioregion == sp_loc$bioregion[x], species == sp_loc$species[x])
-    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99))
+    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99), seed = x)
     return(fit_new)
   }, mc.cores = 8)
   
@@ -422,7 +422,7 @@ fit_contribution_Fc <- function(contributions, sp_loc){
   list <- parallel::mclapply(1:nrow(sp_loc), function(x){
     print(x)
     subsp <- filter(contributions, bioregion == sp_loc$bioregion[x], species == sp_loc$species[x])
-    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99))
+    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99), seed = x)
     return(fit_new)
   }, mc.cores = 8)
   
@@ -439,7 +439,7 @@ fit_contribution_Ic <- function(contributions, sp_loc){
   list <- parallel::mclapply(1:nrow(sp_loc), function(x){
     print(x)
     subsp <- filter(contributions, bioregion == sp_loc$bioregion[x], species == sp_loc$species[x])
-    fit_new <- update(fit, newdata = subsp, recompile = FALSE, chains = 3, control = list(adapt_delta = 0.99))
[…]

### 2020-01-03 text/suppl_methods.Rmd

@@
 ---
-author: "N.S."
-date: "15 October 2019"
-output: html_document
+output:
+  pdf_document: default
 ---
 
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 # Supplementary methods
-## 1. Underwater visual census database
+# 1. Underwater visual census database
 \noindent We used a published global database of field data collection of belt transects [@Barneche2019].
@@
 
-## Phylogeny
+# 2. Phylogeny
 
-## 2. Parameter estimates
+# 3. Parameter estimates
 
-### 2.1. Growth parameters
+\newpage
 
-#### Data compilation
+\begin{table}[h!]
+\centering
+\caption{. Overview of model input parameters. VBGC = von Bertalanffy growth curve.}
+\begin{tabular}{l l l}
+\hline
+\rowcolor{lightgrey}
+Symbol & Description & Unit\\
+\hline
+$k$ & Index for element C, N or P & \_ \\
+$a_\textrm{k}$  & Element-specific assimilation efficiency & \% \\
+$l_\textrm{t}$  & Total length of individual at time t & cm \\
+$l_{\infty}$  & Asymptotic adult length (VBGC) & cm \\
+$\kappa$  & Growth rate parameter (VBGC) & $\textrm{yr}^{-1}$ \\
+$t_0$  & Age at settlement (VBGC) & $\textrm{yr}$ \\
+$lw_a$  & Parameter length-weight relationship & $\textrm{g cm}^{-1}$ \\
+$lw_b$  & Parameter length-weight relationship & \_\\
+$Q_\textrm{k}$  & Element-specific body content percentage of dry mass & \% \\
+$f_\textrm{0}$  & Metabolic normalisation constant independent of body mass & $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$ \\
+$\alpha$  & Mass-scaling exponent &  \_\\
+$\theta$  & Activity scope & \_ \\
+$v$  & Environmental temperature & \textdegree C \\
+$h$  & trophic level & \_ \\
+$r$  & Aspect ratio of caudal fin & \_ \\
+$F_\textrm{0Nz}$  & Mass-specific turnover rate of N & $\textrm{g N} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
+$F_\textrm{0Pz}$  & Mass-specific turnover rate of P & $\textrm{g P} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
+$D_\textrm{k}$  & Elemental stoichiometry of diet & \% \\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+## 3.1. Growth parameters
+
+### 3.1.1 Data compilation
 We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF).
@@
 
-#### Statistical analysis and extrapolation
+### 3.1.2 Statistical analysis and extrapolation
 
@@
 \begin{equation}
-	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}size +  \beta_\textrm{2} sst + \epsilon,
+	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}sizemax +  \beta_\textrm{2} sst + \epsilon,
 	\label{kmax}
@@
 \noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature.
-The Bayesian R2 of the model was 0.73759 (95%CI: 0.702-0.769).
-\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$ (REF)) was estimated as the proportion of total variance, conditioned on the effects, attributable to the  phylogeny(i.e.
+The Bayesian R2 of the model was 0.73759 (95\%CI: 0.702-0.769).
+\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects, attributable to the  phylogeny(i.e.
 $\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2  / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)$).
-This calculation resulted in a phylogenetic signal of 0.74 (95% CI: 0.70 - 0.77).
+This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).
 
@@
 ~phylo (Number of levels: 181) 
-              Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
+              Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
 sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00
@@
 Population-Level Effects: 
-           Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
+           Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
 Intercept      0.66      0.58    -0.48     1.81       1498 1.00
@@
 Family Specific Parameters: 
-      Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
+      Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
 sigma     0.46      0.02     0.43     0.50       1991 1.00
@@
 
-### 2. Body stoichiometry
-#### 3.1 Data collection
+## 3.2 Body stoichiometry    
+### 3.2.1 Data collection    
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, Carribean and Palmyra.
+Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser.
+$Q_\textrm{k}$ (\%) were then measured in the lab using standard methods.
+Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis (Allen et al.
+1974).
+Elemental content was calculated based on dry mass.
 
-#### 3.2 Data analysis
+### 3.2.2 Data analysis and extrapolation
 
-only species with nrep >= 3
+\noindent We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.
 
-Stoichiometry is well conserved within taxonomic entities. Through a database of 1633 individuals, 108 species, locations: Moorea, Palmyra, Carribean
+\begin{equation}
+	\begin{bmatrix}Y_1 \\ Y_2 \\ Y_3\end{bmatrix} \sim MVNormal(\begin{bmatrix}mu1 \\ mu2 \\ mu3\end{bmatrix}, S),
+	\label{cnp}
+\end{equation}
 
-25 families
- [1] "Acanthuridae"   "Balistidae"     "Bothidae"       "Chaetodontidae" "Cirrhitidae"    "Fistulariidae" 
- [7] "Haemulidae"     "Holocentridae"  "Kyphosidae"     "Labridae"       "Lethrinidae"    "Lutjanidae"    
-[13] "Monacanthidae"  "Mugilidae"      "Mullidae"       "Ostraciidae"    "Pempheridae"    "Pomacanthidae" 
-[19] "Pomacentridae"  "Sciaenidae"     "Scorpaenidae"   "Serranidae"     "Siganidae"      "Tetraodontidae"
-[25] "Zanclidae"
+\begin{equation}
+	mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},
+	\label{cnp2}
+\end{equation}
 
-multivariate model
+\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$ respectively,   $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the intercept variation, based on the relatedness as described by the phylogeny per element k, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the residual species-level intercept variation per element k.
 
-extrapolation
+\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
+\noindent The Bayesian R2 of the model was 0.39 (95\%CI: 0.36-0.42), 0.50 (95\%CI: 0.48-0.53), and 0.43 (95\%CI: 0.40-0.46) for C, N and P respectively. 
+\noindent The phylogenetic heritability was 0.41 (95\%CI: 0.28-0.55), 0.58 (95\%CI: 0.4-0.66), and 0.57 (95\%CI: 0.46-0.69) for C, N, and P respectively.
 
-phylopars from rphylopars
-for each iteration of 1 chain, for each tree of 100 trees
+\noindent As before, we used 1000 fitted draws for each species, and 100 phylogenetic trees to extrapolate to all species with unknown body stoichiometry.
+Specifically, we used the phylopars function from the Rphylopars package [@Bruggeman2009].
+This function uses ancectral state reconstruction and brownian motion, and takes the correlation between C, N and P into account.
 
-### 3. Diet
+## 3.3 Diet stoichiometry    
+### 3.3.1 Data collection 
+\noindent We collected 345 adult individuals of 37 species and 12 families between 2018 and 2019 in Mo'orea and Tetiaroa, two Polynesian islands.
+We extracted the stomach content and stored it in a 2ml tube.
+After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder.
+Then, samples were sent to the lab (more info!!) for CNP% content analysis.
+
+### 3.3.2 Data analysis and extrapolation  
+\noindent We extracted trophic group information from ref diet paper.
+We constructed a simple multivariate Bayesian regression model to summarize CNP\% content data per trophic group with a random effect at the species level.
+This model had a Bayesian R2 of 0.61 (0.56-0.65), 0.31 (0.23-0.38), and 0.48 (0.42-0.54).
+bayes_R2(fit_cnpdiet)
+     Estimate  Est.Error      Q2.5     Q97.5
+R2c 0.6250538 0.02299497 0.5756378 0.6642792
+R2n 0.3043510 0.03973636 0.2271046 0.3771861
+R2p 0.4857449 0.03164611 0.4191740 0.5417580
+
+\noindent We then predicted the CNP\% per diet category.
+
+   cat    Dc_m  Dn_m  Dp_m Dc_sd Dn_sd Dp_sd
+  <chr> <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>
+1 1      30.6  4.13 0.424  2.88 0.865 0.197
+2 2      35.1  7.96 1.50   2.71 0.857 0.193
+3 3      33.1  5.79 0.751  3.52 1.06  0.242
+4 4      38.1  7.45 0.879  5.14 1.60  0.360
+5 5      28.9  5.10 0.619  3.35 1.03  0.239
+
+## 3.4 Metabolic parameters    
+### 3.4.1 Data collection

### 2020-04-24 text/methods.Rmd
many edits pre-cleanup commit

---
title: "Methods"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Underwater visual census database
\noindent We used a published global database of field data collection of belt transects [@Barneche2019]. This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Suppl. table). This database only includes sites with a hard reef bottom at the outer reef slope and were carried out at a constant depth, parallel to the reef crest. We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all transects. The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).

# 2. Bioenergetic modeling
\noindent We applied a series of bioenergetic models for each existing combination of species identity, body size, and sea surface temperature (n = 30668). The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [Schiettekatte2020]. As such, this model is well suited for the application of a wide variety of fish species. The model relies on a set of input parameters including elements of metabolism, growth, and diet and body stoichiometry. We quantified the input parameters for all species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods). The bioenergetic model then allows for the prediction of elemental fluxes mediated by individuals, including ingestion rate, excretion rates of N and P, and growth rate. Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production (g C/day), herbivory (g/day), and piscivory (g/day). We summed the contribution of each individual to each process on the transect-level, to get community-level estimates, then dividing it by the surface area that was surveyed. Each process is thus expressed in dry mass per day per square meter. We note that N excretion, P excretion, and production include contributions of each individual, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild (Parravicini et al. 2020).

# 3. Variation beyond biomass and temperature
\noindent To quantify the fold variation that exists across transects with a similar total standing fish biomass, we grouped transects into 320 bins with an interval of 50g/m2. We then quantified the fold-variation by dividing the maximum by the minimum value for each process within each bin.

\noindent To assess the covariation that exists among processes without the positive effect of standing biomass and sea surface temperature, we performed a Bayesian mixed effect regression of each log-transformed function for transect-scale observations ($y_j$):
\begin{equation}
	y_\textrm{j} \sim N(\mu_j, \sigma_j)),
	\label{modbiom1}
\end{equation}

\begin{equation}
	\mu_\textrm{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}
	\label{modbiom2}
\end{equation}
and then extracted the median residuals for each process per transect. In some transects, there were no piscivores or herbivores observed. In those cases, we did not include these transects in the analysis. To assess the covariation, we then quantified the correlations that exist among the different proocesses. To visualize the residuals per locality on a world map, we first grouped all transects per site by taking the median value for each process across multiple transect. We then grouped the sites again into localities by taking the median.

# 4. Community structure 
\noindent To investigate the effect of the community structure together with the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community. Specifically, we took the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect. The total length is based on the visual estimation by divers. The immaturity is quantified using the following formula: 
\begin{equation}
	\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),
	\label{imm}
\end{equation}
where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i. Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual. Finally, the trophic level was extracted from fishbase [@Froese2018]. Additionally, we quantified the transect-level species richness. 
For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:

\begin{equation}
	y_\textrm{j} \sim N(\mu_j, \sigma_j)),
	\label{modcom1}
\end{equation}

\begin{equation}
 \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} 
	\label{modcom2}
\end{equation}

To compare effects across functions and assess the relative importance of each variable we standardized all variables prior to model fitting. We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations. We used weakly-informative priors [@Burkner2017].

# 5. Contributions and dominance
To investigate the role of each species for each function, we quantified the contribution of each species to each function for all transects as followed:
\begin{equation}
	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},
	\label{con}
\end{equation}
where i is a certain species, j is a transect, F is the value of function f.

Then, we quantified the degree of species dominance per function for each transect. 
We did this by first ranking species according to their contribution, followed by quantifying the cumulative contributions. Then, we used the area under the species accumulation curve as a measure for the degree of dominance.
Specifically, the degree of dominance (DD) was calculated as followed:
\begin{equation}
	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},
	\label{dd}
\end{equation}
where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, $A_max$ is the theoretical area under the curve where one species performs the entire function. They are quantified as:
\begin{equation}
	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},
	\label{Amin}
\end{equation}

\begin{equation}
	\textrm{A}_{max} = R - 1,
	\label{Amax}
\end{equation}

\begin{equation}
	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},
	\label{A}
\end{equation}

where C_i is the contribution of a certain species and R is the species richness. The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that one species performs the entire function, which is only possible in practice if there is only one species performing a particular function.

Finally, to know how often species are contributing a lot for a certain function, we quantified the frequency of dominance, i.e. the number of times a species is dominant divided by the total number of transects in which that species is observed. A species is considered dominant for a certain function in a given transect if their contribution is higher than 1/R, i.e. they contribute more than the situation in which each species contributes equally to a certain function.

# 6. Species vulnerability 
For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure. For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals. Vulnerability to climate change is related to diet specialization, habitat specialization, recruitment specialization for live coral and body size [@Graham2011]. @Graham2011 developed a score for climate change vulnerability for 134 species. We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from fishbase), the dependence on coral for food (3 categories: not dependent, facultative corralivore, and obligate corralivore), and dependence on coral for habitat (2 categories: dependent vs. not dependent). We also included a random effect for family. This model had a Bayesian R2 of 0.97. We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset. For species' vulnerability to fishing, we extracted the index from @Cheung2005.

### 2020-04-24 text/outline.Rmd
many edits pre-cleanup commit

---
title: "Outline"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

title options:

# Functional mismatch and importance of species redefine global coral reef management targets

# Functional mismatch and occasional keystones redefine global coral reef management targets

# Functional mismatch and the lack of global keystone species redefine global coral reef management targets

# Functioning beyond biomass redefines global coral reef management targets

# A multi-process analysis of global coral reefs reveals a functional mismatch and the importance of local keystones

Paragraphs:

## 1) Intro (1 or 2 paragraphs)
- Coral reefs are diverse, productive and threatened
- fishes contribute to a high proportion of biomass, are important for functioning, crucial for humans 
- fishes are threatened by intensive fishing and habitat destruction
- Will the reefs of the future be able to sustain function? How do we maximize functioning?

Ecosystem functioning and services in times of extreme human impacts; maximizing function and multifunctionality is the hallmark of many conservation strategies and calls from scientist, mostly derived from an ecosystem economics approach (maximize function and services).  However, this pertains predominantly to grasslands, forests and other heavily managed, cultivated systems. Marine ecosystems differ dramatically from terrestrial by being much less manageable; coral reefs provide tremendous services and are one of the most vulnerable ecosystems worldwide. Fishes are the most important consumer taxon, have a close relationship with corals, and are a critical source of livelihoods.

- First challenge is to properly define function  
- We know that more biomass = more function, more sst = more function  
- Beyond biomass and temperature, what defines functioning?  
- Here we quantify 5 key processes: N excretion, P excretion, production, herbivory, piscivory   
- 2 targets:     
     1) functions beyond biomass    
     how does community structure affect functioning? Can all functions be maximized? 
     2) Species identity and vulnerability    
     Are there a consistent set of species that are more important than others and how vulnerable are "important" species to fishing and climate change (habitat destruction)?

## 2) Summary
- There is a mismatch between different functions   
- Maximized multifunctionality can only be achieved where all functions are below the maximum    
- Most communities have a high degree of dominance, and most species are occasional keystones      
- There are no super hero species that are always important      
- Species that are important for functioning are more vulnerable to fishing than to climate change, but there is some regional variation

Here, we show that, superficially equal fish communities on the world's coral reefs can vary up to 100-fold in their functionality, depending on various aspects of their community structure. However, due to inherent biological trade-offs, no single configuration can maximize all functions. Furthermore, we reveal unpredictable local functional dominance by a wide range of species,changing contributions of families to ecological processes, and varying vulnerabilities of processes to fishing and climate-related stressors.Our results suggest that current local and global conservation objectives for coral reefs and other marine ecosystems need to be reconsidered: management for functionality and targeted conservation of species or functional groups need to be adjusted for local conditions and needs, but holistic protection of a diverse pool of species will increase the likelihood of sustaining critical ecological processes.

## 3) Mismatch between functions + ecological structure
- All functions are definitely related to biomass    
- But, for communities with similar biomass, functions can still vary 10- to 100-fold   
- Beyond biomass, there is a mismatch between the different functions (fig1)   
- Trophic, size, and age structure affect functions in different ways (fig1 + 2)   
- Maximizing "multifunctionality" is defined by intermediate values of certain community variables. (fig2)

## 4) Species dominance and vulnerability
- Locally there is often a high degree of dominance, i.e. a couple of species perform most of the function. (A bit less for herbivory-> more complementary) (fig3, maps)   
- On the family level, across geographical regions there is some variation in the contributions to functions (fig3, heatmaps)    
- Globally, there is no species that is always important (beta regressions, distribution parameters, supplemental)
- Important species are generally more vulnerable to fishing, double jeapardy seems rare
- About 70% of all species can be locally important (defined as performing more than 1/total nb of species in a community)     
- Species important to piscivory are most vulnerable to fishing (fig4)    
- Most herbivores and piscivores are important somewhere
- A bit more species are important to P excretion compared to N excretion and biomass production     
- Important species are generally more vulnerable to fishing that to climate change (Important note: climate change only includes dependance on corals of adults)

## 5) Discussion human impact on functioning and community structure
- We know that multiple human stressors are causing species to decline, and are affecting the size, age, and trophic structure of fish communities.   
- More details about human impact on community structure, and how in turn that affects functioning.   
- Indeed, we see that N excretion and production increase with human impact (suppl. figure) (see also Morais as example). 
- Due to the observed mismatch, it is untenable to achieve maximized values for all functions. Relate to other ecosystems.
- The effect of potential extinctions of species varies across locations. Provide an example? For most species, total extinction would have a big effect on functioning somewhere.

## 6) Consequences for conservation
- 1) Important to consider multiple functions beyond biomass. Only looking at N excretion for example would give va biased view. Maximized function does not nescessarily represent a "healthy" ecosystem.
We need to step away from economics approach and define conservation targets locally.  
Examples:      
      - Reefs that are most crucial for fishing -> Maximize biomass production   
      - Reefs that are succeptible to algae growth -> Maximize herbivory   
      - Reefs that are vulnerable to bleaching -> Maximize P excretion   
- 2) Secondly, species important for the different functions are not the same ones across locations. Most species are occasionally important, but none are always important. Species conservation targets cannot be generalized globally. Species importance and conservation should be planned locally, taking into acount historical knowledge (i.e. some species that are rare/depleted may have played an important role in the past)  
- 3) Third, important species seem to be most vulnerable to fishing. Local fisheries management may prioritize species that are extra vulnerable. Note that also long-term effects of habitat loss will affect a greater amunt of species than presented herein so there is no doubt that climate change should be targeted by global action. 
- Thus, conservation needs to be planned locally and in general we essentially want to conserve all species

## 7) Future perspective ?????
- Need to take variability in behavior within each function into account    
- A fish peeing in a cave does not equal a fish peeing in the water column    
- Herbivores target different types of algae    
- Fishes producing biomass may vary in terms of the micronutrient/vitamin content

## 8) Conclusion ?? probably not
- Analyzing the functioning of reefs really requires the quantification of processes    
- There is no magical community structure that maximizes all functions    
- Need to rethink multifunctionality case by case    
- There are no superhero's for functioning, but most species are occasional superhero's    
- Conservation should be planned locally with extra attention to fishes vulnerable to fishing

## Figures  
### Figure 1 option 1:

![](../output/plots/fig1_simple.png)

## figure 1 option 2:

![](../output/plots/fig1_simple_v2.png)

Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities. 
b) Correlation matrix od the residuals of the five functions.

![](../output/plots/figure2.png)

Figure 2: a: Slope values of the Bayesian linear regression for each function with community variables. All data was standardized to be able to compare across functions and variables. Functions were log-transformed before standardisation. b-d: Marginal effect plots, where each predicted value was normalised a posteriori. The solid black line represents the multifunctionality.

![](../output/plots/multimap.png)
\  
Figure 3: Left: Median degree of dominance of each function per location. A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function. Size of dots represents the median value of the function itself. Right: Heat maps of median family-level contributions to each function per bioregion. CIP = Central Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, EP = Eastern Pacific, WA = Western Atlantic, WI = Western Indian

![](../figures/figure4_allspecies.png)

Figure 4: Vulnerability and importance to each function of fish species included in this study. Transparant bars represent the relative number of species in each category of vulnerability. Filled bars show the proportion of species that are locally important (i.e. perform more than 1/N of the function, where N is the number of species observed in a certain transect).

## Supplementary figures

![](../output/plots/residuals_multipanel.png)
\

![](../output/plots/gravity_markets.png)
\

![](../output/plots/beta_params.png)

### 2020-04-24 text/summary.Rmd
many edits pre-cleanup commit

--- 2020-04-24 text/outline.Rmd
@@
 ---
-title: "Outline"
 output: html_document
@@
 
-title options:
+# Functions beyond biomass reveal global mismatch in coral reefs
+(title not final at all)
 
-# Functional mismatch and importance of species redefine global coral reef management targets
+## At a glance
+- In times of extreme human impacts on natural systems, conservation strategies focus on maximizing function and multifunctionality.
+Such an economics approach pertains mostly to terrestrial systems.
+Fish contribute to a high proportion of consumer biomass and are important for coral reef functioning and human livelihood.
+Yet, the effect of community structure and species identity on functioning remains poorly understood.
+It is crucial to understand the community drivers of functions in order to guide management targets towards the conservation of coral reef functioning.
+- Beyond biomass, there is still a large variation of 5 key functions that needs to be considered
+- Quantifying functions reveals a mismatch between the different functions (fig.
+1), that is driven by differences in community structure (fig.
+2).
+As a consequence, the idea of maximizing all functions to reach multifunctionality is an illusion.
+- Even though there is a high degree of species dominance for each function across all communities (fig.3, left), global keystone species do not exist.
+Instead, most species are occasional keystones (fig.3, middle) that are most vulnerable to fishing (fig.
+4).
+- Our results suggest that current local and global conservation objectives for coral reefs and other marine ecosystems need to be reconsidered: management for functionality and targeted conservation of species need to be adjusted for local conditions and needs, but holistic protection of a diverse pool of species will increase the likelihood of sustaining critical ecological processes.
 
-# Functional mismatch and occasional keystones redefine global coral reef management targets
+## Main figures
 
-# Functional mismatch and the lack of global keystone species redefine global coral reef management targets
+![](../output/plots/multimap2.png)
+Figure 1: World maps of five key ecosystem functions.
+Dots indicate the localities that are included in this study.
+Dot size represents the average of the residuals of each log-transformed function after regression with the log-transformed standing biomass and sea surface temperature.
+Similarly, the color scales show the value of the residuals categorically (low = lower 20%, medium = 20-80%, high = >80%).
+Squares indicate the five localities with the highest average residuals of multifuctionality.
+Circles highlight the five localities with the highest average residuals of each function respectively.
 
-# Functioning beyond biomass redefines global coral reef management targets
+![](../output/plots/figure2.png)
 
-# A multi-process analysis of global coral reefs reveals a functional mismatch and the importance of local keystones
+Figure 2: a: Slope values of the Bayesian linear regression for each function with community variables.
+The log-transformed standing biomass was also included as a covariable, but not shown in this figure.
+All data was standardized to be able to compare across functions and variables.
+Functions were log-transformed before standardisation.
+b-d: Marginal effect plots, where each predicted value was normalised a posteriori.
+The solid black line represents the multifunctionality.
 
-Paragraphs:
+![](../output/plots/figure3_option2.png)
 
-## 1) Intro (1 or 2 paragraphs)
-- Coral reefs are diverse, productive and threatened
-- fishes contribute to a high proportion of biomass, are important for functioning, crucial for humans 
-- fishes are threatened by intensive fishing and habitat destruction
-- Will the reefs of the future be able to sustain function? How do we maximize functioning?
+Figure 3: Left: Distribution of the degree of dominance of communities per function.
+A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function.
+Middle: Distributions of frequency of being important to each function of all species.
+A value of 1 thus means that a species is always important whenever present.
+A species is counted as being important in a community if that species contributes to more than 1 divided by the species richness.
+Dots represent the median value, while lines indicate the interquartile range.
+Right: Heat maps of median family-level contributions to each function per bioregion.
+Only the nine most important families are shown here.
+CIP = Central Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, EP = Eastern Pacific, WA = Western Atlantic, WI = Western Indian
+\  
+![](../figures/figure4_allspecies.png)
+
+Figure 4: Vulnerability and importance to each function of fish species included in this study.
+Transparant bars represent the relative number of species in each category of vulnerability.
+Filled bars show the proportion of species that are locally important (i.e.
+perform more than 1/N of the function, where N is the number of species observed in a certain transect).
+
+## Outline 
+### 1) Introduction (1 or 2 paragraphs)
 
@@
 
-## 2) Summary
-- There is a mismatch between different functions   
-- Maximized multifunctionality can only be achieved where all functions are below the maximum    
-- Most communities have a high degree of dominance, and most species are occasional keystones      
-- There are no super hero species that are always important      
-- Species that are important for functioning are more vulnerable to fishing than to climate change, but there is some regional variation
+### 2) Summary
 
@@
 However, due to inherent biological trade-offs, no single configuration can maximize all functions.
-Furthermore, we reveal unpredictable local functional dominance by a wide range of species,changing contributions of families to ecological processes, and varying vulnerabilities of processes to fishing and climate-related stressors.Our results suggest that current local and global conservation objectives for coral reefs and other marine ecosystems need to be reconsidered: management for functionality and targeted conservation of species or functional groups need to be adjusted for local conditions and needs, but holistic protection of a diverse pool of species will increase the likelihood of sustaining critical ecological processes.
+Furthermore, we reveal unpredictable local functional dominance by a wide range of species, changing contributions of families to ecological processes, and varying vulnerabilities of processes to fishing and climate-related stressors.
+Our results suggest that current local and global conservation objectives for coral reefs and other marine ecosystems need to be reconsidered: management for functionality and targeted conservation of species and community structure need to be adjusted for local conditions and needs, but holistic protection of a diverse pool of species will increase the likelihood of sustaining critical ecological processes.
 
-## 3) Mismatch between functions + ecological structure
-- All functions are definitely related to biomass    
-- But, for communities with similar biomass, functions can still vary 10- to 100-fold   
-- Beyond biomass, there is a mismatch between the different functions (fig1)   
-- Trophic, size, and age structure affect functions in different ways (fig1 + 2)   
-- Maximizing "multifunctionality" is defined by intermediate values of certain community variables. (fig2)
+### 3) Communities: Mismatch between functions ~ ecological drivers
+- All functions are definitely related to biomass, but for communities with similar biomass, functions can still vary up to 10- to 1000-fold (fig. S1a). 
+- Beyond biomass, there is a mismatch between the different functions (fig1) with some functions being negatively correlated (fig. S1b, fig. S2) 
+- Trophic, size, and age structure affect functions in different ways (fig.2, a)   
+- Maximizing "multifunctionality" is defined by intermediate values of certain community variables. (fig2:b,c,d)
 
-## 4) Species dominance and vulnerability
-- Locally there is often a high degree of dominance, i.e. a couple of species perform most of the function. (A bit less for herbivory-> more complementary) (fig3, maps)   
-- On the family level, across geographical regions there is some variation in the contributions to functions (fig3, heatmaps)    
-- Globally, there is no species that is always important (beta regressions, distribution parameters, supplemental)
-- Important species are generally more vulnerable to fishing, double jeapardy seems rare
-- About 70% of all species can be locally important (defined as performing more than 1/total nb of species in a community)     
-- Species important to piscivory are most vulnerable to fishing (fig4)    
-- Most herbivores and piscivores are important somewhere
-- A bit more species are important to P excretion compared to N excretion and biomass production     
-- Important species are generally more vulnerable to fishing that to climate change (Important note: climate change only includes dependance on corals of adults)
+### 4) Role of species identity: dominance and vulnerability
+- Locally there is often a high degree of dominance, i.e. a couple of species perform most of the function. (A bit less for herbivory-> more complementary) (fig3, left)   
+- Globally, absolute keystone species rarely exist, most species (~70%) are locally important (fig.
+3, middle).
+This is supported by fitting beta distributions per species (a species with high phi and mu does not exist, i.e.
+no species consistently has a high contribution to a function, fig.
+S3).
+On the other hand about 70% of all species are locally important.
+- On the family level, across geographical regions there is some variation in the contributions to functions, and there is variability within the same region across functions (fig3, right)    
+- Important species are generally more vulnerable to fishing, double jeapardy seems rare (fig.4)
+Most herbivores and piscivores are important somewhere, species important to piscivory are most vulnerable to fishing, there's an considerable proportion of herbivores that has lower vulnerability compared to other functions (fig4).
 
-## 5) Discussion human impact on functioning and community structure
+### 5) Discussion human impact on community structure and functioning
 - We know that multiple human stressors are causing species to decline, and are affecting the size, age, and trophic structure of fish communities.   
 - More details about human impact on community structure, and how in turn that affects functioning.   
-- Indeed, we see that N excretion and production increase with human impact (suppl. figure) (see also Morais as example). 
-- Due to the observed mismatch, it is untenable to achieve maximized values for all functions. Relate to other ecosystems.
+- Indeed, we see that N excretion and production increase with human impact (fig. S4) (see also Morais as example). 
+- Due to the observed mismatch, it is untenable to achieve maximized values for all functions. Relate to other (terrestrial) ecosystems.
 - The effect of potential extinctions of species varies across locations. Provide an example? For most species, total extinction would have a big effect on functioning somewhere.
 
-## 6) Consequences for conservation
+### 6) Consequences for conservation
 - 1) Important to consider multiple functions beyond biomass.
@@
 
-## 7) Future perspective ?????
-- Need to take variability in behavior within each function into account    
-- A fish peeing in a cave does not equal a fish peeing in the water column    
-- Herbivores target different types of algae    
-- Fishes producing biomass may vary in terms of the micronutrient/vitamin content
-
-## 8) Conclusion ?? probably not
-- Analyzing the functioning of reefs really requires the quantification of processes    
-- There is no magical community structure that maximizes all functions    
-- Need to rethink multifunctionality case by case    
-- There are no superhero's for functioning, but most species are occasional superhero's    
-- Conservation should be planned locally with extra attention to fishes vulnerable to fishing
-
-## Figures  
-### Figure 1 option 1:
+## Supplementary figures
 
@@
 
-## figure 1 option 2:
-
-![](../output/plots/fig1_simple_v2.png)
-
-Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities. 
-b) Correlation matrix od the residuals of the five functions.
-
-![](../output/plots/figure2.png)
-
-Figure 2: a: Slope values of the Bayesian linear regression for each function with community variables.
-All data was standardized to be able to compare across functions and variables.
-Functions were log-transformed before standardisation.
-b-d: Marginal effect plots, where each predicted value was normalised a posteriori.
-The solid black line represents the multifunctionality.
-
-![](../output/plots/multimap.png)
-\  
-Figure 3: Left: Median degree of dominance of each function per location.
-A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function.
-Size of dots represents the median value of the function itself.
-Right: Heat maps of median family-level contributions to each function per bioregion.
-CIP = Central Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, EP = Eastern Pacific, WA = Western Atlantic, WI = Western Indian
-
-![](../figures/figure4_allspecies.png)
-
-Figure 4: Vulnerability and importance to each function of fish species included in this study.
-Transparant bars represent the relative number of species in each category of vulnerability.
-Filled bars show the proportion of species that are locally important (i.e.
-perform more than 1/N of the function, where N is the number of species observed in a certain transect).
-
-## Supplementary figures
+Figure S1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities. 
+b) Correlation matrix of the residuals of the five functions.
 
 ![](../output/plots/residuals_multipanel.png)
+
+Figure S2: Scatter plots of residuals of all functions and multifunctionality. 
+\
+
+![](../output/plots/beta_params.png)
+
+Figure S3: Relationship of parameters mu and phi of the fitted beta distributions per species per function. Beta distributions were fitted with random effects for sites and localities.  
 \
@@
 ![](../output/plots/gravity_markets.png)
+
+Figure S4: Predicted residuals of each function with varying gravity to fish markets.  
 \
-
-![](../output/plots/beta_params.png)

### 2020-04-24 R/functions_analysis.R

@@ -1,3 +1,280 @@
+standard <- function(x){
+  m <- mean(x, na.rm = TRUE)
+  sd <- sd(x, na.rm = TRUE)
+  st <- sapply(x, FUN = function(i){
+    st <- (i - m)/sd
+    return(st)
+  })
+  return(st)
+}
+
+normalize <- function(x){
+  100 * (x - min(x, na.rm = TRUE))/(max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
+}
+
+##### calculate multifunctionality #####
+add_multi <- function(summary_transect, herb_pisc){
+  
+  flux <- summary_transect
+  hp <- herb_pisc$summary_herb_pisc
+  sst <- read.csv("data/avSst.csv")
+  flux <- left_join(flux, hp) %>% left_join(sst)
+  
+  # transform into centiles then divide by 100
+  scores <- select(flux, transect_id, Fn, Fp, Gc, I_herb, I_pisc)  %>% 
+    filter(I_herb>0, I_pisc>0) %>%
+    mutate_at(2:6, function(x){normalize(log(x))}) %>%
+    drop_na()
+  # correlation for weighing
+  m <-  cor(scores[2:6])
+  m <- 1-m
+  we <-  rowSums((m))
+  we <- we/sum(we)
+  
+
+  multi <- scores %>%
+    rowwise() %>% 
+    mutate(multi = mean(c(Fn, Fp, Gc, I_herb, I_pisc)), 
+           var = var(c( Fn, Fp, Gc, I_herb, I_pisc))) %>%
+    group_by() %>%
+    mutate(multi = multi*(1-(var/3000))/100) # 3000 = maximum theoretical variance
+  
+  flux <- flux %>% left_join(select(multi, transect_id, multi))
+  
+  return(flux)
+  
+}
+
+flux <- left_join(flux, res)
+flux$good <- ( flux$biomass_tot< 50 & flux$multi < quantile(flux$multi, 0.05, na.rm = TRUE))
+
+flux <- flux %>%
+  mutate(cat = case_when(
+    biomass_tot < 50 & 
+      multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "bb",
+    biomass_tot < 50 & 
+      multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "bg",
+    biomass_tot > 150 & 
+      multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "gb",
[…]

### 2020-04-24 R/functions_plots.R

@@ -1,0 +1,311 @@
+
+make_fig1 <- function(location_effect){
+  
+  library("rnaturalearth")
+  library("rnaturalearthdata")
+  library(rgeos)
+  library(sf)
+  world <- ne_countries(scale = "medium", returnclass = "sf")
+  class(world)
+  
+  
+  
+  theme_worldmap <- function(){
+    theme_bw()+
+      theme(legend.position = "none", 
+            panel.grid = element_blank(),
+            panel.border = element_rect(fill = NA, color = "grey", size = 1),
+            axis.title = element_blank(),
+            axis.text.x = element_text(size = 6),
+            axis.text.y = element_text(size = 6),
+            plot.title = element_text(size = 8, hjust = 0, face = "bold"), 
+            plot.margin = unit(c(0.01,0.01,0.01,0.01), units = , "cm"),
+            panel.spacing = unit(0, "cm")
+      ) 
+  }
+  
+  col <- fish(n = 5, option = "Callanthias_australis")
+  
+  get_scale <- function(f){
+    quant1 <- quantile(f[f < 0], c(0, 0.5, 1), na.rm = TRUE)
+    quant2 <- quantile(f[f > 0], c(0, 0.5, 1), na.rm = TRUE)
+    quant <- c(quant1[1:2], 0, quant2[2:3])
+    quant <- quantile(f, c(0,0.2,0.8,1), na.rm = TRUE)
+    quant[1] <- quant[1] - 0.5   # adjust lower bound
+    factor(cut(f, breaks = quant), labels = c( "low", "medium", "high"))
+  }
+  
+  get_scale(location_effect$r_loc_Fn)
+  
+  getcol <- colorRampPalette(c("white", col[1]))
+  pal2 <- getcol(n = 3)
+  getcol <- colorRampPalette(c("black","white"))
+  pal1 <- getcol(n = 3)
+  pal <- c(pal1[1], pal2[2:3])
+  pal <- c("black", "grey50", col[1])
+  
+  
+  
+  a <-
+    ggplot(location_effect) + 
+    geom_sf(data = world, color = NA, fill = "lightgrey") +
+    geom_point(aes(x = lon, y = lat, color = get_scale(r_loc_Fn), 
+                   size = get_scores(r_loc_Fn)),  alpha = 0.8,
+               position = position_jitter(0,0), shape = 16) +
[…]

### 2020-04-24 R/functions_wrangling.R

@@ -733,8 +733,8 @@ colnames(summary) <- c(
 return(summary)
 }
 
-combine_contributions <- function(sp_loc, contributions_Fc, contributions_Fn, 
-                                  contributions_Fp, contributions_Ic, contributions_Gc, 
+combine_contributions <- function(sp_loc, contributions_Fn, 
+                                  contributions_Fp, contributions_Gc, 
                                   contributions_I_herb, contributions_I_pisc, herb_pisc){
   
   herb <-  herb_pisc$contributions_herb_pisc %>%
@@ -750,8 +750,8 @@ combine_contributions <- function(sp_loc, contributions_Fc, contributions_Fn,
     cbind(contributions_I_pisc)
   
   comb <- cbind(
-    sp_loc, contributions_Fc, contributions_Fn, contributions_Fp,
-    contributions_Ic, contributions_Gc
+    sp_loc, contributions_Fn, contributions_Fp,
+    contributions_Gc
   ) %>% left_join(sploc_h) %>% left_join(sploc_p) %>% replace(., is.na(.), 0)
   
   return(comb)
@@ -770,15 +770,15 @@ add_occurence <- function(contributions, contributions_sp_loc, herb_pisc){
     dplyr::select(-tot)
   result <- left_join(contributions_sp_loc, occ)
   
-  correct <- filter(result, (Fc_p_q3 - Fc_p_q1) > 0.99) %>% select(1:2) %>%
-    inner_join(select(ungroup(contributions), bioregion, species, Fc_p, Fn_p, Fp_p, Ic_p, Gc_p)) %>%
+  correct <-  select(result, 1:2) %>%
+    inner_join(select(ungroup(contributions), bioregion, species, Fn_p, Fp_p, Gc_p)) %>%
     left_join(herb_pisc$contributions_herb_pisc) %>%
     group_by(bioregion, species) %>%
     summarise(
-      Fc_p_m = median(Fc_p),
-      Fc_p_sd = sd(Fc_p),
-      Fc_p_q1 = quantile(Fc_p, 0.025),
-      Fc_p_q3 = quantile(Fc_p, 0.975),
+      # Fc_p_m = median(Fc_p),
+      # Fc_p_sd = sd(Fc_p),
[…]

### 2020-04-24 R/packages.R

@@ -14,5 +14,10 @@ library(fishualize)
 library(ggnewscale)
 library(tidytree)
 library(ggtree)
+library(forcats)
+library(ggrepel)
+library(tidyr)
+library(readr)
+
 
 Sys.setlocale("LC_MESSAGES", "en_US.utf8")

### 2020-04-24 R/plan.R

@@ -28,40 +28,39 @@ plan <- drake_plan(
   contributions = get_contributions(tfish, cnpflux, params, summary_transect),
   sp_loc = unique(select(ungroup(contributions), bioregion, species)),
   
+  # herbivory, piscivory --> in g dry mass
+  herb_pisc = get_herb_pisc(tfish, cnpflux, params, summary_transect),
+  
+  # add multifunctionality, sst 
+  summary_transect_complete = add_multi(summary_transect, herb_pisc),
+  
+  # run models proc ~ biomass et al
+  procmodels = run_procmodels(summary_transect_complete),
+  residuals = get_residuals(summary_transect_complete, procmodels),
+  location_effect = get_location_effect(procmodels, summary_transect),
+  
   # run models to get relative contribution of each ecosystem process
   models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
   models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
-  models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
-  models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
-#  models_contributions_In = fit_contribution_In(contributions, sp_loc),
-#  models_contributions_Ip = fit_contribution_Ip(contributions, sp_loc),
+  #models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
+  #models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
   models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
-#  models_contributions_Gn = fit_contribution_Gn(contributions, sp_loc),
-#  models_contributions_Gp = fit_contribution_Gp(contributions, sp_loc),
-#  models_contributions_Wp = fit_contribution_Wp(contributions, sp_loc),
-#  models_contributions_Wn = fit_contribution_Wn(contributions, sp_loc),
-#  models_contributions_Wc = fit_contribution_Wc(contributions, sp_loc),
-  
-  # herbivory, piscivory --> in g dry mass
-  herb_pisc = get_herb_pisc(tfish, cnpflux, params, summary_transect),
   
   # run models to get relative contribution herbivory piscivory
   models_contributions_I_herb = fit_contribution_I_herb(herb_pisc, sp_loc),
   models_contributions_I_pisc = fit_contribution_I_pisc(herb_pisc, sp_loc),
   
   # extract contributions from model
[…]

### 2020-04-24 R/play.R

@@ -3,7 +3,7 @@ loadd(vulnerability)
 
 con <- left_join(contributions_sp_loc_occ, vulnerability) %>% 
   drop_na(vuln_fi, vuln_climate) 
-  
+
 
 
 tax <- rfishbase::load_taxa()
@@ -44,7 +44,7 @@ tree1d <- as.treedata(tree1t)
 
 data <- filter(sub, species%in% tree1$tip.label) %>% 
   mutate(I_herb_p_m = case_when(I_herb_p_m == 0 ~ NA_real_, 
-                                      TRUE ~ I_herb_p_m),
+                                TRUE ~ I_herb_p_m),
          I_pisc_p_m = case_when(I_pisc_p_m == 0 ~ NA_real_, 
                                 TRUE ~ I_pisc_p_m)) %>%
   mutate(Fp_q = quant(Fp_p_m/rel_occ),
@@ -57,7 +57,7 @@ data <- filter(sub, species%in% tree1$tip.label) %>%
          Gc_n = normalize(Gc_p_m/rel_occ),
          I_herb_n = normalize(I_herb_p_m/rel_occ),
          I_pisc_n = normalize(I_pisc_p_m/rel_occ)
-         ) %>%
+  ) %>%
   as.data.frame()
 
 rownames(data) <- data$species
@@ -72,7 +72,7 @@ p1 <-
            offset = 0.2, width=1, 
            colnames_position = "top", font.size=2, color = "white") + 
   scale_fill_fish_d("Hypsypops_rubicundus", begin = 0, 
-                     labels=c("[0,0.05[", "[0.05,0.25[", "[0.25,0.75[",  "[0.75, 0.95[", "[0.95,0.99[", "[0.99,1[")) + 
+                    labels=c("[0,0.05[", "[0.05,0.25[", "[0.25,0.75[",  "[0.75, 0.95[", "[0.95,0.99[", "[0.99,1[")) + 
   geom_tiplab(aes(angle = angle, label = tree1d@data$Family), size = 2, offset = 150)
 
 ggsave("output/plots/phyloplot_con_c_indopacific.pdf", p1, height = 12, width = 12)
@@ -482,7 +482,7 @@ plots <- lapply(unique(rank$bioregion), function(i){
     subset(value>0)
   print(i)
   plot <-
-  ggplot(sub) +
+    ggplot(sub) +
     geom_bar(aes(y = value, x = spname, fill = Family), stat = "identity") +
[…]

### 2020-04-28 text/suppl_methods.Rmd
adding new diet categories parravicini et al. 2020

@@
 # Supplementary methods
-# 1. Underwater visual census database
-\noindent We used a published global database of field data collection of belt transects [@Barneche2019].
-This database encompasses transect data across 585 sites in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Figure).
-This database only includes sites with a hard reef bottom are at the outer reef slope and were carried out at a constant depth, parallel to the reef crest.
-We splected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all sites.
-The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
 
-# 2. Phylogeny
-
-# 3. Parameter estimates
-
-\newpage
+To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required (Table 1).
+Here, we describe how these parameters were quantified for all 1110 species in our database.
 
@@
 
-## 3.1. Growth parameters
+## 1. Growth parameters
 
-### 3.1.1 Data compilation
+### 1.1 Data compilation
 We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF).
@@
 
-### 3.1.2 Statistical analysis and extrapolation
+### 1.2 Statistical analysis and extrapolation
 
@@
 
-We use the R package brms to fit a bayesian phylogenetic regression model We predict log(kmax) in function of log(sizemax), sst with varying intercept per species.
-The intercept per species is structured by the covariance matrix.
-
- Family: gaussian 
-  Links: mu = identity; sigma = identity 
-Formula: log(kmax) ~ log(sizemax) + sstmean + (1 | phylo) 
-   Data: oto (Number of observations: 496) 
-Samples: 4 chains, each with iter = 2000; warmup = 1000; thin = 1;
-         total post-warmup samples = 4000
-
-Group-Level Effects: 
-~phylo (Number of levels: 181) 
-              Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
-sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00
-
-Population-Level Effects: 
-           Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
-Intercept      0.66      0.58    -0.48     1.81       1498 1.00
-logsizemax    -0.76      0.10    -0.96    -0.57       1281 1.00
-sstmean        0.02      0.01    -0.00     0.05       4071 1.00
-
-Family Specific Parameters: 
-      Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
-sigma     0.46      0.02     0.43     0.50       1991 1.00
-
-Samples were drawn using sampling(NUTS). For each parameter, Eff.Sample 
-is a crude measure of effective sample size, and Rhat is the potential 
-scale reduction factor on split chains (at convergence, Rhat = 1).
-
 \noindent We extrapolated $\kappa$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
@@
 
-## 3.2 Body stoichiometry    
-### 3.2.1 Data collection    
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, Carribean and Palmyra.
+## 2 Body stoichiometry    
+### 2.1 Data collection    
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Carribean, and Palmyra.
 Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser.
@@
 
-### 3.2.2 Data analysis and extrapolation
+### 2.2 Data analysis and extrapolation
 
@@
 
-## 3.3 Diet stoichiometry    
-### 3.3.1 Data collection 
-\noindent We collected 345 adult individuals of 37 species and 12 families between 2018 and 2019 in Mo'orea and Tetiaroa, two Polynesian islands.
+## 3 Diet stoichiometry    
+### 3.1 Data collection 
+\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian islands.
 We extracted the stomach content and stored it in a 2ml tube.
 After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder.
-Then, samples were sent to the lab (more info!!) for CNP% content analysis.
+Then, samples were sent to the lab for CNP% content analysis using similar methods as for the fish body stoichiometry.
 
-### 3.3.2 Data analysis and extrapolation  
-\noindent We extracted trophic group information from ref diet paper.
-We constructed a simple multivariate Bayesian regression model to summarize CNP\% content data per trophic group with a random effect at the species level.
-This model had a Bayesian R2 of 0.61 (0.56-0.65), 0.31 (0.23-0.38), and 0.48 (0.42-0.54).
-bayes_R2(fit_cnpdiet)
+### 3.2 Data analysis and extrapolation  
+\noindent We used trophic guilds defined by Parravicini et al.
+(2020).
+We fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level.
+This model had a median Bayesian R2 of 0.62, 0.62, and 0.48 for C, N and P respectively.
+Next, we extracted 1000 draws of the predicted the CNP\% per trophic guild.
+Parravicini et al.
+(2020) provides the probability of reef fish species to be assigned to each of the 8 defined trophic guilds.
+By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database.
+We then took the average and standard deviation across all 1000 draws.
+
+## 4 Metabolic parameters    
+### 4.1 Data collection    
+In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species.
+Individuals were collected using handnets and clove oil by scuba divers.
+After arrival in the lab, individuals were kept starved for a period of x hours/days.
+Then, they were held in respirometry chambers for 23 hours.
+
+## 4.2 SMR and MMR
+
+## 4.3 metabolic parameters
+
+fit_mr <- brm(log10(mr) ~ 1 + log10(mass) + (0 + log10(mass)|Family) + (0 + log10(mass)|Species) + 
+                (1|Family:mr_type) + (1|Species:mr_type) + (0 + log10(mass)|Family:mr_type) +
+                (0 + log10(mass)|Species:mr_type), data = test,
+              control = list(adapt_delta = 0.9),#, max_treedepth = 12),
+              prior = set_prior(class = "b", "log10mass", prior = "normal(0.8, 0.5)"), cores = 4,
+              warmup = 2000, iter = 4000)
+
 Estimate    Est.Error      Q2.5   Q97.5
-R2c 0.6250538 0.02299497 0.5756378 0.6642792
-R2n 0.3043510 0.03973636 0.2271046 0.3771861
-R2p 0.4857449 0.03164611 0.4191740 0.5417580
-
-\noindent We then predicted the CNP\% per diet category.
-
-   cat    Dc_m  Dn_m  Dp_m Dc_sd Dn_sd Dp_sd
-  <chr> <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>
-1 1      30.6  4.13 0.424  2.88 0.865 0.197
-2 2      35.1  7.96 1.50   2.71 0.857 0.193
-3 3      33.1  5.79 0.751  3.52 1.06  0.242
-4 4      38.1  7.45 0.879  5.14 1.60  0.360
-5 5      28.9  5.10 0.619  3.35 1.03  0.239
-
-## 3.4 Metabolic parameters    
-### 3.4.1 Data collection
+R2 0.9728325 0.0004120478 0.9719845 0.97362

### 2020-04-28 _drake.R

@@ -1,0 +1,6 @@
+source("R/packages.R")  # loads packages
+source("R/functions_wrangling.R") # defines the create_plot() function
+source("R/functions_analysis.R") # defines the create_plot() function
+source("R/plan.R")      # creates the drake plan
+
+config <- drake_config(plan, lock_envir = FALSE)

### 2020-07-11 text/main.Rmd
draft edits after seb comments

---
output:
  word_document:
    fig_caption: yes
    reference_docx: ../text/word_template.docx
bibliography: ../text/global_proc.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functional trade-offs reveal coral reef vulnerability

Energy and nutrient fluxes underpin the functioning and productivity of all global ecosystems [@Welti2017]. 
As such, monitoring and conserving energy flow is critical to natural systems and humanity. Due to the efficient cycling of nutrients, coral reefs flourish as hyperdiverse and economically important ecosystems. 
Understanding their ability to cycle energy and nutrients is key to conserving coral reefs and the services they provide to humanity, especially under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017]. 
Yet, we primarily assess coral reef functioning based on static variables such as fish biomass and the diversity of species traits [e.g. @Mouillot2014; @Cinner2020; @Mora2011plos]. 
The lack of global quantitative assessments across multiple functions impedes our capacity to define the drivers of functional coral reefs [@Bellwood2019; @Brandl2019front]. 
Here, we quantify ecosystem functioning on global coral reefs using five key biogeochemical fluxes that are mediated by reef fishes, then we disentangle their ecological drivers and estimate their vulnerability to anthropogenic pressure. 
We demonstrate that beyond biomass, the most commonly used indicator to quantify reef fish functioning, functions vary from 10 to 100-fold. Further, critical trade-offs exist between functions, which are driven by differences in community structure; therefore, it is impossible to simultaneously maximize all functions. 
In addition, we reveal that strikingly few species contribute disproportionally to each ecosystem function. 
However, the identity of these species varies significantly across reefs, with ~70% of all species assuming a key role on a local scale. 
Thus, maintaining coral reef ecosystem functioning is a multifaceted objective that requires the protection of a large proportion of species, a considerably more complex management strategy than maximising fish biomass. 
The existence of trade-offs between multiple functions and the lack of key species over large spatial scales provides critical context for coral reef conservation. 
Although it is impossible to maximize all aspects of functioning, we can preserve the integrity of coral reef  fluxes of elements by applying locally administered solutions that go beyond the simple protection of biomass.

The flow of elements through biological communities fuels all life on Earth [@Welti2017] 
Although there is a strong consensus on the importance of these fluxes, also known as ecosystem functions, our ability to manage for ecosystem functioning remains poor [@Welti2017]. 
For millennia, humans have managed nature with an economic mindset to maximize desirable components such as plant or animal biomass [@Weisser2017]. 
However, Earth’s resources are finite, and the existence of multiple ecosystem functions comes with trade-offs, whereby efforts to maximize one function may negatively impact another [@Tallis2008]. 
To make informed management decisions that pertain to ecosystem functioning, it is critical to understand the mechanisms that drive these trade-offs [@Rodriguez2006].

In the marine realm, coral reefs are the most diverse and productive ecosystem, and they underpin indispensable ecosystem services to humans. 
As coral reefs thrive in nutrient-poor waters, efficient nutrient cycling is the key to their productivity. 
However, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
Over the past decade, severe biodiversity declines have strained the ability of coral reefs to maintain ecosystem functioning and brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front]. 
However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish biomass, coral cover, and the richness of species traits [e.g. @Mora2011plos; @Cinner2020; @Mouillot2014]. 
Consequently, we know little about the co-occurrence of multiple ecosystem functions and their drivers, which provides us with limited guidance for coral reef management in our rapidly changing world.

Integrating principles of biogeochemistry and traditional ecological assessments provides a promising path toward understanding and conserving the fluxes that underpin reef functioning. 
Here, we integrate reef fish trait databases across 9,118 communities with bioenergetic modelling to (1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory), (2) disentangle their ecological drivers, and (3) investigate the contribution and vulnerability of different species to each function.

Fish biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front]. 
However, biomass is a product of nutrient cycling that drives productivity on reefs [@Szmant-Froelich1983]. 
Although there was a strong relationship between biomass and all five functions, after controlling for biomass, different functions varied up to 10 to 100-fold (see Extended Data Fig. 1a). 
This striking community-level variability is driven by the species-specific biological traits of fishes [@Schiettekatte2020]. 
Further, the residual variability of functions revealed strong trade-offs among different functions (see Extended Data Fig. 1b). As a consequence, at a given biomass, no reef can maximize all functions (fig. 1). 
For example, when extending the proposed baseline of ~100g/m2 standing fish biomass to define a healthy reef [@MacNeil2015] to our dataset, 46% of global fish communities reached this biomass baseline, yet only 19% showed adequate functioning to satisfy the predicted threshold of each function based on the biomass baseline. 
In fact, due to existing trade-offs between functions, a biomass of ~450g/m2 is necessary to ensure above-threshold levels for each function. 
Our proposed biomass is 450% higher than previously estimated, and, notably, a mere 13% of the fish communities in our dataset meet this threshold (Extended Data Fig. 2).

What underpins the trade-offs between multiple functions on coral reefs? 
To explore the ecological drivers of each function, we fit Bayesian mixed models using variables that describe fish community structure, including body size, trophic level, age structure (expressed as immaturity), and species richness. 
We found that functional trade-offs are mediated by contrasting aspects of community structure (fig. 2). 
For example, phosphorous excretion is maximized in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels (See also @Allgeier2014). 
In contrast, biomass production is maximised in communities dominated by small, immature fishes at lower trophic levels. 
Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate [@Brown2004], and as a consequence, small individuals have elevated consumption rates and highly contribute to functions that rely on rapid energetic turnover [@Barneche2014]. 
In contrast, fishes in early life stages or with small body sizes feed on nutrient-poor diets that are limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion. 
These results highlight the critical need to integrate organismal biology with community ecology to understand ecosystem-wide biogeochemical fluxes.

Beyond community structure, species identity profoundly affects rates of functioning [@Ruttenberg2019; @Topor2019]. 
To explore whether some species or families consistently contribute more to functioning than expected by their biomass, we estimated the functional dominance of species and their frequency across communities. 
Across global coral reefs, functions are consistently dominated by a few species (fig. 3b). 
However, despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally dominant species varies remarkably. 
In fact, ~70% of all species contribute disproportionally to a function in a given community, but worldwide, the frequency of dominance is strikingly low for each species (fig. 3c). 
Despite high species richness on coral reefs, researchers often report the existence functionally dominant “key species” [e.g. @Bellwood2006]. 
In contrast, we demonstrate that while dominance is indeed prevalent, the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].

Thus, the local decline of a few species can have a large impact if those species are not functionally redundant. 
By coupling species’ functional contributions with their vulnerability to fishing and climate change, we demonstrate that the most profound human-mediated changes are likely to impact piscivory via fishing (fig. 4). 
Like piscivory, herbivory is almost exclusively upheld by few key species; therefore, herbivory is also vulnerable to species loss due to lack of redundancy. 
Given the local nature of species’ functional contributions, the determination of species-based conservation efforts at a global scale will fail to sustain coral reef functioning. 
Rather, ecosystem functioning can be supported by local actions that avert the functional extinction of species [@Mccauley2015].

Human impact has already caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs. 
While the effects of these alterations on ecological processes are more difficult to monitor than declines in biomass, the loss of functioning may have profound consequences for reef ecosystems. 
For example, intensive fishing leads to biomass declines, which particularly impacts large fishes and consequently changes the size, age, and trophic structure of fish communities [@Graham2017]. 
These effects can favor nitrogen excretion and production [e.g. @Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (Extended Data Fig. 3). 
On the other hand, changes in community structure triggered by coral cover declines are associated with a shift toward herbivores [@Graham2006; @Ceccarelli2016]. 
Herbivores have a minor contribution to phosphorus excretion [@Schiettekatte2020], so herbivore dominance and the subsequent community-level decline of phosphorus may induce a negative feedback loop for coral growth [@Shantz2015]. 
This is particularly problematic when considered in conjunction with climate change, as phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].

Our results demonstrate the challenges of managing one of Earth’s most diverse and vulnerable ecosystems. 
Rooted in our agroeconomic history, maximizing ecosystem functioning is the dominant objective of many 21st century conservation initiatives. 
The revealed functional trade-offs challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
Traditionally, marine reserves have been the main conservation strategy for coral reefs [@Graham2020].
While they provide benefits for biomass and herbivory, they provide little insurance for diversity in populated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020]. 
Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential energetic pathways. 
Thus, it is essential to gauge reef “health” based on multiple, complementary, process-based functions [@Brandl2019front]. 
Furthermore, individual reefs require local management plans to protect species with key roles in multiple functions, and the presence of multiple stakeholders may require the prioritisation of various functions based on local needs and stressors. 
Globally, given that majority of species are locally important for functioning in a certain community, the conservation of a wide range of species is desirable, in addition to tackling the primary threat to coral reefs, climate change [@Bruno2019].

Biomass alone does not suffice to explain coral reef ecosystem functioning, and, in fact, there is a strong mismatch among different functions performed by coral reef fishes. 
Our results contribute to an ongoing discussion surrounding the question: what constitutes a healthy reef? 
We posit that the answer cannot be rooted in a purely economic mindset that aims for the maximization of all functions. 
Rather, a diverse community that supports intermediate levels of each function is ideal, with many species emerging as key local players. 
In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring beyond biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].

# Figures

![Figure 1: World maps of five key ecosystem functions, independent of fish biomass. Dots indicate the localities that are included in this study. Dot size represents the rank of the average of the residuals of each log-transformed function after regression with the log-transformed standing biomass and sea surface temperature. Similarly, the color scales show the value of the residuals categorically (low = lower 25%, medium = 25-75%, high = >75%). Circles highlight the five localities with the highest average residuals of each function respectively.](../output/plots/fig1_multimap.png)

![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables. The log-transformed standing biomass was also included as a covariable, but not shown in this figure. All data was standardized to be able to compare across functions and variables. Functions were log-transformed before standardisation.](../output/plots/fig2_com_slopes.png)

![Figure 3: a) Median family-level contributions to each function, relative to their contribution to biomass. Only the 12 most important family’s are shown here, and families are ordered by their median contribution to biomass. b) Distribution of the degree of dominance of communities per function. A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function. c) Distributions of frequency of being dominant to each function of all species across all communities. A value of 1 means that a species is always important whenever present. A species is counted as being dominant in a community if that species contributes to more than 1 divided by the species richness. Dots represent the median value, while lines indicate the interquartile range.](../output/plots/fig3_contributions.png)

![Figure 4: Vulnerability and importance to each function of fish species included in this study. Transparant bars represent the relative number of species in each category of vulnerability. Filled bars show the proportion of species that are locally important (i.e. perform more than 1/N of the function, where N is the number of species observed in a certain transect).](../figures/figure4_all_species.png)

![Extended Data Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities. b) Correlation matrix od the residuals of the five functions.](../output/plots/annex_fig1_mf_logbiomass.png)

![Extended Data Figure 2: Predicted probability of crossing a reference threshold for all five functions with the log-transformed biomass.](../output/plots/annex_fig2.png)

![Extended Data Figure 3: Fitted linear regression of each function with the log-transormed gravity to markets. Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

# References

### 2020-07-11 text/methods.Rmd
draft edits after seb comments

@@
 ---
-title: "Methods"
 output:
-  html_document: default
+  word_document:
+    fig_caption: yes
+    reference_docx: ../text/word_template.docx
+bibliography: ../text/global_proc.bib
+csl: nature.csl
 ---
@@
 
-# 1. Underwater visual census database
-\noindent We used a published global database of field data collection of belt transects [@Barneche2019].
-This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Suppl.
-table).
-This database only includes sites with a hard reef bottom at the outer reef slope and were carried out at a constant depth, parallel to the reef crest.
-We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
-The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+# Methods
 
-# 2. Bioenergetic modeling
+## 1. Underwater visual census database
+\noindent We used a published global database of reef fish abundance and sizes collected along belt transects [@Barneche2019].
+This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic.
+The database only includes sites with a hard reef bottom at the outer reef slope.
+Transects were carried out at a constant depth, parallel to the reef crest.
+We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize the bias related to the indentification of small individuals, and finally we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
+The dataset then included 1110 species that belong to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+
+## 2. Bioenergetic modeling
 \noindent We applied a series of bioenergetic models for each existing combination of species identity, body size, and sea surface temperature (n = 30668).
-The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [Schiettekatte2020].
+The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
 As such, this model is well suited for the application of a wide variety of fish species.
@@
 The bioenergetic model then allows for the prediction of elemental fluxes mediated by individuals, including ingestion rate, excretion rates of N and P, and growth rate.
-Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production (g C/day), herbivory (g/day), and piscivory (g/day).
+Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production of body mass through growth (g C/day), herbivory, i.e.
+ingestion rate of macrophytes (g/day), and piscivory, i.e.
+ingestion rate of fishes (g/day).
 We summed the contribution of each individual to each process on the transect-level, to get community-level estimates, then dividing it by the surface area that was surveyed.
 Each process is thus expressed in dry mass per day per square meter.
-We note that N excretion, P excretion, and production include contributions of each individual, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild (Parravicini et al.
-2020).
+We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild (@Parravicini2020).
 
-# 3. Variation beyond biomass and temperature
-\noindent To quantify the fold variation that exists across transects with a similar total standing fish biomass, we grouped transects into 320 bins with an interval of 50g/m2.
-We then quantified the fold-variation by dividing the maximum by the minimum value for each process within each bin.
+## 3. Relationship between functions and biomass
 
-\noindent To assess the covariation that exists among processes without the positive effect of standing biomass and sea surface temperature, we performed a Bayesian mixed effect regression of each log-transformed function for transect-scale observations ($y_j$):
-\begin{equation}
-	y_\textrm{j} \sim N(\mu_j, \sigma_j)),
-	\label{modbiom1}
-\end{equation}
+To assess the effect of biomass and sea surface temperature sst), we performed a Bayesian mixed effect regression of each log-transformed function for transect-scale observations ($y_j$):
+<!-- \begin{equation} -->
+	$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
+<!-- 	\label{modbiom1} -->
+<!-- \end{equation}      -->
 
-\begin{equation}
-	\mu_\textrm{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}
-	\label{modbiom2}
-\end{equation}
-and then extracted the median residuals for each process per transect.
+<!-- \begin{equation} -->
+$$\mu_{\textrm{j}} = \beta_0 +{\beta_1} {x_{log(biomass),j}} + {\beta_2} {x_{sst,j}}$$
+<!-- 	\label{modbiom2} -->
+<!-- \end{equation} -->
+
+\noindent We then assessed the covariation between functions, independent of biomass and sst.
+To do so, we first extracted the median residuals for each function per transect.
 In some transects, there were no piscivores or herbivores observed.
 In those cases, we did not include these transects in the analysis.
-To assess the covariation, we then quantified the correlations that exist among the different proocesses.
+To assess the covariation, we then quantified the correlations that exist among the different functions.
 To visualize the residuals per locality on a world map, we first grouped all transects per site by taking the median value for each process across multiple transect.
@@
 
-# 4. Community structure 
-\noindent To investigate the effect of the community structure together with the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
+\noindent Finally, we quantified baseline values for each function and assessed the occurrence of communities that reach baseline values for each function.
+Based on the biomass reference for a healthy reef of ~100g/m2 (@MacNeil2015), we predicted the baseline for each function for the full range of sst's.
+Then, for all communities, we quantified whether or not the community had higher values for all functions compared to their baselines.
+Using this logical variable, we fitted a Bernoulli model with a logit-link to predict the probability of having all five functions above their threshold in relation to biomass and sea surface temperature, similar to the model specified above.
+
+## 4. Effect of community structure on ecosystem functions 
+\noindent To investigate the effect of the community structure accounting for the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
+These variables discribe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
 Specifically, we took the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
@@
 The immaturity is quantified using the following formula:
-\begin{equation}
-	\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),
-	\label{imm}
-\end{equation}
+<!-- \begin{equation} -->
+	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
+<!-- 	\label{imm} -->
+<!-- \end{equation} -->
 where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i.
@@
 
-\begin{equation}
-	y_\textrm{j} \sim N(\mu_j, \sigma_j)),
-	\label{modcom1}
-\end{equation}
+<!-- \begin{equation} -->
+$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
+<!-- 	\label{modcom1} -->
+<!-- \end{equation}      -->
 
-\begin{equation}
- \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j}
-	\label{modcom2}
-\end{equation}
+<!-- \begin{equation} -->
+$\begin{array}{c} \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \\ \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} \end{array}$
+<!-- 	\label{modcom2} -->
+<!-- \end{equation} -->
 
-To compare effects across functions and assess the relative importance of each variable we standardized all variables prior to model fitting.
+To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
 We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations.
@@
 
-# 5. Contributions and dominance
+## 5. Species dominance and contributions to functions
 To investigate the role of each species for each function, we quantified the contribution of each species to each function for all transects as followed:
-\begin{equation}
-	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},
-	\label{con}
-\end{equation}
+<!-- \begin{equation} -->
+$$	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},$$
+<!-- 	\label{con} -->
+<!-- \end{equation} -->
 where i is a certain species, j is a transect, F is the value of function f.
@@
 Then, we quantified the degree of species dominance per function for each transect. 
-We did this by first ranking species according to their contribution, followed by quantifying the cumulative contributions.
+We did this by first ranking species according to their contribution to function, followed by quantifying the cumulative contributions of species to functions.
 Then, we used the area under the species accumulation curve as a measure for the degree of dominance.
 Specifically, the degree of dominance (DD) was calculated as followed:
-\begin{equation}
-	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},
-	\label{dd}
-\end{equation}
+<!-- \begin{equation} -->
+$$	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},$$
+<!-- 	\label{dd} -->
+<!-- \end{equation} -->
 where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, $A_max$ is the theoretical area under the curve where one species performs the entire function.
 They are quantified as:
-\begin{equation}
-	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},
-	\label{Amin}
-\end{equation}
+<!-- \begin{equation} -->
+$$	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},$$
+<!-- 	\label{Amin} -->
+<!-- \end{equation} -->
 
-\begin{equation}
-	\textrm{A}_{max} = R - 1,
-	\label{Amax}
-\end{equation}
+<!-- \begin{equation} -->
+$$	\textrm{A}_{max} = R - 1,$$
+<!-- 	\label{Amax} -->
+<!-- \end{equation} -->
 
-\begin{equation}
-	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},
-	\label{A}
-\end{equation}
+<!-- \begin{equation} -->
+$$	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},$$
+<!-- 	\label{A} -->
+<!-- \end{equation} -->
 
-where C_i is the contribution of a certain species and R is the species richness.
-The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that one species performs the entire function, which is only possible in practice if there is only one species performing a particular function.
+where $C_i$ is the contribution of a certain species and R is the species richness.
+The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that one species performs the entire function.
 
-Finally, to know how often species are contributing a lot for a certain function, we quantified the frequency of dominance, i.e.
+Finally, to know how often species are contributing more than average for a certain function, we quantified the frequency of dominance, i.e.
 the number of times a species is dominant divided by the total number of transects in which that species is observed.
@@
 
-# 6. Species vulnerability 
-For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure.
+## 6. Species vulnerability to fishing and clilate change
+For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
 For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals.
 Vulnerability to climate change is related to diet specialization, habitat specialization, recruitment specialization for live coral and body size [@Graham2011].
-@Graham2011 developed a score for climate change vulnerability for 134 species.
-We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from fishbase), the dependence on coral for food (3 categories: not dependent, facultative corralivore, and obligate corralivore), and dependence on coral for habitat (2 categories: dependent vs.
+Graham et al.
+(2011) [@Graham2011] developed a score for climate change vulnerability for 134 species.
+We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
 not dependent).
@@
 We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
-For species' vulnerability to fishing, we extracted the index from @Cheung2005.
+For species' vulnerability to fishing, we extracted the index from Cheung et al.
+(2005) @Cheung2005.
+
+## References

### 2020-07-11 text/suppl_methods.Rmd
draft edits after seb comments

@@
 output:
-  pdf_document: default
+  word_document:
+    fig_caption: yes
+    reference_docx: ../text/word_template.docx
+bibliography: ../text/global_proc.bib
+csl: nature.csl
 ---
@@
 ```
+\usepackage[dvipsnames]{xcolor}
 
@@
 
-To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required (Table 1).
-Here, we describe how these parameters were quantified for all 1110 species in our database.
-
-\begin{table}[h!]
-\centering
-\caption{. Overview of model input parameters. VBGC = von Bertalanffy growth curve.}
-\begin{tabular}{l l l}
-\hline
-\rowcolor{lightgrey}
-Symbol & Description & Unit\\
-\hline
-$k$ & Index for element C, N or P & \_ \\
-$a_\textrm{k}$  & Element-specific assimilation efficiency & \% \\
-$l_\textrm{t}$  & Total length of individual at time t & cm \\
-$l_{\infty}$  & Asymptotic adult length (VBGC) & cm \\
-$\kappa$  & Growth rate parameter (VBGC) & $\textrm{yr}^{-1}$ \\
-$t_0$  & Age at settlement (VBGC) & $\textrm{yr}$ \\
-$lw_a$  & Parameter length-weight relationship & $\textrm{g cm}^{-1}$ \\
-$lw_b$  & Parameter length-weight relationship & \_\\
-$Q_\textrm{k}$  & Element-specific body content percentage of dry mass & \% \\
-$f_\textrm{0}$  & Metabolic normalisation constant independent of body mass & $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$ \\
-$\alpha$  & Mass-scaling exponent &  \_\\
-$\theta$  & Activity scope & \_ \\
-$v$  & Environmental temperature & \textdegree C \\
-$h$  & trophic level & \_ \\
-$r$  & Aspect ratio of caudal fin & \_ \\
-$F_\textrm{0Nz}$  & Mass-specific turnover rate of N & $\textrm{g N} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
-$F_\textrm{0Pz}$  & Mass-specific turnover rate of P & $\textrm{g P} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
-$D_\textrm{k}$  & Elemental stoichiometry of diet & \% \\
-\hline
-\end{tabular}
-\end{table}
-
-\newpage
+To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required [see @Schiettekatte2020].
+Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models.
+All analyzes were carried out in R v.3.6.3 and Bayesian modes were run using Stan [@Carpenter2017] and the R package brms [@Burkner2017].
 
@@
 ### 1.1 Data compilation
-We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF).
+We first compiled maximum lengths for all species with Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$ .
 For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e.
-$k_{max}$, @Morais2019].
+$k_{max}$, @Morais2018].
 $t0$ was kept constant at 0 for all species.
 
-We extracted the data for $k_{max}$ from @Morais2019 and filtered out only the species of our species list.
+We extracted the data for $k_{max}$ from Morais et al.
+(2018) @Morais2018 and filtered out only the species of our species list.
 As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method.
@@
 
-Further, we used the otolith data provided by Morat et al., including measurements of fishes from five Polynesian islands and fitted the Von Bertalanffy growth models to all species at each location for which there were at least 3 individuals.
-We fitted the model using Bayesian regression models as provided by fishflux.
+Further, we collected additional otolith data, including measurements of fishes from five Polynesian islands. 
+We collected data across four archipelagos, including six distinct islands: Moorea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018.
+All fishes were collected in the lagoon and/or outer slope, depending on the accessibility of the respective habitats.
 
-After combining the two data sources, we obtained a database of 496 observations and 181 species.
+For each species, otoliths were cut transversely, using a diamond disc saw (Presi Mecatome T210) to obtain a section of 500 μm.
+Sections were then fixed on a glass side with thermoplastic glue (Crystalbond TM).
+Small otoliths were directly embedded in the thermoplastic glue and polished until obtained of a transversal section.
+Otoliths were sanded with abrasive discs of decreasing grain size (2,400 and 1,200 grains cm- 130 2) and polished with a 0.25 μm diamond suspension in order to be closest to the nucleus.
+All sections were photographed under a Leica DM750 light microscope with a Leica ICC50 HD microscope camera and LAS software (Leica Microsystems).
 
-### 1.2 Statistical analysis and extrapolation
+A standardized transect across the otoliths (from the nucleus to the edge) was chosen for each species, and distances between annual growth increments were measured using the software ImageJ.
+This procedure was performed twice by two independent researchers to prevent biases induced by a single observer.
+When the coefficient of variation between the two observers was greater than 5%, a common reading was reached by averaging the measurements for each section.
 
-\noindent Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2019].
+We then used a back-calculation procedure to estimate fish length at previous ages, modified to also quantify the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
 
-We applied a Bayesian hierarchical model to predict the growth rate of fishes in function of body size, temperature and phylogeny:
+Finally, we fitted the Von Bertalanffy growth models to all species at each location for which there were at least 3 individuals.
+We fitted the models using Bayesian hierarchical regression models provided by the R package fishgrowbot (ref).
 
-\begin{equation}
-	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}sizemax +  \beta_\textrm{2} sst + \epsilon,
-	\label{kmax}
-\end{equation}
+After combining the two data sources, we obtained 496 estimates of $k_{max}$ for 181 species.
 
-\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
+### 1.2 Data analysis and extrapolation
+
+\noindent Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
+
+We applied a Bayesian hierarchical model to predict the growth rate of fishes as a function of body size, temperature and phylogeny:
+
+<!-- \begin{equation} -->
+$$\textrm{ln}kmax = (\beta_{\textrm{0}} + \gamma_{\textrm{0phy}}) +  \beta_{\textrm{1}} \textrm{ln}sizemax +  \beta_{\textrm{2}} sst + \epsilon,$$
+<!-- \label{kmax} -->
+<!-- \end{equation} -->
+
+\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
 \noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
 \noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature.
-The Bayesian R2 of the model was 0.73759 (95\%CI: 0.702-0.769).
+The Bayesian R2 of the model was 0.738 (95\%CI: 0.702-0.769).
 \noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects, attributable to the phylogeny(i.e.
-$\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2  / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)$).
+$\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
 This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).
 
-\noindent We extrapolated $\kappa$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
+\noindent We extrapolated $kmax$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
 There is currently no streamlined method to make predictions to new species from a phylogenetic regression model.
@@
 ### 2.1 Data collection    
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Carribean, and Palmyra.
-Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser.
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Caribbean, and Palmyra.
+Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
 $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods.
-Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis (Allen et al.
-1974).
+Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974].
 Elemental content was calculated based on dry mass.
@@
 
-\begin{equation}
-	\begin{bmatrix}Y_1 \\ Y_2 \\ Y_3\end{bmatrix} \sim MVNormal(\begin{bmatrix}mu1 \\ mu2 \\ mu3\end{bmatrix}, S),
-	\label{cnp}
-\end{equation}
+<!-- \begin{equation} -->
+$$\begin{bmatrix}Y_1 \\ Y_2 \\ Y_3\end{bmatrix} \sim MVNormal(\begin{bmatrix}mu1 \\ mu2 \\ mu3\end{bmatrix}, S),$$
+<!-- 	\label{cnp} -->
+<!-- \end{equation} -->
 
-\begin{equation}
-	mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},
-	\label{cnp2}
-\end{equation}
+$$mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},$$
+<!-- 	\label{cnp2} -->
+<!-- \end{equation} -->
 
@@
 After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder.
-Then, samples were sent to the lab for CNP% content analysis using similar methods as for the fish body stoichiometry.
+Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry.
 
 ### 3.2 Data analysis and extrapolation  
-\noindent We used trophic guilds defined by Parravicini et al.
-(2020).
+\noindent We used trophic guilds defined by @Parravicini2020.
 We fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level.
@@
 Parravicini et al.
-(2020) provides the probability of reef fish species to be assigned to each of the 8 defined trophic guilds.
+2020 [@Parravicini2020] provides the probability of reef fish species to be assigned to each of the eight defined trophic guilds(i.e.
+sessile invertivores; herbivores, microvores, and detrivores; corallivores; piscivores; microinvertivores; macroinvertivores; crustacivores; planktivores).
 By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database.
@@
 
-## 4 Metabolic parameters    
+### 4 Metabolic parameters    
 ### 4.1 Data collection    
@@
 Individuals were collected using handnets and clove oil by scuba divers.
-After arrival in the lab, individuals were kept starved for a period of x hours/days.
-Then, they were held in respirometry chambers for 23 hours.
 
-## 4.2 SMR and MMR
+### 4.2 Metabolic rate
+To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we conducted intermittent-closed respirometry experiments at 28°C [@Steffensen1989; @Clark2013].
+After an acclimatization and fasting period of 48 h in aquaria, the fish were individually transferred to a water-filled tub at 28°C and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
+Then, they were placed in respirometry chambers submersed in an ambient and temperature-controlled tank, where they were left for ~23 h.
+The intermittent respirometry cycles started immediately after a fish was placed in its respirometry chamber.
+The cycles consisted of a measurement (sealed) period followed by a flush period during which the respirometry chambers were flushed with fully aerated water from the ambient tank.
+Because fish were exhausted right before entering the respirometry chambers, it is possible to measure the approximate MMR.
+Depending on fish size, 8 respirometry chambers ranging in volume (including tubes and pumps) from 0.4 to 4.4 L were run in parallel, and measurement and flush periods lasted between 3 to 15 min and 3 to 5 min, respectively.
+SMR was calculated as the average of the 10 % lowest  values measured during the entire period, after the removal of outliers [@Chabot2016].
+MMR was calculated from the slope of the first measurement period.
 
-## 4.3 metabolic parameters
+### 4.3 Data analysis and extrapolation
+To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$) and $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a Bayesian mixed effect model predicting the log10-transformed metabolic rate with the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the intercept and the species.
+We ran the model for 4000 iterations, with a warm-up of 2000 iterations.
+Further, we used an informative prior for the slope ($\alpha \sim normal(0.8, 0.5)$.
+The model had a Bayesian R2 of 0.973 (95\%CI: 0.972-0.974).
+We then extracted the family-level $\alpha$ by summing the slope of the model with the effects of the family on the slope of the SMR.
+We did this for 1000 iterations and then took the mean and standard deviation.
+In a similar way we extracted the family-level intercept for SMR, and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of 1000 iterations of the intercept.
+Finally, $\theta$ was quantified as followed, based on the assumption that fishes rest 12h a day and they on average spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
+<!-- \begin{equation} -->
+$$\theta = \frac{3\textrm{SMR} + \textrm{MMR}}{4\textrm{SMR}},$$
+<!-- 	\label{theta} -->
+<!-- \end{equation} -->
+where 1000 iterations of the back-transformed family-level intercepts were used for SMR and MMR. We then summarized these predictions by taking the mean and standard deviation. 
+We used the family-level estimates for these three parameters for all species in our database.
+For families that were not represented in our respirometry dataset, we used an average across all families.
 
-fit_mr <- brm(log10(mr) ~ 1 + log10(mass) + (0 + log10(mass)|Family) + (0 + log10(mass)|Species) + 
-                (1|Family:mr_type) + (1|Species:mr_type) + (0 + log10(mass)|Family:mr_type) +
-                (0 + log10(mass)|Species:mr_type), data = test,
-              control = list(adapt_delta = 0.9),#, max_treedepth = 12),
-              prior = set_prior(class = "b", "log10mass", prior = "normal(0.8, 0.5)"), cores = 4,
-              warmup = 2000, iter = 4000)
+## 5. Additional parameters  
+We retrieved the parameters $lw_a$, $lw_b$, $h$, and $r$ from fishbase [@Froese2018].
+For the mass-specific turnover rates for N and P($F_\textrm{0Nz}$; $F_\textrm{0Pz}$), we used the estimates provided in Schiettekatte et al.
+(2020) [@Schiettekatte2020].
 
-Estimate    Est.Error      Q2.5   Q97.5
-R2 0.9728325 0.0004120478 0.9719845 0.97362
+## References

### 2020-07-11 R/functions_analysis.R

@@ -12,135 +12,130 @@ normalize <- function(x){
   100 * (x - min(x, na.rm = TRUE))/(max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
 }
 
-##### calculate multifunctionality #####
-add_multi <- function(summary_transect, herb_pisc){
-  
-  flux <- summary_transect
-  hp <- herb_pisc$summary_herb_pisc
-  sst <- read.csv("data/avSst.csv")
-  flux <- left_join(flux, hp) %>% left_join(sst)
-  
-  # transform into centiles then divide by 100
-  scores <- select(flux, transect_id, Fn, Fp, Gc, I_herb, I_pisc)  %>% 
-    filter(I_herb>0, I_pisc>0) %>%
-    mutate_at(2:6, function(x){normalize(log(x))}) %>%
-    drop_na()
-  # correlation for weighing
-  m <-  cor(scores[2:6])
-  m <- 1-m
-  we <-  rowSums((m))
-  we <- we/sum(we)
-  
 
-  multi <- scores %>%
-    rowwise() %>% 
-    mutate(multi = mean(c(Fn, Fp, Gc, I_herb, I_pisc)), 
-           var = var(c( Fn, Fp, Gc, I_herb, I_pisc))) %>%
-    group_by() %>%
-    mutate(multi = multi*(1-(var/3000))/100) # 3000 = maximum theoretical variance
-  
-  flux <- flux %>% left_join(select(multi, transect_id, multi))
-  
-  return(flux)
-  
-}
 
-flux <- left_join(flux, res)
-flux$good <- ( flux$biomass_tot< 50 & flux$multi < quantile(flux$multi, 0.05, na.rm = TRUE))
-
-flux <- flux %>%
-  mutate(cat = case_when(
-    biomass_tot < 50 & 
-      multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "bb",
-    biomass_tot < 50 & 
-      multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "bg",
-    biomass_tot > 150 & 
-      multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "gb",
-    biomass_tot > 150 & 
-      multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "gg",
-    TRUE~"other"
-  ))
-
-t <-flux %>%
[…]

### 2020-07-11 R/functions_plots.R

@@ -19,7 +19,7 @@ make_fig1 <- function(location_effect){
             axis.text.x = element_text(size = 6),
             axis.text.y = element_text(size = 6),
             plot.title = element_text(size = 8, hjust = 0, face = "bold"), 
-            plot.margin = unit(c(0.01,0.01,0.01,0.01), units = , "cm"),
+            plot.margin = unit(c(0.002,0.002,0.002,0.002), units = , "cm"),
             panel.spacing = unit(0, "cm")
       ) 
   }
@@ -27,16 +27,19 @@ make_fig1 <- function(location_effect){
   col <- fish(n = 5, option = "Callanthias_australis")
   
   get_scale <- function(f){
-    quant1 <- quantile(f[f < 0], c(0, 0.5, 1), na.rm = TRUE)
-    quant2 <- quantile(f[f > 0], c(0, 0.5, 1), na.rm = TRUE)
-    quant <- c(quant1[1:2], 0, quant2[2:3])
-    quant <- quantile(f, c(0,0.2,0.8,1), na.rm = TRUE)
+    quant <- quantile(f, c(0,0.25,0.75,1), na.rm = TRUE)
     quant[1] <- quant[1] - 0.5   # adjust lower bound
     factor(cut(f, breaks = quant), labels = c( "low", "medium", "high"))
   }
   
-  get_scale(location_effect$r_loc_Fn)
+  get_scores <- function(proc){
+    probs <- seq(0,1,0.01)
+    quantiles <- quantile(proc, prob = probs, na.rm = TRUE)
+    quant <- as.numeric(factor(findInterval(proc, quantiles)))/100
+    return(quant)
+  }
   
+
   getcol <- colorRampPalette(c("white", col[1]))
   pal2 <- getcol(n = 3)
   getcol <- colorRampPalette(c("black","white"))
@@ -53,22 +56,19 @@ make_fig1 <- function(location_effect){
                    size = get_scores(r_loc_Fn)),  alpha = 0.8,
                position = position_jitter(0,0), shape = 16) +
     geom_point(aes(x = lon, y = lat),  alpha = 0.7,
-               shape = 0, size = 4,
-               data = filter(location_effect, r_loc_multi > quantile(location_effect$r_loc_multi, 0.95, na.rm = TRUE))) +
-    geom_point(aes(x = lon, y = lat),  alpha = 0.7,
                shape = 1, size = 4,
[…]

### 2020-07-11 R/functions_wrangling.R

@@ -325,19 +325,22 @@ return(tfs)
 
 get_contributions <- function(tfish, cnpflux, params, summary_transect){
   
-  tfish <- left_join(tfish, cnpflux) %>% left_join(select(params, Species, Dp_m)) %>% mutate(
-    Fc = Fc_median * abun,
-    Fn = Fn_median * abun,
-    Fp = Fp_median * abun,
-    Ic = Ic_median * abun,
-    In = In_median * abun,
-    Ip = Ip_median * abun,
-    Gc = Gc_median * abun,
-    Gn = Gn_median * abun,
-    Gp = Gp_median * abun,
-    Wc = Wc_median * abun,
-    Wn = Wn_median * abun,
-    Wp = Wp_median * abun)
+  tfish <- left_join(tfish, cnpflux) %>% 
+    left_join(select(params, Species, lwa_m, lwb_m, diet_cat)) %>% 
+    mutate(
+      Fc = Fc_median * abun,
+      Fn = Fn_median * abun,
+      Fp = Fp_median * abun,
+      Ic = Ic_median * abun,
+      In = In_median * abun,
+      Ip = Ip_median * abun,
+      Gc = Gc_median * abun,
+      Gn = Gn_median * abun,
+      Gp = Gp_median * abun,
+      Wc = Wc_median * abun,
+      Wn = Wn_median * abun,
+      Wp = Wp_median * abun,
+      biomass = abun * lwa_m * size_cm^lwb_m)
   
   tfs <- group_by(tfish, studyName, region, locality, sites, area, transect_id, lon, lat) %>% 
     dplyr::summarise(
@@ -352,9 +355,13 @@ get_contributions <- function(tfish, cnpflux, params, summary_transect){
       Fc_s = sum(Fc),
       Wc_s = sum(Wc),
       Wn_s = sum(Wn),
-      Wp_s = sum(Wp)
+      Wp_s = sum(Wp),
+      biomass_s = sum(biomass),
+      biomass_h_s = sum(biomass[diet_cat == 2 & Family != "Mugilidae"]),
+      biomass_p_s = sum(biomass[diet_cat == 4])
     ) %>% right_join(tfish) %>% 
-    group_by(studyName, region, locality, sites, area, transect_id, lon, lat, species) %>%
+    group_by(studyName, region, locality, sites, area, transect_id, lon, lat, 
+             Family, species, diet_cat) %>%
[…]

### 2020-07-11 R/plan.R

@@ -1,5 +1,8 @@
 
 plan <- drake_plan(
+  
+  ##### Bioenergetic model #####
+  
   # load all parameters
   sptl = get_sptl(),
   kmax = get_kmax(),
@@ -18,6 +21,8 @@ plan <- drake_plan(
   cnpflux = run_fishflux(tfish_unique, params),
   output_cnpflux = write.csv(cnpflux, "output/data/flux_results.csv", row.names = FALSE),
   
+  ##### Summarize transect level #####
+  
   # load all transect data
   tfish = read.csv("data/tfish_corr.csv"),
   
@@ -31,42 +36,70 @@ plan <- drake_plan(
   # herbivory, piscivory --> in g dry mass
   herb_pisc = get_herb_pisc(tfish, cnpflux, params, summary_transect),
   
-  # add multifunctionality, sst 
-  summary_transect_complete = add_multi(summary_transect, herb_pisc),
+  # combine summary data, sst 
+  summary_transect_complete = combine_summary(summary_transect, herb_pisc),
+  
+  ##### models #####
+  # run models only with biomass ans sst
+  bmmodels = run_bmmodels(summary_transect_complete),
+  residuals = get_residuals(summary_transect_complete, procmodels),
   
   # run models proc ~ biomass et al
   procmodels = run_procmodels(summary_transect_complete),
-  residuals = get_residuals(summary_transect_complete, procmodels),
   location_effect = get_location_effect(procmodels, summary_transect),
   
+  # run models proc ~ community vars
+  commodels = run_commodels(summary_transect_complete),
+  
   # run models to get relative contribution of each ecosystem process
-  models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
-  models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
+  #models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
+  #models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
   #models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
   #models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
-  models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
+  #models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
   
   # run models to get relative contribution herbivory piscivory
[…]

### 2020-07-11 R/play.R

@@ -927,7 +927,7 @@ test <- flux %>%
   filter(!value == 1)
 
 
-ggplot(test, aes(x = biomass_bin, y = value, fill = var, color = var)) +
+ggplot(bins, aes(x = biomass_bin, y = value, fill = var, color = var)) +
   geom_point(size = 1, alpha = 0.8) +
   scale_y_continuous(trans = "log10", breaks = c(2,10,100,1000, 10000)) +
   scale_x_continuous(trans = "log10") +
@@ -1372,8 +1372,9 @@ summary(lm(normalize(log(I_pisc)) ~ log(grav_Nmarket) + log(biomass_tot), data =
 
 
 ###### suppl. gravity markets ######
-tall <- pivot_longer(wild, c(Fn_r, Fp_r, Gc_r, I_herb_r, I_pisc_r)) %>%
+tall <- pivot_longer(fluxs, c(Fn_r, Fp_r, Gc_r, I_herb_r, I_pisc_r)) %>%
   group_by(name) %>%
+  left_join(hum) %>%
   mutate(value = standard(value))
 a <-
 ggplot(tall, aes(x = log(grav_Nmarket), y = value), alpha = 0.2) +
@@ -2406,7 +2407,7 @@ spi <- parallel::mclapply(unique(con$transect_id), function(x){
            I_herb_i = case_when(I_herb_p == 0 ~ NA, TRUE ~ I_herb_i)) %>%
     dplyr::select(bioregion, transect_id, species, Gc_i, Fn_i, Fp_i, I_pisc_i, I_herb_i)
   return(sub)
-}, mc.cores = 50) %>% plyr::ldply()
+}, mc.cores = 30) %>% plyr::ldply()
 
 
 # proportion when important 
@@ -3278,6 +3279,180 @@ dt <- data.frame(
 dt$y <- dt$x^0.6
 plot(dt)
 plot(dt$y, dt$y/dt$x)
+
+##### Supplemental analysis remote reefs #####
+loadd(summary_transect_complete)
+
+hum <- read_csv("data/humanPopulation.csv") 
+
+remote <- read_csv("data/humanPopulation.csv") %>%
+  mutate(remote = case_when(linear_dist > 200 & pop_100 == 0 ~ "yes",
+         TRUE ~ "no")) %>%
+  select(sites, remote, grav_markets) %>%
+  inner_join(summary_transect_complete) %>%
+  left_join(residuals)
+
+nd <- remote %>%
[…]

### 2020-07-11 _drake.R

@@ -1,6 +1,7 @@
 source("R/packages.R")  # loads packages
 source("R/functions_wrangling.R") # defines the create_plot() function
 source("R/functions_analysis.R") # defines the create_plot() function
+source("R/functions_plots.R") # defines the create_plot() function
 source("R/plan.R")      # creates the drake plan
 
 config <- drake_config(plan, lock_envir = FALSE)

### 2020-08-01 text/main.Rmd
changed back calculation model, redid all bc plus sp vbgc models are ok

@@
 
-# Functional trade-offs reveal coral reef vulnerability
+*diego general comments*
+
+**1) no need to emphasise how misleading it might be to rely solely on standing biomass for conservation targets. Your results are powerful and novel enough without any of that. **
+
+**2) We need to wordsmith the text some more to get readers onboard with the equality fluxes = functions.**
+
+**3) The chosen model predictors.
+It would help I think if their justifications were intertwined with the early main-text paragraphs.
+Not drivers, perhaps "predictors" or "potential drivers" might be a safer solution.**
+
+**4) The main text needs a succinct, yet clear description of how the modelling choice outputs a "trade-off" among the five fluxes.
+While the ugly details can be shoved in the Methods and Supplementary Info, the reader needs those ingredients to appreciate what you mean by the term trade-off, and how important / reliable they are.**
+
+*comments Nick*
+**some circularity in there at present**
+**missing clarity regarding why each step in the analyses (e.g. moving from organismal traits to species level) is a logical progression from the last. **
+
+*comments jake*
+**overall message is a bit vague and you would be better served to pull a few key things out and run with htem. **
+**I think instead of mixing messages about global and local conseravation you just be all out there with it and say: real conservation of coral reefs will require both actions global and local.
+I think your 70% stat is really really cool and is something to hang your hat on.**
+
+*comments Deron*
+**I wonder if the heat map showing tradeoffs among the ecosystem functions would be worth putting in the main MS.
+I thought it was really cool!
+Maybe integrate it into Fig 2 or something if possible.
+**
+
+**should production be in gC?**
+
+**Nowhere are the actual rates of the different fluxes presented. All that readers get to see are residuals or effect size plots or correlations. **
+
+**I think one thing that would be really nice in the supplement would be to have a figure identical to that of Fig 1.
+that actually presented the data on the maps instead of the residuals.
+It would be really informative to be able to look at the residuals in Fig 1 vs.
+the real data in the supplement.
+Something to consider.
+**
+
+**Also on figure 1 maybe putting the units of each flux to emphasize to the reader that you are measuring things in N, P, or C for all of the different metrics. **
+
+# Functional trade-offs redefine global reef fish vulnerability
+
+Nina M.
+D.
+Schiettekatte, (core team:) Simon J.
+Brandl, Jordan M.
+Casey, Nicholas A.
+J.
+Graham, Diego R.
+Barneche, Deron E.
+Burkepile, Jacob E.
+Allgeier, (other data contributors:) Katrina S.
+Munsterman, Fabien Morat, Alexandre Mercière, Yves Letourneur, Enrico L.
+Rezende, Graham J.
+Edgar, Rick D.
+Stuart-Smith, Jesús E.
+Arias-Gonzaléz, Alan M.
+Friedlander, Alison L.
+Green, Osmar J.
+Luiz,  F.
+A.
+Rodríguez‐Zaragoza, Laurent Vigliola, Michel Kulbicki, Sergio R.
+Floeter  (supervisors:) Sébastien Villéger, Valeriano Parravicini
 
@@
 The flow of elements through biological communities fuels all life on Earth [@Welti2017] 
-Although there is a strong consensus on the importance of these fluxes, also known as ecosystem functions, our ability to manage for ecosystem functioning remains poor [@Welti2017]. 
+Although there is strong consensus on the importance of these fluxes, also known as ecosystem functions, our ability to manage for ecosystem functioning remains poor [@Welti2017]. 
+*NG: Need to say why remains poor - is it because the flow of elements (or most of them) have been poorly quantified, or because the drivers, trade-offs and vulnerability among different biochemical fluxes are not understood?
+I think if you can define the problem like this in the first paragraph it sets up what the manuscript then does.
+*
+*JA: Not a very good citation in my view. There are a handful of papers in science that talk about this more generally interms of management – largely terrestrial. *
 For millennia, humans have managed nature with an economic mindset to maximize desirable components such as plant or animal biomass [@Weisser2017]. 
-However, Earth’s resources are finite, and the existence of multiple ecosystem functions comes with trade-offs, whereby efforts to maximize one function may negatively impact another [@Tallis2008]. 
+*NG:I don't think this sentence is useful - detracts from the flux narrative of the paragraph*
+*JA: It seems you need a transition statement that links plant or animal biomass with the next sentence.
+This sentence – especially given your last sentence, is critical because it justifies why ‘eco functioning’ is important.
+*
+However, efforts to maximize one function may negatively impact another [@Tallis2008]. 
 To make informed management decisions that pertain to ecosystem functioning, it is critical to understand the mechanisms that drive these trade-offs [@Rodriguez2006].
 
-In the marine realm, coral reefs are the most diverse and productive ecosystem, and they underpin indispensable ecosystem services to humans. 
-As coral reefs thrive in nutrient-poor waters, efficient nutrient cycling is the key to their productivity. 
+*JA: : I think that the text is quite verbose and has too many fancy words.
+I will minimize the extent to which I edit out your adjectives moving forward because it is your MS your and your right to word things how you want – and that is fine.
+But as you see how I have edited things so far that I think there are an excessive number of adjectives (and the ones that are used are a bit over the top) and importantly they distract from the message.
+Again, that is just my opinion, you do you.*
+Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans. 
+As coral reefs thrive in nutrient-poor waters, efficient nutrient recycling is the key to their productivity. 
+*DRB: Brandl et al. Science would be good to cite here?*
 However, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
-Over the past decade, severe biodiversity declines have strained the ability of coral reefs to maintain ecosystem functioning and brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+Over the past decade, severe biodiversity declines have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+
 However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish biomass, coral cover, and the richness of species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Consequently, we know little about the co-occurrence of multiple ecosystem functions and their drivers, which provides us with limited guidance for coral reef management in our rapidly changing world.
+*JA: This is a bit confusing because it sounds like you are saying richness is a static proxy of functions (I totally dig the point you are making though – just don’t want it to be confused)*
+Consequently, we know little about the co-occurrence of biogeochemical fluxes and their drivers, which currently provides us with limited guidance for coral reef management in our rapidly changing world.
+*JA: You should cite some key papers that have done the multifunction stuff – there is loads of it in the BEF literature in fancy journals.
+I am not saying you should my papers, but I have two papers that measure multifunction’s on coral reefs – both of which do speak to conservation issues (one in particular), but neither of which do anything close to what you are doing here.
+(just a heads up, I comment on citations a lot because I am constantly getting nailed for my citations all the time in review).
+As with all of my comments feel free to ignore*
 
-Integrating principles of biogeochemistry and traditional ecological assessments provides a promising path toward understanding and conserving the fluxes that underpin reef functioning. 
-Here, we integrate reef fish trait databases across 9,118 communities with bioenergetic modelling to (1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory), (2) disentangle their ecological drivers, and (3) investigate the contribution and vulnerability of different species to each function.
+Here, we integrate principles of biogeochemistry and traditional ecological assessments to advance understanding and conservation of the fluxes that underpin reef functioning.
+We integrate reef fish trait databases across 9,118 communities with bioenergetic modelling to
+*ng: not clear how this fits with the 585 reefs mentioned in the abstract*
+(1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory), 
+*db: In the abstract you pitched this as quantifying ‘five key biogeochemical fluxes’.
+Its not clear to me here that these are fluxes unless you are presenting them as say the amount of carbon produced/consumed.
+*
+(2) characterize their potential ecological predictors, and 
+*ng: seems vague? - determine the drivers of variation in ecosystem functions*
+*I do not think this is well worded. I roughly know what you mean, but I think it can be said more clearly. *
+*DB: Also, we do not know for sure if they are truly drivers.
+Ultimately, we show that these fluxes are correlated with some chosen predictors, so maybe we want to say “predictors” rather than “drivers”.
+To me “driver” implies an understood mechanistic explanation, whereas “predictor” does not.
+It doesn’t necessarily mean that some predictors (e.g.
+body size) are not drivers—they likely are.
+But I think overall predictor would be a safer choice.*
+(3) investigate the contribution and vulnerability of different species to each function.
+*NG: This seems like 2 aims (spcies contribution, and vulnerability - perhaps add vulnerability as (4) ?*
+*DB: We need a simple sentence summarising how this was done.
+Up until the figures the reader would not have any idea that used Bayesian hierarchical models.
+Also, maybe it is worth selling the phylogenetic extrapolation here, which is entirely novel as well?In any case, it is not clear whether you analysed each function separately, or if somehow you used some multivariate approach to estimate the predictors.*
 
 Fish biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front]. 
-However, biomass is a product of nutrient cycling that drives productivity on reefs [@Szmant-Froelich1983]. 
-Although there was a strong relationship between biomass and all five functions, after controlling for biomass, different functions varied up to 10 to 100-fold (see Extended Data Fig. 1a). 
+*NG: I would add a sentence or two at the start to say how emerging / novel approaches have enables these 5 fluxes to be quantified across reefs globally for the first time, showing x and y.
+The fih biomass comparison is a bit of a dry start, and means the novelty of estimating the fluxes is somewhat buried.*
+However, biomass is a product of nutrient cycling that drives productivity on coral reefs [@Szmant-Froelich1983]. 
+Although there was a strong relationship between biomass and all five functions, after controlling for biomass, different functions varied up to 10 to 100-times (see Extended Data Fig. 1a). 
+*JA: This is a really cool and critical point, but I think you need to spell out what that means to people.
+When I did this in the nat comms paper it took forever to get people to understand what the significance of this was.
+I think it is super cool, but to me you should make the point that it provides an absolute species-level effect size per unit mass*
 This striking community-level variability is driven by the species-specific biological traits of fishes [@Schiettekatte2020]. 
-Further, the residual variability of functions revealed strong trade-offs among different functions (see Extended Data Fig.
-1b).
-As a consequence, at a given biomass, no reef can maximize all functions (fig.
-1).
+Further, the residual variability of functions revealed strong trade-offs among different functions (see Extended Data Fig. 1b). 
+*DB: Here I think some specificity would be good.
+Something that a reviewer could come away with here.
+Say that there appears to be tradeoffs between herbivory and P excretion or N excretion and P excretion.
+*
+*JA:Holy shit that matrix is fucking awesome – can you include the error in it? That is, the numbers look amazing, but is there a ton of error in the estimates?*
+As a consequence, at a given biomass, no reef can maximize all functions (fig. 1). 
+*JA: If this is a key ‘goal’ I think it is weakly set up still. I dig it, but I just think it needs better development. *
 For example, when extending the proposed baseline of ~100g/m2 standing fish biomass to define a healthy reef [@MacNeil2015] to our dataset, 46% of global fish communities reached this biomass baseline, yet only 19% showed adequate functioning to satisfy the predicted threshold of each function based on the biomass baseline.
+*DB: I’m not quite sure I understand how you assessed what ‘adequate functioning’ means. *
+*NG: How are these threshold values defined*
+*JA:I like what you are doing here. The last bit of the sentence is a bit confusing.*
 In fact, due to existing trade-offs between functions, a biomass of ~450g/m2 is necessary to ensure above-threshold levels for each function. 
+*JA: This is something that I think should be in the abstract. I think you need more concrete points in it up there.*
 Our proposed biomass is 450% higher than previously estimated, and, notably, a mere 13% of the fish communities in our dataset meet this threshold (Extended Data Fig. 2).
+*NG: There is a certain amount of circularity in this paragraph - say at the start that biomass is underpinned by the 5 fluxes measured, then relate relate the target levels of the fluxes to biomass targets.
+Not clear if or why the fluxes may be important in their own right - i.e.
+need to be clear why they are a step beyond using biomass targets.
+Perhaps the biomass target side is a red herring that undermines the novelty of quanitifying the 5 fluxes.
+For example, none of the actual 5 fluxes are named in this paragraph, or the patterns in fig 1 described*
+*DB: I don’t see this in extended data fig 2. *
 
-What underpins the trade-offs between multiple functions on coral reefs? 
-To explore the ecological drivers of each function, we fit Bayesian mixed models using variables that describe fish community structure, including body size, trophic level, age structure (expressed as immaturity), and species richness.
+To uncover what underpins the trade-offs between multiple functions on coral reefs, we explored the ecological predictors of each function We fitted Bayesian mixed models using variables that describe fish community structure, including body size, trophic level, age structure (expressed as immaturity), and species richness.
 We found that functional trade-offs are mediated by contrasting aspects of community structure (fig. 2). 
+*JA/DB: unclear; DB: Adding to this: I don’t quite understand how trade-offs were estimated in your model.
+This point needs to be crystal clear in the main text, after all it is the main point of the paper.*
+*NG: Based on previous sentence, this is all that was looked at, so a bit of a self explanatory sentence*
 For example, phosphorous excretion is maximized in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels (See also @Allgeier2014). 
 In contrast, biomass production is maximised in communities dominated by small, immature fishes at lower trophic levels. 
-Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate [@Brown2004], and as a consequence, small individuals have elevated consumption rates and highly contribute to functions that rely on rapid energetic turnover [@Barneche2014].
+Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate [@Brown2004], and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2014].
+*DB: I would drop both Brown et al.
+2004 and Barneche et al.
+2014 and replace them with Barneche & Allen 2018 which is more relevant to this paper because it measures both metabolic and growth rates and demonstrates the mass-specific scaling issue in fishes.*
 In contrast, fishes in early life stages or with small body sizes feed on nutrient-poor diets that are limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
+*JA: What evidence do you have for this?
+I don’t agree with this blanket statement at all.
+In fact many species feed on higher nutrient content diets as juveniles (eg.
+Parrotfish do, many species are zooplantivorous as juveniles and zoops are high P content diets).
+A more probable reason for them not peeing P is high growth rate and they are retaining more P for their bones.
+That hypothesis is best supported by the literature*
 These results highlight the critical need to integrate organismal biology with community ecology to understand ecosystem-wide biogeochemical fluxes. 
+*JA: I find this statement unnecessary.
+People have been doing this for ages – re: freshwater ecology, ecological stoichiometry, terrestrial ecology, BEF literature, etc.
+I think you can just end your paragraph with the last sentence.*
+*DB: I’m still a bit confused by the ‘biogeochemical flux’ framing as only two of the functions are really what I would consider a ‘biogeochemical flux’.
+That is unless you quantify herbivory in carbon.*
 
 Beyond community structure, species identity profoundly affects rates of functioning [@Ruttenberg2019; @Topor2019]. 
+*NG: How is this related to the organismal biology assessed and described in the previus paragrah.
+Seems like either a species approach, or a biological trait approach should be used ?
+Surely the organismal traits should underpin why some species profoundly affect rates.
+Or does abundance drive more of the species results?
+Need a linking sentence to explain why this is also important to look at.
+*
+*JA: Not a big deal, but there are numersou foundational papers that show this (e.g., Paine 1966, Vanni et al.
+2002 Eco Letters etc…)– so I found these a bit odd here – I am sure these papers you cite are good, but this concept is very old and citations should reflect that I think*
 To explore whether some species or families consistently contribute more to functioning than expected by their biomass, we estimated the functional dominance of species and their frequency across communities.
@@
 In fact, ~70% of all species contribute disproportionally to a function in a given community, but worldwide, the frequency of dominance is strikingly low for each species (fig. 3c). 
+*DB: I’m confused about where this number comes from.*
+*JA: That is totally wild.
+I would never have guessed that.
+To me that is a big finding.
+I see what you were saying in the abstract now, but it just needs to be more clear – i.e., just say it like you do here – very simply.
+*
+
 Despite high species richness on coral reefs, researchers often report the existence functionally dominant “key species” [e.g. @Bellwood2006]. 
-In contrast, we demonstrate that while dominance is indeed prevalent, the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].
+*DRB: And they are typically only thinking about one process at a time. The power of this work is that multiple processes are being considered at once. *
+In contrast, we demonstrate that while dominance is indeed prevalent, the identity of the dominant species is unpredictable, suggesting the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].
 
-Thus, the local decline of a few species can have a large impact if those species are not functionally redundant. 
+The local decline of a few species can have a large impact if those species are not functionally redundant. 
+*NG: Again, the rationale doesn't quite fit with last paragraph.
+In this case, the previous paragraph said most species important (70%) as it varies among location, and this paragraph starts by saying a few species are important.
+I know there is more nuance than that, but need to make it really clear for the reader.*
 By coupling species’ functional contributions with their vulnerability to fishing and climate change, we demonstrate that the most profound human-mediated changes are likely to impact piscivory via fishing (fig.
 4).
+*DB: Complicated wording to make a relatively simple point – fishing impacts piscivores. *
 Like piscivory, herbivory is almost exclusively upheld by few key species; therefore, herbivory is also vulnerable to species loss due to lack of redundancy. 
@@
 
-Human impact has already caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
+Human impact has caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
 While the effects of these alterations on ecological processes are more difficult to monitor than declines in biomass, the loss of functioning may have profound consequences for reef ecosystems. 
@@
 These effects can favor nitrogen excretion and production [e.g. @Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (Extended Data Fig. 3). 
+*DB: This is because small fishes excrete more N and are P limited right? You might want to bring this back around to the patterns in Fig 2 just so readers get the connections here. *
 On the other hand, changes in community structure triggered by coral cover declines are associated with a shift toward herbivores [@Graham2006; @Ceccarelli2016]. 
 Herbivores have a minor contribution to phosphorus excretion [@Schiettekatte2020], so herbivore dominance and the subsequent community-level decline of phosphorus may induce a negative feedback loop for coral growth [@Shantz2015].
+*JA: On a per unit basis, not on a community level.
+I hate saying this but adding my GCB paper here would bolster this point as that is an important point we make  (the functional groups and how they contribute).
+But it may not be a good citation depending on where you are going with this – see next comment*
+*JA: I am not sure you are using ‘negative feedback loop’ correctly.
+Also this paper you cite (which is great) and Deron’s Sci Rep 2013, are about hotspots – so you have aggregating fishes that make coral and algae grow – these are more behavioral mechanisms, and Deron’s is saying more specifically that this might promote algae.(I just read the sentence after this one so this next point is a bit redundant.) What it seems you are talking about is community-level reductions in P, which is quite different to me.
+That would cause shifts in ratios.
+The Weidenmann et al.
+2014?
+Nat Climate Change paper is a rad paper and shows plimitation in corals – there is Ezzats paper about Plimitation.
+Andy S also has a great Eco Letts paper about nutrients and mutualisms that would be possibly appropriate.
+We also just had a paper in GCB showing that changes in ratios of NP have negative implications for coral.
+Also herbivory is what people always say matters so much.
+You are saying increased herbs is bad, but many would argue top-down is way more important that excretion – so you will likely get kickback on that point without acknowledging that the top down mechanisms are important.
+*
+*DB: All good points here by Jake. Some places here to tighten this argument. *
+*NG: too vague - say how fish phosphorus excretion increases coral growth*
 This is particularly problematic when considered in conjunction with climate change, as phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].
@@
 Our results demonstrate the challenges of managing one of Earth’s most diverse and vulnerable ecosystems. 
-Rooted in our agroeconomic history, maximizing ecosystem functioning is the dominant objective of many 21st century conservation initiatives. 
-The revealed functional trade-offs challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
+Maximizing ecosystem functioning is the dominant objective of contemporary conservation initiatives. 
+*JA:  I would argue that maintaining biodvierstiy is the “dominant” objective.
+A motivation for this is maintaining ecosystem function.
+But if you ask conservation and managers they will not say “maximizing ecosystem function” – in my experience at least.
+I think you might get a lot of blowback on a statement like this.
+You can say it is a clear objective or an important objective and that would be fine.*
+The functional trade-offs revealed between key ecosystem functions challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
 Traditionally, marine reserves have been the main conservation strategy for coral reefs [@Graham2020].
 While they provide benefits for biomass and herbivory, they provide little insurance for diversity in populated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
+*DB: not also piscivory?*
 Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential energetic pathways. 
@@
 Furthermore, individual reefs require local management plans to protect species with key roles in multiple functions, and the presence of multiple stakeholders may require the prioritisation of various functions based on local needs and stressors.
-Globally, given that majority of species are locally important for functioning in a certain community, the conservation of a wide range of species is desirable, in addition to tackling the primary threat to coral reefs, climate change [@Bruno2019].
+*NG: Perhaps tie to some examples, e.g.
+gear restrictions, co-management, restoring seabird nutrient fluxes.
+Or tie to the bright spots approach for learning and disseminating successful management approaches*
+Globally, given that the majority of species are locally important for functioning in a certain community, the conservation of a wide range of species is desirable, in addition to tackling the primary threat to coral reefs, climate change [@Bruno2019].
+*NG: Again, need to more clearly delineate the key species and the majority of species approaches. *
+*JA: This sentence is not doing very much.
+You say above that global efforts are not easy and maybe not useful.
+Then you say it needs to be local.
+And now you say it needs to be global again (I realize I am overgeneralizing, but you get my point hopefully).
+I just sort of think you shoot yourself in the foot a bit here.
+I think you could either drop it, or make the argument a bit stronger by clarify the need to balance global efforts (climate change, general species conservation) and local efforts (where, how whatmanagement).
+*
 
-Biomass alone does not suffice to explain coral reef ecosystem functioning, and, in fact, there is a strong mismatch among different functions performed by coral reef fishes. 
 Our results contribute to an ongoing discussion surrounding the question: what constitutes a healthy reef? 
+*JA: There is some redundancy in this paragraph and the one before. I like this wording and framing, but it seems like this should be up in the paragraph above*
 We posit that the answer cannot be rooted in a purely economic mindset that aims for the maximization of all functions. 
 Rather, a diverse community that supports intermediate levels of each function is ideal, with many species emerging as key local players.
+*JA: One thing that you can include here is that coral reefs themselves are diverse, so what is a criticl function in one reef is simply less critical in another – context dependence is everything on coral reefs.*
 In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring beyond biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].
+*JA: But you generated all this data form biomass monitoring. So I would say that it is critical, but we need to include scaling these additional processes.*
 
@@
 
+*DB: But you generated all this data form biomass monitoring. So I would say that it is critical, but we need to include scaling these additional processes.*
+*DRB: Indeed. I would also perhaps add the actual flux units at the top-left corners to make this visually clearer.*
+*DB: I don’t see the color scales here unless you mean black, gray, and then the colored dots. *
+*DRB: Good point, it may be best to add different symbols to the different fluxes.*
+
 ![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables.
@@
 Functions were log-transformed before standardisation.](../output/plots/fig2_com_slopes.png)
+*JA: What do the numbers in the parentheses mean? What are the dashed lines for? Just help you see? Why do some not have data (eg Immaturity – no estimate for piscivory)*
+*DB: Agree with Jake here.
+We need some more guidance on the details of the figures.
+What are the confidence intervals?
+Why is median size missing two data points?
+Several other traits are also missing data points.
+Does that mean they weren’t significant predictors?*
+*DB: I’m also confused about the order of the predictors on the Y axis.
+All of the Trophic Level predictors are grouped together at the top.
+But the Immaturity metrics are spread out along the Y axis.
+Is this meaningful somehow?
+If not I would suggest grouping predictors by type.
+*
 
@@
 
+*JA: I like what you did below for B and C and say what a given number means.
+For A) the axis is not that intuitive – e.g., what a negative number means –  I think you can def present it more simply so people can see it and move on.
+I like how you did B and C, which are super cool – but I don’t really get how you determined dominant for C.
+*
+*Just a thought, I would be curious to see how well your package predicts Caribbean fish pee.
+We only used moorea fish right?
+They pee on average WAY less than Caribbean fishes – just a random though….*
+
+*DB: So does a negative number mean that taxa contributes less to a function than would be expected based on biomass alone?
+So that Labridae contribiutes less to P excretion than one would expect based on biomass?
+I think this needs to be explained in the legend better.
+*
+*DB: So this is saying that Piscivory is almost always driven by one species on a reef? That each reef has one dominant piscivores species? That is honestly pretty hard to imagine.*
+*DB: What does the shading represent? The distribution of the data?*
+
 ![Figure 4: Vulnerability and importance to each function of fish species included in this study.
@@
 
+*DB: I’ll be honest that I really don’t understand what this means. *
+
 ![Extended Data Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities.
 b) Correlation matrix od the residuals of the five functions.](../output/plots/annex_fig1_mf_logbiomass.png)
+*DRB: wrong fig, no a and b?*
 
@@
 # References
+
+check cinner and rodriguez refs!

### 2020-08-01 text/suppl_methods.tex
changed back calculation model, redid all bc plus sp vbgc models are ok

%!TEX TS-program = xelatex

\documentclass[12pt,a4paper]{article}

\RequirePackage[hmargin=2.5cm,vmargin=2.5cm]{geometry}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{tcolorbox}
\usepackage{textcomp}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{mathptmx}
\usepackage{caption}

\usepackage{lineno}

\usepackage{csvsimple}

\DeclareCaptionFont{xipt}{\fontsize{12}{14}\mdseries}
\usepackage[margin=10pt,font=xipt,labelfont=bf,justification=raggedleft]{caption}
\usepackage{wrapfig}

\usepackage{longtable}
\usepackage{booktabs}

%ns
\usepackage{colortbl}
\usepackage{pifont}
%\documentclass[UTF8]{ctexart}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{inputenc}
%

\usepackage{fontspec}
\usepackage{xcolor}

\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Times New Roman}
\setmainfont{Times New Roman}

\pagenumbering{gobble}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% Set formats for each heading level
\titleformat*{\section}{\fontsize{12}{14}\bfseries\sffamily}
\titleformat*{\subsection}{\fontsize{12}{14}\bfseries\sffamily}
\titleformat*{\subsubsection}{\itshape\fontsize{12}{14}\sffamily}

% set title space
%\titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% spacing: how to read {12pt plus 4pt minus 2pt}
%           12pt is what we would like the spacing to be
%           plus 4pt means that TeX can stretch it by at most 4pt
%           minus 2pt means that TeX can shrink it by at most 2pt
%       This is one example of the concept of, 'glue', in TeX

\titlespacing\section{0pt}{10pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

% Reduce space in lists
\usepackage{enumitem}
\setlist{nosep} % or \setlist{noitemsep} to leave space around whole list

\usepackage{caption}
\captionsetup[figure]{labelfont={bf}, justification=raggedright, singlelinecheck=false, font={stretch=1.5}}
\usepackage[labelsep=none]{caption}

% fix floating figures
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}

\usepackage{nameref}

\usepackage{zref-xr}

\zxrsetup{tozreflabel=false, toltxlabel=true, verbose}
\zexternaldocument*{equations_MS_SI}

\usepackage{setspace}
\doublespacing

\setlength{\parindent}{15pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\def\tightlist{}

\setcounter{secnumdepth}{0}

\usepackage[document]{ragged2e}

\definecolor{lightgrey}{HTML}{eeeeee}

% NMDS add line numbers
\usepackage{lineno}
\linenumbers

\begin{document}

\usepackage[dvipsnames]{xcolor}

\hypertarget{supplementary-methods}{%
\section{Supplementary methods}\label{supplementary-methods}}

To apply the bioenergetic model that estimates fluxes of carbon (C),
nitrogen (N), and phosphorus (P), a number of parameters are required
(Table 1). Here, we describe how these parameters were quantified for
all 1110 species in our database, with a comvbination of literature,
empirical measures, and Bayesian models. All analysis wes carried out in
R v.3.6.3 (REF) and Bayesian modes were run using Stan (REF) and the R
package brms (REF).

\begin{table}[h!]
\centering
\caption{. Overview of model input parameters. VBGC = von Bertalanffy growth curve.}
\begin{tabular}{l l l}
\hline
\rowcolor{lightgrey}
Symbol & Description & Unit\\
\hline
$k$ & Index for element C, N or P & \_ \\
$a_\textrm{k}$  & Element-specific assimilation efficiency & \% \\
$l_\textrm{t}$  & Total length of individual at time t & cm \\
$l_{\infty}$  & Asymptotic adult length (VBGC) & cm \\
$\kappa$  & Growth rate parameter (VBGC) & $\textrm{yr}^{-1}$ \\
$t_0$  & Age at settlement (VBGC) & $\textrm{yr}$ \\
$lw_a$  & Parameter length-weight relationship & $\textrm{g cm}^{-1}$ \\
$lw_b$  & Parameter length-weight relationship & \_\\
$Q_\textrm{k}$  & Element-specific body content percentage of dry mass & \% \\
$f_\textrm{0}$  & Metabolic normalisation constant independent of body mass & $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$ \\
$\alpha$  & Mass-scaling exponent &  \_\\
$\theta$  & Activity scope & \_ \\
$v$  & Environmental temperature & \textdegree C \\
$h$  & trophic level & \_ \\
$r$  & Aspect ratio of caudal fin & \_ \\
$F_\textrm{0Nz}$  & Mass-specific turnover rate of N & $\textrm{g N} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
$F_\textrm{0Pz}$  & Mass-specific turnover rate of P & $\textrm{g P} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
$D_\textrm{k}$  & Elemental stoichiometry of diet & \% \\
\hline
\end{tabular}
\end{table}

\newpage

\hypertarget{growth-parameters}{%
\subsection{1. Growth parameters}\label{growth-parameters}}

\hypertarget{data-compilation}{%
\subsubsection{1.1 Data compilation}\label{data-compilation}}

We first compiled maximum lengths for all species with FishBase and used
these lengths for the \(l_{\infty}\) (REF). For \(\kappa\), we used a
standardized coefficient that describes the potential growth trajectory
of an individual if \(l_{\infty}\) were to be equal to equal to its
maximum length {[}i.e. \$k\_\{max\}\$, @Morais2019{]}. \(t0\) was kept
constant at 0 for all species.

We extracted the data for \(k_{max}\) from @Morais2019 and filtered out
only the species of our species list. As the Lenth-Frequency method
consistently overestimates kmax, we omitted the \(k_{max}\) estimates
coming from this method. In total, this selection process resulted in
439 observations of kmax for different species and temperatures.

Further, we used the otolith data provided by Morat et al., including
measurements of fishes from five Polynesian islands and fitted the Von
Bertalanffy growth models to all species at each location for which
there were at least 3 individuals. We fitted the model using Bayesian
regression models provided by fishgrowbot (REF).

After combining the two data sources, we obtained 496 estimates of
\(k_{max}\) for 181 species.

\hypertarget{data-analysis-and-extrapolation}{%
\subsubsection{1.2 Data analysis and
extrapolation}\label{data-analysis-and-extrapolation}}

\noindent Aside from phylogeny, \(k_{max}\) is mostly determined by body
size and temperature {[}@Morais2019{]}.

We applied a Bayesian hierarchical model to predict the growth rate of
fishes in function of body size, temperature and phylogeny:

\begin{equation}
\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}sizemax +  \beta_\textrm{2} sst + \epsilon,
    \label{kmax}
\end{equation}

\noindent where \(\textrm{ln}kmax\) represents the natural
log-transformed kmax value, \(\beta_\textrm{0}\) is the fixed-effect
intercept, \(\gamma_\textrm{0phy}\) is the vector of random-effect
coefficients that account for the resisual intercept variation, based on
the relatedness as described by the phylogeny, \(\beta_\textrm{1}\) is
the slope for the natural transformed maximum body size,
\(\beta_\textrm{2}\) is the slope for the average ambient sea surface
temperature, \(\epsilon\) is the residual variation. \noindent We used
uninformative priors and ran the model for 2000 iterations with a
warm-up of 1000 iteration for 4 chains. \noindent The model fit
confirmed a negative relationship of \(\textrm{ln}kmax\) with
\(\textrm{ln}size\), and a positive relationship with sea surface
temperature. The Bayesian R2 of the model was 0.73759 (95\%CI:
0.702-0.769). \noindent The phylogenetic heritability (equivalent to
Pagel'\(\lambda\)) was estimated as the proportion of total variance,
conditioned on the effects, attributable to the phylogeny(i.e.
\(\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2 / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)\)).
This calculation resulted in a phylogenetic signal of 0.74 (95\% CI:
0.70 - 0.77).

\noindent We extrapolated \(\kappa\) for all species across the full
temperature range in which those species occur in the database, with
temperature rounded to the °C, which results in 4712 unique temperature
and species combinations.\\
There is currently no streamlined method to make predictions to new
species from a phylogenetic regression model. We circumvent the issue by
extracting draws of the phylogenetic effect, \(\gamma_\textrm{0phy}\)
for each species included in the model. We subsequently predicted these
phylogenetic effects for missing species with the help of the function
phyEstimate in the picante package for R {[}@Kembel2010{]}. This
function uses phylogenetic ancestral state estimation to infer trait
values for new species on a phylogenetic tree by rerooting the tree to
the parent edge for the node to be predicted {[}@Kembel2012{]}. We
repeated this for all 100 trees and 1000 draws. Per draw, we averaged
the extrapolated values per species for the hundred trees. Then, by
combining the predicted phylogenetic effects with the global intercept
and slopes for body size and temperatures for each draw, we predicted
\(\kappa\) for each species. We only use one chain in order to keep
computational time reasonable. Finally, we summarised all \(\kappa\)
predictions per sst per species by taking the mean and standard
deviation across the 1000 draws.

\hypertarget{body-stoichiometry}{%
\subsection{2 Body stoichiometry}\label{body-stoichiometry}}

\hypertarget{data-collection}{%
\subsubsection{2.1 Data collection}\label{data-collection}}

\noindent 1633 individuals of 108 species and 25 families were collected
between 2015 and 2017 in Moorea, the Carribean, and Palmyra. Their gut
contents were removed, and the whole body was freeze-dried and ground to
powder with a Precellys homogeniser. \(Q_\textrm{k}\) (\%) were then
measured in the lab using standard methods. Ground samples were analysed
for \%C and \%N content using a CHN Carlo-Erba elemental analyzer
(NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed
by a colorimetric analysis (Allen et al.~1974). Elemental content was
calculated based on dry mass.

\hypertarget{data-analysis-and-extrapolation-1}{%
\subsubsection{2.2 Data analysis and
extrapolation}\label{data-analysis-and-extrapolation-1}}

\noindent We fitted C, N and P contents (\%) through a hierarchical
phylogenetic multivariate normal model with phylogenetic effects and
random effects per species.

\begin{equation}
    \begin{bmatrix}Y_1 \\ Y_2 \\ Y_3\end{bmatrix} \sim MVNormal(\begin{bmatrix}mu1 \\ mu2 \\ mu3\end{bmatrix}, S),
    \label{cnp}
\end{equation}

\begin{equation}
    mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},
    \label{cnp2}
\end{equation}

\noindent where \(Y_1\), \(Y_2\) and \(Y_3\) are the \% content of
\(\textrm{C}\), \(\textrm{N}\), and \(\textrm{P}\) respectively,
\(mu_{\textrm{n}\times\textrm{k}}\) represents the average \% content of
element \(k\) (\(\textrm{C}\), \(\textrm{N}\), and \(\textrm{P}\)) per
species, \(\beta_\textrm{0 k}\) is the fixed-effect intercept for each
element \(k\), \(\gamma_{\textrm{0phy}\times\textrm{k}}\) is the matrix
of random-effect coefficients that account for the intercept variation,
based on the relatedness as described by the phylogeny per element k,
\(\gamma_{\textrm{0sp}\times\textrm{k}}\) is the matrix of random-effect
coefficients that account for the residual species-level intercept
variation per element k.

\noindent We used uninformative priors and ran the model for 2000
iterations with a warm-up of 1000 iteration for 4 chains. \noindent The
Bayesian R2 of the model was 0.39 (95\%CI: 0.36-0.42), 0.50 (95\%CI:
0.48-0.53), and 0.43 (95\%CI: 0.40-0.46) for C, N and P respectively.
\noindent The phylogenetic heritability was 0.41 (95\%CI: 0.28-0.55),
0.58 (95\%CI: 0.4-0.66), and 0.57 (95\%CI: 0.46-0.69) for C, N, and P
respectively.

\noindent As before, we used 1000 fitted draws for each species, and 100
phylogenetic trees to extrapolate to all species with unknown body
stoichiometry. Specifically, we used the phylopars function from the
Rphylopars package {[}@Bruggeman2009{]}. This function uses ancectral
state reconstruction and brownian motion, and takes the correlation
between C, N and P into account.

\hypertarget{diet-stoichiometry}{%
\subsection{3 Diet stoichiometry}\label{diet-stoichiometry}}

\hypertarget{data-collection-1}{%
\subsubsection{3.1 Data collection}\label{data-collection-1}}

\noindent We collected 571 adult individuals of 51 species between 2018
and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian
islands. We extracted the stomach content and stored it in a 2ml tube.
After freezing the samples, we dry-froze all samples for at least 24
hours, and ground to powder. Then, samples were sent to the lab for
CNP\% content analysis using similar methods as for the fish body
stoichiometry.

\hypertarget{data-analysis-and-extrapolation-2}{%
\subsubsection{3.2 Data analysis and
extrapolation}\label{data-analysis-and-extrapolation-2}}

\noindent We used trophic guilds defined by Parravicini et al. (2020).
We fitted a multivariate Bayesian regression model to summarize CNP\%
content data per trophic guild with random effects at the species level.
This model had a median Bayesian R2 of 0.62, 0.62, and 0.48 for C, N and
P respectively.\\
Next, we extracted 1000 draws of the predicted the CNP\% per trophic
guild. Parravicini et al. (2020) provides the probability of reef fish
species to be assigned to each of the 8 defined trophic guilds. By
combining these probabilities with the predicted diet contents per
trophic guild, we finally estimated the diet CNP\% for each species in
our database. We then took the average and standard deviation across all
1000 draws.

\hypertarget{metabolic-parameters}{%
\subsubsection{4 Metabolic parameters}\label{metabolic-parameters}}

\hypertarget{data-collection-2}{%
\subsubsection{4.1 Data collection}\label{data-collection-2}}

In the period between 2018 and 2019, we collected 1393 individuals of 61
species and 18 families with a minimum of 3 replicates per species.
Individuals were collected using handnets and clove oil by scuba divers.

\hypertarget{metabolic-rate}{%
\subsubsection{4.2 metabolic rate}\label{metabolic-rate}}

To quantify standard metabolic rate (SMR) and maximum metabolic rate
(MMR), we conducted intermittent-closed respirometry experiments at 28°C
(Steffensen 1989; Clark, Sandblom, and Jutfelt 2013). After an
acclimatization and fasting period of 48 h in aquaria, the fish were
individually transferred to a water-filled tub at 28°C and manually
chased by the experimenter until exhausted (Norin and Malte 2011; Clark
et al.~2012). Then, they were placed in respirometry chambers submersed
in an ambient and temperature-controlled tank, where they were left for
\textasciitilde{}23 h. The intermittent respirometry cycles started
immediately after a fish was placed in its respirometry chamber. The
cycles consisted of a measurement (sealed) period followed by a flush
period during which the respirometry chambers were flushed with fully
aerated water from the ambient tank. Because fish were exhausted right
before entering the respirometry chambers, it is possible to measure the
approximate MMR. Depending on fish size, 8 respirometry chambers ranging
in volume (including tubes and pumps) from 0.4 to 4.4 L were run in
parallel, and measurement and flush periods lasted between 3 to 15 min
and 3 to 5 min, respectively. SMR was calculated as the average of the
10 \% lowest values measured during the entire period, after the removal
of outliers (Chabot, Steffensen, and Farrell 2016). MMR was calculated
from the slope of the first measurement period.

\hypertarget{data-analysis-and-extrapolation-3}{%
\subsubsection{4.3 Data analysis and
extrapolation}\label{data-analysis-and-extrapolation-3}}

To retrieve the parameters \(f_\textrm{0}\) (Metabolic normalisation
constant independent of body mass;
\(\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}\)) and \(\alpha\)
(mass-scaling exponent), and \(\theta\) (factorial activity scope), we
fitted a Bayesian mixed effect model predicting the log10-transformed
metabolic rate with the log10-transformed biomass including random
effects of family, species, and mr type (SMR or MMR) on both the
intercept and the species. We ran the model for 4000 iterations, with a
warm-up of 2000 iterations. Further, we used an informative prior for
the slope (\(\alpha \sim normal(0.8, 0.5)\). The model had a Bayesian R2
of 0.973 (95\%CI: 0.972-0.974). We then extracted the family-level
\(\alpha\) by summing the slope of the model with the effects of the
family on the slope of the SMR. We did this for 1000 iterations and then
took the mean and standard deviation. In a similar way we extracted the
family-level intercept for SMR, and then quantified mean and standard
deviation of \(f_\textrm{0}\) after the back-transformation of 1000
iterations of the intercept. Finally, \(\theta\) was quantified as
followed, based on the assumption that fishes rest 12h a day and they on
average spend the remaining 12 hours at a metabolic rate that is the
average of their SMR and MMR: \begin{equation}
    \theta = \frac{3\textrm{SMR} + \textrm{MMR}}{4\textrm{SMR}},
    \label{theta}
\end{equation} where 1000 iterations of the back-transformed
family-level intercepts were used for SMR and MMR. We then summarized
these predictions by taking the mean and standard deviation. We used the
family-level estimates for these three parameters for all species in our
database. For familues that were not represented in our respirometry
dataset, we used an average across all families.

\hypertarget{additional-parameters}{%
\subsection{5. Additional parameters}\label{additional-parameters}}

We retrieved the parameters \(lw_a\), \(lw_b\), \(h\), and \(r\) from
fishbase (REF). For the mass-specific turnover rates for N and
P(\(F_\textrm{0Nz}\); \(F_\textrm{0Pz}\)), we used the estimates
provided in (Schiettekatte et al.~2020).

\end{document}

### 2020-08-10 text/main.Rmd
untrack output / update structure

--- 2020-07-11 text/main.Rmd
@@
 
-# Functional trade-offs reveal coral reef vulnerability
+*diego general comments*
 
-Energy and nutrient fluxes underpin the functioning and productivity of all global ecosystems [@Welti2017]. 
-As such, monitoring and conserving energy flow is critical to natural systems and humanity.
-Due to the efficient cycling of nutrients, coral reefs flourish as hyperdiverse and economically important ecosystems.
-Understanding their ability to cycle energy and nutrients is key to conserving coral reefs and the services they provide to humanity, especially under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017].
-Yet, we primarily assess coral reef functioning based on static variables such as fish biomass and the diversity of species traits [e.g. @Mouillot2014; @Cinner2020; @Mora2011plos]. 
-The lack of global quantitative assessments across multiple functions impedes our capacity to define the drivers of functional coral reefs [@Bellwood2019; @Brandl2019front]. 
-Here, we quantify ecosystem functioning on global coral reefs using five key biogeochemical fluxes that are mediated by reef fishes, then we disentangle their ecological drivers and estimate their vulnerability to anthropogenic pressure.
-We demonstrate that beyond biomass, the most commonly used indicator to quantify reef fish functioning, functions vary from 10 to 100-fold.
-Further, critical trade-offs exist between functions, which are driven by differences in community structure; therefore, it is impossible to simultaneously maximize all functions.
-In addition, we reveal that strikingly few species contribute disproportionally to each ecosystem function. 
-However, the identity of these species varies significantly across reefs, with ~70% of all species assuming a key role on a local scale. 
-Thus, maintaining coral reef ecosystem functioning is a multifaceted objective that requires the protection of a large proportion of species, a considerably more complex management strategy than maximising fish biomass.
-The existence of trade-offs between multiple functions and the lack of key species over large spatial scales provides critical context for coral reef conservation. 
-Although it is impossible to maximize all aspects of functioning, we can preserve the integrity of coral reef  fluxes of elements by applying locally administered solutions that go beyond the simple protection of biomass.
+**1) no need to emphasise how misleading it might be to rely solely on standing biomass for conservation targets. Your results are powerful and novel enough without any of that. **
 
-The flow of elements through biological communities fuels all life on Earth [@Welti2017] 
-Although there is a strong consensus on the importance of these fluxes, also known as ecosystem functions, our ability to manage for ecosystem functioning remains poor [@Welti2017]. 
-For millennia, humans have managed nature with an economic mindset to maximize desirable components such as plant or animal biomass [@Weisser2017]. 
-However, Earth’s resources are finite, and the existence of multiple ecosystem functions comes with trade-offs, whereby efforts to maximize one function may negatively impact another [@Tallis2008]. 
-To make informed management decisions that pertain to ecosystem functioning, it is critical to understand the mechanisms that drive these trade-offs [@Rodriguez2006].
+**2) We need to wordsmith the text some more to get readers onboard with the equality fluxes = functions.**
 
-In the marine realm, coral reefs are the most diverse and productive ecosystem, and they underpin indispensable ecosystem services to humans. 
-As coral reefs thrive in nutrient-poor waters, efficient nutrient cycling is the key to their productivity. 
+**3) The chosen model predictors.
+It would help I think if their justifications were intertwined with the early main-text paragraphs.
+Not drivers, perhaps "predictors" or "potential drivers" might be a safer solution.**
+
+**4) The main text needs a succinct, yet clear description of how the modelling choice outputs a "trade-off" among the five fluxes.
+While the ugly details can be shoved in the Methods and Supplementary Info, the reader needs those ingredients to appreciate what you mean by the term trade-off, and how important / reliable they are.**
+
+*comments Nick*
+**some circularity in there at present**
+**missing clarity regarding why each step in the analyses (e.g. moving from organismal traits to species level) is a logical progression from the last. **
+
+*comments jake*
+**overall message is a bit vague and you would be better served to pull a few key things out and run with htem. **
+**I think instead of mixing messages about global and local conseravation you just be all out there with it and say: real conservation of coral reefs will require both actions global and local.
+I think your 70% stat is really really cool and is something to hang your hat on.**
+**JA: : I think that the text is quite verbose and has too many fancy words.
+I will minimize the extent to which I edit out your adjectives moving forward because it is your MS your and your right to word things how you want – and that is fine.
+But as you see how I have edited things so far that I think there are an excessive number of adjectives (and the ones that are used are a bit over the top) and importantly they distract from the message.
+Again, that is just my opinion, you do you.**
+
+*comments Deron*
+**I wonder if the heat map showing tradeoffs among the ecosystem functions would be worth putting in the main MS.
+I thought it was really cool!
+Maybe integrate it into Fig 2 or something if possible.
+**
+
+**nmds: should production be in gC?**
+
+**Nowhere are the actual rates of the different fluxes presented. All that readers get to see are residuals or effect size plots or correlations. **
+
+**I think one thing that would be really nice in the supplement would be to have a figure identical to that of Fig 1.
+that actually presented the data on the maps instead of the residuals.
+It would be really informative to be able to look at the residuals in Fig 1 vs.
+the real data in the supplement.
+Something to consider.
+**
+
+**Also on figure 1 maybe putting the units of each flux to emphasize to the reader that you are measuring things in N, P, or C for all of the different metrics. **
+**fluxes vs functions!!**
+
+# Trade-offs redefine the vulnerability of reef fish functions
+
+Nina M.
+D.
+Schiettekatte, (core team:) Simon J.
+Brandl, Jordan M.
+Casey, Nicholas A.
+J.
+Graham, Diego R.
+Barneche, Deron E.
+Burkepile, Jacob E.
+Allgeier, (other data contributors:) Katrina S.
+Munsterman, Fabien Morat, Alexandre Mercière, Yves Letourneur, Enrico L.
+Rezende, Graham J.
+Edgar, Rick D.
+Stuart-Smith, Jesús E.
+Arias-Gonzaléz, Alan M.
+Friedlander, Alison L.
+Green, Osmar J.
+Luiz,  F.
+A.
+Rodríguez‐Zaragoza, Laurent Vigliola, Michel Kulbicki, Sergio R.
+Floeter  (supervisors:) Sébastien Villéger, Valeriano Parravicini
+
+**Elemental fluxes underpin the functioning and productivity of all global ecosystems, thus maintaining fluxes (i.e.
+functions) is essential to the preservation of life [@Welti2017].
+Coral reefs flourish under nutrient-poor environments, and host a high diversity of fishes providing nutrition to millions of people [@Teh2013].
+Understanding the ability of coral reefs to maintain healthy functioning is essential to conserving coral reefs and the services they provide to humanity, especially under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017].
+Here, we determine the predictors and vulnerability of five key functions that are mediated by fishes across the tropics.
+We demonstrate that critical trade-offs exist among functions, such that no reef fish community structure is capable of maximizing all five functions simultaneously.
+In addition, we reveal that there is a high degree of functional dominance across communities.
+However, the identity of these species varies significantly across reefs, with ~70% of all species contributing disproportionally to a function in a given community.
+Finally, we highlight unbalanced vulnerability to human stressors across functions.
+Our results introduce a conundrum in coral reef conservation, i.e.
+we cannot maximize all functions, and imply that the successful preservation of coral reef functioning requires both conserving high fish diversity globally, and applying locally administered solutions.**
+
+The flow of elements through biological communities fuels all life on Earth [@Welti2017].
+There is a strong consensus on the importance of preserving these fluxes, also defined as ecosystem functions [@Welti2017].
+However, quantitative monitoring of multiple functions is still in its infancy for many ecosystems due to methodological challenges, and therefore their trade-offs, drivers, and vulnerability remain poorly understood, impeding informed management [@Brandl2019front].
+For millennia, humans have managed nature with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
+However, efforts to maximize one function may negatively impact another [@Tallis2008]. 
+To make informed management decisions that pertain to ecosystem functioning, it is critical to quantify multiple functions simultaneously in order to understand the mechanisms that drive potential trade-offs [@Rodriguez2006].
+
+Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans [@Teh2013]. 
+As coral reefs thrive in nutrient-poor waters, efficient nutrient recycling is the key to their productivity [@Brandl2019science]. 
 However, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
-Over the past decade, severe biodiversity declines have strained the ability of coral reefs to maintain ecosystem functioning and brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish biomass, coral cover, and the richness of species traits [e.g.
+Over the past decade, severe biodiversity declines have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish biomass, and functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Consequently, we know little about the co-occurrence of multiple ecosystem functions and their drivers, which provides us with limited guidance for coral reef management in our rapidly changing world.
+Consequently, we know little about the co-occurrence of functions and their drivers, which currently provides us with limited guidance for coral reef management in our rapidly changing world [@Allgeier2016].
 
-Integrating principles of biogeochemistry and traditional ecological assessments provides a promising path toward understanding and conserving the fluxes that underpin reef functioning. 
-Here, we integrate reef fish trait databases across 9,118 communities with bioenergetic modelling to (1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory), (2) disentangle their ecological drivers, and (3) investigate the contribution and vulnerability of different species to each function.
+Here, we integrate principles of biogeochemistry and traditional ecological assessments to advance understanding and conservation of the fluxes that underpin reef functioning.
+Specifically, we use a combination of novel data and phylogenetic extrapolation techniques to parametrize bioenergetic models on an individual level for 1010 reef fish species.
+We integrate these bioenergetic models with 9,118 reef fish communities at 585 sites across the world's reefs to
+(1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory) as well as their trade-offs, 
+(2) determine the ecological predictors of variation in ecosystem functions using Bayesian mixed models, 
+(3) estimate the contribution and dominance of different species to each function, and
+(4) assess the vulnerability of functions.
 
-Fish biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front]. 
-However, biomass is a product of nutrient cycling that drives productivity on reefs [@Szmant-Froelich1983]. 
-Although there was a strong relationship between biomass and all five functions, after controlling for biomass, different functions varied up to 10 to 100-fold (see Extended Data Fig. 1a). 
-This striking community-level variability is driven by the species-specific biological traits of fishes [@Schiettekatte2020]. 
-Further, the residual variability of functions revealed strong trade-offs among different functions (see Extended Data Fig.
-1b).
-As a consequence, at a given biomass, no reef can maximize all functions (fig.
-1).
-For example, when extending the proposed baseline of ~100g/m2 standing fish biomass to define a healthy reef [@MacNeil2015] to our dataset, 46% of global fish communities reached this biomass baseline, yet only 19% showed adequate functioning to satisfy the predicted threshold of each function based on the biomass baseline.
-In fact, due to existing trade-offs between functions, a biomass of ~450g/m2 is necessary to ensure above-threshold levels for each function. 
-Our proposed biomass is 450% higher than previously estimated, and, notably, a mere 13% of the fish communities in our dataset meet this threshold (Extended Data Fig. 2).
+Combining novel approaches including phylogenetic extrapolation of quantitative traits and individual-level bioenergetic models with underwater visual census community data enabled us to quantify five key ecosystem functions performed by fishes (i.e.
+nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory) across the world's reefs for the first time, highlighting the functional variation that exists beyond biomass effects.
+Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and there is a strong relationship between biomass and all five functions.
+Yet, for communities with similar total fish biomass, different functions varied up to 10 to 100-times (Extended Data Fig. 1a). 
+Further, correcting each function for biomass revealed strong trade-offs among the different functions (Fig.1, Extended Data Fig. 1b). 
+For example, communities with high herbivory rates or N exretion are negatively correlated with rates of P excretion.
+Strikingly, less than 3% of all communities had an above average value of biomass-corrected function for all five functions simultaneously. 
+As a consequence, at a given biomass, no reef can maximize all functions, i.e. a location may be a hotspot for one biomass-corrected function while being a cold spot for another (Fig. 1).
 
-What underpins the trade-offs between multiple functions on coral reefs? 
-To explore the ecological drivers of each function, we fit Bayesian mixed models using variables that describe fish community structure, including body size, trophic level, age structure (expressed as immaturity), and species richness.
-We found that functional trade-offs are mediated by contrasting aspects of community structure (fig. 2). 
+To uncover what underpins the trade-offs between multiple functions on coral reefs, we explored the relationship of each function with ecological predictors discribing fish community structure including body size, trophic level, age structure (expressed as immaturity) by fitting Bayesian mixed models (fig.
+2).
+We found that negative correlations between functions are mediated by contrasting aspects of community structure (fig. 2). 
 For example, phosphorous excretion is maximized in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels (See also @Allgeier2014). 
 In contrast, biomass production is maximised in communities dominated by small, immature fishes at lower trophic levels. 
-Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate [@Brown2004], and as a consequence, small individuals have elevated consumption rates and highly contribute to functions that rely on rapid energetic turnover [@Barneche2014].
-In contrast, fishes in early life stages or with small body sizes feed on nutrient-poor diets that are limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
-These results highlight the critical need to integrate organismal biology with community ecology to understand ecosystem-wide biogeochemical fluxes.
+Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018].
+On the other hand, fishes in early life stages that are highly dependent on phosphorus to grow, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
+These results confirm the need to integrate organismal biology with community ecology to understand ecosystem-wide biogeochemical fluxes.
 
-Beyond community structure, species identity profoundly affects rates of functioning [@Ruttenberg2019; @Topor2019]. 
-To explore whether some species or families consistently contribute more to functioning than expected by their biomass, we estimated the functional dominance of species and their frequency across communities.
-Across global coral reefs, functions are consistently dominated by a few species (fig. 3b). 
-However, despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally dominant species varies remarkably. 
-In fact, ~70% of all species contribute disproportionally to a function in a given community, but worldwide, the frequency of dominance is strikingly low for each species (fig. 3c). 
-Despite high species richness on coral reefs, researchers often report the existence functionally dominant “key species” [e.g. @Bellwood2006]. 
-In contrast, we demonstrate that while dominance is indeed prevalent, the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].
-
-Thus, the local decline of a few species can have a large impact if those species are not functionally redundant. 
-By coupling species’ functional contributions with their vulnerability to fishing and climate change, we demonstrate that the most profound human-mediated changes are likely to impact piscivory via fishing (fig.
-4).
-Like piscivory, herbivory is almost exclusively upheld by few key species; therefore, herbivory is also vulnerable to species loss due to lack of redundancy. 
-Given the local nature of species’ functional contributions, the determination of species-based conservation efforts at a global scale will fail to sustain coral reef functioning. 
-Rather, ecosystem functioning can be supported by local actions that avert the functional extinction of species [@Mccauley2015].
-
-Human impact has already caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
+Human impact has caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
 While the effects of these alterations on ecological processes are more difficult to monitor than declines in biomass, the loss of functioning may have profound consequences for reef ecosystems. 
 For example, intensive fishing leads to biomass declines, which particularly impacts large fishes and consequently changes the size, age, and trophic structure of fish communities [@Graham2017]. 
-These effects can favor nitrogen excretion and production [e.g. @Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (Extended Data Fig. 3). 
-On the other hand, changes in community structure triggered by coral cover declines are associated with a shift toward herbivores [@Graham2006; @Ceccarelli2016]. 
-Herbivores have a minor contribution to phosphorus excretion [@Schiettekatte2020], so herbivore dominance and the subsequent community-level decline of phosphorus may induce a negative feedback loop for coral growth [@Shantz2015].
+These effects can favor biomass corrected nitrogen excretion and production [e.g.
+@Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (fig.
+2, Extended Data Fig.
+2).
+On the other hand, changes in community structure triggered by coral cover declines are associated with a shift toward herbivores, which may avoid shifts to algal domination [@Graham2006; @Ceccarelli2016].
+In contrast, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent community-level decline of phosphorus excretion may change elemental ratios.
+Lower N to P ratios can in fact favor algal growth [@Burkepile2013], and promotes symbiont dominance within the coral holobiont [@Allgeier2020].
 This is particularly problematic when considered in conjunction with climate change, as phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
+Considering multiple functions thus paints a more nuanced and complete picture to help us understand how human-induced shifts in community structure affect coral reef health.
+
+Alongside community structure, functional vulnerability can also be affected by the cumulative vulnerability of the species that are performing the functions, i.e.
+the vulnerability of a largely dominant species highly affects the vulnerability of the function itself.
+Due to species-specific charachteristics, certain species or entire families tend to contribute more or less to function, relative to their contribution to biomass (fig. 3a).
+Further, abundant species with a certain set of traits can profoundly affect rates of functioning on the community level [@Ruttenberg2019; @Topor2019]. 
+Therefore, we assessed the role of species by quantified the degree of dominance for each community. 
+We demonstrate that for most communities, functions are consistently dominated by a few species (fig. 3b).
+We then asked if species consistently perform a key role when present across communities by quantifying the frequency of their dominance.
+Despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally dominant species varies remarkably and the frequency of dominance per species tends to be low (fig.
+3c).
+Consequently, while worldwide, species that consistently perform a key role whenever present are rare, our results suggest that most species perform a key role on a local scale. 
+Indeed, ~70% of all species contribute disproportionally to a function in a given community.
+Despite high species richness on coral reefs, researchers often report the existence functionally dominant “key species” [e.g. @Bellwood2006]. 
+We demonstrate that while dominance is indeed prevalent, the identity of the dominant species is unpredictable, suggesting the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].
+
+As a consequence of the widespread high degree of dominance on a local scale, the vulnerability of key species highly affects the vulnerability of functions. 
+However, the identity and vulnerability of key species varies among functions. 
+To uncover divergence in functional vulnerability, we quantified the vulnerability of each function on the community level to fishing and climate change by averaging species vulnerabilities, weighted by their contribution to each function.
+We demonstrate that vulnerability is relatively the highest for piscivory, through fishing, followed by P excretion, while climate change has the largest effects on P excretion, N excretion, and production (fig.
+4).
+Double jeapordy tends to be the highest for P excretion and piscivory.
+Given the local nature of species’ functional contributions, the determination of specific species-based conservation efforts at a global scale will fail to sustain coral reef functioning. 
+Rather, ecosystem functioning can be supported by local actions, taking into account the dominance and vulnerability, to avert the functional extinction of species [@Mccauley2015], while maintaining a high diversity on a global scale.
 
 Our results demonstrate the challenges of managing one of Earth’s most diverse and vulnerable ecosystems. 
-Rooted in our agroeconomic history, maximizing ecosystem functioning is the dominant objective of many 21st century conservation initiatives. 
-The revealed functional trade-offs challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
+Maximizing ecosystem functioning is an important objective of contemporary conservation initiatives. 
+The functional trade-offs revealed between key ecosystem functions challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
 Traditionally, marine reserves have been the main conservation strategy for coral reefs [@Graham2020].
 While they provide benefits for biomass and herbivory, they provide little insurance for diversity in populated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
-Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential energetic pathways. 
-Thus, it is essential to gauge reef “health” based on multiple, complementary, process-based functions [@Brandl2019front]. 
-Furthermore, individual reefs require local management plans to protect species with key roles in multiple functions, and the presence of multiple stakeholders may require the prioritisation of various functions based on local needs and stressors.
-Globally, given that majority of species are locally important for functioning in a certain community, the conservation of a wide range of species is desirable, in addition to tackling the primary threat to coral reefs, climate change [@Bruno2019].
+Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
+Thus, it is nescessary to gauge reef “health” based on multiple, complementary, process-based functions [@Brandl2019front]. 
+Furthermore, individual reefs require local management plans to protect species with key roles for each function and community structure components, and the presence of multiple stakeholders may require the prioritisation of various functions based on local needs and stressors.
+Finally, as most species play an important role on a local scale, local management efforts should go hand in hand with global action to conserve the high diversity of species in addition to tackling climate change, the primary threath to coral reefs [@Bruno2019].
 
-Biomass alone does not suffice to explain coral reef ecosystem functioning, and, in fact, there is a strong mismatch among different functions performed by coral reef fishes. 
 Our results contribute to an ongoing discussion surrounding the question: what constitutes a healthy reef? 
@@
 Rather, a diverse community that supports intermediate levels of each function is ideal, with many species emerging as key local players.
-In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring beyond biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].
+In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring of multiple functions alongside biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].
 
@@
 
-![Figure 1: World maps of five key ecosystem functions, independent of fish biomass.
-Dots indicate the localities that are included in this study.
-Dot size represents the rank of the average of the residuals of each log-transformed function after regression with the log-transformed standing biomass and sea surface temperature.
-Similarly, the color scales show the value of the residuals categorically (low = lower 25%, medium = 25-75%, high = >75%).
-Circles highlight the five localities with the highest average residuals of each function respectively.](../output/plots/fig1_multimap.png)
+![Figure 1: World maps of five key ecosystem functions, biomass-corrected and standardised.
+Dots indicate the locations that are included in this study.
+Dot size represents the rank of the biomass-corrected function.
+Similarly, the color scales show the value of the biomass-corrected function categorically (black = lower 25%, grey = 25-75%, color = >75%).
+Circles highlight the five locations with the highest value of each biomass-corrected function respectively.](../output/plots/fig1_multimap.png)
 
 ![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables.
+Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community.
 The log-transformed standing biomass was also included as a covariable, but not shown in this figure.
 All data was standardized to be able to compare across functions and variables.
-Functions were log-transformed before standardisation.](../output/plots/fig2_com_slopes.png)
+Functions were log-transformed before standardisation.
+Dots represent the average of the effect, and filled lines indicate the 95% credible interval.
+Effects are not shown when their 95% CI intersects with zero.
+Variables are ordered by the maximum absolute effect across the five models.](../output/plots/fig2_com_slopes.png)
 
 ![Figure 3: a) Median family-level contributions to each function, relative to their contribution to biomass.
+Positive values mean that a family contributes more relative to its contribution to total biomass.
 Only the 12 most important family’s are shown here, and families are ordered by their median contribution to biomass.
@@
 A value of 1 means that a species is always important whenever present.
-A species is counted as being dominant in a community if that species contributes to more than 1 divided by the species richness.
+A species is counted as being dominant in a community if the contribution of that species is higher than the scenario in which all species contribute equally (i.e.
+1 divided by the species richness).
+Shaded areas show the distribution of the values.
 Dots represent the median value, while lines indicate the interquartile range.](../output/plots/fig3_contributions.png)
 
-![Figure 4: Vulnerability and importance to each function of fish species included in this study.
+![Figure 4: Vulnerability of species included in this study related to local dominance.
 Transparant bars represent the relative number of species in each category of vulnerability.
-Filled bars show the proportion of species that are locally important (i.e. perform more than 1/N of the function, where N is the number of species observed in a certain transect).](../figures/figure4_all_species.png)
+Filled bars show the proportion of species that are locally dominant.
+A species is considered locally dominant if in any community, it contributes more to a function than 1 divided by the total number of species.](../figures/figure4_all_species.png)
 
 ![Extended Data Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities.
-b) Correlation matrix od the residuals of the five functions.](../output/plots/annex_fig1_mf_logbiomass.png)
+b) Correlation matrix of the residuals of the five functions.
+Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig2.png)
 
-![Extended Data Figure 2: Predicted probability of crossing a reference threshold for all five functions with the log-transformed biomass.](../output/plots/annex_fig2.png)
-
-![Extended Data Figure 3: Fitted linear regression of each function with the log-transormed gravity to markets.
+![Extended Data Figure 2: Fitted linear regression of each function with the log-transormed gravity to markets.
 Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

### 2020-08-10 R/functions_analysis.R

@@ -12,96 +12,6 @@ normalize <- function(x){
   100 * (x - min(x, na.rm = TRUE))/(max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
 }
 
-
-
-# flux <- left_join(flux, res)
-# flux$good <- ( flux$biomass_tot< 50 & flux$multi < quantile(flux$multi, 0.05, na.rm = TRUE))
-# 
-# flux <- flux %>%
-#   mutate(cat = case_when(
-#     biomass_tot < 50 & 
-#       multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "bb",
-#     biomass_tot < 50 & 
-#       multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "bg",
-#     biomass_tot > 150 & 
-#       multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "gb",
-#     biomass_tot > 150 & 
-#       multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "gg",
-#     TRUE~"other"
-#   ))
-# 
-# t <-flux %>%
-#   group_by(sites, locality) %>% summarise_if(is.numeric, mean)
-# 
-# t <- t %>%
-#   mutate(cat = case_when(
-#     biomass_tot < 50 & 
-#       multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "bb",
-#     biomass_tot < 50 & 
-#       multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "bg",
-#     biomass_tot > 150 & 
-#       multi < quantile(flux$multi, 0.1, na.rm = TRUE) ~ "gb",
-#     biomass_tot > 200 & 
-#       multi > quantile(flux$multi, 0.9, na.rm = TRUE) ~ "gg",
-#     TRUE~"other"
-#   ))
-# test <- table(flux$cat, flux$sites) %>% as.data.frame() %>%
-#   group_by(Var2) %>%
-#   mutate(tot = sum(Freq)) %>%
-#   mutate(Freq/tot) %>%
-#   filter(!(Var1 %in% c("bb", "bg") & Freq>1))
-# 
-# ggplot(flux) +
-#   geom_boxplot(aes(x = cat, y = imm_m))
-# ggplot(flux) +
-#   geom_boxplot(aes(x = cat, y = imm_q1))
-# ggplot(flux) +
-#   geom_boxplot(aes(x = cat, y = imm_q3))
-# ggplot(flux) +
[…]

### 2020-08-10 R/functions_plots.R

@@ -18,7 +18,7 @@ make_fig1 <- function(location_effect){
             axis.title = element_blank(),
             axis.text.x = element_text(size = 6),
             axis.text.y = element_text(size = 6),
-            plot.title = element_text(size = 8, hjust = 0, face = "bold"), 
+            plot.title = element_text(size = 6, hjust = 0, face = "bold"), 
             plot.margin = unit(c(0.002,0.002,0.002,0.002), units = , "cm"),
             panel.spacing = unit(0, "cm")
       ) 
@@ -60,7 +60,7 @@ make_fig1 <- function(location_effect){
                data = filter(location_effect, r_loc_Fn > quantile(location_effect$r_loc_Fn, 0.95, na.rm = TRUE))) +
     scale_color_manual(values = pal, name = "") +
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
-    geom_text(aes(x = -170, y = 30, label = "N excretion"), size = 4, hjust = 0) +
+    geom_text(aes(x = -175, y = 30, label = "N excretion (g N/m²day)"), size = 3, hjust = 0) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.8))) +
     scale_size_continuous(range = c(0.5, 3), guide = FALSE) +
     theme_worldmap() + 
@@ -90,7 +90,7 @@ make_fig1 <- function(location_effect){
                data = filter(location_effect, r_loc_Fp > quantile(location_effect$r_loc_Fp, 0.95, na.rm = TRUE))) +
     scale_color_manual(values = pal, name = "") +
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
-    geom_text(aes(x = -170, y = 30, label = "P excretion"), size = 4, hjust = 0) +
+    geom_text(aes(x = -175, y = 30, label = "P excretion (g P/m²day)"), size = 3, hjust = 0) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.8))) +
     scale_size_continuous(range = c(0.5, 3), guide = FALSE) +
     theme_worldmap() + 
@@ -120,7 +120,7 @@ make_fig1 <- function(location_effect){
                data = filter(location_effect, r_loc_Gc > quantile(location_effect$r_loc_Gc, 0.95, na.rm = TRUE))) +
     scale_color_manual(values = pal, name = "") +
[…]

### 2020-08-10 R/plan.R

@@ -1,6 +1,12 @@
 
 plan <- drake_plan(
   
+  ##### set up output #####
+  out_folder = dir.create("output"),
+  out_folder_data = dir.create("output/data"),
+  out_folder_plots = dir.create("output/plots"),
+  out_folder_text = dir.create("output/text"),
+  
   ##### Bioenergetic model #####
   
   # load all parameters

### 2020-08-10 R/play.R

@@ -3450,7 +3450,341 @@ ggplot(summary_transect_complete) +
   geom_abline(aes(intercept = -11.46, slope = 1.05), color = "black")
 
 
+####### multivariate correlation model ######
 
+# flux <- summary_transect_complete
+# 
+# # run model
+# fit <- brm(
+#   mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc)) ~ (log(biomass_tot)), 
+#               data = flux[flux$I_herb>0 & flux$I_pisc>0,][1:100,], cores = 4)
+# fails
+
+
+##### vulnerability per community #####
+
+loadd(vulnerability)
+loadd(contributions)
+loadd(herb_pisc)
+loadd(summary_transect)
+
+
+con <- left_join(contributions, vulnerability) %>%
+  left_join(herb_pisc$contributions_herb_pisc) %>%
+  group_by(transect_id) %>%
+  dplyr::summarize(
+    vuln_Fn_fi = sum(Fn_p * vuln_fi, na.rm = TRUE),#/sum(vuln_fi, na.rm = TRUE),
+    vuln_Fp_fi = sum(Fp_p * vuln_fi, na.rm = TRUE),#/sum(vuln_fi, na.rm = TRUE),
+    vuln_Gc_fi = sum(Gc_p * vuln_fi, na.rm = TRUE),#/sum(vuln_fi, na.rm = TRUE),
+    vuln_Iherb_fi = sum(I_herb_p[I_herb_p > 0] * vuln_fi[I_herb_p > 0], na.rm = TRUE),#/sum(vuln_fi[I_herb_p > 0], na.rm = TRUE),
+    vuln_Ipisc_fi = sum(I_pisc_p[I_pisc_p > 0] * vuln_fi[I_pisc_p > 0], na.rm = TRUE),#/sum(vuln_fi[I_pisc_p > 0], na.rm = TRUE),
+    vuln_Fn_cl = sum(Fn_p * vuln_climate, na.rm = TRUE),#/sum(vuln_climate, na.rm = TRUE),
+    vuln_Fp_cl = sum(Fp_p * vuln_climate, na.rm = TRUE),#/sum(vuln_climate, na.rm = TRUE),
+    vuln_Gc_cl = sum(Gc_p * vuln_climate, na.rm = TRUE),#/sum(vuln_climate, na.rm = TRUE),
[…]

### 2020-08-10 make.R
cleaner project

@@ -1,20 +1,0 @@
-source("R/packages.R")  # loads packages
-source("R/functions_wrangling.R") # defines the create_plot() function
-source("R/functions_analysis.R") # defines the create_plot() function
-source("R/plan.R")      # creates the drake plan
-# options(clustermq.scheduler = "multicore") # optional parallel computing. Also needs parallelism = "clustermq"
-
-make(
-  plan, # defined in R/plan.R
-  verbose = 2, lock_envir = FALSE
-)
-
-#make(plan, targets = c("models_contributions_Wc", "models_contributions_Wn", "models_contributions_Wp"))
-
-config <- drake_config(plan)
-drake::r_vis_drake_graph(targets_only = TRUE)
-
-drake::r_make()
-
-# drake::clean("models_contributions_Wn")
-# make(plan, targets = "herb_pisc", lock_envir = FALSE)

### 2020-08-20 text/main.Rmd
rerun with all specie

@@
 
-*diego general comments*
-
-**1) no need to emphasise how misleading it might be to rely solely on standing biomass for conservation targets. Your results are powerful and novel enough without any of that. **
-
-**2) We need to wordsmith the text some more to get readers onboard with the equality fluxes = functions.**
-
-**3) The chosen model predictors.
-It would help I think if their justifications were intertwined with the early main-text paragraphs.
-Not drivers, perhaps "predictors" or "potential drivers" might be a safer solution.**
-
-**4) The main text needs a succinct, yet clear description of how the modelling choice outputs a "trade-off" among the five fluxes.
-While the ugly details can be shoved in the Methods and Supplementary Info, the reader needs those ingredients to appreciate what you mean by the term trade-off, and how important / reliable they are.**
-
-*comments Nick*
-**some circularity in there at present**
-**missing clarity regarding why each step in the analyses (e.g. moving from organismal traits to species level) is a logical progression from the last. **
-
-*comments jake*
-**overall message is a bit vague and you would be better served to pull a few key things out and run with htem. **
-**I think instead of mixing messages about global and local conseravation you just be all out there with it and say: real conservation of coral reefs will require both actions global and local.
-I think your 70% stat is really really cool and is something to hang your hat on.**
-**JA: : I think that the text is quite verbose and has too many fancy words.
-I will minimize the extent to which I edit out your adjectives moving forward because it is your MS your and your right to word things how you want – and that is fine.
-But as you see how I have edited things so far that I think there are an excessive number of adjectives (and the ones that are used are a bit over the top) and importantly they distract from the message.
-Again, that is just my opinion, you do you.**
-
-*comments Deron*
-**I wonder if the heat map showing tradeoffs among the ecosystem functions would be worth putting in the main MS.
-I thought it was really cool!
-Maybe integrate it into Fig 2 or something if possible.
-**
-
-**nmds: should production be in gC?**
-
-**Nowhere are the actual rates of the different fluxes presented. All that readers get to see are residuals or effect size plots or correlations. **
-
-**I think one thing that would be really nice in the supplement would be to have a figure identical to that of Fig 1.
-that actually presented the data on the maps instead of the residuals.
-It would be really informative to be able to look at the residuals in Fig 1 vs.
-the real data in the supplement.
-Something to consider.
-**
-
-**Also on figure 1 maybe putting the units of each flux to emphasize to the reader that you are measuring things in N, P, or C for all of the different metrics. **
-**fluxes vs functions!!**
-
 # Trade-offs redefine the vulnerability of reef fish functions
@@
 D.
-Schiettekatte, (core team:) Simon J.
+Schiettekatte, Simon J.
 Brandl, Jordan M.
@@
 Burkepile, Jacob E.
-Allgeier, (other data contributors:) Katrina S.
+Allgeier, Katrina S.
 Munsterman, Fabien Morat, Alexandre Mercière, Yves Letourneur, Enrico L.
@@
 Rodríguez‐Zaragoza, Laurent Vigliola, Michel Kulbicki, Sergio R.
-Floeter  (supervisors:) Sébastien Villéger, Valeriano Parravicini
+Floeter, Sébastien Villéger, Valeriano Parravicini
 
-**Elemental fluxes underpin the functioning and productivity of all global ecosystems, thus maintaining fluxes (i.e.
-functions) is essential to the preservation of life [@Welti2017].
-Coral reefs flourish under nutrient-poor environments, and host a high diversity of fishes providing nutrition to millions of people [@Teh2013].
+**Coral reefs flourish under nutrient-poor environments, and host a high diversity of fishes providing nutrition to millions of people [@Teh2013].
 Understanding the ability of coral reefs to maintain healthy functioning is essential to conserving coral reefs and the services they provide to humanity, especially under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017].
-Here, we determine the predictors and vulnerability of five key functions that are mediated by fishes across the tropics.
-We demonstrate that critical trade-offs exist among functions, such that no reef fish community structure is capable of maximizing all five functions simultaneously.
+Here, we characterize the predictors as well as the vulnerability of five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans.
+We demonstrate that critical trade-offs exist among functions, such as between biomass production and phosphorous cycling, with no single reef fish community sustaining high values for all five functions simultaneously.
 In addition, we reveal that there is a high degree of functional dominance across communities.
@@
 Finally, we highlight unbalanced vulnerability to human stressors across functions.
-Our results introduce a conundrum in coral reef conservation, i.e.
-we cannot maximize all functions, and imply that the successful preservation of coral reef functioning requires both conserving high fish diversity globally, and applying locally administered solutions.**
+Our results introduce a conundrum for coral reef conservation, i.e. we cannot maximize all functions, and imply that the successful preservation of coral reef functioning requires both conserving high fish diversity globally, and applying locally administered actions.
+**
 
-The flow of elements through biological communities fuels all life on Earth [@Welti2017].
+The flow of elements through biological communities represent key ecosystem functions that fuel all life on Earth [@Welti2017].
 There is a strong consensus on the importance of preserving these fluxes, also defined as ecosystem functions [@Welti2017].
-However, quantitative monitoring of multiple functions is still in its infancy for many ecosystems due to methodological challenges, and therefore their trade-offs, drivers, and vulnerability remain poorly understood, impeding informed management [@Brandl2019front].
+However, understanding the dynamics of multiple ecosystem functions simultaneously is challenging because the drivers, vulnerability, and trade-offs among functions are still poorly characterized, impeding informed management [@Brandl2019front].
 For millennia, humans have managed nature with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
-However, efforts to maximize one function may negatively impact another [@Tallis2008]. 
-To make informed management decisions that pertain to ecosystem functioning, it is critical to quantify multiple functions simultaneously in order to understand the mechanisms that drive potential trade-offs [@Rodriguez2006].
+However, trade-offs likely exist among ecosystem functions with efforts to maximize one function possibly negatively impacting another (e.g. timber vs. erosion control) [@Tallis2008]. 
+To make informed management decisions that conserve ecosystem functioning, it is critical to quantify multiple functions simultaneously in order to understand the mechanisms that drive their potential trade-offs [@Rodriguez2006].
 
 Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans [@Teh2013]. 
-As coral reefs thrive in nutrient-poor waters, efficient nutrient recycling is the key to their productivity [@Brandl2019science]. 
+As coral reefs thrive in nutrient-poor waters, efficient nutrient recycling is key to their productivity [@Brandl2019science]. 
  However, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
 Over the past decade, severe biodiversity declines have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish biomass, and functional richness based on qualitative species traits [e.g.
+Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish standing biomass, and functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Consequently, we know little about the co-occurrence of functions and their drivers, which currently provides us with limited guidance for coral reef management in our rapidly changing world [@Allgeier2016].
+Consequently, we know little about the co-occurrence of functions and their drivers, which currently hinders our ability to provide information that could be useful to coral reef management in a rapidly changing world [@Allgeier2016].
 
-Here, we integrate principles of biogeochemistry and traditional ecological assessments to advance understanding and conservation of the fluxes that underpin reef functioning.
-Specifically, we use a combination of novel data and phylogenetic extrapolation techniques to parametrize bioenergetic models on an individual level for 1010 reef fish species.
-We integrate these bioenergetic models with 9,118 reef fish communities at 585 sites across the world's reefs to
-(1) quantify five key ecosystem functions performed by fishes (nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory) as well as their trade-offs, 
-(2) determine the ecological predictors of variation in ecosystem functions using Bayesian mixed models, 
-(3) estimate the contribution and dominance of different species to each function, and
-(4) assess the vulnerability of functions.
+Here, we integrate, for the first time, biogeochemistry and community ecology to advance understanding and conservation of the fluxes of nutrients that underpin reef functioning. 
+Specifically, we use a combination of novel data and phylogenetic extrapolation techniques to parametrize individual-level bioenergetic models which output five key ecosystem functions. 
+We apply these models for 1,010 reef fish species and integrate their output functions with community structure data from 9,118 reefs at 585 sites across the world’s coral reefs to: 
+(1) quantify nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory, 
+(2) determine if there are trade-offs among these functions, 
+(3) determine the ecological predictors of variation in ecosystem functions using Bayesian mixed models, 
+(4) estimate the contribution and dominance of different species to each function, and 
+(5) assess the vulnerability of these functions to climate change and fishing.
 
-Combining novel approaches including phylogenetic extrapolation of quantitative traits and individual-level bioenergetic models with underwater visual census community data enabled us to quantify five key ecosystem functions performed by fishes (i.e.
-nitrogen excretion, phosphorous excretion, biomass production, herbivory, and piscivory) across the world's reefs for the first time, highlighting the functional variation that exists beyond biomass effects.
-Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and there is a strong relationship between biomass and all five functions.
-Yet, for communities with similar total fish biomass, different functions varied up to 10 to 100-times (Extended Data Fig. 1a). 
-Further, correcting each function for biomass revealed strong trade-offs among the different functions (Fig.1, Extended Data Fig. 1b). 
-For example, communities with high herbivory rates or N exretion are negatively correlated with rates of P excretion.
-Strikingly, less than 3% of all communities had an above average value of biomass-corrected function for all five functions simultaneously. 
-As a consequence, at a given biomass, no reef can maximize all functions, i.e. a location may be a hotspot for one biomass-corrected function while being a cold spot for another (Fig. 1).
+Combining novel approaches enabled us to quantify five key ecosystem functions performed by fishes across the world's reefs for the first time, highlighting the functional variation that exists beyond biomass effects.
+Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and we observed a strong relationship between biomass and all five functions.
+Yet, correcting each function for biomass shows a high variability (Fig.
+1), and for communities with similar total fish biomass, different functions often varied by over two orders of magnitude (Extended Data Fig.
+1a).
+Further, we revealed strong trade-offs among the different biomass-corrected functions (Fig.1, Extended Data Fig.
+1b).
+For example, communities with high herbivory rates or N excretion were negatively correlated with rates of P excretion.
+Strikingly, less than 3% of all communities had an above average value of biomass-corrected function for all five functions simultaneously, and not a single community reached maximum values (upper 10%) for all functions.
+As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here, i.e.
+while many reefs may stand out as hotspots for one function, they may also output less of other functions (Fig.
+1).
 
-To uncover what underpins the trade-offs between multiple functions on coral reefs, we explored the relationship of each function with ecological predictors discribing fish community structure including body size, trophic level, age structure (expressed as immaturity) by fitting Bayesian mixed models (fig.
+To uncover what underpins the trade-offs between multiple functions on coral reefs, we explored the relationship of each function with ecological predictors describing fish community structure and representing the variation of fish traits that affect elemental fluxes [@Schiettekatte2020] including body size, trophic level, species richness, and age structure (expressed as immaturity) by fitting Bayesian mixed models (Fig.
 2).
-We found that negative correlations between functions are mediated by contrasting aspects of community structure (fig. 2). 
-For example, phosphorous excretion is maximized in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels (See also @Allgeier2014). 
-In contrast, biomass production is maximised in communities dominated by small, immature fishes at lower trophic levels. 
-Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018].
+We found that negative correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
+For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig.
+1b) (See also ref.
+@Allgeier2014).
+In contrast, biomass production is highest in communities dominated by small, immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
+Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
 On the other hand, fishes in early life stages that are highly dependent on phosphorus to grow, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
-These results confirm the need to integrate organismal biology with community ecology to understand ecosystem-wide biogeochemical fluxes.
+These results vindicate the need to integrate size scaling and species-specific biological traits at the individual level with community ecology to understand ecosystem-wide elemental fluxes [@Schramski2015].
 
-Human impact has caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
-While the effects of these alterations on ecological processes are more difficult to monitor than declines in biomass, the loss of functioning may have profound consequences for reef ecosystems. 
-For example, intensive fishing leads to biomass declines, which particularly impacts large fishes and consequently changes the size, age, and trophic structure of fish communities [@Graham2017]. 
-These effects can favor biomass corrected nitrogen excretion and production [e.g.
-@Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (fig.
-2, Extended Data Fig.
-2).
-On the other hand, changes in community structure triggered by coral cover declines are associated with a shift toward herbivores, which may avoid shifts to algal domination [@Graham2006; @Ceccarelli2016].
-In contrast, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent community-level decline of phosphorus excretion may change elemental ratios.
-Lower N to P ratios can in fact favor algal growth [@Burkepile2013], and promotes symbiont dominance within the coral holobiont [@Allgeier2020].
-This is particularly problematic when considered in conjunction with climate change, as phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
+Human impacts have caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
+For example, intensive fishing leads to reductions in biomass, which particularly selects for large fishes and consequently truncates the size, age, and trophic structure of fish communities [@Graham2017].
+These effects can favor biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
+On the other hand, changes in community structure triggered by coral cover declines related to climate change are associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
+In contrast, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
+Higher N:P ratios can in fact favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
+This is particularly problematic when considered in conjunction with climate change, because phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
 Considering multiple functions thus paints a more nuanced and complete picture to help us understand how human-induced shifts in community structure affect coral reef health.
 
-Alongside community structure, functional vulnerability can also be affected by the cumulative vulnerability of the species that are performing the functions, i.e.
-the vulnerability of a largely dominant species highly affects the vulnerability of the function itself.
-Due to species-specific charachteristics, certain species or entire families tend to contribute more or less to function, relative to their contribution to biomass (fig. 3a).
-Further, abundant species with a certain set of traits can profoundly affect rates of functioning on the community level [@Ruttenberg2019; @Topor2019]. 
-Therefore, we assessed the role of species by quantified the degree of dominance for each community. 
-We demonstrate that for most communities, functions are consistently dominated by a few species (fig. 3b).
+Alongside features of community structure, the vulnerability of specific species that play a dominant role affects the vulnerability of community-level functions to human stressors such as climate change and fishing.
+Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
+Further, abundant species can profoundly affect rates of functioning on the community level [@Ruttenberg2019; @Topor2019]. 
+Therefore, we assessed the role of species by quantified the degree of dominance per function for each community.
+The degree of dominance describes the extent to which a function is performed by a single or only a couple of species.
+We demonstrate that for most communities, functions are consistently dominated by a few species (Fig. 3b).
 We then asked if species consistently perform a key role when present across communities by quantifying the frequency of their dominance.
-Despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally dominant species varies remarkably and the frequency of dominance per species tends to be low (fig.
+Despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally-dominant species varied remarkably and the frequency of dominance per species tends to be low (Fig.
 3c).
-Consequently, while worldwide, species that consistently perform a key role whenever present are rare, our results suggest that most species perform a key role on a local scale. 
-Indeed, ~70% of all species contribute disproportionally to a function in a given community.
-Despite high species richness on coral reefs, researchers often report the existence functionally dominant “key species” [e.g. @Bellwood2006]. 
-We demonstrate that while dominance is indeed prevalent, the identity of the dominant species is unpredictable, suggesting the extreme species richness of coral reefs is essential to sustain global functioning [@Topor2019].
+Consequently, while individual species that consistently perform a key role whenever present globally are rare, our results suggest that most species perform a key role in at least a few reefs. 
+Indeed, ~70% of all species contributed disproportionally to a function in at least one reef.
+Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
+We demonstrate that while dominance is indeed prevalent, the identity of the dominant species may be less predictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
 
-As a consequence of the widespread high degree of dominance on a local scale, the vulnerability of key species highly affects the vulnerability of functions. 
-However, the identity and vulnerability of key species varies among functions. 
-To uncover divergence in functional vulnerability, we quantified the vulnerability of each function on the community level to fishing and climate change by averaging species vulnerabilities, weighted by their contribution to each function.
-We demonstrate that vulnerability is relatively the highest for piscivory, through fishing, followed by P excretion, while climate change has the largest effects on P excretion, N excretion, and production (fig.
+As many species locally play a dominant role for one or more functions, the vulnerability of these functionally-dominant species heavily affects the vulnerability of the functions on the community scale.
+Species may be more vulnerable to fishing (e.g.
+large herbivores, predators) or to climate change through coral cover decline (e.g.
+butterfly fishes) [@Graham2011].
+By combining species-level vulnerability scores to fishing and climate change [@Graham2011] with the contributions of each species to the community-scale functions, we estimated the vulnerability of all five functions to both stressors.
+We demonstrate that vulnerability to fishing is relatively the highest for piscivory, followed by P excretion, while climate change vulnerability is the highest for P excretion, N excretion, and production (Fig.
 4).
-Double jeapordy tends to be the highest for P excretion and piscivory.
-Given the local nature of species’ functional contributions, the determination of specific species-based conservation efforts at a global scale will fail to sustain coral reef functioning. 
-Rather, ecosystem functioning can be supported by local actions, taking into account the dominance and vulnerability, to avert the functional extinction of species [@Mccauley2015], while maintaining a high diversity on a global scale.
+Double jeopardy tends to be the highest for P excretion and piscivory. 
+Surprisingly, since fishing is known to heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory comes out as the least vulnerable of all five functions. 
+This is a result of the high variety of unique ecosystem roles within the large pool of herbivores. 
+Small herbivores are abundant and contribute a lot to herbivory, while they are not as vulnerable. 
+Large herbivores may be rarer, particularly in reefs surrounding regions with a high human density, yet they can play crucial roles with low redundancy (e.g. bioerosoion @Bellwood2011).
+Thus, our results reflect the overall vulnerability of functions such as herbivory, but in order to conserve specialized functional roles, it is necessary to consider the high vulnerability of specific species that play unique roles [@Bellwood2011].
+Given the local nature of species’ functional contributions, ecosystem functioning can be supported by local actions, taking into account the dominance and vulnerability, to avert the functional extinction of species [@Mccauley2015], while maintaining a high diversity on a global scale.
 
-Our results demonstrate the challenges of managing one of Earth’s most diverse and vulnerable ecosystems. 
-Maximizing ecosystem functioning is an important objective of contemporary conservation initiatives. 
+Our results quantitatively exemplify why it is challenging to manage Earth’s most diverse and vulnerable marine ecosystems. 
+Enhancing ecosystem functioning is an important objective of contemporary conservation initiatives [@Cinner2020]. 
 The functional trade-offs revealed between key ecosystem functions challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
 Traditionally, marine reserves have been the main conservation strategy for coral reefs [@Graham2020].
-While they provide benefits for biomass and herbivory, they provide little insurance for diversity in populated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
+While they provide benefits for biomass and herbivory, they provide little insurance for diversity in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
 Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
-Thus, it is nescessary to gauge reef “health” based on multiple, complementary, process-based functions [@Brandl2019front]. 
-Furthermore, individual reefs require local management plans to protect species with key roles for each function and community structure components, and the presence of multiple stakeholders may require the prioritisation of various functions based on local needs and stressors.
-Finally, as most species play an important role on a local scale, local management efforts should go hand in hand with global action to conserve the high diversity of species in addition to tackling climate change, the primary threath to coral reefs [@Bruno2019].
+Thus, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front]. 
+Furthermore, individual reefs require local management plans to protect species with key roles for each function, community structure components, and the presence of multiple stakeholders may require the prioritization of various functions based on local needs and stressors.
+Finally, as most species play an important role on a local scale, local management efforts should go hand in hand with global action to conserve the high diversity of species in addition to tackling climate change, the primary threat to coral reefs [@Bruno2019].
 
@@
 We posit that the answer cannot be rooted in a purely economic mindset that aims for the maximization of all functions. 
-Rather, a diverse community that supports intermediate levels of each function is ideal, with many species emerging as key local players.
+Over the past decades, there has been an increasing emphasis on multifunctionality, particularly in terrestrial ecology of plant communities.  
+Through the quantification of multiple functions, we exemplify that the concept of multifunctionality may not applicable to hyper-diverse coral reefs.  
+Acknowledging and quantifying the complexity of coral reef fish functions is a first step towards a better understanding of reef functioning and vulnerability at the global scale. 
+Additionally, there is a need to do this for other groups, such as invertebrates and cryptobenthic fishes that undoubtedly have an important contribution to turnover and fluxes of elements given their small body sizes [@Brandl2019science].
+Therefore, the majority of coral-reef ecosystem functioning remains to be characterized.
 In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring of multiple functions alongside biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].
@@
 Functions were log-transformed before standardisation.
-Dots represent the average of the effect, and filled lines indicate the 95% credible interval.
+Dots represent the average of the effect.
+Filled lines indicate the 95% credible interval, with some credible intervals being too small to visualize.
 Effects are not shown when their 95% CI intersects with zero.
@@
 
-![Figure 4: Vulnerability of species included in this study related to local dominance.
-Transparant bars represent the relative number of species in each category of vulnerability.
-Filled bars show the proportion of species that are locally dominant.
-A species is considered locally dominant if in any community, it contributes more to a function than 1 divided by the total number of species.](../figures/figure4_all_species.png)
+![Figure 4: Vulnerability of functions based on the cumulative vulnerability of the contribution of species to the five functions per community.
+Filled bars show the proportion of communities that belong to a certain category of vulnerability.
+Categories of vulnerability to fishing and climate change are defined using quantiles.
+Very low: <20%; Low: 20%-40%; Medium: 40%-60%; High: 60%-80%; Very high: > 80%.
+High vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are either high or very high.
+Similarly, low vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are either low or very low.](../output/plots/figure_4_vuln_com.png)
 
@@
 
-![Extended Data Figure 2: Fitted linear regression of each function with the log-transormed gravity to markets.
+![Extended Data Figure 2: Fitted linear regression of each function with the log-transormed gravity to fish markets, as a proxy for fishing pressure.
 Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

### 2020-08-20 R/functions_plots.R

@@ -269,8 +269,8 @@ make_fig2 <- function(commodels){
     geom_vline(xintercept = seq(1, 10 ,1) + .5, color = "lightgrey", 
                size = 0.5, linetype = 1, alpha = 0.7) +
     geom_hline(yintercept = 0, size = 1, color = "black") +
-    geom_linerange(aes(x = variable, ymin = 0, ymax = mean, color = model),
-                   position = position_dodge(.7), size = 0.5, linetype = 2) + 
+    # geom_linerange(aes(x = variable, ymin = 0, ymax = mean, color = model),
+    #                position = position_dodge(.7), size = 0.5, linetype = 2) + 
     geom_linerange(aes(x = variable, ymin = lq, ymax = uq, color = model),
                    position = position_dodge(.7), size = 1, linetype = 1) + 
     geom_point(aes(x = variable, y = mean, color = model), position = position_dodge(.7), size = 3) +

### 2020-08-20 R/play.R

@@ -740,6 +740,70 @@ pca_wild <-
   )
 pca_wild
 
+## pca with hotspots
+dpca_res<- inner_join(select(res2, transect_id, hot, cold, all_q), dpca)
+
+pca <-
+  ggplot(dpca_res) +
+  geom_hline(yintercept = 0, lty = 2, color = "grey") +
+  geom_vline(xintercept = 0, lty = 2, color = "grey") +
+  geom_point(aes(x = PC1, y = PC2), color = "grey" ,
+             data = dpca, alpha = 0.5, shape = 16)  +
+  geom_point(aes(x = PC1, y = PC2, color = "red"), 
+             data = dpca_res[dpca_res$hot == TRUE ,],  shape = 8, size = 3, alpha = 0.6)  +
+  geom_point(aes(x = PC1, y = PC2, color = "blue"), 
+             data = dpca_res[dpca_res$cold == TRUE ,],  shape = 3, size = 3, alpha = 0.6)  +
+  # stat_density_2d(aes(x = PC1, y = PC2, fill = bioregion, color = bioregion),
+  #                 alpha = 0.3 , geom = "polygon", data = dpca_wild, bins = 2) +
+  labs(x = "PC1", y = "PC2") +
+  
+  theme_minimal() +
+  theme(panel.grid = element_blank(), 
+        panel.border = element_rect(fill= "transparent")) +
+  scale_color_fish_d(option = "Scarus_quoyi",
+                     labels = c("CIP", "CP", "EP", "WA")) +
+  scale_fill_fish_d(option = "Scarus_quoyi",
+                    labels = c("CIP", "CP", "EP", "WA")) +
+  coord_equal() +
+  theme(
+    legend.position = c(0.99, .99),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(6, 6, 6, 6)
+  ) +
+  facet_wrap(~ bioregion)
+pca
+pca <-
+  ggplot(dpca_res) +
+  geom_hline(yintercept = 0, lty = 2, color = "grey") +
+  geom_vline(xintercept = 0, lty = 2, color = "grey") +
+  geom_point(aes(x = PC3, y = PC4), color = "grey" ,
+             data = dpca, alpha = 0.5, shape = 16)  +
+  geom_point(aes(x = PC3, y = PC4, color = "red"), 
[…]

### 2020-09-24 text/main.Rmd
commit before deep clean

@@
 
-# Trade-offs redefine the vulnerability of reef fish functions
+# Drivers and vulnerability of global coral reef fish functions
 
@@
 Burkepile, Jacob E.
-Allgeier, Katrina S.
-Munsterman, Fabien Morat, Alexandre Mercière, Yves Letourneur, Enrico L.
-Rezende, Graham J.
-Edgar, Rick D.
-Stuart-Smith, Jesús E.
-Arias-Gonzaléz, Alan M.
+Allgeier, Jesús E.
+Arias-Gonzaléz, Graham J.
+Edgar, Carlos E.
+L.
+Ferreira, Sergio R.
+Floeter, Alan M.
 Friedlander, Alison L.
-Green, Osmar J.
-Luiz,  F.
+Green, Michel Kulbicki, Yves Letourneur, Osmar J.
+Luiz, Alexandre Mercière, Fabien Morat, Katrina S.
+Munsterman, Enrico L.
+Rezende, F.
 A.
-Rodríguez‐Zaragoza, Laurent Vigliola, Michel Kulbicki, Sergio R.
-Floeter, Sébastien Villéger, Valeriano Parravicini
+Rodríguez‐Zaragoza, Rick D.
+Stuart-Smith, Laurent Vigliola, Sébastien Villéger, Valeriano Parravicini
 
-**Coral reefs flourish under nutrient-poor environments, and host a high diversity of fishes providing nutrition to millions of people [@Teh2013].
-Understanding the ability of coral reefs to maintain healthy functioning is essential to conserving coral reefs and the services they provide to humanity, especially under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017].
-Here, we characterize the predictors as well as the vulnerability of five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans.
-We demonstrate that critical trade-offs exist among functions, such as between biomass production and phosphorous cycling, with no single reef fish community sustaining high values for all five functions simultaneously.
-In addition, we reveal that there is a high degree of functional dominance across communities.
-However, the identity of these species varies significantly across reefs, with ~70% of all species contributing disproportionally to a function in a given community.
-Finally, we highlight unbalanced vulnerability to human stressors across functions.
-Our results introduce a conundrum for coral reef conservation, i.e. we cannot maximize all functions, and imply that the successful preservation of coral reef functioning requires both conserving high fish diversity globally, and applying locally administered actions.
-**
+**The high diversity and productivity of coral reefs, despite their location in nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013].
+Protecting reef function (cycling of elements) under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation.
+Here, we quantify five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans.
+We demonstrate that critical trade-offs exist among functions (e.g.
+biomass production and phosphorous cycling), and that no reef fish community worldwide can sustain high values for all five functions simultaneously.
+Further, functions tend to be dominated by few species, where on average ~12% of species provide more than 50% of a function.
+However, the identity of these species varies across reefs: ~70% of all species contribute disproportionally to functioning in a given community.
+Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef functioning.
+Our findings introduce a conundrum for coral reef conservation, i.e.we cannot maximize all functions, and stress the need for quantitative monitoring of multiple functions to make informed management decisions.**
 
-The flow of elements through biological communities represent key ecosystem functions that fuel all life on Earth [@Welti2017].
-There is a strong consensus on the importance of preserving these fluxes, also defined as ecosystem functions [@Welti2017].
-However, understanding the dynamics of multiple ecosystem functions simultaneously is challenging because the drivers, vulnerability, and trade-offs among functions are still poorly characterized, impeding informed management [@Brandl2019front].
-For millennia, humans have managed nature with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
-However, trade-offs likely exist among ecosystem functions with efforts to maximize one function possibly negatively impacting another (e.g. timber vs. erosion control) [@Tallis2008]. 
-To make informed management decisions that conserve ecosystem functioning, it is critical to quantify multiple functions simultaneously in order to understand the mechanisms that drive their potential trade-offs [@Rodriguez2006].
+The flow of elements through biological communities fuel all life on Earth [@Welti2017].
+There is now strong consensus on the importance of preserving these fluxes, often termed ecosystem functions [@Welti2017].
+For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
+However, in agro-ecological settings efforts to maximize one function have been shown to negatively impacting another (e.g.
+timber vs.
+erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
+Therefore, sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
+To make informed management decisions, it is critical to quantify multiple functions and their potential trade-offs [@Rodriguez2006]. 
+However, beyond well-studied ecosystems such as grasslands, quantifying multiple ecosystem functions simultaneously is challenging, and therefore trade-offs between functions, their drivers, and vulnerability are often poorly understood, impeding informed management [@Brandl2019front].
 
 Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans [@Teh2013]. 
-As coral reefs thrive in nutrient-poor waters, efficient nutrient recycling is key to their productivity [@Brandl2019science]. 
- However, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
-Over the past decade, severe biodiversity declines have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as fish standing biomass, and functional richness based on qualitative species traits [e.g.
+As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic productivity [@Brandl2019science]. 
+Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
+Over the past decade, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, fish standing biomass, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Consequently, we know little about the co-occurrence of functions and their drivers, which currently hinders our ability to provide information that could be useful to coral reef management in a rapidly changing world [@Allgeier2016].
+Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently hinders effective management [@Brandl2019front].
 
-Here, we integrate, for the first time, biogeochemistry and community ecology to advance understanding and conservation of the fluxes of nutrients that underpin reef functioning. 
-Specifically, we use a combination of novel data and phylogenetic extrapolation techniques to parametrize individual-level bioenergetic models which output five key ecosystem functions. 
-We apply these models for 1,010 reef fish species and integrate their output functions with community structure data from 9,118 reefs at 585 sites across the world’s coral reefs to: 
-(1) quantify nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory, 
-(2) determine if there are trade-offs among these functions, 
-(3) determine the ecological predictors of variation in ecosystem functions using Bayesian mixed models, 
-(4) estimate the contribution and dominance of different species to each function, and 
-(5) assess the vulnerability of these functions to climate change and fishing.
+Here, we integrate biogeochemistry and community ecology to advance our understanding of the fluxes of elements that underpin reef fish functioning. 
+Using species-specific data on basic organismal processes and phylogenetic extrapolation techniques, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
+We apply these models to 9,118 reef fish communities across 585 sites worldwide to: 
+(1) quantify reef fish functions and their trade-offs, 
+(2) extract the community- and species-level predictors of these functions, and 
+(3) gauge the vulnerability of reef fish functioning in the Anthropocene.
 
-Combining novel approaches enabled us to quantify five key ecosystem functions performed by fishes across the world's reefs for the first time, highlighting the functional variation that exists beyond biomass effects.
-Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and we observed a strong relationship between biomass and all five functions.
-Yet, correcting each function for biomass shows a high variability (Fig.
-1), and for communities with similar total fish biomass, different functions often varied by over two orders of magnitude (Extended Data Fig.
+Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers the functional variation that exists beyond biomass, the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front].
+Even though we observed a strong relationship between fish standing biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig.
+1), and for fish communities with similar biomass, functions tend to vary by over two orders of magnitude (Extended Data Fig.
 1a).
-Further, we revealed strong trade-offs among the different biomass-corrected functions (Fig.1, Extended Data Fig.
-1b).
-For example, communities with high herbivory rates or N excretion were negatively correlated with rates of P excretion.
-Strikingly, less than 3% of all communities had an above average value of biomass-corrected function for all five functions simultaneously, and not a single community reached maximum values (upper 10%) for all functions.
-As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here, i.e.
-while many reefs may stand out as hotspots for one function, they may also output less of other functions (Fig.
+Thus, monitoring biomass alone can obscure differences in community-level functioning. 
+Further, there are strong trade-offs among the different functions when taking out the effect of biomass (Fig.1, Extended Data Fig. 1b). 
+For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
+Strikingly, less than 3% of all communities had an above average biomass-corrected value for all five functions simultaneously, and not a single community reached maximum values (upper 10%) for all functions.
+As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here.
+While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig.
 1).
 
-To uncover what underpins the trade-offs between multiple functions on coral reefs, we explored the relationship of each function with ecological predictors describing fish community structure and representing the variation of fish traits that affect elemental fluxes [@Schiettekatte2020] including body size, trophic level, species richness, and age structure (expressed as immaturity) by fitting Bayesian mixed models (Fig.
+Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences.  
+First, we explored the relationship of each function with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
+body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
 2).
-We found that negative correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
+We found that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
 For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig.
@@
 @Allgeier2014).
-In contrast, biomass production is highest in communities dominated by small, immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
+In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
 Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
 On the other hand, fishes in early life stages that are highly dependent on phosphorus to grow, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
-These results vindicate the need to integrate size scaling and species-specific biological traits at the individual level with community ecology to understand ecosystem-wide elemental fluxes [@Schramski2015].
+These results emphasize the importance of fish community structure for ecosystem-wide functioning [@Schramski2015; @Allgeier2016].
 
-Human impacts have caused severe global declines of reef fish biomass and shifts in community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings demonstrate that these changes will continue to fundamentally alter ecosystem functioning on reefs.
-For example, intensive fishing leads to reductions in biomass, which particularly selects for large fishes and consequently truncates the size, age, and trophic structure of fish communities [@Graham2017].
-These effects can favor biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting phosphorus excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
-On the other hand, changes in community structure triggered by coral cover declines related to climate change are associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
-In contrast, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
-Higher N:P ratios can in fact favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
-This is particularly problematic when considered in conjunction with climate change, because phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
-Considering multiple functions thus paints a more nuanced and complete picture to help us understand how human-induced shifts in community structure affect coral reef health.
+Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning.   
+Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
+Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019]. 
+Therefore, we assessed the role of species by quantifying the degree to which they disproportionally induce (i.e. dominate) different functions for each community. 
+We demonstrate that for most communities, functions are consistently dominated by a few species (Fig.
+3b).
+This means for example that on average ~12% of the species inside a community contribute to more than 50% of a function.
+However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
+Thus, while there are almost no globally important species, most species are locally important.
+Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
+Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
+We demonstrate that while functional dominance is indeed prevalent, the identity of the dominant species is unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
 
-Alongside features of community structure, the vulnerability of specific species that play a dominant role affects the vulnerability of community-level functions to human stressors such as climate change and fishing.
-Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
-Further, abundant species can profoundly affect rates of functioning on the community level [@Ruttenberg2019; @Topor2019]. 
-Therefore, we assessed the role of species by quantified the degree of dominance per function for each community.
-The degree of dominance describes the extent to which a function is performed by a single or only a couple of species.
-We demonstrate that for most communities, functions are consistently dominated by a few species (Fig. 3b).
-We then asked if species consistently perform a key role when present across communities by quantifying the frequency of their dominance.
-Despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003], the identity of functionally-dominant species varied remarkably and the frequency of dominance per species tends to be low (Fig.
-3c).
-Consequently, while individual species that consistently perform a key role whenever present globally are rare, our results suggest that most species perform a key role in at least a few reefs. 
-Indeed, ~70% of all species contributed disproportionally to a function in at least one reef.
-Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
-We demonstrate that while dominance is indeed prevalent, the identity of the dominant species may be less predictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
+The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in the Anthropocene. 
+Exploitation and anthropogenic climate change have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs.
+For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017]. 
+These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
+On the other hand, climate change related declines in coral cover are associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
+Yet, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
+Higher N:P ratios may in fact favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
+This is particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
+Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in community structure affect coral reef functioning.
 
-As many species locally play a dominant role for one or more functions, the vulnerability of these functionally-dominant species heavily affects the vulnerability of the functions on the community scale.
-Species may be more vulnerable to fishing (e.g.
-large herbivores, predators) or to climate change through coral cover decline (e.g.
-butterfly fishes) [@Graham2011].
-By combining species-level vulnerability scores to fishing and climate change [@Graham2011] with the contributions of each species to the community-scale functions, we estimated the vulnerability of all five functions to both stressors.
-We demonstrate that vulnerability to fishing is relatively the highest for piscivory, followed by P excretion, while climate change vulnerability is the highest for P excretion, N excretion, and production (Fig.
-4).
-Double jeopardy tends to be the highest for P excretion and piscivory. 
-Surprisingly, since fishing is known to heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory comes out as the least vulnerable of all five functions. 
-This is a result of the high variety of unique ecosystem roles within the large pool of herbivores. 
-Small herbivores are abundant and contribute a lot to herbivory, while they are not as vulnerable. 
-Large herbivores may be rarer, particularly in reefs surrounding regions with a high human density, yet they can play crucial roles with low redundancy (e.g. bioerosoion @Bellwood2011).
-Thus, our results reflect the overall vulnerability of functions such as herbivory, but in order to conserve specialized functional roles, it is necessary to consider the high vulnerability of specific species that play unique roles [@Bellwood2011].
-Given the local nature of species’ functional contributions, ecosystem functioning can be supported by local actions, taking into account the dominance and vulnerability, to avert the functional extinction of species [@Mccauley2015], while maintaining a high diversity on a global scale.
+Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
+By combining species-level vulnerability scores to fishing and climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that vulnerability to fishing is highest for piscivory, followed by P excretion, while climate change vulnerability is the highest for P excretion, N excretion, and production (Fig.
+4), creating a potential double jeopardy of vulnerability for P excretion in particular.
+Surprisingly, although fishing pressure can heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
+This may be due to the high variability in unique ecosystem roles within the large pool of herbivorous fish species. 
+While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to become functionally extinct in regions with high human density [@Bellwood2012].
+While herbivores of all body sizes and functional groups are united in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
+Thus, our results reflect the overall vulnerability of functions, yet this doesn't exclude potential risk of functional extinction of unique roles by a small group of species, nested in a broad function (e.g.
+@Bellwood2011).
 
-Our results quantitatively exemplify why it is challenging to manage Earth’s most diverse and vulnerable marine ecosystems. 
-Enhancing ecosystem functioning is an important objective of contemporary conservation initiatives [@Cinner2020]. 
-The functional trade-offs revealed between key ecosystem functions challenges the feasibility of this approach and introduces a conundrum for coral reef conservation. 
-Traditionally, marine reserves have been the main conservation strategy for coral reefs [@Graham2020].
-While they provide benefits for biomass and herbivory, they provide little insurance for diversity in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
-Measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
-Thus, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front]. 
-Furthermore, individual reefs require local management plans to protect species with key roles for each function, community structure components, and the presence of multiple stakeholders may require the prioritization of various functions based on local needs and stressors.
-Finally, as most species play an important role on a local scale, local management efforts should go hand in hand with global action to conserve the high diversity of species in addition to tackling climate change, the primary threat to coral reefs [@Bruno2019].
+Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020]. 
+Even though increased fish biomass enhances function, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another.
+For example, marine reserves, which are the main conservation approach for coral reefs [@Graham2020], may provide benefits for herbivory, but they often offer little insurance for diversity in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
+Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
+Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may leed to informed decisions to prioritize certain functions based on local needs and stressors.
+Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of species identity and dominance at the local scale.
+While globally, conserving a high diversity of fishes is indeed beneficial to functioning, on the local scale, species richness only has minor effects on functions.
+Rather, community structure and the identity of dominant species tend to play an important role, which emphasizes the importance of monitoring common species to conserve ecosystem functioning [@Gaston2008].
+Still, as no species provides high contributions for all functions simultaneously, high species diversity enhances performance across multiple functions [@Duffy2009; @Zavaleta2010].
 
-Our results contribute to an ongoing discussion surrounding the question: what constitutes a healthy reef? 
-We posit that the answer cannot be rooted in a purely economic mindset that aims for the maximization of all functions. 
-Over the past decades, there has been an increasing emphasis on multifunctionality, particularly in terrestrial ecology of plant communities.  
-Through the quantification of multiple functions, we exemplify that the concept of multifunctionality may not applicable to hyper-diverse coral reefs.  
-Acknowledging and quantifying the complexity of coral reef fish functions is a first step towards a better understanding of reef functioning and vulnerability at the global scale. 
-Additionally, there is a need to do this for other groups, such as invertebrates and cryptobenthic fishes that undoubtedly have an important contribution to turnover and fluxes of elements given their small body sizes [@Brandl2019science].
-Therefore, the majority of coral-reef ecosystem functioning remains to be characterized.
-In light of the rapid degradation of coral reefs worldwide [@Hughes2017], quantitative monitoring of multiple functions alongside biomass is critical to create viable conservation targets and uphold coral reef functioning, as well as associated services to humanity, beyond the 21st century [@Brandl2019front].
+Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be fruitful. 
+While enhancing fish biomass is important, the variability of reef fish communities in the cycling of critical elements is striking. 
+Conserving these elemental fluxes in the 21st century will require a more nuanced approach to coral reef management.
 
@@
 Categories of vulnerability to fishing and climate change are defined using quantiles.
-Very low: <20%; Low: 20%-40%; Medium: 40%-60%; High: 60%-80%; Very high: > 80%.
-High vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are either high or very high.
-Similarly, low vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are either low or very low.](../output/plots/figure_4_vuln_com.png)
+Low: <20%; High: >80%.
+High vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are high.
+Similarly, low vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are low.](../output/plots/figure_4_vuln_com.png)
 

### 2020-09-24 text/methods.Rmd
commit before deep clean

@@
 Transects were carried out at a constant depth, parallel to the reef crest.
-We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize the bias related to the indentification of small individuals, and finally we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
+We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize the bias related to the identification of small individuals, and finally we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
 The dataset then included 1110 species that belong to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
@@
 
-\noindent Finally, we quantified baseline values for each function and assessed the occurrence of communities that reach baseline values for each function.
-Based on the biomass reference for a healthy reef of ~100g/m2 (@MacNeil2015), we predicted the baseline for each function for the full range of sst's.
-Then, for all communities, we quantified whether or not the community had higher values for all functions compared to their baselines.
-Using this logical variable, we fitted a Bernoulli model with a logit-link to predict the probability of having all five functions above their threshold in relation to biomass and sea surface temperature, similar to the model specified above.
-
 ## 4. Effect of community structure on ecosystem functions 
 \noindent To investigate the effect of the community structure accounting for the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
-These variables discribe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
+These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
 Specifically, we took the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
@@
 
-## 6. Species vulnerability to fishing and clilate change
+## 6. Vulnerability to fishing and climate change
 For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
@@
 (2005) @Cheung2005.
+Then, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
+Finally, we calculated proportions of communities with either high (upper quartile) or low (lower quartile) vulnerability for each function.
+We also report the proportion of communities that have high or low vulnerability scores for both climate change and fishing.
 

### 2020-09-24 R/functions_analysis.R

@@ -157,6 +157,41 @@ run_commodels <- function(summary_transect_complete){
   return(result)
 }
 
+####### community models absolute values ######
+run_commodels_abs <- function(summary_transect_complete){
+  
+  flux <- summary_transect_complete
+  
+  flux$logbiomass <- log(flux$biomass_tot)
+  
+  fit_Fn <- brm(log(Fn) ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+                     size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
+                   data = flux, chain = 3, cores = 1)
+  
+  fit_Fp <- brm(log(Fp)~ ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+                  size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
+                   data = flux, chain = 3, cores = 1)
+  
+  fit_Gc <- brm(log(Gc) ~ ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+                  size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
+                   data = flux, chain = 3, cores = 1)
+  
+  fit_Iherb <- brm(log(I_herb) ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+                     size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
+                      data = flux[flux$I_herb>0,], chain = 3, cores = 1)
+  
+  fit_Ipisc <- brm(log(I_pisc) ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+                     size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
+                      data = flux[flux$I_pisc>0,], chain = 3, cores = 1)
+  
+  result <- list(fit_Fn, fit_Fp, fit_Gc, fit_Iherb, fit_Ipisc)
+  
+  lapply(result, function(x){
+    brms::bayes_R2(x)
+  })
+  
+  return(result)
+}
 
 ####### contributions ######
 

### 2020-09-24 R/functions_plots.R

@@ -250,14 +250,14 @@ make_fig2 <- function(commodels){
   result <- mutate(result, diff = (uq > 0 & lq < 0)) 
   
   # Specify importance of variables per slope values
-  importance <- group_by(result, variable) %>%
-    summarise(tot = max(abs(mean))) 
+  tot <- group_by(result, model) %>%
+    summarise(tot = sum(abs(mean))) 
   
   # filter out variables that we don't need 
   result <- result %>%
     dplyr::filter(!variable == "b_Intercept") %>%
-    left_join(importance) %>% 
-    mutate(variable = fct_reorder(variable, tot)) %>%
+    left_join(tot) %>% 
+    #mutate(variable = fct_reorder(variable, tot)) %>%
     filter(diff == FALSE) %>%
     filter(!variable == "b_standardlogbiomass") %>%
     filter(!variable == "b_standardmean") 
@@ -280,10 +280,12 @@ make_fig2 <- function(commodels){
                        labels = c("N excretion", "P excretion", "Production", "Herbivory", "Piscivory"),
                        name = "")  + 
     labs(y = "Effect size", x = "") +
-    scale_x_discrete(labels = c(  "Immaturity (2.5%)", "Size (median)",  "Immaturity (97.5%)", 
-                                  "Size (2.5%)", "Richness",  "Immaturity (median)",
-                                  "Size (97.5%)", "Trophic level (2.5%)",  "Trophic level (median)",
-                                  "Trophic level (97.5%)")) +
+    scale_x_discrete(
+      labels = c(   "Immaturity (median)", "Immaturity (2.5%)",  "Immaturity (97.5%)",
+                                  "Richness",  "Size (median)", "Size (2.5%)",
+                                  "Size (97.5%)",  "Trophic level (median)", "Trophic level (2.5%)",
+                                  "Trophic level (97.5%)")
+      ) +
    
     theme(legend.position = "bottom", axis.text = element_text(size = 12, color = "black"),
           axis.title = element_text(size = 12), legend.text = element_text(size = 12), 

### 2020-09-24 R/functions_wrangling.R

@@ -407,7 +407,7 @@ get_herb_pisc <- function(tfish, cnpflux, params, summary_transect){
 tfish <- left_join(tfish, unique(dplyr::select(cnpflux, species, v_m, size_cm, (ends_with("_median"))))) %>% 
   left_join(select(params, Species, v_m, diet_cat, Dc_m)) %>% 
   mutate(Ic = Ic_median * abun) %>%
-  mutate(I = 100 * Ic/Dc_m/area) # convert to dry mass
+  mutate(I = Ic/area) 
 
 
 tfish$herb <- "no"

### 2020-09-24 R/play.R

@@ -3531,6 +3531,7 @@ loadd(vulnerability)
 loadd(contributions)
 loadd(herb_pisc)
 loadd(summary_transect)
+loadd(residuals)
 
 
 con <- left_join(contributions, vulnerability) %>%
@@ -3554,9 +3555,6 @@ con_long <- con %>%#/sum(vuln_climate[I_pisc_p > 0], na.rm = TRUE)) %>%
   filter(value>0) %>%
   pivot_wider(names_from = impact, values_from = value)
 
-ggplot(con_long) +
-  geom_boxplot(aes(x = fun, y = (value))) +
-  facet_wrap(~impact)
 
 con <- left_join(con, unique(select(ungroup(contributions), transect_id, sites, locality, lat, lon)))
 
@@ -3565,25 +3563,6 @@ test <- filter(con) %>%
   summarise_if(is.numeric, median) %>%
   group_by(locality) %>%
   summarise_if(is.numeric, median)
-
-ggplot(test) + 
-  geom_sf(data = world, color = NA, fill = "lightgrey") +
-  geom_point(aes(x = lon, y = lat, color = (value), 
-                 size = get_scores(value)),  alpha = 0.8,
-             position = position_jitter(0,0), shape = 16) +
-  # geom_point(aes(x = lon, y = lat),  alpha = 0.7,
-  #            shape = 1, size = 4,
-  #            data = filter(location_effect, r_loc_Fp > quantile(location_effect$r_loc_Fp, 0.95, na.rm = TRUE))) +
-  scale_color_gradient(low = "green", high = "red", name = "") +
-  coord_sf(ylim = c(-35, 35), expand = FALSE) +
-  geom_text(aes(x = -175, y = 30, label = "P excretion (g P/m²day)"), size = 3, hjust = 0) +
-  scale_size_continuous(range = c(0.5, 3), guide = FALSE) +
-  theme_worldmap() + 
-  theme(legend.position = "bottom", 
-        axis.text.x = element_blank(), 
-        axis.ticks.x = element_blank(),
-        plot.title = element_text(vjust = -8, hjust = 0.005),
-        plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), units = , "cm"))
 
 
 res_long <- pivot_longer(residuals, 2:6, values_to = "residual") %>%
@@ -3638,14 +3617,14 @@ q_cl <- quantile(c(
[…]

### 2020-09-29 R/functions_analysis.R
cleaned up unnescesary functions

@@ -237,84 +237,6 @@ get_vuln <- function(sptl){
 }
 
 
-plot_con_vuln_all <- function(contributions_sp_loc_occ, vulnerability){
-  
-  con <- left_join(contributions_sp_loc_occ, vulnerability) %>% drop_na(vuln_fi, vuln_climate)
-  
-  plot_con_vuln <- function(var, ylab){
-    
-    data <- con
-    data <- data %>% filter(!.data[[var]] == 0)
-    probs <- c(0.05, 0.25, 0.75, 0.95)
-    quantiles <- quantile(data[[var]], prob = probs, na.rm = TRUE)
-    data$quant <- factor(findInterval(data[[var]], quantiles))
-    
-    data$density1 <- fields::interp.surface(
-      MASS::kde2d(data[["vuln_fi"]], data[[var]]), as.data.frame(data[,c("vuln_fi", var)]))
-    data$density2 <- fields::interp.surface(
-      MASS::kde2d(data[["vuln_climate"]], data[[var]]), as.data.frame(data[,c("vuln_climate", var)]))
-    
-    data <- filter(data, .data[[var]] > 0.00001)
-    
-    p1 <-
-      ggplot(data) +
-      geom_point(aes(x = 100 * vuln_fi, y = 100 * .data[[var]], size = rel_occ, color = quant, alpha = 1/density1)) +
-      #geom_density2d(aes(x = 100 * vuln_fi, y = 100 * .data[[var]]), color = "grey") +   
-      geom_hline(aes(yintercept = 100 * (median(.data[[var]]))), linetype = 2, color = "grey", size = 1) +
-      geom_vline(aes(xintercept =  100 *  median(con$vuln_fi, na.rm = TRUE) ), linetype = 2,  color = "grey", size = 1) +
-      scale_x_continuous(trans = "log", breaks = c(15, 25, 50, 100)) +
-      scale_y_continuous(trans = "log", breaks = c(0.0009, 0.04, 2, 100)) +
-      scale_alpha(range = c(.25, .75) ) +
-      xlab("Vulnerability to fishing") +
-      ylab(ylab) +
-      labs(color = "Quantile", size = "Relative occurrence") +
-      scale_color_fish_d("Hypsypops_rubicundus", begin = 0 ,
[…]

### 2020-09-29 R/functions_plots.R

@@ -456,99 +456,174 @@ make_fig3 <- function(contributions, herb_pisc, degree_dominance, freq_dominance
   
 }
 
-make_fig4 <- function(spi_vuln){
-  
-  # barplots for each function with labels at angles
-  
-  bp1 <-
-    ggplot(filter(spi_vuln, vulncat == "vuln_high") %>% drop_na()) +
-    geom_bar(aes(x = name, y = n_prop, fill = name), stat = "identity", alpha = 0.5) +
-    geom_bar(aes(x = name, y = ep_prop, fill = name), stat = "identity") +
-    geom_text(aes(x = name, y = n_prop + 0.1, label = paste0(round(perc), "%")), angle = 45) +
-    scale_fill_fish_d(option = "Callanthias_australis",
-                      labels = c("N excretion", "P excretion",
-                                 "Production", "Herbivory", "Piscivory"),
-                      name = "Function") +
-    scale_y_continuous(limits = c(0, 1)) +
-    theme_void() +
-    theme(legend.position = "none",
-          text = element_text(angle = 45), plot.margin = unit(c(0,0,0,0), "cm")
-    )
-  ggsave("output/plots/fig4_glob_vuln_high.png", bp1, width = 4, height = 4)
-  
-  bp2 <-
-    ggplot(filter(spi_vuln, vulncat == "vuln_cli") %>% drop_na()) +
-    geom_bar(aes(x = name, y = n_prop, fill = name), stat = "identity", alpha = 0.5) +
-    geom_bar(aes(x = name, y = ep_prop, fill = name), stat = "identity") +
-    geom_text(aes(x = name, y = n_prop + 0.1, label = paste0(round(perc), "%")), angle = 135) +
-    scale_fill_fish_d(option = "Callanthias_australis",
-                      labels = c("N excretion", "P excretion",
-                                 "Production", "Herbivory", "Piscivory"),
-                      name = "Function") +
-    scale_y_continuous(limits = c(0, 1)) +
-    theme_void() +
-    theme(legend.position = "none", plot.margin = unit(c(0,0,0,0), "cm")
-    )
-  
-  ggsave("output/plots/fig4_glob_vuln_cc.png", bp2, width = 4, height = 4)
-  
-  bp3 <-
[…]

### 2020-09-29 R/functions_wrangling.R

@@ -55,12 +55,47 @@ get_cnp <- function(){
 
 ##### cnpdiet #####
 get_cnpdiet <- function(){
-  cnpdiet <- read.csv("data/cnpdiet_glob.csv") 
-  cnpdiet[,3:8] <- cnpdiet[,3:8] * 100
-  colnames(cnpdiet) <-
+  
+  cnpdiet <- read.csv("data/cnp_per_trophic_guild_1000draws.csv")
+  diet <- read.csv("data/extrapolation_trophic_guilds.csv")
+  
+  diets <- diet %>%
+    select(family, species, intersect(ends_with("_m"), starts_with("p"))) %>%
+    pivot_longer(cols = intersect(ends_with("_m"), starts_with("p")),
+                 names_to = "pred_cat", values_to = "probability") %>%
+    mutate(pred_cat = as.factor(pred_cat)) %>%
+    mutate(pred_cat = fct_recode(pred_cat, 
+                                 "1" = "p1_m",
+                                 "2" = "p2_m",
+                                 "3" = "p3_m",
+                                 "4" = "p4_m",
+                                 "5" = "p5_m",
+                                 "6" = "p6_m",
+                                 "7" = "p7_m",
+                                 "8" = "p8_m")) %>%
+    right_join(mutate(cnpdiet, pred_cat = as.factor(pred_cat)))
+  
+  result <- diets %>%
+    group_by(family, species, draw) %>%
+    summarise(c = sum(probability * c)/100,
+              n = sum(probability * n)/100,
+              p = sum(probability * p)/100) %>%
+    ungroup() %>%
+    group_by(family, species) %>%
+    summarise(c_m = mean(c), c_sd = sd(c),
+              n_m = mean(n), n_sd = sd(n),
+              p_m = mean(p), p_sd = sd(p)) 
+  
+  result <- result %>% 
+    left_join(select(diet, species, diet_cat = trophic_guild_predicted)) %>%
+    ungroup()
+  
+  result[,3:8] <- result[,3:8] * 100
+  colnames(result) <-
     c("family", "species", "Dc_m", "Dc_sd", 
       "Dn_m", "Dn_sd", "Dp_m", "Dp_sd", "diet_cat")
-  return(cnpdiet)
+  
+  return(result)
 }
 
 ##### growth #####
[…]

### 2020-09-29 R/packages.R

@@ -18,6 +18,6 @@ library(forcats)
 library(ggrepel)
 library(tidyr)
 library(readr)
-
+library(Rcpp)
 
 Sys.setlocale("LC_MESSAGES", "en_US.utf8")

### 2020-09-29 R/plan.R

@@ -39,7 +39,7 @@ plan <- drake_plan(
   contributions = get_contributions(tfish, cnpflux, params, summary_transect),
   sp_loc = unique(select(ungroup(contributions), bioregion, species)),
   
-  # herbivory, piscivory --> in g dry mass
+  # herbivory, piscivory 
   herb_pisc = get_herb_pisc(tfish, cnpflux, params, summary_transect),
   
   # combine summary data, sst 
@@ -57,31 +57,6 @@ plan <- drake_plan(
   # run models proc ~ community vars
   commodels = run_commodels(summary_transect_complete),
   
-  # run models to get relative contribution of each ecosystem process
-  #models_contributions_Fp = fit_contribution_Fp(contributions, sp_loc),
-  #models_contributions_Fn = fit_contribution_Fn(contributions, sp_loc),
-  #models_contributions_Fc = fit_contribution_Fc(contributions, sp_loc),
-  #models_contributions_Ic = fit_contribution_Ic(contributions, sp_loc),
-  #models_contributions_Gc = fit_contribution_Gc(contributions, sp_loc),
-  
-  # run models to get relative contribution herbivory piscivory
-  #models_contributions_I_herb = fit_contribution_I_herb(herb_pisc, sp_loc),
-  #models_contributions_I_pisc = fit_contribution_I_pisc(herb_pisc, sp_loc),
-  
-  # extract contributions from model
-  # contributions_Fn = extract_contr(models_contributions_Fn),
-  # contributions_Fp = extract_contr(models_contributions_Fp),
-  # contributions_Gc = extract_contr(models_contributions_Gc),
-  # contributions_I_herb = extract_contr(models_contributions_I_herb),
-  # contributions_I_pisc = extract_contr(models_contributions_I_pisc),
-
-  # combine contributions
-  # contributions_sp_loc = combine_contributions(
-  #   sp_loc, contributions_Fn, contributions_Fp,
-  #   contributions_Gc, contributions_I_herb, contributions_I_pisc, herb_pisc),
-
-  #contributions_sp_loc_occ = add_occurence(contributions, contributions_sp_loc, herb_pisc),
-  
   ##### contribution analysis #####
   contr_family = get_cf(contributions, herb_pisc),
   degree_dominance = get_dd(contributions, herb_pisc),
@@ -93,19 +68,28 @@ plan <- drake_plan(
   spi_vuln = get_spi_vuln(sp_importance, vulnerability),
[…]

### 2020-09-29 R/play.R

@@ -3664,7 +3664,7 @@ ggplot(con_long[con_long$fun == "Fp",]) +
   geom_point(aes(x = cl, y = fi), size = 1, alpha = 0.1) +
   theme_bw()
 
-test2_fi <- con_long %>%
+prop_fi <- con_long %>%
   left_join(res_long) %>%
   left_join(vu) %>%
   mutate(cat_fi = case_when(fi > q_fi[4] ~ "High",
@@ -3679,7 +3679,7 @@ test2_fi <- con_long %>%
   mutate(ntot_fi = sum(n_fi)) %>%
   mutate(prop_high_fi = n_high_fi / ntot_fi, prop_fi = n_fi/ntot_fi) %>%
   mutate(cat = factor(cat_fi, levels = c("Very low", "Low", "Medium", "High", "Very high")))
-test2_cl <- con_long %>%
+prop_cl <- con_long %>%
   left_join(res_long) %>%
   left_join(vu) %>%
   mutate(cat_cl = case_when(cl > q_cl[4] ~ "High",
@@ -3695,7 +3695,7 @@ test2_cl <- con_long %>%
   mutate(prop_high_cl = n_high_cl / ntot_cl, prop_cl = n_cl/ntot_cl) %>%
   mutate(cat = factor(cat_cl, levels = c("Very low", "Low", "Medium", "High", "Very high")))
 
-p1 <- ggplot(test2_fi[!test2_fi$cat_fi == "Medium",]) +
+p1 <- ggplot(prop_fi[!prop_fi$cat_fi == "Medium",]) +
   # geom_bar(aes(x = cat_fi, y = -(prop - prop_high), fill = fun), 
   #          alpha = 0.5, stat = "identity", position = "dodge") +
   geom_bar(aes(x = cat, y = prop_fi, fill = fun), 
@@ -3713,7 +3713,7 @@ p1 <- ggplot(test2_fi[!test2_fi$cat_fi == "Medium",]) +
         panel.grid.minor = element_blank(), legend.position = "top",
         text = element_text(size = 12))  
 
-p2 <- ggplot(test2_cl[!test2_cl$cat_cl == "Medium",]) +
+p2 <- ggplot(prop_cl[!prop_cl$cat_cl == "Medium",]) +
   # geom_bar(aes(x = cat_cl, y = -(prop - prop_high), fill = fun), 
   #          alpha = 0.5, stat = "identity", position = "dodge") +
   geom_bar(aes(x = cat, y = prop_cl, fill = fun), 

### 2020-09-29 _drake.R
update make

@@ -4,4 +4,9 @@ source("R/functions_analysis.R") # defines the create_plot() function
 source("R/functions_plots.R") # defines the create_plot() function
 source("R/plan.R")      # creates the drake plan
 
-config <- drake_config(plan, lock_envir = FALSE)
+config <- drake_config(plan,
+                       lock_envir = FALSE,
+                       lock_cache = FALSE,
+                       garbage_collection = TRUE,
+                       memory_strategy = "autoclean",
+                       history = FALSE)

### 2020-10-01 text/main.Rmd
updates comemnts rick and rerun aanlysis

@@
 biomass production and phosphorous cycling), and that no reef fish community worldwide can sustain high values for all five functions simultaneously.
-Further, functions tend to be dominated by few species, where on average ~12% of species provide more than 50% of a function.
-However, the identity of these species varies across reefs: ~70% of all species contribute disproportionally to functioning in a given community.
-Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef functioning.
-Our findings introduce a conundrum for coral reef conservation, i.e.we cannot maximize all functions, and stress the need for quantitative monitoring of multiple functions to make informed management decisions.**
+Further, functions tend to be dominated by few species, where on average ~12% of species in a community provide more than 50% of a function.
+However, despite such local dominance of functions by few species, most species were important somewhere; ~70% of all species contribute disproportionally to functioning in at least one local community.
+Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystems.
+Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions, so we stress the need for quantitative monitoring of multiple functions to make informed management decisions.**
 
@@
 For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
-However, in agro-ecological settings efforts to maximize one function have been shown to negatively impacting another (e.g.
+Sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
+However, in agro-ecological settings efforts to maximize one function have been shown to negatively impact another (e.g.
 timber vs.
 erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
-Therefore, sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
-To make informed management decisions, it is critical to quantify multiple functions and their potential trade-offs [@Rodriguez2006]. 
-However, beyond well-studied ecosystems such as grasslands, quantifying multiple ecosystem functions simultaneously is challenging, and therefore trade-offs between functions, their drivers, and vulnerability are often poorly understood, impeding informed management [@Brandl2019front].
+An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging. 
+Therefore, trade-offs between functions, their drivers, and vulnerability are poorly understood for many ecosystems [@Brandl2019front].
 
@@
 Over the past decade, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, fish standing biomass, or functional richness based on qualitative species traits [e.g.
+Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
@@
 1a).
-Thus, monitoring biomass alone can obscure differences in community-level functioning. 
+Thus, considering biomass alone can obscure differences in community-level functioning. 
 Further, there are strong trade-offs among the different functions when taking out the effect of biomass (Fig.1, Extended Data Fig. 1b). 
 For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
-Strikingly, less than 3% of all communities had an above average biomass-corrected value for all five functions simultaneously, and not a single community reached maximum values (upper 10%) for all functions.
+Strikingly, not a single community reached high biomass-corrected rates (upper 10% across all communities) for all functions. 
 As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here.
@@
 Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences. 
-First, we explored the relationship of each function with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
+First, we explored the relationship of each function on the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
 body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
@@
 3b).
-This means for example that on average ~12% of the species inside a community contribute to more than 50% of a function.
+This means for example that on average ~12% of the species in a community contribute to more than 50% of a function.
 However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
-Thus, while there are almost no globally important species, most species are locally important.
+Thus, while there are almost no globally important species for a given function, most species are locally important somewhere.
 Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
 Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
-We demonstrate that while functional dominance is indeed prevalent, the identity of the dominant species is unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
+Our results imply that while functional dominance is indeed prevalent, the identity of the dominant species can be unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
 
@@
 These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
-On the other hand, climate change related declines in coral cover are associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
+On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
 Yet, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
@@
 This is particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
-Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in community structure affect coral reef functioning.
+Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect coral reef ecosystems.
 
 Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
-By combining species-level vulnerability scores to fishing and climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that vulnerability to fishing is highest for piscivory, followed by P excretion, while climate change vulnerability is the highest for P excretion, N excretion, and production (Fig.
-4), creating a potential double jeopardy of vulnerability for P excretion in particular.
+By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion, while loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig.
+4).
+Fishing and loss of live corals both appear to impact species important for P excretion.
 Surprisingly, although fishing pressure can heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
@@
 While herbivores of all body sizes and functional groups are united in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
-Thus, our results reflect the overall vulnerability of functions, yet this doesn't exclude potential risk of functional extinction of unique roles by a small group of species, nested in a broad function (e.g.
+Thus, our results reflect the overall vulnerability of functions, yet does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g.
 @Bellwood2011).
@@
 Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may leed to informed decisions to prioritize certain functions based on local needs and stressors.
-Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of species identity and dominance at the local scale.
-While globally, conserving a high diversity of fishes is indeed beneficial to functioning, on the local scale, species richness only has minor effects on functions.
-Rather, community structure and the identity of dominant species tend to play an important role, which emphasizes the importance of monitoring common species to conserve ecosystem functioning [@Gaston2008].
-Still, as no species provides high contributions for all functions simultaneously, high species diversity enhances performance across multiple functions [@Duffy2009; @Zavaleta2010].
+Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species identity at the local scale.
+While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales.
+Rather, it may be beta-diversity and local differences in community structure that are most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
 
-Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be fruitful. 
-While enhancing fish biomass is important, the variability of reef fish communities in the cycling of critical elements is striking. 
+Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be possible 
+While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking. 
 Conserving these elemental fluxes in the 21st century will require a more nuanced approach to coral reef management.

### 2020-10-01 R/functions_plots.R

@@ -257,20 +257,29 @@ make_fig2 <- function(commodels){
   result <- result %>%
     dplyr::filter(!variable == "b_Intercept") %>%
     left_join(tot) %>% 
-    #mutate(variable = fct_reorder(variable, tot)) %>%
     filter(diff == FALSE) %>%
     filter(!variable == "b_standardlogbiomass") %>%
-    filter(!variable == "b_standardmean") 
+    filter(!variable == "b_standardmean") %>%
+    mutate(variable = fct_relevel(variable, 
+                                  "b_standardimm_q1",
+                                  "b_standardimm_m",
+                                  "b_standardimm_q3",
+                                  "b_standardsize_q1",
+                                  "b_standardsize_m",
+                                  "b_standardsize_q3",
+                                  "b_standardtroph_q1",
+                                  "b_standardtroph_m",
+                                  "b_standardtroph_q3",
+                                  "b_standardnspec"
+                                  ))
     
   
   # plot
   slopes <-
     ggplot(result) +
-    geom_vline(xintercept = seq(1, 10 ,1) + .5, color = "lightgrey", 
+    geom_vline(xintercept = seq(1, 10 ,1) + .5, color = "lightgrey",
                size = 0.5, linetype = 1, alpha = 0.7) +
     geom_hline(yintercept = 0, size = 1, color = "black") +
-    # geom_linerange(aes(x = variable, ymin = 0, ymax = mean, color = model),
-    #                position = position_dodge(.7), size = 0.5, linetype = 2) + 
     geom_linerange(aes(x = variable, ymin = lq, ymax = uq, color = model),
                    position = position_dodge(.7), size = 1, linetype = 1) + 
     geom_point(aes(x = variable, y = mean, color = model), position = position_dodge(.7), size = 3) +
@@ -281,10 +290,10 @@ make_fig2 <- function(commodels){
                        name = "")  + 
     labs(y = "Effect size", x = "") +
     scale_x_discrete(
-      labels = c(   "Immaturity (median)", "Immaturity (2.5%)",  "Immaturity (97.5%)",
-                                  "Richness",  "Size (median)", "Size (2.5%)",
-                                  "Size (97.5%)",  "Trophic level (median)", "Trophic level (2.5%)",
-                                  "Trophic level (97.5%)")
+      labels = rev(c( "Richness", "Trophic level (97.5%)", "Trophic level (median)", "Trophic level (2.5%)",
[…]

### 2020-10-01 R/functions_wrangling.R

@@ -56,15 +56,17 @@ get_cnp <- function(){
 ##### cnpdiet #####
 get_cnpdiet <- function(){
   
-  cnpdiet <- read.csv("data/cnp_per_trophic_guild_1000draws.csv")
-  diet <- read.csv("data/extrapolation_trophic_guilds.csv")
+  cnpdiet <- read.csv("data/cnp_per_trophic_guild_1000draws.csv") %>%
+    rename(trophic_guild_predicted = pred_cat)
+  diet <- read.csv("data/extrapolation_trophic_guilds.csv") 
+  
   
   diets <- diet %>%
     select(family, species, intersect(ends_with("_m"), starts_with("p"))) %>%
     pivot_longer(cols = intersect(ends_with("_m"), starts_with("p")),
-                 names_to = "pred_cat", values_to = "probability") %>%
-    mutate(pred_cat = as.factor(pred_cat)) %>%
-    mutate(pred_cat = fct_recode(pred_cat, 
+                 names_to = "trophic_guild_predicted", values_to = "probability") %>%
+    mutate(trophic_guild_predicted = as.factor(trophic_guild_predicted)) %>%
+    mutate(trophic_guild_predicted = fct_recode(trophic_guild_predicted, 
                                  "1" = "p1_m",
                                  "2" = "p2_m",
                                  "3" = "p3_m",
@@ -73,7 +75,7 @@ get_cnpdiet <- function(){
                                  "6" = "p6_m",
                                  "7" = "p7_m",
                                  "8" = "p8_m")) %>%
-    right_join(mutate(cnpdiet, pred_cat = as.factor(pred_cat)))
+    right_join(mutate(cnpdiet, trophic_guild_predicted = as.factor(trophic_guild_predicted)))
   
   result <- diets %>%
     group_by(family, species, draw) %>%
@@ -86,14 +88,14 @@ get_cnpdiet <- function(){
               n_m = mean(n), n_sd = sd(n),
               p_m = mean(p), p_sd = sd(p)) 
   
-  result <- result %>% 
-    left_join(select(diet, species, diet_cat = trophic_guild_predicted)) %>%
+  result <- ungroup(result) %>% 
[…]

### 2020-10-01 _drake.R

@@ -4,9 +4,11 @@ source("R/functions_analysis.R") # defines the create_plot() function
 source("R/functions_plots.R") # defines the create_plot() function
 source("R/plan.R")      # creates the drake plan
 
+
+future::plan(future.callr::callr)
+
 config <- drake_config(plan,
                        lock_envir = FALSE,
-                       lock_cache = FALSE,
                        garbage_collection = TRUE,
                        memory_strategy = "autoclean",
                        history = FALSE)

### 2020-10-01 R/functions_wrangling.R
before server shut down

@@ -37,7 +37,7 @@ get_metpar <- function(kmax, sptl){
   colnames(spt) <- c("sst", "Family")
   
   param <- left_join(spt, metpar)
-  param$B0_adj <- 
+  param$B0_adj <- 0.1 *   # adjusting unit
     param$B0 * exp(0.59 / 8.62e-5 * (1 / (28 + 273.15) - 1 / (param$sst + 273.15)))
   metpar <- dplyr::select(param, Family, sst,
                    alpha_m = alpha, alpha_sd,

### 2020-10-01 R/play.R

@@ -4078,4 +4078,12 @@ plot(data$x, data$y)
 library(brms)
 ftest <- brm(y ~ x, data = data)
 
+##########" test species ######
+loadd(cnpflux)
+loadd(cnpdiet)
+
+test <- left_join(cnpflux, cnpdiet)
+
+
+
 

### 2020-10-01 R/functions_wrangling.R
fixed f0 parameter vallue

@@ -37,7 +37,8 @@ get_metpar <- function(kmax, sptl){
   colnames(spt) <- c("sst", "Family")
   
   param <- left_join(spt, metpar)
-  param$B0_adj <- 0.1 *   # adjusting unit
+  # temperature adjustment of metabolic constant 
+  param$B0_adj <- 
     param$B0 * exp(0.59 / 8.62e-5 * (1 / (28 + 273.15) - 1 / (param$sst + 273.15)))
   metpar <- dplyr::select(param, Family, sst,
                    alpha_m = alpha, alpha_sd,

### 2020-10-02 text/main.Rmd
some edits from comments LV

@@
 Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
-Over the past decade, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+Over the past decades, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
 Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently hinders effective management [@Brandl2019front].
+Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently limits effective management [@Brandl2019front].
 
@@
 Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
+For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
 Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019]. 
@@
 3b).
-This means for example that on average ~12% of the species in a community contribute to more than 50% of a function.
+This means for example that on average ~12% of the species in a local community contribute to more than 50% of a function.
 However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
@@
 Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
-Our results imply that while functional dominance is indeed prevalent, the identity of the dominant species can be unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
+Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
 
@@
 
-Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be possible 
+Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be possible. 
 While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking. 

### 2020-10-02 text/suppl_methods.Rmd
some edits from comments LV

@@
 
-We then used a back-calculation procedure to estimate fish length at previous ages, modified to also quantify the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
+We then used the Modified Fry back-calculation model (MF) [@Vigliola2000].
+to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
 
@@
 
-\noindent We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.
+\noindent The CNP\% content of organisms is known to be highly conserved within families (REF).
+We therefore use phylogeny to extrapolate these values.
+We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.
 
@@
 We then took the average and standard deviation across all 1000 draws.
+While we recognize the bias of using diet CNP\% estimates of a dataset in one region, we argue that variability between food categories e.g.
+animal material and primary producers is likely to be higher than regional differences within trophic categorizations.
+Further, as the used trophic guild classification includes probabilities to belong to each group, variation is included when the trophic categorization is not well known.
+For example, if a species has a 50% probability to be a herbivore and a 50% probability to be a sessile invertivore this uncertainty will be reflected the estimation of the diet CNP\%.
 
-### 4 Metabolic parameters    
+## 4 Metabolic parameters    
 ### 4.1 Data collection    

### 2020-10-05 text/main.Rmd
text edits

@@
 
-**The high diversity and productivity of coral reefs, despite their location in nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013].
+Affiliations
+
+A. Green: 
+Red Sea Research Center, King Abdullah University of Science and Technology 
+Thuwal 23955-6900, Saudi Arabia
+
+K.S. Munsterman: 
+Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109, USA
+
+**The high diversity and productivity of coral reefs, despite their location in generally nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013].
 Protecting reef function (cycling of elements) under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation.
@@
 However, despite such local dominance of functions by few species, most species were important somewhere; ~70% of all species contribute disproportionally to functioning in at least one local community.
-Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystems.
-Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions, so we stress the need for quantitative monitoring of multiple functions to make informed management decisions.**
+Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning.
+Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions simultaneously, so we stress the need for quantitative assessment of multiple functions to make informed management decisions.**
 
 The flow of elements through biological communities fuel all life on Earth [@Welti2017].
-There is now strong consensus on the importance of preserving these fluxes, often termed ecosystem functions [@Welti2017].
+There is now strong consensus on the importance of preserving these fluxes, a set of processes often termed ecosystem functions [@Welti2017].
 For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
@@
 
-Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans [@Teh2013]. 
-As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic productivity [@Brandl2019science]. 
+Coral reefs are among the most diverse and productive ecosystems on earth, and they provide essential ecosystem services to humans [@Teh2013]. 
+As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic high productivity [@Brandl2019science]. 
 Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
-Over the past decades, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+Over the past decades, severe declines in coral reef habitat quality and fish biomass, and shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
 Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
@@
 
+*statement of importance/relevance of using excretion*
+
 Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers the functional variation that exists beyond biomass, the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front].
-Even though we observed a strong relationship between fish standing biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig.
+Even though we observed a strong relationship between fish standing stock biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig.
 1), and for fish communities with similar biomass, functions tend to vary by over two orders of magnitude (Extended Data Fig.
@@
 Strikingly, not a single community reached high biomass-corrected rates (upper 10% across all communities) for all functions. 
-As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here.
+As a consequence, for a fixed amount of standing biomass, no reef appears to possess high values for all of the five functions analyzed.
 While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig.
@@
 For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig.
-1b) (See also ref.
-@Allgeier2014).
+1b; See @Allgeier2014).
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
 Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
-On the other hand, fishes in early life stages that are highly dependent on phosphorus to grow, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
+On the other hand, fishes in early life stages that are highly dependent on phosphorus for growth, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to P excretion.
 These results emphasize the importance of fish community structure for ecosystem-wide functioning [@Schramski2015; @Allgeier2016].
@@
 Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning. 
-Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
+Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig. 3a).
 For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
@@
 Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
-Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
+Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable and variable across regions, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
 
 The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in the Anthropocene. 
-Exploitation and anthropogenic climate change have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs.
+Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs.
 For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017]. 
@@
 On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
-Yet, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
-Higher N:P ratios may in fact favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
-This is particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
-Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect coral reef ecosystems.
+However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
+Higher N:P ratios may favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
+Shifts in elemental ratios may be particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].
+Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect overall coral reef ecosystems.
 
 Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
-By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion, while loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig.
-4).
+By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion.
+Conversely, loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig. 4). 
 Fishing and loss of live corals both appear to impact species important for P excretion.
-Surprisingly, although fishing pressure can heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
+Surprisingly, although fishing pressure can negatively affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
 This may be due to the high variability in unique ecosystem roles within the large pool of herbivorous fish species. 
-While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to become functionally extinct in regions with high human density [@Bellwood2012].
-While herbivores of all body sizes and functional groups are united in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
-Thus, our results reflect the overall vulnerability of functions, yet does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g.
+While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to functional extinction in regions with high fishing pressure [@Bellwood2012].
+While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
+Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g.
 @Bellwood2011).
 
+*This is a very important point that needs more elaboration.
+By losing the big parrotfishes, you lose herbivores with different functional roles.
+First to go are the bioeroders (e.g., Bolbo, Chlorurus microrhinus) and excavators (e.g., other big Chlorurus species).
+Being left with a lot of small parrots mean you are often left with just one functional group of parrotfishes (scrapers).
+So I think we are missing an important point here.
+For example as DRB says “a reef without the bioeroding parrotfishes such as Bolbo is very different to one without them”  I see you have already cited many of DRB’s papers.
+For more info on functional groups see https://www.researchgate.net/publication/237411023_Monitoring_Functional_Groups_of_Herbivorous_Reef_Fishes_as_Indicators_of_Coral_Reef_Resilience_A_practical_guide_for_coral_reef_managers_in_the_Asia_Pacifi_c_Region*
+
 Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020]. 
-Even though increased fish biomass enhances function, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another.
-For example, marine reserves, which are the main conservation approach for coral reefs [@Graham2020], may provide benefits for herbivory, but they often offer little insurance for diversity in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
+Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another.
+For example, marine protected area's, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory for example, but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
@@
 
-Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be possible. 
+Overall, our results demonstrate that managing coral reefs for ecosystem functioning is unlikely to be possible. 
 While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking. 
@@
 Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community.
-The log-transformed standing biomass was also included as a covariable, but not shown in this figure.
-All data was standardized to be able to compare across functions and variables.
+The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure.
+All data was standardized to compare across functions and variables.
 Functions were log-transformed before standardisation.
 Dots represent the average of the effect.
-Filled lines indicate the 95% credible interval, with some credible intervals being too small to visualize.
+Horizontal lines indicate the 95% credible interval, with some credible intervals being too small to visualize.
 Effects are not shown when their 95% CI intersects with zero.
@@
 Positive values mean that a family contributes more relative to its contribution to total biomass.
-Only the 12 most important family’s are shown here, and families are ordered by their median contribution to biomass.
+Only the 12 most important families are shown here, and families are ordered by their median contribution to biomass.
 b) Distribution of the degree of dominance of communities per function.
@@
 
-![Extended Data Figure 2: Fitted linear regression of each function with the log-transormed gravity to fish markets, as a proxy for fishing pressure.
+![Extended Data Figure 2: Fitted linear regression of each function with the log-transformed gravity to fish markets, as a proxy for fishing pressure.
 Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

### 2020-10-05 text/suppl_methods.Rmd
text edits

@@
 We first compiled maximum lengths for all species with Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$ .
-For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e.
+For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e.
 $k_{max}$, @Morais2018].
@@
 Sections were then fixed on a glass side with thermoplastic glue (Crystalbond TM).
-Small otoliths were directly embedded in the thermoplastic glue and polished until obtained of a transversal section.
+Small otoliths were directly embedded in the thermoplastic glue and polished until obtaining a transversal section.
 Otoliths were sanded with abrasive discs of decreasing grain size (2,400 and 1,200 grains cm- 130 2) and polished with a 0.25 μm diamond suspension in order to be closest to the nucleus.
@@
 
-We then used the Modified Fry back-calculation model (MF) [@Vigliola2000].
-to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
+We then used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
 
@@
 \noindent We extrapolated $kmax$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
-There is currently no streamlined method to make predictions to new species from a phylogenetic regression model.
-We circumvent the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model.
+There is currently no streamlined method to make predictions for new species from a phylogenetic regression model.
+We circumvented the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model.
 We subsequently predicted these phylogenetic effects for missing species with the help of the function phyEstimate in the picante package for R [@Kembel2010].

### 2020-10-16 text/coverletter.Rmd
last edits before sending to all coauthors

---
output:
  word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Editor,

Please find attached our manuscript entitled “Drivers and vulnerability of global coral reef fish functions” for consideration as a research article in Nature.

Focusing on coral reefs, we have performed the largest collection of reef fish physiological traits to date and used novel bioenergetic models to quantify five key ecosystem functions at a global scale for the first time; biomass production, nitrogen and phosphorous cycling, herbivory and predation. Our global analysis reveals a trade-off between different functions, challenging the classical view of ‘healthy’ reefs maximizing across multiple functions. Indeed, we show that at a given biomass, coral reefs display a large array of functional configurations. We demonstrate that this variability within and among functions is driven by community structure and species dominance. However, while local species dominance is a major driver of ecosystem functioning, the identity of dominant species varies among reefs, thus challenging the applicability of conservation practices related to the concept of keystone species. Finally, we illustrate the variable vulnerability of functions to two major stressors: overfishing and coral loss.

We believe our manuscript is ideally suited for the broad readership of Nature because, 1) it provides the first global maps of ecosystem functioning for coral reefs; 2) it challenges the mainstream view of maximizing multiple functions concurrently; and 3) it identifies the key drivers of coral reef functioning at a global scale, which is crucial for the conservation of this vulnerable ecosystem. In light of the fundamental importance of coral reefs for humanity, the ecological complexity of this hyperdiverse ecosystem, and the intensifying anthropogenic threats to coral reefs, we believe the study will be of great interest to a wide array of scientists, policy makers, conservation practitioners, and the general public.

Thank you for your consideration. We look forward to working with you during the editorial process.

Kind regards,

Nina M. D. Schiettekatte, on behalf of all co-authors

### 2020-10-16 text/main.Rmd
last edits before sending to all coauthors

@@
 D.
-Schiettekatte, Simon J.
-Brandl, Jordan M.
-Casey, Nicholas A.
+Schiettekatte^1,2^, Simon J.
+Brandl^3^, Jordan M.
+Casey^3^, Nicholas A.
 J.
-Graham, Diego R.
-Barneche, Deron E.
-Burkepile, Jacob E.
-Allgeier, Jesús E.
-Arias-Gonzaléz, Graham J.
-Edgar, Carlos E.
+Graham^4^, Diego R.
+Barneche^5,6^, Deron E.
+Burkepile^7,8^, Jacob E.
+Allgeier^9^, Jesús E.
+Arias-Gonzaléz^10^, Graham J.
+Edgar^11^, Carlos E.
 L.
-Ferreira, Sergio R.
-Floeter, Alan M.
-Friedlander, Alison L.
-Green, Michel Kulbicki, Yves Letourneur, Osmar J.
-Luiz, Alexandre Mercière, Fabien Morat, Katrina S.
-Munsterman, Enrico L.
-Rezende, F.
-A.
-Rodríguez‐Zaragoza, Rick D.
-Stuart-Smith, Laurent Vigliola, Sébastien Villéger, Valeriano Parravicini
+Ferreira^12^, Sergio R.
+Floeter^13^, Alan M.
+Friedlander^14^, Alison L.
+Green^15^, Michel Kulbicki^16^, Yves Letourneur^17^, Osmar J.
+Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S.
+Munsterman^8^, Enrico L.
+Rezende^19^, Fabian A.
+Rodríguez‐Zaragoza^20^, Rick D.
+Stuart-Smith^11^, Laurent Vigliola^17^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^
 
-Affiliations
-
-A. Green: 
-Red Sea Research Center, King Abdullah University of Science and Technology 
-Thuwal 23955-6900, Saudi Arabia
-
-K.S. Munsterman: 
-Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109, USA
+^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France; 
+^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France; 
+^3^Marine Science Institute, The University of Texas, Port Aransas, TX 78373, USA;
+^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;
+^5^Australian Institute of Marine Science, Crawley, WA, Australia; 
+^6^Oceans Institute, The University of Western Australia, Crawley, WA, Australia;
+^7^Department of Ecology, Evolution, and Marine Biology, University of California, Santa Barbara, CA, USA; 
+^8^Marine Science Institute, University of California, Santa Barbara, CA, USA;
+^9^Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, USA;
+^10^Laboratorio Ecología de Ecosistemas de Arrecifes Coralinos, Departamento Recursos del Mar, CINVESTAV Unidad Mérida, AP73 Cordemex, CP97310, Mérida, Yucatán, Mexico; 
+^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia; 
+^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói, Brazil; 
+^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil; 
+^14^Department of Biology, University of Hawaii, Honolulu, HI, USA; 
+^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia; 
+^16^Institut de Recherche pour le Développement, Laboratoire d’Excellence Labex Corail, UMR IRD‐UR‐CNRS ENTROPIE, Université de Perpignan, Perpignan, France; 
+^17^Institut de Recherche pour le Développement, UMR ENTROPIE (IRD-UR-UNC-CNRS-IFREMER), Nouméa, New Caledonia;
+^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;
+^19^Departamento de Ecología, Center of Applied Ecology and Sustainability (CAPES), Facultad de Ciencias Biológicas, Pontificia Universidad Católica de Chile, Santiago 6513677, Chile;
+^20^Laboratorio de Ecosistemas Marinos y Acuicultura (LEMA), Departamento de 12 Ecología, CUCBA, Universidad de Guadalajara.
+México.
+Carr.
+Guadalajara-Nogales 13 km.
+15.5, Las Agujas Nextipac, Zapopan, C.P.
+45110, Jalisco, 14, Mexico;
+^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France
 
@@
 Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning.
-Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions simultaneously, so we stress the need for quantitative assessment of multiple functions to make informed management decisions.**
+Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all functions simultaneously, so we stress the need for quantitative assessment of multiple functions to make informed management decisions.**
 
@@
 Here, we integrate biogeochemistry and community ecology to advance our understanding of the fluxes of elements that underpin reef fish functioning. 
-Using species-specific data on basic organismal processes and phylogenetic extrapolation techniques, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
-We apply these models to 9,118 reef fish communities across 585 sites worldwide to: 
-(1) quantify reef fish functions and their trade-offs, 
-(2) extract the community- and species-level predictors of these functions, and 
+Using species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to new species, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
+We apply these models to all individuals in 9,118 reef fish communities across 585 sites worldwide (Extended Data Table 1) to: 
+(1) quantify community-level reef fish functions and their trade-offs, 
+(2) extract the community- and species-level effects on these functions, and 
 (3) gauge the vulnerability of reef fish functioning in the Anthropocene.
 
-*statement of importance/relevance of using excretion*
-
-Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers the functional variation that exists beyond biomass, the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front].
-Even though we observed a strong relationship between fish standing stock biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig.
-1), and for fish communities with similar biomass, functions tend to vary by over two orders of magnitude (Extended Data Fig.
-1a).
-Thus, considering biomass alone can obscure differences in community-level functioning. 
-Further, there are strong trade-offs among the different functions when taking out the effect of biomass (Fig.1, Extended Data Fig. 1b). 
+Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers high functional variation (Fig. 1)
+Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the additive nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
+1a-e, Extended Data Fig.
+2).
+However, there is a remarkable variability within reef fish functions beyond the effect of biomass, where communities with similar biomass tend to vary by over two orders of magnitude.
+For example, a two-fold increase in biomass may yield similar function (Extended Data Fig.
+1a-f).
+Thus, using biomass as a single proxy for functioning can mask strong variation in community-level functions that may be driven by community structure and high-contributing species. 
+Further, we reveal strong trade-offs among the different functions, independent of biomass (Fig.1, Extended Data Fig. 1g). 
 For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
-Strikingly, not a single community reached high biomass-corrected rates (upper 10% across all communities) for all functions. 
-As a consequence, for a fixed amount of standing biomass, no reef appears to possess high values for all of the five functions analyzed.
-While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig.
-1).
+As a consequence, for a certain amount of standing stock biomass, no reef appears to possess high values for all of the five functions analyzed. 
+While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig. 1).
 
@@
 2).
-We found that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
+We found that correlations between functions are mediated by contrasting aspects of community structure by fitting Bayesian regression models (Fig. 2; Extended Data Table 2; Extended Data Fig. 2). 
 For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig.
-1b; See @Allgeier2014).
+1g; See @Allgeier2014).
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
@@
 Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning. 
-Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig. 3a).
+Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig.
+3a; Extended Data Fig.
+3,4).
 For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
@@
 3b).
-This means for example that on average ~12% of the species in a local community contribute to more than 50% of a function.
+For example, on average ~12% of the species of a local community contribute to more than 50% of a function.
 However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
-Thus, while there are almost no globally important species for a given function, most species are locally important somewhere.
+Thus, while there are almost no species that are important across their natural range for a given function, most species are locally important somewhere.
 Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
@@
 For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017]. 
-These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
+These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion herbivory, and piscivory (Fig. 2). 
 On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
@@
 Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
-By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion.
+By combining species-level vulnerability scores to fishing and climate change induced corall loss [@Graham2011] with the contributions of each species to each function, we demonstrate that loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion (Fig.
+4).
 Conversely, loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig. 4). 
@@
 While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to functional extinction in regions with high fishing pressure [@Bellwood2012].
-While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
-Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g.
-@Bellwood2011).
-
-*This is a very important point that needs more elaboration.
-By losing the big parrotfishes, you lose herbivores with different functional roles.
-First to go are the bioeroders (e.g., Bolbo, Chlorurus microrhinus) and excavators (e.g., other big Chlorurus species).
-Being left with a lot of small parrots mean you are often left with just one functional group of parrotfishes (scrapers).
-So I think we are missing an important point here.
-For example as DRB says “a reef without the bioeroding parrotfishes such as Bolbo is very different to one without them”  I see you have already cited many of DRB’s papers.
-For more info on functional groups see https://www.researchgate.net/publication/237411023_Monitoring_Functional_Groups_of_Herbivorous_Reef_Fishes_as_Indicators_of_Coral_Reef_Resilience_A_practical_guide_for_coral_reef_managers_in_the_Asia_Pacifi_c_Region*
+While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary, and it is important to recognize the specific crucial functional roles performed by subsets of herbivores (e.g.
+bioerosion @Bellwood2011; @Green2009).
+Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory.
 
 Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020]. 
-Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another.
-For example, marine protected area's, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory for example, but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020].
+Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a to date unrecognised challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
+For example, marine protected area's, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory, but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020], potentially affecting functions such as P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
@@
 The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure.
-All data was standardized to compare across functions and variables.
+All data was standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-stansardised data).
 Functions were log-transformed before standardisation.
@@
 Effects are not shown when their 95% CI intersects with zero.
-Variables are ordered by the maximum absolute effect across the five models.](../output/plots/fig2_com_slopes.png)
+](../output/plots/fig2_com_slopes.png)
 
@@
 
-![Figure 4: Vulnerability of functions based on the cumulative vulnerability of the contribution of species to the five functions per community.
-Filled bars show the proportion of communities that belong to a certain category of vulnerability.
-Categories of vulnerability to fishing and climate change are defined using quantiles.
-Low: <20%; High: >80%.
-High vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are high.
-Similarly, low vulnerability to both is assigned in the case where both vulnerability to fishing and vulnerability to climate change are low.](../output/plots/figure_4_vuln_com.png)
-
-![Extended Data Figure 1: a) Fold variation of each function per biomass class of 50g/m2 across fish communities.
-b) Correlation matrix of the residuals of the five functions.
-Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig2.png)
-
-![Extended Data Figure 2: Fitted linear regression of each function with the log-transformed gravity to fish markets, as a proxy for fishing pressure.
-Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)
+![Figure 4: Vulnerability of functions based on the cumulative vulnerability of the contribution of species to the five functions per community relative to the vulnerability based on biomass.
+Filled bars show the proportion of communities that have a higher functional vulnerability compared to vulnerability based on fish biomass.
+We show proportions of high functional vulnerability to fishing, climate change-induced coral loss, and high vulnerability to both stressors simultaneously.
+](../output/plots/figure_4_vuln_com.png)
 

### 2020-10-16 text/methods.Rmd
some edits from comments LV
last edits before sending to all coauthors

@@
 Each process is thus expressed in dry mass per day per square meter.
-We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild (@Parravicini2020).
+We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
+To reduce the occurrence of misclassification of herbivores and piscivores, we only categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion (Extended data figure 5).
+We can conclude that overall the herbivory and piscivory rates are very similar across trophic guild classifications, we are slightly conservative in piscivory rate estimations, and herbivory rates are almost equal to rates based on Siqueira et al.
+(2020) [@Siqueira2020], and exceed estimations based on Mouillot et al.
+(2014) [@Mouillot2014], which can be explained by the fact that this database classified many herbivores as omnivores.
+Thus, we opted to use the trophic classification by Parravicini et al.
+(2020), that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
 
@@
 
-To assess the effect of biomass and sea surface temperature sst), we performed a Bayesian mixed effect regression of each log-transformed function for transect-scale observations ($y_j$):
+The standing stock biomass of communities is inevitably related to all functions because of the additive nature of the quantification and general metabolic theory.
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, all functions are also positively correlated with temperature.
+To model the effect of biomass and sea surface temperature (sst), independent of other factors, we performed a Bayesian mixed effect regression of each log-transformed function for community-level observations ($y_j$):
 <!-- \begin{equation} -->
@@
 In those cases, we did not include these transects in the analysis.
-To assess the covariation, we then quantified the correlations that exist among the different functions.
-To visualize the residuals per locality on a world map, we first grouped all transects per site by taking the median value for each process across multiple transect.
-We then grouped the sites again into localities by taking the median.
+We then quantified the correlations that exist among the different functions using these median residuals.
+Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
+We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
 
 ## 4. Effect of community structure on ecosystem functions 
-\noindent To investigate the effect of the community structure accounting for the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
+\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
 These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
-Specifically, we took the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
+Specifically, we calculated the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
 The total length is based on the visual estimation by divers.
@@
 Additionally, we quantified the transect-level species richness.
-For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:
+For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).
 
@@
 ## 5. Species dominance and contributions to functions
-To investigate the role of each species for each function, we quantified the contribution of each species to each function for all transects as followed:
+To investigate the role of species for each function, we quantified the contribution of each species to each function for all transects as followed:
 <!-- \begin{equation} -->
@@
 For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals.
-Vulnerability to climate change is related to diet specialization, habitat specialization, recruitment specialization for live coral and body size [@Graham2011].
+Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral and body size [@Graham2011].
 Graham et al.
@@
 We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
-not dependent).
+not dependent) [@Coker2014; @Cole2008].
 We also included a random effect for family.
-This model had a Bayesian R2 of 0.97.
-We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
+To verify the fit of the model we inspected the posterior predictive plot, which indicated a good fit.
+Further, the model had a Bayesian R2 of 0.97.
+We thus used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
 For species' vulnerability to fishing, we extracted the index from Cheung et al.
-(2005) @Cheung2005.
-Then, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
-Finally, we calculated proportions of communities with either high (upper quartile) or low (lower quartile) vulnerability for each function.
-We also report the proportion of communities that have high or low vulnerability scores for both climate change and fishing.
+(2005) [@Cheung2005].
+Next, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
+We also calculated community-level vulnerability scores based on biomass contributions as a comparison.
+Finally, we calculated the proportions of communities that had a higher vulnerability score of functions, compared to the vulnerability score based on biomass alone.
+In other words, we quantified the proportions of communities that have an increased functional vulnerability.
 

### 2020-10-16 text/suppl_methods.Rmd
last edits before sending to all coauthors

@@
 We extracted the data for $k_{max}$ from Morais et al.
-(2018) @Morais2018 and filtered out only the species of our species list.
+(2018) [@Morais2018] and filtered out only the species of our species list.
 As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method.
@@
 Further, we collected additional otolith data, including measurements of fishes from five Polynesian islands. 
-We collected data across four archipelagos, including six distinct islands: Moorea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018.
+We collected data across four archipelagos, including six distinct islands: Mo'orea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018.
 All fishes were collected in the lagoon and/or outer slope, depending on the accessibility of the respective habitats.
@@
 ### 2.1 Data collection    
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Caribbean, and Palmyra.
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea, the Caribbean, and Palmyra.
 Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
@@
 
-## 3 Diet stoichiometry    
+## 3 Diet     
 ### 3.1 Data collection 

### 2020-10-16 text/suppl_tables_figures.Rmd
last edits before sending to all coauthors

---
output:
  word_document:
    fig_caption: yes
    reference_docx: ../text/word_template.docx
bibliography: ../text/global_proc.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(flextable)
library(officer)
library(drake)
library(broom)
```

# Supplementary data figures and tables: Drivers and vulnerability of global coral reef fish functions

## Tables

```{r, echo = FALSE}
data <- drake::readd(summary_transect_complete) %>%
  group_by(bioregion, locality) %>%
  summarize(n_sites = length(unique(sites)),
            n_transects = n())

  flextable(data) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    set_caption("Extended Date table 2: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
    autofit()
head(data)
```

```{r, echo = FALSE}
  list <- readd(commodels_real)
  table <- rbind(
    tidy(list[[1]], par_type = "non-varying") %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(N excretion)"),
    tidy(list[[2]], par_type = "non-varying") %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(P excretion)"),
    tidy(list[[3]], par_type = "non-varying") %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(Production)"),
    tidy(list[[4]], par_type = "non-varying") %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(Herbivory)"),
    tidy(list[[5]], par_type = "non-varying") %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(Piscivory)")) %>%
    select(response, term, estimate, std.error, lower, upper)

  flextable(table) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    merge_v(j = 1) %>% 
    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
    set_caption("Extended Date table 2: Overview of parameters of the regressions relating the five functions to the community structure variables") %>%
    autofit()
```

## Figures

![Extended Data Figure 1: a-e) Relationship between biomass and the five functions. Lines and shaded areas show the average and 95% credible interval of the predicted functions respectively, for a constant sea surface temperature of 26°C (the average across all sites). Vertical lines show the range of the estimated functions across fish communities per biomass class of 100g/m2. f) Fold variation of each function per biomass class of 100g/m2 across fish communities. g) Correlation matrix of the residuals of the five functions after regression with biomass and sea surface temperature. Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig1.png)

![Extended Data Figure 2: Posterior predictive checks of the five models relating functions  with biomass and sea surface temperature only (a) N excretion, b) P excretion, c) Production, d) Herbivory, e) Piscivory), and the five models relating functions with community variables (f) N excretion, g) P excretion, h) Production, i) Herbivory, j) Piscivory)](../output/plots/pp_plots.png)

![Extended Data Figure 3: Average relative contribution of fish families to all five functions per biogeographical ocean basin. CIP = Central-Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, WA = Western Atlantic, WI = Western Indian](../output/plots/con_family_rank.png)
![Extended Data Figure 4: Average relative contribution of the top ten most contributing species to all five functions per biogeographical ocean basin. CIP = Central-Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, WA = Western Atlantic, WI = Western Indian](../output/plots/con_species_rank.png)

![Extended Data Figure 5: Comparison herbivory and piscivory rates when using alternative diet classifications](../output/plots/Supplemental_herbivory_piscivory_alternative_classification.png)

### 2020-10-16 R/functions_analysis.R

@@ -168,11 +168,11 @@ run_commodels_abs <- function(summary_transect_complete){
                      size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
                    data = flux, chain = 3, cores = 1)
   
-  fit_Fp <- brm(log(Fp)~ ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+  fit_Fp <- brm(log(Fp) ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
                   size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
                    data = flux, chain = 3, cores = 1)
   
-  fit_Gc <- brm(log(Gc) ~ ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
+  fit_Gc <- brm(log(Gc)  ~ mean + logbiomass + nspec + size_m + troph_m + imm_m +
                   size_q3 + troph_q3 + imm_q1 + imm_q3 + troph_q1 + size_q1 ,
                    data = flux, chain = 3, cores = 1)
   

### 2020-10-16 R/functions_plots.R

@@ -342,6 +342,7 @@ make_fig3 <- function(contributions, herb_pisc, degree_dominance, freq_dominance
   con_fam <- con_fam %>%
     arrange(biomass_p) %>%
     filter(biomass_p > 0.025) %>%
+    filter(!Family == "Fistulariidae") %>%
     mutate(Family = factor(Family, unique(Family)))
 
   
@@ -362,27 +363,27 @@ make_fig3 <- function(contributions, herb_pisc, degree_dominance, freq_dominance
                        name = "") +
     
     add_fishape(family = "Acanthuridae", option = NA, alpha = 0.7,
-                xmin = 0.075, xmax = 0.11, ymin = 11.75, ymax = 12.25) +
+                xmin = -0.075, xmax = -0.11, ymin = 11.75, ymax = 12.25) +
     add_fishape(family = "Labridae", option = NA, alpha = 0.7,
-                xmax = -0.07, xmin = -0.11, ymin = 10.75, ymax = 11.25) +
+                xmax = -0.075, xmin = -0.11, ymin = 10.75, ymax = 11.25) +
     add_fishape(family = "Pomacentridae", option = NA,  alpha = 0.7,
-                xmin = 0.075, xmax = 0.11, ymin = 9.75, ymax = 10.25) +
+                xmin = -0.075, xmax = -0.11, ymin = 9.75, ymax = 10.25) +
     add_fishape(family = "Haemulidae", option = NA,  alpha = 0.7,
                 xmax = -0.075, xmin = -0.11, ymin = 8.75, ymax = 9.25) +
     add_fishape(family = "Lutjanidae", option = NA,  alpha = 0.7,
-                xmin = 0.075, xmax = 0.11, ymin = 7.75, ymax = 8.25) +
+                xmin = -0.075, xmax = -0.11, ymin = 7.75, ymax = 8.25) +
     add_fishape(family = "Serranidae", option = "Cephalopholis_argus",  alpha = 0.7,
                 xmax = -0.075, xmin = -0.11, ymin = 6.75, ymax = 7.25) +
     add_fishape(family = "Balistidae", option = NA,  alpha = 0.7,
-                xmin = 0.075, xmax = 0.11, ymin = 5.75, ymax = 6.25) +
+                xmin = -0.075, xmax = -0.11, ymin = 5.75, ymax = 6.25) +
[…]

### 2020-10-16 R/functions_wrangling.R

@@ -495,108 +495,5 @@ combine_summary <- function(summary_transect, herb_pisc){
   
 }
 
-####### extra analysis diets #######
-alt_diet <- function(tfish, cnpflux){
-  
-  diet <- read.csv("data/extrapolation_trophic_guilds.csv") 
-  
-  diet_experts <- read.csv("data/original_experts_classification.csv")%>%
-    select(species = Genus_and_species_, Gaspar, Siquiera)
-  
-  diets <- diet %>%
-    select(family, species, p2_m, p4_m, trophic_guild_predicted) %>% 
-    left_join(diet_experts) %>%
-    mutate(herb = trophic_guild_predicted == 2,
-           herb_gas = Gaspar == "HD",
-           herb_siq = Siquiera == "HD",
-           herb_t1 = trophic_guild_predicted == 2 & p2_m > 0.5,
-           pisc = trophic_guild_predicted == 4,
-           pisc_gas = Gaspar == "FC",
-           pisc_siq = Siquiera == "GC",
-           pisc_t1 = trophic_guild_predicted == 4 & p4_m > 0.5
-    )
-  
-  
-  tfish <- left_join(tfish, unique(dplyr::select(cnpflux, species, v_m, size_cm, (ends_with("_median"))))) %>% 
-    left_join(diets) %>%
-    mutate(Ic = Ic_median * abun) %>%
-    mutate(I = Ic/area) 
-  
-  
-  tfs <- dplyr::group_by(tfish, region, locality, sites, area, transect_id) %>% 
-    dplyr::summarise(
-      I_herb = sum(I[herb == TRUE], na.rm = TRUE),
-      I_pisc = sum(I[pisc == TRUE], na.rm = TRUE),
-      I_herb_t1 = sum(I[herb_t1 == TRUE], na.rm = TRUE),
-      I_pisc_t1 = sum(I[pisc_t1 == TRUE], na.rm = TRUE),
-      I_herb_gas= sum(I[herb_gas == TRUE], na.rm = TRUE),
-      I_pisc_gas = sum(I[pisc_gas == TRUE], na.rm = TRUE),
-      I_herb_siq = sum(I[herb_siq == TRUE], na.rm = TRUE),
-      I_pisc_siq = sum(I[pisc_siq == TRUE], na.rm = TRUE)
-    ) %>% ungroup() %>%
-    mutate(d_herb1 =  (I_herb_t1 - I_herb),
-           d_pisc1 =  (I_pisc_t1 - I_pisc),
[…]

### 2020-10-16 R/packages.R

@@ -19,5 +19,8 @@ library(ggrepel)
 library(tidyr)
 library(readr)
 library(Rcpp)
+library(broom)
+library(flextable)
+library(officer)
 
 Sys.setlocale("LC_MESSAGES", "en_US.utf8")

### 2020-10-16 R/plan.R

@@ -56,6 +56,7 @@ plan <- drake_plan(
   
   # run models proc ~ community vars
   commodels = run_commodels(summary_transect_complete),
+  commodels_real = run_commodels_abs(summary_transect_complete),
   
   ##### contribution analysis #####
   contr_family = get_cf(contributions, herb_pisc),
@@ -74,10 +75,15 @@ plan <- drake_plan(
   fig3 = make_fig3(contributions, herb_pisc, degree_dominance, freq_dominance),
   fig4 = make_fig4(contributions, vulnerability, herb_pisc, residuals),
   
-  # annex
-  annex_fig1 = make_annex_fig1(summary_transect_complete, bmmodels),
-  annex_fig2 = make_annex_fig2(summary_transect_complete, residuals),
-  annex_fig3 = make_annex_fig3(summary_transect_complete, residuals),
+  # Supplemental data figures
+  SI_fig1 = make_annex_fig1(summary_transect_complete, residuals, bmmodels),
+  SI_fig2 = make_annex_fig2(summary_transect_complete, residuals),
+  
+  # Supplemental information figures
+  SI_rank_plots = make_rank_plots(contributions, herb_pisc),
+  SI_pp_plots = make_pp_plots(bmmodels, procmodels, commodels)
+  
+  
   
   ##### TEXT #####
   # main_text_doc = rmarkdown::render(knitr_in("text/main.Rmd"), 

### 2020-10-16 R/play.R

@@ -413,14 +413,33 @@ ggsave("output/plots/phyloplot_vuln.pdf", p1, height = 12, width = 12)
 
 
 ####### rank barplots #####
+con <- left_join(contributions, herb_pisc$contributions_herb_pisc) %>%
+  ungroup() %>%
+  dplyr::group_by(bioregion) %>%
+  dplyr::mutate(n_transect = length(unique(as.character(transect_id)))) %>%
+  group_by(bioregion, Family, species) %>%
+  summarize(rel_occ = length(Fn_p)/unique(n_transect),
+            Fn_p_m = median(Fn_p),
+            Fp_p_m = median(Fp_p),
+            Gc_p_m = median(Gc_p),
+            I_herb_p_m = median(I_herb_p),
+            I_pisc_p_m = median(I_pisc_p))
+
 con[con$Family == "Scaridae", "Family"] <- "Labridae"
 
 main_fam <- dplyr::select(con, species, Family, bioregion) %>%
   group_by(Family) %>%
-  summarize(n())
+  summarize(n = n()) %>%
+  mutate(
+    rank = row_number(desc(n) )
+  ) %>%
+  filter(rank < 12) %>%
+  filter(!Family == "Pomacanthidae")
+  
 
 rank <- con %>%
-  filter(rel_occ > 0.001) %>%
+  filter(Family %in% main_fam$Family) %>%
+  filter(rel_occ > 0.01) %>%
   group_by(bioregion) %>%
   mutate(
     Fn_r = dense_rank(desc(Fn_p_m)),
@@ -449,7 +468,9 @@ rank <- con %>%
   mutate(Family = as_factor(as.character(Family))) %>%
   filter(value> 0) %>%
   group_by(bioregion, name) %>%
-  dplyr::mutate(value2 = value/max(value))
+  dplyr::mutate(value2 = value/max(value))%>%
+  ungroup() %>%
+  mutate(Family = as_factor(as.character(Family)))
 
 rank_fam <- con %>%
   group_by(bioregion, Family) %>%
@@ -469,7 +490,9 @@ rank_fam <- con %>%
   mutate(Family = as_factor(as.character(Family))) %>%
   filter(value> 0) %>%
   group_by(bioregion, name) %>%
-  dplyr::mutate(value2 = value/max(value))
+  dplyr::mutate(value2 = value/max(value))  %>%
+  ungroup() %>%
[…]

### 2020-11-09 text/main.Rmd
comments SV KM LV, SF, YL, MK :fish:

@@
 Friedlander^14^, Alison L.
-Green^15^, Michel Kulbicki^16^, Yves Letourneur^17^, Osmar J.
+Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J.
 Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S.
-Munsterman^8^, Enrico L.
+Munsterman^9^, Enrico L.
 Rezende^19^, Fabian A.
 Rodríguez‐Zaragoza^20^, Rick D.
-Stuart-Smith^11^, Laurent Vigliola^17^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^
+Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^
 
@@
 ^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia;
-^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói, Brazil; 
+^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói,  the state of Rio de Janeiro (RJ), Brazil;
 ^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil;
@@
 ^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
-^16^Institut de Recherche pour le Développement, Laboratoire d’Excellence Labex Corail, UMR IRD‐UR‐CNRS ENTROPIE, Université de Perpignan, Perpignan, France; 
-^17^Institut de Recherche pour le Développement, UMR ENTROPIE (IRD-UR-UNC-CNRS-IFREMER), Nouméa, New Caledonia;
+^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;;
+^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;
 ^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;
@@
 Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning.
-Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all functions simultaneously, so we stress the need for quantitative assessment of multiple functions to make informed management decisions.**
+Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all functions simultaneously, thus stressing the need for quantitative assessment of multiple functions to make informed management decisions.**
 
-The flow of elements through biological communities fuel all life on Earth [@Welti2017].
+The flow of elements through biological communities fuels all life on Earth [@Welti2017].
 There is now strong consensus on the importance of preserving these fluxes, a set of processes often termed ecosystem functions [@Welti2017].
@@
 Sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
-However, in agro-ecological settings efforts to maximize one function have been shown to negatively impact another (e.g.
+However, in agro-ecological settings, efforts to maximize one function have been shown to negatively impact another (e.g.
 timber vs.
@@
 
-Coral reefs are among the most diverse and productive ecosystems on earth, and they provide essential ecosystem services to humans [@Teh2013]. 
+Coral reefs are among the most diverse and productive ecosystems on earth, that provide essential ecosystem services to humans [@Teh2013].
 As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic high productivity [@Brandl2019science].
-Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
+Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as exploitation and climate change [@Hughes2017].
 Over the past decades, severe declines in coral reef habitat quality and fish biomass, and shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
+Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
@@
 Here, we integrate biogeochemistry and community ecology to advance our understanding of the fluxes of elements that underpin reef fish functioning.
-Using species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to new species, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
+Using species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
 We apply these models to all individuals in 9,118 reef fish communities across 585 sites worldwide (Extended Data Table 1) to:
@@
 
-Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers high functional variation (Fig. 1)
+Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers high functional variation (Fig. 1).
 Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the additive nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
@@
 2).
-However, there is a remarkable variability within reef fish functions beyond the effect of biomass, where communities with similar biomass tend to vary by over two orders of magnitude.
-For example, a two-fold increase in biomass may yield similar function (Extended Data Fig.
+However, there is a remarkable variability within reef fish functions beyond the effect of biomass.
+Some communities with similar biomass perform functions with a difference of two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
+production, Extended Data Fig.
 1a-f).
@@
 3,4).
-For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
+For example, because Serranidae feed on P-rich prey, they contribute disproportionally to P excretion, and many Labridae have high growth rates making them important contributors to biomass production.
 Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
@@
 For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017].
-These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion herbivory, and piscivory (Fig. 2). 
+These effects can enhance N excretion and production when accounting for the effect of biomass [e.g. @Morais2020glob], while negatively impacting P excretion herbivory, and piscivory (Fig. 2).
 On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
-However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
+However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on reefs.
 Higher N:P ratios may favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
@@
 While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary, and it is important to recognize the specific crucial functional roles performed by subsets of herbivores (e.g.
-bioerosion @Bellwood2011; @Green2009).
+bioerosion [@Bellwood2011; @Green2009]).
 Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory.
@@
 Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a to date unrecognised challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
-For example, marine protected area's, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory, but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020], potentially affecting functions such as P excretion.
+For example, marine protected areas, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020], potentially affecting functions such as P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
-Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may leed to informed decisions to prioritize certain functions based on local needs and stressors.
+Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may lead to informed decisions to prioritize certain functions based on local needs and stressors.
 Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species identity at the local scale.
 While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales.
-Rather, it may be beta-diversity and local differences in community structure that are most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
+Rather, it may be dissimilarity between local communtiies that is most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
 
-Overall, our results demonstrate that managing coral reefs for ecosystem functioning is unlikely to be possible. 
+Overall, our results demonstrate that managing coral reefs for ecosystem functioning is even more challenging than previously assumed.
 While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking.
@@
 Similarly, the color scales show the value of the biomass-corrected function categorically (black = lower 25%, grey = 25-75%, color = >75%).
-Circles highlight the five locations with the highest value of each biomass-corrected function respectively.](../output/plots/fig1_multimap.png)
+Circles highlight the five locations with the highest value of each biomass-corrected function, respectively.](../output/plots/fig1_multimap.png)
 
@@
 The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure.
-All data was standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-stansardised data).
+All data were standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-stansardised data).
 Functions were log-transformed before standardisation.
@@
 
-![Figure 4: Vulnerability of functions based on the cumulative vulnerability of the contribution of species to the five functions per community relative to the vulnerability based on biomass.
-Filled bars show the proportion of communities that have a higher functional vulnerability compared to vulnerability based on fish biomass.
-We show proportions of high functional vulnerability to fishing, climate change-induced coral loss, and high vulnerability to both stressors simultaneously.
-](../output/plots/figure_4_vuln_com.png)
+![Figure 4: Vulnerability of 5 fish functions to fishing, climate change-induced coral loss, and to both stressors simultaneously.
+functional vulnerability was computed for the five functions in each community based on the contribution of species to the function and on their vulnerability score.
+High vulnerability is defined as proportion of communities (filled bars) which functional vulnerability is higher than vulnerability based on fish biomass (i.e.
+not accounting for species contributions to function).](../output/plots/figure_4_vuln_com.png)
 

### 2020-11-10 text/main.Rmd
comments DEB :fish:

@@
 **The high diversity and productivity of coral reefs, despite their location in generally nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013].
-Protecting reef function (cycling of elements) under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation.
+Protecting ecosystem functions of reefs under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation.
 Here, we quantify five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans.
@@
 Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning.
-Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all functions simultaneously, thus stressing the need for quantitative assessment of multiple functions to make informed management decisions.**
+Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all ecosystem functions simultaneously, thus stressing the need for quantitative assessment of multiple functions to make informed management decisions.**
 
 The flow of elements through biological communities fuels all life on Earth [@Welti2017].
-There is now strong consensus on the importance of preserving these fluxes, a set of processes often termed ecosystem functions [@Welti2017].
-For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017].
-Sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
+Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
+For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
+Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
 However, in agro-ecological settings, efforts to maximize one function have been shown to negatively impact another (e.g.
-timber vs.
+timber production vs.
 erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
 An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
-Therefore, trade-offs between functions, their drivers, and vulnerability are poorly understood for many ecosystems [@Brandl2019front].
+Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood for many ecosystems [@Brandl2019front].
 
@@
 Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as exploitation and climate change [@Hughes2017].
-Over the past decades, severe declines in coral reef habitat quality and fish biomass, and shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
+Over the past decades, severe declines in coral reef habitat quality and fish biomass as well as shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
+Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
@@
 2).
-However, there is a remarkable variability within reef fish functions beyond the effect of biomass.
+However, reef fish functions vary remarkably  beyond the effect of biomass.
 Some communities with similar biomass perform functions with a difference of two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
@@
 Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences.
-First, we explored the relationship of each function on the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
+First, we explored the relationship of each function at the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
 body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
@@
 Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020].
-Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a to date unrecognised challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
-For example, marine protected areas, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020], potentially affecting functions such as P excretion.
+Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces an as yet unrecognised challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
+For example, marine protected areas, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory.
+However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards domination of herbivores may affect functions such as P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
@@
 While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking.
-Conserving these elemental fluxes in the 21st century will require a more nuanced approach to coral reef management.
+Trying to enhance individual functions to conserve or restore the integrity of coral reefs will not be fruitful.
+Conserving ecosystem functioning in the 21st century will require a more nuanced approach to coral reef management.
 

### 2020-11-11 text/main.Rmd
last minor edits before sending out to SJB and JMC for last check

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(drake)
+loadd(fig1)
+loadd(fig2)
+loadd(fig3)
+loadd(fig4)
 ```
@@
 Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning.
-By combining species-level vulnerability scores to fishing and climate change induced corall loss [@Graham2011] with the contributions of each species to each function, we demonstrate that loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion (Fig.
+By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] with the contributions of each species to each function, we demonstrate that loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion (Fig.
 4).
@@
 Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020].
-Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces an as yet unrecognised challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
+Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces an as yet unrecognized challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
 For example, marine protected areas, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory.
@@
 While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales.
-Rather, it may be dissimilarity between local communtiies that is most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
+Rather, it may be dissimilarity between local communities that is most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
 
@@
 
-![Figure 1: World maps of five key ecosystem functions, biomass-corrected and standardised.
+![Figure 1: World maps of five key ecosystem functions, biomass-corrected and standardized.
 Dots indicate the locations that are included in this study.
@@
 Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community.
+We opted to include the lower and upper quantiles of the 95% CI on top of the median to represent the spread of the distribution of sizes, trophic level, and immaturity across all individuals in communities.
 The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure.
-All data were standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-stansardised data).
-Functions were log-transformed before standardisation.
+All data were standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-standardized data).
+Functions were log-transformed before standardization.
 Dots represent the average of the effect.
-Horizontal lines indicate the 95% credible interval, with some credible intervals being too small to visualize.
-Effects are not shown when their 95% CI intersects with zero.
-](../output/plots/fig2_com_slopes.png)
+Horizontal lines indicate the 95% credible interval, with some credible intervals being too small to visualize.](../output/plots/fig2_com_slopes.png)
 
@@
 A species is counted as being dominant in a community if the contribution of that species is higher than the scenario in which all species contribute equally (i.e.
-1 divided by the species richness).
+1 divided by the number of species that are present and contribute to the function).
 Shaded areas show the distribution of the values.

### 2020-11-11 text/methods.Rmd
last minor edits before sending out to SJB and JMC for last check

@@
 This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic.
-The database only includes sites with a hard reef bottom at the outer reef slope.
+The database only includes sites at the outer reef slope and with a hard reef bottom.
 Transects were carried out at a constant depth, parallel to the reef crest.
@@
 ## 2. Bioenergetic modeling
-\noindent We applied a series of bioenergetic models for each existing combination of species identity, body size, and sea surface temperature (n = 30668).
+\noindent Here, we focused on 5 key processes mediated by fish: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e.
+ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e.
+ingestion rate of fishes (g/day/m^2^).
+These 5 processes were estimated in each transect using individual-based bioenergetic models that predicts elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
 The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
-As such, this model is well suited for the application of a wide variety of fish species.
-The model relies on a set of input parameters including elements of metabolism, growth, and diet and body stoichiometry.
-We quantified the input parameters for all species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
-The bioenergetic model then allows for the prediction of elemental fluxes mediated by individuals, including ingestion rate, excretion rates of N and P, and growth rate.
-Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production of body mass through growth (g C/day), herbivory, i.e.
-ingestion rate of macrophytes (g/day), and piscivory, i.e.
-ingestion rate of fishes (g/day).
-We summed the contribution of each individual to each process on the transect-level, to get community-level estimates, then dividing it by the surface area that was surveyed.
+We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
+We ran the model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the cumulated estimates for the fish community per surface area.
 Each process is thus expressed in dry mass per day per square meter.
-We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
-To reduce the occurrence of misclassification of herbivores and piscivores, we only categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database [@Parravicini2020].
-Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion (Extended data figure 5).
-We can conclude that overall the herbivory and piscivory rates are very similar across trophic guild classifications, we are slightly conservative in piscivory rate estimations, and herbivory rates are almost equal to rates based on Siqueira et al.
-(2020) [@Siqueira2020], and exceed estimations based on Mouillot et al.
-(2014) [@Mouillot2014], which can be explained by the fact that this database classified many herbivores as omnivores.
-Thus, we opted to use the trophic classification by Parravicini et al.
-(2020), that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
+We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
+To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Extended data figure 5).
+Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.
 
@@
 Additionally, we quantified the transect-level species richness.
-For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).
+For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).
 
@@
 To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
-We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations.
-We used weakly-informative priors [@Burkner2017].
+We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations, and used weakly-informative priors [@Burkner2017].
 
 ## 5. Species dominance and contributions to functions
-To investigate the role of species for each function, we quantified the contribution of each species to each function for all transects as followed:
+We quantified the relative contribution of each species to each function for all transects as followed:
 <!-- \begin{equation} -->
@@
 
-where $C_i$ is the contribution of a certain species and R is the species richness.
-The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that one species performs the entire function.
+where $C_i$ is the contribution of a certain species and R is the number of species contributing to a certain function.
+The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that a single species performs the entire function.
+In the case of N excretion, P excretion, and production, R equals the species richness, while for herbivory and piscivory R represents the number of herbivores and piscivores, respectively.
 

### 2020-11-11 text/suppl_tables_figures.Rmd
last minor edits before sending out to SJB and JMC for last check

@@
 library(broom)
+
+loadd(SI_fig1)
+loadd(SI_fig2)
+loadd(SI_pp_plots)
+loadd(SI_rank_plots)
 ```
@@
     autofit()
-head(data)
 ```
@@
 
-![Extended Data Figure 5: Comparison herbivory and piscivory rates when using alternative diet classifications](../output/plots/Supplemental_herbivory_piscivory_alternative_classification.png)
+![Extended Data Figure 5: Comparison herbivory and piscivory rates when using alternative diet classifications from Mouillot et al.
+(2014) and Siqueira et al.
+2020](../output/plots/Supplemental_herbivory_piscivory_alternative_classification.png)

### 2020-11-11 R/functions_plots.R

@@ -257,7 +257,7 @@ make_fig2 <- function(commodels){
   result <- result %>%
     dplyr::filter(!variable == "b_Intercept") %>%
     left_join(tot) %>% 
-    filter(diff == FALSE) %>%
+    #filter(diff == FALSE) %>%
     filter(!variable == "b_standardlogbiomass") %>%
     filter(!variable == "b_standardmean") %>%
     mutate(variable = fct_relevel(variable, 
@@ -1035,9 +1035,9 @@ make_rank_plots <- function(contributions, herb_pisc){
     mutate(Family = as_factor(as.character(Family)))
   
   rank_fam <- con %>%
+    ungroup() %>%    
     group_by(bioregion, Family) %>%
-    summarise_if(is.numeric, sum
-    ) %>%
+    summarise_if(is.numeric, sum) %>%
     ungroup() %>%
     pivot_longer(
       c(Fn_p_m, Fp_p_m, Gc_p_m, I_herb_p_m, I_pisc_p_m),
@@ -1054,7 +1054,15 @@ make_rank_plots <- function(contributions, herb_pisc){
     group_by(bioregion, name) %>%
     dplyr::mutate(value2 = value/max(value))  %>%
     ungroup() %>%
-    mutate(Family = as_factor(as.character(Family)))
+    mutate(Family = as_factor(as.character(Family))) %>%
+    # adjust tie 
+    mutate(rank = case_when(
+      Family == "Fistulariidae" &
+        bioregion == "w_atlantic" &
+        name == "I_pisc_p_m" ~ as.integer(3),
+      TRUE ~ rank
+    ))
+
   
  
   ggplot(rank) +
@@ -1065,7 +1073,7 @@ make_rank_plots <- function(contributions, herb_pisc){
                  name = c(Fn_p_m = "N excretion",
                           Fp_p_m = "P excretion",
                           Gc_p_m = "Production",
-                          I_herb_p_m = "Herbovory",
+                          I_herb_p_m = "Herbivory",
                           I_pisc_p_m = "Piscivory"),
                  bioregion = c(c_indopacific = "CIP",
                                c_pacific = "CP",
@@ -1211,13 +1219,13 @@ alt_diet <- function(tfish, cnpflux){
     geom_histogram(aes(x = (d_herb_gas), y = stat(count) / sum(count)), bins = 30) +
[…]

### 2020-11-11 R/plan.R

@@ -78,24 +78,28 @@ plan <- drake_plan(
   # Supplemental data figures
   SI_fig1 = make_annex_fig1(summary_transect_complete, residuals, bmmodels),
   SI_fig2 = make_annex_fig2(summary_transect_complete, residuals),
-  
-  # Supplemental information figures
+
   SI_rank_plots = make_rank_plots(contributions, herb_pisc),
-  SI_pp_plots = make_pp_plots(bmmodels, procmodels, commodels)
+  SI_pp_plots = make_pp_plots(bmmodels, procmodels, commodels),
   
-  
+  extra_diet_analysis = alt_diet(tfish, cnpflux),
   
   ##### TEXT #####
-  # main_text_doc = rmarkdown::render(knitr_in("text/main.Rmd"), 
-  #                                   output_format = "word_document", 
-  #                                   output_dir = "./output/text/",
-  #                                   output_file = "Schiettekatte_global_functions_main.docx"),
-  # methods_text_doc = rmarkdown::render(knitr_in("text/methods.Rmd"), 
-  #                                   output_format = "word_document", 
-  #                                   output_dir = "./output/text/",
-  #                                   output_file = "Schiettekatte_global_functions_methods.docx"),
-  # suppl_methods_text_doc = rmarkdown::render(knitr_in("text/suppl_methods.Rmd"), 
-  #                                   output_format = "word_document", 
-  #                                   output_dir = "./output/text/",
-  #                                   output_file = "Schiettekatte_global_functions_suppl_methods.docx")
+  main_text_doc = rmarkdown::render(knitr_in("text/main.Rmd"),
+                                    output_format = "word_document",
+                                    output_dir = "./output/text/",
+                                    output_file = "Schiettekatte_global_functions_main.docx"),
+  methods_text_doc = rmarkdown::render(knitr_in("text/methods.Rmd"),
+                                    output_format = "word_document",
+                                    output_dir = "./output/text/",
+                                    output_file = "Schiettekatte_global_functions_methods.docx"),
+  suppl_methods_text_doc = rmarkdown::render(knitr_in("text/suppl_methods.Rmd"),
+                                    output_format = "word_document",
+                                    output_dir = "./output/text/",
+                                    output_file = "Schiettekatte_global_functions_suppl_methods.docx"),
+  suppl_figs_doc = rmarkdown::render(knitr_in("text/suppl_tables_figures.Rmd"),
+                                             output_format = "word_document",
[…]

### 2020-11-11 _setup.R
Update project organisation and add readme :dog:

@@ -1,0 +1,31 @@
+packages <- c(
+  "purrr",
+  "tidybayes",
+  "ggplot2",
+  "fishflux",
+  "Rphylopars",
+  "dplyr",
+  "tidyr",
+  "drake",
+  "e1071",
+  "brms",
+  "utils",
+  "patchwork",
+  "fishualize",
+  "ggnewscale",
+  "tidytree",
+  "ggtree",
+  "forcats",
+  "ggrepel",
+  "tidyr",
+  "readr",
+  "Rcpp",
+  "broom",
+  "flextable",
+  "officer",
+  "drake")
+
+to_install <- packages[!packages %in% installed.packages()]
+
+install.packages(to_install)
+

### 2020-11-11 make.R

@@ -1,0 +1,11 @@
+# Running this file will reproduce this project
+
+## Step 1: install all packages needed
+source("_setup.R")
+
+## Step 2: Reproduce all analyses to create figures, tables, and documents
+drake::r_make()
+
+
+
+

### 2020-11-25 text/main.Rmd
last edits text before submission to nature

@@
 
-# Drivers and vulnerability of global coral reef fish functions
+# Global drivers and vulnerabilities of coral reef fish functions
 
@@
 ^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;
-^3^Marine Science Institute, The University of Texas, Port Aransas, TX 78373, USA;
+^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;
 ^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;
@@
 ^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
-^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;;
+^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;
 ^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;
@@
 
-**The high diversity and productivity of coral reefs, despite their location in generally nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013].
-Protecting ecosystem functions of reefs under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation.
-Here, we quantify five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans.
-We demonstrate that critical trade-offs exist among functions (e.g.
-biomass production and phosphorous cycling), and that no reef fish community worldwide can sustain high values for all five functions simultaneously.
-Further, functions tend to be dominated by few species, where on average ~12% of species in a community provide more than 50% of a function.
-However, despite such local dominance of functions by few species, most species were important somewhere; ~70% of all species contribute disproportionally to functioning in at least one local community.
-Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning.
-Our findings introduce a challenge for coral reef conservation, in that we cannot maximize all ecosystem functions simultaneously, thus stressing the need for quantitative assessment of multiple functions to make informed management decisions.**
+**Preserving the integrity of ecosystems – their functioning – is a critical challenge of the 21st century.
+The world’s coral reefs are highly diverse, productive, and valuable to millions of people [@Teh2013], and protecting their ecosystem functioning under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] underpins most of today’s coral reef conservation efforts.
+However, a quantitative assessment of multiple, process-based functions on reefs is lacking.
+Here, we show that five key functions mediated by fishes —nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory— exhibit critical trade-offs that are driven by diverging community structures and species dominance.
+Contrary to the concept of maximizing functioning as a single currency, no reef fish community worldwide can simultaneously sustain high values across all functions.
+Furthermore, functions are locally dominated by few species, but worldwide, 70% of the 1110 species in our dataset contribute disproportionally to functioning in at least one local community.
+This leads to disparate vulnerabilities of functions to anthropogenic stressors.
+Our findings reveal a profound challenge in coral reef conservation: there is no clear objective for protecting coral reef functioning and there are no global keystone species to target.
+Instead, quantitative assessments of multiple functions are necessary to design informed conservation strategies.**
 
@@
 For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
-Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
-However, in agro-ecological settings, efforts to maximize one function have been shown to negatively impact another (e.g.
+Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
+However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g.
 timber production vs.
@@
 An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
-Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood for many ecosystems [@Brandl2019front].
+Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].
 
-Coral reefs are among the most diverse and productive ecosystems on earth, that provide essential ecosystem services to humans [@Teh2013].
-As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic high productivity [@Brandl2019science].
-Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as exploitation and climate change [@Hughes2017].
+Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services to humanity [@Teh2013].
+As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their high productivity [@Brandl2019science].
+Yet, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as exploitation and climate change [@Hughes2017].
 Over the past decades, severe declines in coral reef habitat quality and fish biomass as well as shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
+However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
 @Mora2011plos; @Cinner2020; @Mouillot2014].
-Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently limits effective management [@Brandl2019front].
+Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]).
+This constitutes a severe limitation to effective conservation management of coral reefs [@Brandl2019front].
 
-Here, we integrate biogeochemistry and community ecology to advance our understanding of the fluxes of elements that underpin reef fish functioning.
-Using species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parametrize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed in mass of carbon), and piscivory (daily consumption of fishes, expressed in mass of carbon).
-We apply these models to all individuals in 9,118 reef fish communities across 585 sites worldwide (Extended Data Table 1) to:
+Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
+Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed as mass of carbon), and piscivory (daily consumption of fishes, expressed as mass of carbon).
+We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Extended Data Table 1) to:
 (1) quantify community-level reef fish functions and their trade-offs,
@@
 
-Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers high functional variation (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the additive nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
+The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
+Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
 1a-e, Extended Data Fig.
 2).
-However, reef fish functions vary remarkably  beyond the effect of biomass.
-Some communities with similar biomass perform functions with a difference of two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
-production, Extended Data Fig.
+However, our analyses demonstrate that reef fish functions vary remarkably  after accounting for biomass, as functions of communities with similar biomass may differ with two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
+biomass production, Extended Data Fig.
 1a-f).
-Thus, using biomass as a single proxy for functioning can mask strong variation in community-level functions that may be driven by community structure and high-contributing species.
-Further, we reveal strong trade-offs among the different functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
-For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
-As a consequence, for a certain amount of standing stock biomass, no reef appears to possess high values for all of the five functions analyzed.
-While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig. 1).
+Thus, using biomass as a sole proxy for functioning can mask differences in critical community-level functions.
+Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
+For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
+As a consequence, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
+In other words, while many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).
 
-Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences.
-First, we explored the relationship of each function at the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e.
-body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
+Community structure and species-specific traits clearly impact rates of functioning. 
+First, using community-level ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
+2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig.
+2; Extended Data Table 2; Extended Data Fig.
 2).
-We found that correlations between functions are mediated by contrasting aspects of community structure by fitting Bayesian regression models (Fig. 2; Extended Data Table 2; Extended Data Fig. 2).
-For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig.
+For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Extended Fig.
 1g; See @Allgeier2014).
-In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion.
-Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
-On the other hand, fishes in early life stages that are highly dependent on phosphorus for growth, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to P excretion.
-These results emphasize the importance of fish community structure for ecosystem-wide functioning [@Schramski2015; @Allgeier2016].
+In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
+Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportional contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
+Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions of these individuals to phosphorus excretion.
+Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Allgeier2016], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].
 
-Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning.
+Secondly, alongside features of community structure, ecosystem functioning may also be influenced by specific high-performing taxa. 
 Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig.
@@
 3,4).
-For example, because Serranidae feed on P-rich prey, they contribute disproportionally to P excretion, and many Labridae have high growth rates making them important contributors to biomass production.
-Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
-Therefore, we assessed the role of species by quantifying the degree to which they disproportionally induce (i.e. dominate) different functions for each community.
-We demonstrate that for most communities, functions are consistently dominated by a few species (Fig.
+Further, abundant species can impact rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
+Therefore, we assessed the role of each species by quantifying their relative contributions and the degree to which they disproportionally induce (i.e. dominate) different functions in each community.
+We show that functions consistently hinge a few dominant species (Fig.
 3b).
-For example, on average ~12% of the species of a local community contribute to more than 50% of a function.
-However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
-Thus, while there are almost no species that are important across their natural range for a given function, most species are locally important somewhere.
-Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
-Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006].
-Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable and variable across regions, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].
+Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
+However, the identity of these species varies dramatically (Fig. 3c), despite evidence for some species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
+While few high-performing taxa dominate functioning in each location, there are almost no species that are important across their entire range, and most species are locally important in at least one community.
+Indeed, 70% of all species contributed disproportionally to a specific function in at least one reef fish community.
+Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
+Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations, suggesting that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem functioning [@Topor2019].
 
-The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in the Anthropocene.
-Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs.
+The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in our changing world.
+Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest that these changes will have strong effects on ecosystem functioning.
 For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017].
-These effects can enhance N excretion and production when accounting for the effect of biomass [e.g. @Morais2020glob], while negatively impacting P excretion herbivory, and piscivory (Fig. 2).
-On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
-However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on reefs.
-Higher N:P ratios may favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
-Shifts in elemental ratios may be particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].
-Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect overall coral reef ecosystems.
+When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g.
+@Morais2020glob], while negatively impacting phosphorus excretion herbivory, and piscivory (Fig.
+2).
+On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
+However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
+Higher N:P ratios may favor algal growth [@Burkepile2013], and promote algal symbiont dominance within the coral holobiont [@Allgeier2020].
+Shifts in elemental ratios may be particularly problematic when considered in concert with climate change since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].
+Thus, considering multiple functions paints a more nuanced, holistic picture of how human-induced shifts in reef fish community structure impact coral reef ecosystems.
 
 Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning.
-By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] with the contributions of each species to each function, we demonstrate that loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion (Fig.
+By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] and the contributions of each species to each function, we demonstrate that the loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by phosphorus excretion (Fig.
 4).
-Conversely, loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig. 4).
-Fishing and loss of live corals both appear to impact species important for P excretion.
-Surprisingly, although fishing pressure can negatively affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function.
-This may be due to the high variability in unique ecosystem roles within the large pool of herbivorous fish species.
-While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to functional extinction in regions with high fishing pressure [@Bellwood2012].
-While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary, and it is important to recognize the specific crucial functional roles performed by subsets of herbivores (e.g.
+Conversely, the loss of individuals due to climate change and consequent coral mortality may disproportionally reduce phosphorus excretion, nitrogen excretion, and biomass production.
+Fishing and the loss of live coral impact species important for phosphorus excretion.
+Surprisingly, although fishing pressure can negatively impact large herbivores such as parrotfishes [@Bellwood2011], herbivory is the least vulnerable function.
+This may be due to the high variability in ecosystem roles within the comparatively large pool of herbivorous fish species.
+While small herbivores are abundant and not particularly vulnerable to fishing, larger herbivorous species are frequently targeted and prone to functional extinction in areas with high fishing pressure [@Bellwood2012].
+While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are strongly complementary, and it is important to recognize the specific functional roles performed by small subsets of herbivorous species (e.g.
 bioerosion [@Bellwood2011; @Green2009]).
-Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory.
+Thus, our results reflect the overall vulnerability of functions; yet, this does not consider the distinct roles played by small groups of species nested within a broad function such as herbivory.
 
-Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020].
-Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces an as yet unrecognized challenge for coral reef conservation, where actions to enhance one function may negatively affect another.
-For example, marine protected areas, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory.
-However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards domination of herbivores may affect functions such as P excretion.
+Conserving biomass, diversity, and ecosystem functioning are important objectives of most current conservation initiatives [@Cinner2020].
+Even though safeguarding fish biomass enhances coral reef functioning, the strong trade-offs between key ecosystem functions reveals a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
+For example, the establishment of marine protected areas, which are one of the primary conservation tactics for coral reefs [@Graham2020], may protect herbivorous species and thus provide benefits for herbivory.
+However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards domination of herbivores may result in the decline of phosphorus excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
-Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may lead to informed decisions to prioritize certain functions based on local needs and stressors.
-Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species identity at the local scale.
-While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales.
-Rather, it may be dissimilarity between local communities that is most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].
+It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], as well as making informed decisions on local needs and stressors.
+Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species at the local scale.
+While, maintaining the diversity of fishes is critical for coral reef functioning, at local scales, species richness only has a minor impact on individual functions.
+Rather, dissimilarity between local communities may be the most critical factor in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Duffy2009; @Zavaleta2010; @Lefcheck2019].
 
-Overall, our results demonstrate that managing coral reefs for ecosystem functioning is even more challenging than previously assumed.
-While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking.
-Trying to enhance individual functions to conserve or restore the integrity of coral reefs will not be fruitful.
-Conserving ecosystem functioning in the 21st century will require a more nuanced approach to coral reef management.
+Overall, through coral reef fishes, we demonstrate that the striking variability in processes that govern the cycling of elements presents a critical, unrecognized challenge for coral reef ecosystem functioning.
+Management strategies that call for the enhancement of coral reef functioning via an economic mindset, where higher functioning is better, are not feasible.
+Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to variable, local trade-offs, drivers, and anthropogenic threats.
 
@@
 
-![Figure 1: World maps of five key ecosystem functions, biomass-corrected and standardized.
-Dots indicate the locations that are included in this study.
-Dot size represents the rank of the biomass-corrected function.
-Similarly, the color scales show the value of the biomass-corrected function categorically (black = lower 25%, grey = 25-75%, color = >75%).
-Circles highlight the five locations with the highest value of each biomass-corrected function, respectively.](../output/plots/fig1_multimap.png)
+![Figure 1: Spatial variation in five key, biomass-corrected ecosystem functions.
+Dots indicate locations of field surveys, with dot sizes representing the ranked values of biomass-corrected function, and color scales showing categorical assignments (black = lower 25%, grey = 25-75%, color = >75%).
+Black circular outlines highlight the five locations with the highest values of each biomass-corrected function.](../output/plots/fig1_multimap.png)
 
-![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables.
-Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community.
-We opted to include the lower and upper quantiles of the 95% CI on top of the median to represent the spread of the distribution of sizes, trophic level, and immaturity across all individuals in communities.
-The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure.
-All data were standardized to compare across functions and variables (See Extended data table 2 for parameter values on non-standardized data).
-Functions were log-transformed before standardization.
-Dots represent the average of the effect.
-Horizontal lines indicate the 95% credible interval, with some credible intervals being too small to visualize.](../output/plots/fig2_com_slopes.png)
+![Figure 2: Fixed effect values from Bayesian linear regressions that examine the effects of community variables on five functions.
+Community variables include species richness, and descriptors of the trophic level, size, and immaturity of fishes.
+To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables.
+All data were log-transformed and standardized to compare across functions and variables (see Extended Data Table 2 for parameter values on non-standardized data).
+Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)
 
-![Figure 3: a) Median family-level contributions to each function, relative to their contribution to biomass.
-Positive values mean that a family contributes more relative to its contribution to total biomass.
-Only the 12 most important families are shown here, and families are ordered by their median contribution to biomass.
-b) Distribution of the degree of dominance of communities per function.
-A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function.
-c) Distributions of frequency of being dominant to each function of all species across all communities.
-A value of 1 means that a species is always important whenever present.
-A species is counted as being dominant in a community if the contribution of that species is higher than the scenario in which all species contribute equally (i.e.
-1 divided by the number of species that are present and contribute to the function).
+![Figure 3: a) The median family-level contributions to each function relative to their contribution to standing stock biomass.
+The twelve included families are ordered by their median contribution to biomass.
+b) The distribution of the degree of dominance of communities for each function.
+Degrees of dominance range between zero (all species contribute equally) and one (a single species is the sole contributor to a given function).
+c) Species-specific frequencies of dominance in each function across all communities, ranging from zero (species are never dominant) to one (dominant wherever present).
+A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).
 Shaded areas show the distribution of the values.
-Dots represent the median value, while lines indicate the interquartile range.](../output/plots/fig3_contributions.png)
+Dots represent the median value, and lines indicate the interquartile range.](../output/plots/fig3_contributions.png)
 
-![Figure 4: Vulnerability of 5 fish functions to fishing, climate change-induced coral loss, and to both stressors simultaneously.
-functional vulnerability was computed for the five functions in each community based on the contribution of species to the function and on their vulnerability score.
-High vulnerability is defined as proportion of communities (filled bars) which functional vulnerability is higher than vulnerability based on fish biomass (i.e.
-not accounting for species contributions to function).](../output/plots/figure_4_vuln_com.png)
+![Figure 4: Vulnerability of five critical functions to fishing, climate change-induced coral loss, and both stressors combined.
+Vulnerability is presented as the proportion of communities (filled bars) in which functional vulnerability is higher than vulnerability based on fish biomass (i.e. not accounting for species contributions to each function).](../output/plots/figure_4_vuln_com.png)
 

### 2020-11-25 R/functions_plots.R

@@ -556,8 +556,7 @@ make_fig4 <- function(contributions, vulnerability, herb_pisc, residuals){
                                  "P excretion", 
                                  "Production",
                                  "Herbivory",
-                                 "Piscivory"),
-                      name = "Proportion communities with increased functional vulnerability") +
+                                 "Piscivory"), name = "") +
     theme_void() +
     theme(panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(), legend.position = c(0.5, 0.95), 

### 2020-11-25 R/plan.R

@@ -96,10 +96,10 @@ plan <- drake_plan(
   suppl_methods_text_doc = rmarkdown::render(knitr_in("text/suppl_methods.Rmd"),
                                     output_format = "word_document",
                                     output_dir = "./output/text/",
-                                    output_file = "Schiettekatte_global_functions_suppl_methods.docx"),
-  suppl_figs_doc = rmarkdown::render(knitr_in("text/suppl_tables_figures.Rmd"),
-                                             output_format = "word_document",
-                                             output_dir = "./output/text/",
-                                             output_file = "Schiettekatte_global_functions_suppl_tables_figures.docx")
-  
+                                    output_file = "Schiettekatte_global_functions_suppl_methods.docx")#,
+  # suppl_figs_doc = rmarkdown::render(knitr_in("text/suppl_tables_figures.Rmd"),
+  #                                            output_format = "word_document",
+  #                                            output_dir = "./output/text/",
+  #                                            output_file = "Schiettekatte_global_functions_suppl_tables_figures.docx")
+  # 
 )

### 2020-12-30 text/main.Rmd
Rejected from nature, edits abstract for science

@@
     fig_caption: yes
-    reference_docx: ../text/word_template.docx
+    reference_docx: ../text/word_template_science.docx
 bibliography: ../text/global_proc.bib
-csl: nature.csl
+csl: science.csl
 ---
@@
 
-**Preserving the integrity of ecosystems – their functioning – is a critical challenge of the 21st century.
-The world’s coral reefs are highly diverse, productive, and valuable to millions of people [@Teh2013], and protecting their ecosystem functioning under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] underpins most of today’s coral reef conservation efforts.
-However, a quantitative assessment of multiple, process-based functions on reefs is lacking.
-Here, we show that five key functions mediated by fishes —nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory— exhibit critical trade-offs that are driven by diverging community structures and species dominance.
-Contrary to the concept of maximizing functioning as a single currency, no reef fish community worldwide can simultaneously sustain high values across all functions.
-Furthermore, functions are locally dominated by few species, but worldwide, 70% of the 1110 species in our dataset contribute disproportionally to functioning in at least one local community.
-This leads to disparate vulnerabilities of functions to anthropogenic stressors.
-Our findings reveal a profound challenge in coral reef conservation: there is no clear objective for protecting coral reef functioning and there are no global keystone species to target.
-Instead, quantitative assessments of multiple functions are necessary to design informed conservation strategies.**
+## Abstract
+
+Preserving the integrity of coral reefs – their functioning – is a critical challenge of the 21st century. 
+However, a quantitative assessment of multiple functions is needed to guide conservation efforts. 
+Through the integration of empirically-parametrized bioenergetic models and global community surveys, we quantify five key functions mediated by fishes. 
+We show that functions exhibit critical trade-offs driven by diverging community structures. 
+Further, functions are locally dominated by few species, but worldwide, the identity of dominant species varies a lot - 70% of the 1110 species in our dataset are locally dominant. 
+Our quantitative assessment reveals a challenge in global coral reef conservation: no reef fish community can simultaneously sustain high values across all functions and there are no global keystone species to target.
+
+## Main Text
 

### 2020-12-30 text/main.Rmd
minor edit

@@
 
-# Global drivers and vulnerabilities of coral reef fish functions
+# **Title:** Global drivers and vulnerabilities of coral reef fish functions
 
-Nina M.
+**Authors:** Nina M.
 D.
-Schiettekatte^1,2^, Simon J.
+Schiettekatte^1,2,*^, Simon J.
 Brandl^3^, Jordan M.
@@
 ^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
+^*^Correspondance to NMDS (nina.schiettekatte@gmail.com).
 
-## Abstract
+**One Sentence Summary:** A global assessment of multiple ecosystem functions reveals critical trade-offs among functions in coral reefs.
 
+**Abstract:** 
 Preserving the integrity of coral reefs – their functioning – is a critical challenge of the 21st century. 
@@
 
-## Main Text
-
+**Main Text:** 
 The flow of elements through biological communities fuels all life on Earth [@Welti2017].

### 2021-01-05 text/main.Rmd
shortening for science

@@
 Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
-For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
+For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of biomass [@Weisser2017].
 Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
-However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g.
-timber production vs.
-erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
-An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
+However, there can be trade-offs between functions, and efforts to maximize one function negatively impact another [@Zavaleta2010].
+An understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
 Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].
@@
 Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services to humanity [@Teh2013].
-As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their high productivity [@Brandl2019science].
-Yet, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as exploitation and climate change [@Hughes2017].
-Over the past decades, severe declines in coral reef habitat quality and fish biomass as well as shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
-However, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative species traits [e.g.
-@Mora2011plos; @Cinner2020; @Mouillot2014].
-Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]).
-This constitutes a severe limitation to effective conservation management of coral reefs [@Brandl2019front].
+Yet, their integrity of is threatened by a plethora of anthropogenic stressors [@Hughes2017].
+Over the past decades, severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
+However, our capacity to evaluate reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative traits [e.g.
+@Cinner2020].
+Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to management [@Brandl2019front].
 
 Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
-Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed as mass of carbon), and piscivory (daily consumption of fishes, expressed as mass of carbon).
+Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory.
 We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Extended Data Table 1) to:
@@
 The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level functioning, we indeed observed a strong relationship between fish biomass and all five functions (Extended Data Fig.
 1a-e, Extended Data Fig.
@@
 1a-f).
-Thus, using biomass as a sole proxy for functioning can mask differences in critical community-level functions.
+Thus, using biomass as a proxy for functioning can mask differences in critical community-level functions.
 Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
 For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
-As a consequence, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
-In other words, while many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).
+Consequently, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
+While many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).
 
@@
 2).
-For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Extended Fig.
-1g; See @Allgeier2014).
+For example, phosphorus excretion and piscivory are higher in communities with large-bodied fishes that occupy high trophic levels (Extended Fig. 1g; See @Allgeier2014).
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
@@
 Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions of these individuals to phosphorus excretion.
-Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Allgeier2016], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].
+Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].
 
 Secondly, alongside features of community structure, ecosystem functioning may also be influenced by specific high-performing taxa.
-Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig.
-3a; Extended Data Fig.
-3,4).
-Further, abundant species can impact rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
-Therefore, we assessed the role of each species by quantifying their relative contributions and the degree to which they disproportionally induce (i.e. dominate) different functions in each community.
-We show that functions consistently hinge a few dominant species (Fig.
+Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a; Extended Data Fig. 3,4).
+Further, abundant species can impact rates of functioning at the community level [@Topor2019].
+We show that functions consistently hinge on a few dominant species (Fig.
 3b).
 Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
-However, the identity of these species varies dramatically (Fig. 3c), despite evidence for some species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
-While few high-performing taxa dominate functioning in each location, there are almost no species that are important across their entire range, and most species are locally important in at least one community.
-Indeed, 70% of all species contributed disproportionally to a specific function in at least one reef fish community.
+However, the identity of these species varies dramatically (Fig. 3c).
+While few high-performing taxa dominate functioning in each location, there are no species that are important across their entire range, and most species are locally important in at least one community.
+Indeed, 70% of all species contributed disproportionally to a specific function in at least one ommunity.
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
@@
 The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in our changing world.
-Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest that these changes will have strong effects on ecosystem functioning.
+Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Hughes2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
 For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017].
@@
 2).
-On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016].
-However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs.
-Higher N:P ratios may favor algal growth [@Burkepile2013], and promote algal symbiont dominance within the coral holobiont [@Allgeier2020].
-Shifts in elemental ratios may be particularly problematic when considered in concert with climate change since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016].
-Thus, considering multiple functions paints a more nuanced, holistic picture of how human-induced shifts in reef fish community structure impact coral reef ecosystems.
+On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006].
+However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
+Thus, considering multiple functions paints a more nuanced picture of how human-induced shifts in reef fish community structure impact coral reef ecosystems.
 
@@
 It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], as well as making informed decisions on local needs and stressors.
-Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species at the local scale.
-While, maintaining the diversity of fishes is critical for coral reef functioning, at local scales, species richness only has a minor impact on individual functions.
-Rather, dissimilarity between local communities may be the most critical factor in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Duffy2009; @Zavaleta2010; @Lefcheck2019].
+Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010], we highlight the importance of community structure and the identity of dominant species at the local scale.
+While, maintaining the diversity of fishes is critical, at local scales, species richness only has a minor impact on individual functions.
+Rather, dissimilarity between local communities may be the most critical factor in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
 
-Overall, through coral reef fishes, we demonstrate that the striking variability in processes that govern the cycling of elements presents a critical, unrecognized challenge for coral reef ecosystem functioning.
+Overall, through coral reef fishes, we demonstrate that the variability in processes that govern the cycling of elements presents an unrecognized challenge for coral reef ecosystem functioning.
 Management strategies that call for the enhancement of coral reef functioning via an economic mindset, where higher functioning is better, are not feasible.

### 2021-01-05 text/main.Rmd
edits

--- 2020-12-30 text/main.Rmd
@@
 D.
-Schiettekatte^1,2,*^, Simon J.
+Schiettekatte^1,2\*^, Simon J.
 Brandl^3^, Jordan M.
@@
 
+**Affiliations:**     
 ^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;    
@@
 ^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
-^*^Correspondance to NMDS (nina.schiettekatte@gmail.com).
+^\*^Correspondance to Nina M. D. Schiettekatte (nina.schiettekatte@gmail.com)
 
 **One Sentence Summary:** A global assessment of multiple ecosystem functions reveals critical trade-offs among functions in coral reefs.
+
+\newpage
 
@@
 
+\newpage
 **Main Text:** 
@@
 Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed as mass of carbon), and piscivory (daily consumption of fishes, expressed as mass of carbon).
-We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Extended Data Table 1) to:
+We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Table S1) to:
 (1) quantify community-level reef fish functions and their trade-offs,
@@
 The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig.
-1a-e, Extended Data Fig.
-2).
+Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Fig.
+S1a-e, Fig.
+S2).
 However, our analyses demonstrate that reef fish functions vary remarkably  after accounting for biomass, as functions of communities with similar biomass may differ with two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
-biomass production, Extended Data Fig.
-1a-f).
+biomass production, Fig.
+S1a-f).
 Thus, using biomass as a sole proxy for functioning can mask differences in critical community-level functions.
-Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
+Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Fig. S1g).
 For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
@@
 2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig.
-2; Extended Data Table 2; Extended Data Fig.
-2).
-For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Extended Fig.
-1g; See @Allgeier2014).
+2; Table S2; Fig.
+S2).
+For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Fig S1g; See @Allgeier2014).
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
@@
 Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig.
-3a; Extended Data Fig.
-3,4).
+3a; Fig.
+S3,S4).
 Further, abundant species can impact rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
@@
 To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables.
-All data were log-transformed and standardized to compare across functions and variables (see Extended Data Table 2 for parameter values on non-standardized data).
+All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data).
 Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)
@@
 
-# References
+<br>
+
+**References and Notes:**         
+<div id="refs"></div>
+
+**Acknowledgements:** 
+We thank the staff at CRIOBE, Moorea for field support.
+We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Sophie Schiettekatte for proof-reading the manuscript, and Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analyis.
+**Funding:** 
+This research was funded by the BNP Paribas Foundation (Reef Services Project) and the French National Agency for Scientific Research (ANR; REEFLUX Project; ANR‐17‐CE32‐0006).
+This research is product of the SCORE-REEF group funded by the Centre de Synthèse et d’Analyse sur la Biodiversité (CESAB) of the Foundation pour la Recherche sur la Biodiversité (FRB) and the Agence Nationale de la Biodiversité (AFB).
+VP was supported by the Institut Universitaire de France (IUF) and JMC was supported by a Make Our Planet Great Again Postdoctoral Grant (mopga‐pdf‐0000000144).
+**Author contributions:** 
+NMDS and VP conceived the idea and NMDS, VP, SJB, and JMC designed methodology; NMDS, JMC, SJB, AM, FM, VP, KSM, JEA and DEB collected the data; All authors shared existing data.
+NMDS analyzed the data and led the writing of the manuscript.
+All authors contributed significantly to the drafts and approved the final version for publication.
+**Competing interests:** None declared.
+**Data and materials availability:** 
+All data and code to reproduce figures are available online through GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9).
+All data on individual fish traits are available from the corresponding author on reasonable request.
+
+**Supplementary Materials:**
+Materials and Methods     
+Figures S1-S5     
+Table S1     
+Supplementary methods     
+References (##-##)

### 2021-01-05 text/methods.Rmd
edits

@@
 To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
-Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Extended data figure 5).
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Fig.
+S5).
 Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.

### 2021-01-05 text/suppl_methods.Rmd
last edits text before submission to nature
edits

@@
 Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models.
+All protocols related to the capture and handling of fish complied to the ethical standards of CRIOBE and EPHE, and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019).
+Extraction and transport of samples were approved by the government of French Polynesia.
 All analyzes were carried out in R v.3.6.3 and Bayesian modes were run using Stan [@Carpenter2017] and the R package brms [@Burkner2017].
@@
 
-\noindent The CNP\% content of organisms is known to be highly conserved within families (REF).
+\noindent The CNP\% content of organisms is known to be highly conserved within families [@Allgeier2020sci].
 We therefore use phylogeny to extrapolate these values.

### 2021-01-05 text/supplementary_materials.Rmd
edits

--- 2021-01-05 text/suppl_methods.Rmd
@@
     fig_caption: yes
-    reference_docx: ../text/word_template.docx
+    reference_docx: ../text/word_template_science_supp.docx
 bibliography: ../text/global_proc.bib
-csl: nature.csl
+csl: science.csl
 ---
 
-```{r setup, include = FALSE}
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
 ```
-\usepackage[dvipsnames]{xcolor}
+
+```{r setup2, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE)
+library(tidyverse)
+library(flextable)
+library(officer)
+library(drake)
+library(broom)
+library(brms)
+library(broom.mixed)
+
+loadd(SI_fig1)
+loadd(SI_fig2)
+loadd(SI_pp_plots)
+loadd(SI_rank_plots)
+```
+
+# Supplementary Materials for
+
+Global drivers and vulnerabilities of coral reef fish functions
+
+Nina M.
+D.
+Schiettekatte^1,2,*^, Simon J.
+Brandl^3^, Jordan M.
+Casey^3^, Nicholas A.
+J.
+Graham^4^, Diego R.
+Barneche^5,6^, Deron E.
+Burkepile^7,8^, Jacob E.
+Allgeier^9^, Jesús E.
+Arias-Gonzaléz^10^, Graham J.
+Edgar^11^, Carlos E.
+L.
+Ferreira^12^, Sergio R.
+Floeter^13^, Alan M.
+Friedlander^14^, Alison L.
+Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J.
+Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S.
+Munsterman^9^, Enrico L.
+Rezende^19^, Fabian A.
+Rodríguez‐Zaragoza^20^, Rick D.
+Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^
+
+Correspondence to: nina.schiettekatte@gmail.com
+
+This PDF file includes:
+
+Materials and Methods       
+Figs. S1 to S5      
+Table S1 to S2       
+Supplementary methods
+\newpage
+
+# Materials and Methods
+
+## 1. Underwater visual census database
+\noindent We used a published global database of reef fish abundance and sizes collected along belt transects [@Barneche2019].
+This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic.
+The database only includes sites at the outer reef slope and with a hard reef bottom.
+Transects were carried out at a constant depth, parallel to the reef crest.
+We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize the bias related to the identification of small individuals, and finally we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
+The dataset then included 1110 species that belong to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+
+## 2. Bioenergetic modeling
+\noindent Here, we focused on 5 key processes mediated by fish: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e.
+ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e.
+ingestion rate of fishes (g/day/m^2^).
+These 5 processes were estimated in each transect using individual-based bioenergetic models that predicts elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
+The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
+We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
+We ran the model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the cumulated estimates for the fish community per surface area.
+Each process is thus expressed in dry mass per day per square meter.
+We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
+To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Fig.
+S5).
+Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.
+
+## 3. Relationship between functions and biomass
+
+The standing stock biomass of communities is inevitably related to all functions because of the additive nature of the quantification and general metabolic theory.
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, all functions are also positively correlated with temperature.
+To model the effect of biomass and sea surface temperature (sst), independent of other factors, we performed a Bayesian mixed effect regression of each log-transformed function for community-level observations ($y_j$):
+<!-- \begin{equation} -->
+	$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
+<!-- 	\label{modbiom1} -->
+<!-- \end{equation}      -->
+
+<!-- \begin{equation} -->
+$$\mu_{\textrm{j}} = \beta_0 +{\beta_1} {x_{log(biomass),j}} + {\beta_2} {x_{sst,j}}$$
+<!-- 	\label{modbiom2} -->
+<!-- \end{equation} -->
+
+\noindent We then assessed the covariation between functions, independent of biomass and sst.
+To do so, we first extracted the median residuals for each function per transect.
+In some transects, there were no piscivores or herbivores observed.
+In those cases, we did not include these transects in the analysis.
+We then quantified the correlations that exist among the different functions using these median residuals.
+Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
+We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
+
+## 4. Effect of community structure on ecosystem functions 
+\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
+These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
+Specifically, we calculated the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
+The total length is based on the visual estimation by divers.
+The immaturity is quantified using the following formula:
+<!-- \begin{equation} -->
+	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
+<!-- 	\label{imm} -->
+<!-- \end{equation} -->
+where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i.
+Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual.
+Finally, the trophic level was extracted from fishbase [@Froese2018].
+Additionally, we quantified the transect-level species richness.
+For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).
+
+<!-- \begin{equation} -->
+$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
+<!-- 	\label{modcom1} -->
+<!-- \end{equation}      -->
+
+<!-- \begin{equation} -->
+$\begin{array}{c} \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \\ \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} \end{array}$
+<!-- 	\label{modcom2} -->
+<!-- \end{equation} -->
+
+To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
+We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations, and used weakly-informative priors [@Burkner2017].
+
+## 5. Species dominance and contributions to functions
+We quantified the relative contribution of each species to each function for all transects as followed:
+<!-- \begin{equation} -->
+$$	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},$$
+<!-- 	\label{con} -->
+<!-- \end{equation} -->
+where i is a certain species, j is a transect, F is the value of function f.
+
+Then, we quantified the degree of species dominance per function for each transect. 
+We did this by first ranking species according to their contribution to function, followed by quantifying the cumulative contributions of species to functions.
+Then, we used the area under the species accumulation curve as a measure for the degree of dominance.
+Specifically, the degree of dominance (DD) was calculated as followed:
+<!-- \begin{equation} -->
+$$	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},$$
+<!-- 	\label{dd} -->
+<!-- \end{equation} -->
+where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, $A_max$ is the theoretical area under the curve where one species performs the entire function.
+They are quantified as:
+<!-- \begin{equation} -->
+$$	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},$$
+<!-- 	\label{Amin} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A}_{max} = R - 1,$$
+<!-- 	\label{Amax} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},$$
+<!-- 	\label{A} -->
+<!-- \end{equation} -->
+
+where $C_i$ is the contribution of a certain species and R is the number of species contributing to a certain function.
+The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that a single species performs the entire function.
+In the case of N excretion, P excretion, and production, R equals the species richness, while for herbivory and piscivory R represents the number of herbivores and piscivores, respectively.
+
+Finally, to know how often species are contributing more than average for a certain function, we quantified the frequency of dominance, i.e.
+the number of times a species is dominant divided by the total number of transects in which that species is observed.
+A species is considered dominant for a certain function in a given transect if their contribution is higher than 1/R, i.e.
+they contribute more than the situation in which each species contributes equally to a certain function.
+
+## 6. Vulnerability to fishing and climate change
+For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
+For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals.
+Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral and body size [@Graham2011].
+Graham et al.
+(2011) [@Graham2011] developed a score for climate change vulnerability for 134 species.
+We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
+not dependent) [@Coker2014; @Cole2008].
+We also included a random effect for family.
+To verify the fit of the model we inspected the posterior predictive plot, which indicated a good fit.
+Further, the model had a Bayesian R2 of 0.97.
+We thus used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
+For species' vulnerability to fishing, we extracted the index from Cheung et al.
+(2005) [@Cheung2005].
+Next, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
+We also calculated community-level vulnerability scores based on biomass contributions as a comparison.
+Finally, we calculated the proportions of communities that had a higher vulnerability score of functions, compared to the vulnerability score based on biomass alone.
+In other words, we quantified the proportions of communities that have an increased functional vulnerability.
+
+## Figures
+
+![Fig.
+S1: a-e) Relationship between biomass and the five functions.
+Lines and shaded areas show the average and 95% credible interval of the predicted functions respectively, for a constant sea surface temperature of 26°C (the average across all sites).
+Vertical lines show the range of the estimated functions across fish communities per biomass class of 100g/m2.
+f) Fold variation of each function per biomass class of 100g/m2 across fish communities.
+g) Correlation matrix of the residuals of the five functions after regression with biomass and sea surface temperature.
+Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig1.png)
+
+\newpage
+
+![Fig.
+S2: Posterior predictive checks of the five models relating functions  with biomass and sea surface temperature only (a) N excretion, b) P excretion, c) Production, d) Herbivory, e) Piscivory), and the five models relating functions with community variables (f) N excretion, g) P excretion, h) Production, i) Herbivory, j) Piscivory)](../output/plots/pp_plots.png)
+
+\newpage
+
+![Fig.
+S3: Average relative contribution of fish families to all five functions per biogeographical ocean basin.
+CIP = Central-Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, WA = Western Atlantic, WI = Western Indian](../output/plots/con_family_rank.png)
+
+\newpage
+
+![Fig.
+S4: Average relative contribution of the top ten most contributing species to all five functions per biogeographical ocean basin.
+CIP = Central-Indo-Pacific, CP = Central Pacific, EA = Eastern Atlantic, WA = Western Atlantic, WI = Western Indian](../output/plots/con_species_rank.png)
+
+\newpage
+
+![Fig.
+S5: Comparison herbivory and piscivory rates when using alternative diet classifications from Mouillot et al.
+(2014) and Siqueira et al.
+2020](../output/plots/Supplemental_herbivory_piscivory_alternative_classification.png)
+
+\newpage
+
+## Tables
+
+```{r, echo = FALSE}
+data <- drake::readd(summary_transect_complete) %>%
+  dplyr::group_by(bioregion, locality) %>%
+  dplyr::summarize(n_sites = length(unique(sites)),
+            n_transects = n())
+
+  flextable::flextable(data) %>%
+    flextable::fontsize(size = 8) %>%
+    flextable::fontsize(size = 10, part = "header") %>%
+    flextable::set_caption("Table S1: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
+    flextable::autofit()
+```
+\newpage
+
+```{r, echo = FALSE, eval=FALSE}
+  list <- drake::readd(commodels_real)
+  table <- rbind(
+    tidy(list[[1]], par_type = "non-varying") %>%
+    dplyr::mutate_if(is.numeric, round, 4) %>%
+    dplyr::mutate(term = c("intercept",
+                    "sst",
+                    "log(biomass)",
+                    "richness",
+                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
+                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
+                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
+                    )) %>%
+    dplyr::mutate(response = "log(N excretion)"),
+    broom.mixed::tidy(list[[2]], par_type = "non-varying") %>%
+    dplyr::mutate_if(is.numeric, round, 4) %>%
+    dplyr::mutate(term = c("intercept",
+                    "sst",
+                    "log(biomass)",
+                    "richness",
+                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
+                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
+                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
+                    )) %>%
+    dplyr::mutate(response = "log(P excretion)"),
+    broom.mixed::tidy(list[[3]], par_type = "non-varying") %>%
+    dplyr::mutate_if(is.numeric, round, 4) %>%
+    dplyr::mutate(term = c("intercept",
+                    "sst",
+                    "log(biomass)",
+                    "richness",
+                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
+                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
+                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
+                    )) %>%
+    dplyr::mutate(response = "log(Production)"),
+    broom.mixed::tidy(list[[4]], par_type = "non-varying") %>%
+    dplyr::mutate_if(is.numeric, round, 4) %>%
+    dplyr::mutate(term = c("intercept",
+                    "sst",
+                    "log(biomass)",
+                    "richness",
+                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
+                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
+                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
+                    )) %>%
+    dplyr::mutate(response = "log(Herbivory)"),
+    broom.mixed::tidy(list[[5]], par_type = "non-varying") %>%
+    dplyr::mutate_if(is.numeric, round, 4) %>%
+    dplyr::mutate(term = c("intercept",
+                    "sst",
+                    "log(biomass)",
+                    "richness",
+                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
+                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
+                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
+                    )) %>%
+    dplyr::mutate(response = "log(Piscivory)")) %>%
+    dplyr::select(response, term, estimate, std.error, lower, upper)
+
+  flextable::flextable(table) %>%
+    flextable::fontsize(size = 8) %>%
+    flextable::fontsize(size = 10, part = "header") %>%
+    flextable::merge_v(j = 1) %>% 
+    flextable::border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
+    flextable::set_caption("Table S2: Overview of parameters of the regressions relating the five functions to the community structure variables") %>%
+    flextable::autofit()
+```
+
+\newpage
 
@@
 
-## References
+## References and Notes

### 2021-01-05 text/main.Rmd
more pruning

--- 2021-01-05 text/main.Rmd
@@
 For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of biomass [@Weisser2017].
-Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
-However, there can be trade-offs between functions, and efforts to maximize one function negatively impact another [@Zavaleta2010].
+Sustaining multiple functions requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
+However, there can be trade-offs between functions, and efforts to maximize one function can negatively impact another [@Zavaleta2010].
 An understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
@@
 
-Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services to humanity [@Teh2013].
+Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services [@Teh2013].
 Yet, their integrity of is threatened by a plethora of anthropogenic stressors [@Hughes2017].
-Over the past decades, severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
-However, our capacity to evaluate reef functioning primarily relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative traits [e.g.
+Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
+However, our capacity to evaluate reef functioning relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative traits [e.g.
 @Cinner2020].
@@
 The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level functioning, we indeed observed a strong relationship between fish biomass and all five functions (Extended Data Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we indeed observed a strong relationship between fish biomass and all five functions (Extended Data Fig.
 1a-e, Extended Data Fig.
 2).
-However, our analyses demonstrate that reef fish functions vary remarkably  after accounting for biomass, as functions of communities with similar biomass may differ with two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e.
+However, our analyses demonstrate that functions vary remarkably after accounting for biomass - functions of communities with similar biomass may differ with two orders of magnitude or more (i.e.
 biomass production, Extended Data Fig.
@@
 For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
-Consequently, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
+Consequently, for a given value of biomass, no reef can yield above average values across all five functions.
 While many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).
@@
 Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportional contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
-Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions of these individuals to phosphorus excretion.
+Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
 Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].
 
-Secondly, alongside features of community structure, ecosystem functioning may also be influenced by specific high-performing taxa.
-Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a; Extended Data Fig. 3,4).
-Further, abundant species can impact rates of functioning at the community level [@Topor2019].
+Secondly, alongside features of community structure, functions may also be influenced by specific high-performing taxa.
+Certain species tend to contribute more or less to a particular function, relative to their contribution to biomass (Fig. 3a; Extended Data Fig. 3,4).
+Further, abundant species impact rates of functioning at the community level [@Topor2019].
 We show that functions consistently hinge on a few dominant species (Fig.
@@
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
-Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations, suggesting that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem functioning [@Topor2019].
+Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations.
 
@@
 
-Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning.
-By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] and the contributions of each species to each function, we demonstrate that the loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by phosphorus excretion (Fig.
+Similarly, the species-specific vulnerability of functionally-dominant species heavily affects the vulnerability of functions.
+By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] and the contributions of each species to each function, we illustrate that the loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by phosphorus excretion (Fig.
 4).
@@
 
-Conserving biomass, diversity, and ecosystem functioning are important objectives of most current conservation initiatives [@Cinner2020].
-Even though safeguarding fish biomass enhances coral reef functioning, the strong trade-offs between key ecosystem functions reveals a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
+Conserving biomass, diversity, and ecosystem functions are important objectives of most current conservation initiatives [@Cinner2020].
+Even though safeguarding fish biomass enhances functioning, the trade-offs between key functions reveal a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
 For example, the establishment of marine protected areas, which are one of the primary conservation tactics for coral reefs [@Graham2020], may protect herbivorous species and thus provide benefits for herbivory.
@@
 While, maintaining the diversity of fishes is critical, at local scales, species richness only has a minor impact on individual functions.
-Rather, dissimilarity between local communities may be the most critical factor in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
+Rather, dissimilarity between local communities may be critical in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
 

### 2021-01-11 text/main.Rmd
minor edits after comments S. Villéger

@@
 D.
-Schiettekatte^1,2,*^, Simon J.
+Schiettekatte^1,2,\*^, Simon J.
 Brandl^3^, Jordan M.
@@
 
+**Affiliations:**      
 ^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;    
@@
 ^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
-^*^Correspondance to NMDS (nina.schiettekatte@gmail.com).
+^\*^Correspondance to NMDS (nina.schiettekatte@gmail.com).
 
-**One Sentence Summary:** A global assessment of multiple ecosystem functions reveals critical trade-offs among functions in coral reefs.
+**One Sentence Summary:** A global assessment reveals critical trade-offs among multiple ecosystem functions performed by coral reef fishes.
+
+\newpage
 
 **Abstract:**
-Preserving the integrity of coral reefs – their functioning – is a critical challenge of the 21st century.
+Preserving the functioning of coral reefs is a critical challenge of the 21st century.
 However, a quantitative assessment of multiple functions is needed to guide conservation efforts.
@@
 An understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
-Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].
+Therefore, trade-offs between functions, their drivers, and their vulnerability are still poorly understood in many ecosystems [@Brandl2019front].
 
 Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services [@Teh2013].
-Yet, their integrity of is threatened by a plethora of anthropogenic stressors [@Hughes2017].
+Yet, their integrity is threatened by a plethora of anthropogenic stressors [@Hughes2017].
 Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
-However, our capacity to evaluate reef functioning relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or functional richness based on qualitative traits [e.g.
+However, our capacity to evaluate reef functioning relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or diversity of qualitative traits [e.g.
 @Cinner2020].
-Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to management [@Brandl2019front].
+Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to management [@Brandl2019front].
 
@@
 Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory.
-We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Extended Data Table 1) to:
+We apply these bioenergetic models to 9,118 reef fish communities in 585 sites worldwide (Table S1) to:
 (1) quantify community-level reef fish functions and their trade-offs,
@@
 The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we indeed observed a strong relationship between fish biomass and all five functions (Extended Data Fig.
-1a-e, Extended Data Fig.
-2).
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we indeed observed a strong relationship between fish biomass and all five functions (Fig.
+S1a-e, Fig.
+S2).
 However, our analyses demonstrate that functions vary remarkably after accounting for biomass - functions of communities with similar biomass may differ with two orders of magnitude or more (i.e.
-biomass production, Extended Data Fig.
-1a-f).
+biomass production, Fig.
+S1a-f).
 Thus, using biomass as a proxy for functioning can mask differences in critical community-level functions.
-Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
+Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Fig. S1g).
 For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
@@
 2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig.
-2; Extended Data Table 2; Extended Data Fig.
-2).
-For example, phosphorus excretion and piscivory are higher in communities with large-bodied fishes that occupy high trophic levels (Extended Fig. 1g; See @Allgeier2014).
+2; Table S2; Fig.
+S2).
+For example, phosphorus excretion and piscivory are higher in communities with large-bodied fishes that occupy high trophic levels (Fig. S1g; See @Allgeier2014).
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
@@
 Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
-Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].
+Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure significantly impacts ecosystem-wide functioning [@Schramski2015].
 
 Secondly, alongside features of community structure, functions may also be influenced by specific high-performing taxa.
-Certain species tend to contribute more or less to a particular function, relative to their contribution to biomass (Fig. 3a; Extended Data Fig. 3,4).
+Certain species tend to contribute more or less to a particular function, relative to their contribution to biomass (Fig. 3a; Fig. S3,S4).
 Further, abundant species impact rates of functioning at the community level [@Topor2019].
@@
 Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
-However, the identity of these species varies dramatically (Fig. 3c).
-While few high-performing taxa dominate functioning in each location, there are no species that are important across their entire range, and most species are locally important in at least one community.
-Indeed, 70% of all species contributed disproportionally to a specific function in at least one ommunity.
+However, the identity of these species varies dramatically between reefs (Fig. 3c).
+While few high-performing taxa dominate functioning in each location, there are no species that are dominant across their entire range.
+In addition, 70% of all species contributed disproportionally to a specific function in at least one community.
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
@@
 
-Overall, through coral reef fishes, we demonstrate that the variability in processes that govern the cycling of elements presents an unrecognized challenge for coral reef ecosystem functioning.
+Overall, through coral reef fishes, we demonstrate that the variability in processes that govern the cycling of elements presents an unrecognized challenge for protecting ecosystem functioning.
 Management strategies that call for the enhancement of coral reef functioning via an economic mindset, where higher functioning is better, are not feasible.

### 2021-01-12 R/plan.R
reproduction model: change covariance matrix to correlation (relatedness) matrix

@@ -89,17 +89,17 @@ plan <- drake_plan(
                                     output_format = "word_document",
                                     output_dir = "./output/text/",
                                     output_file = "Schiettekatte_global_functions_main.docx"),
-  methods_text_doc = rmarkdown::render(knitr_in("text/methods.Rmd"),
-                                    output_format = "word_document",
-                                    output_dir = "./output/text/",
-                                    output_file = "Schiettekatte_global_functions_methods.docx"),
-  suppl_methods_text_doc = rmarkdown::render(knitr_in("text/suppl_methods.Rmd"),
-                                    output_format = "word_document",
-                                    output_dir = "./output/text/",
-                                    output_file = "Schiettekatte_global_functions_suppl_methods.docx")#,
-  # suppl_figs_doc = rmarkdown::render(knitr_in("text/suppl_tables_figures.Rmd"),
-  #                                            output_format = "word_document",
-  #                                            output_dir = "./output/text/",
-  #                                            output_file = "Schiettekatte_global_functions_suppl_tables_figures.docx")
-  # 
+  # methods_text_doc = rmarkdown::render(knitr_in("text/methods.Rmd"),
+  #                                   output_format = "word_document",
+  #                                   output_dir = "./output/text/",
+  #                                   output_file = "Schiettekatte_global_functions_methods.docx"),
+  # suppl_methods_text_doc = rmarkdown::render(knitr_in("text/suppl_methods.Rmd"),
+  #                                   output_format = "word_document",
+  #                                   output_dir = "./output/text/",
+  #                                   output_file = "Schiettekatte_global_functions_suppl_methods.docx"),
+  suppl_mat_doc = rmarkdown::render(knitr_in("text/supplementary_materials.Rmd"),
+                                              output_format = "word_document",
+                                              output_dir = "./output/text/",
+                                              output_file = "Schiettekatte_global_functions_suppl_materials.docx")
+   
 )

### 2021-07-27 text/main.Rmd
post defense back to work

@@
 
-# **Title:** Global drivers and vulnerabilities of coral reef fish functions
+# **Title:** Biological trade-offs underlie coral reef ecosystem functioning
 
@@
 ^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;     
-^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;      
+^3^Department of Marine Science, The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;      
 ^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;      
@@
 Preserving the functioning of coral reefs is a critical challenge of the 21st century.
-However, a quantitative assessment of multiple functions is needed to guide conservation efforts.
-Through the integration of empirically-parametrized bioenergetic models and global community surveys, we quantify five key functions mediated by fishes.
-We show that functions exhibit critical trade-offs driven by diverging community structures.
-Further, functions are locally dominated by few species, but worldwide, the identity of dominant species varies a lot - 70% of the 1110 species in our dataset are locally dominant.
-Our quantitative assessment reveals a challenge in global coral reef conservation: no reef fish community can simultaneously sustain high values across all functions and there are no global keystone species to target.
+However, a lack of quantitative assessments of multiple functions across large spatial scales has hindered local and regional conservation efforts.
+We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes.
+We show that functions exhibit critical trade-offs driven by diverging community structures, such that no reef can holistically maximize functioning.
+Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; 70% of the 1,110 species in our dataset are functionally dominant.
+Our results underline the need for a nuanced approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.
 
@@
 However, there can be trade-offs between functions, and efforts to maximize one function can negatively impact another [@Zavaleta2010].
-An understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
-Therefore, trade-offs between functions, their drivers, and their vulnerability are still poorly understood in many ecosystems [@Brandl2019front].
+A deeper understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
+Therefore, trade-offs between functions, their drivers, and their vulnerability remain poorly understood in many ecosystems [@Brandl2019front].
 
@@
 Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
-However, our capacity to evaluate reef functioning relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or diversity of qualitative traits [e.g.
+However, our capacity to evaluate reef functioning typically relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
 @Cinner2020].
-Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to management [@Brandl2019front].
+Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to mefficient anagement [@Brandl2019front].
 
@@
 Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory.
-We apply these bioenergetic models to 9,118 reef fish communities in 585 sites worldwide (Table S1) to:
+We apply these bioenergetic models to 9,118 reef fish communities across 585 sites worldwide (Table S1) to:
 (1) quantify community-level reef fish functions and their trade-offs,
@@
 The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we indeed observed a strong relationship between fish biomass and all five functions (Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we observed a predictably strong relationship between fish biomass and all five functions (Fig.
 S1a-e, Fig.
 S2).
-However, our analyses demonstrate that functions vary remarkably after accounting for biomass - functions of communities with similar biomass may differ with two orders of magnitude or more (i.e.
-biomass production, Fig.
-S1a-f).
-Thus, using biomass as a proxy for functioning can mask differences in critical community-level functions.
+However, our analyses demonstrate striking variability after accounting for biomass: in communities with similar biomass, functions may differ by two orders of magnitude or more (Fig. S1a-f).
+Thus, using biomass as a proxy for functioning masks fundamental differences in critical community-level functions.
 Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Fig. S1g).
-For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
+For example, high herbivory rates and nitrogen excretion negatively correlate with rates of phosphorus excretion.
 Consequently, for a given value of biomass, no reef can yield above average values across all five functions.
-While many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).
+While many reefs may stand out as hotspots for one function, none can holistically maximize functioning (Fig. 1).
 
 Community structure and species-specific traits clearly impact rates of functioning.
-First, using community-level ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (body size, trophic level, species richness, biomass, temperature, and age structure; Fig.
+First, using community-level ecological predictors known to affect elemental fluxes (body size, trophic level, species richness, biomass, temperature, and age structure [@Schiettekatte2020]; Fig.
 2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig.
@@
 S2).
-For example, phosphorus excretion and piscivory are higher in communities with large-bodied fishes that occupy high trophic levels (Fig. S1g; See @Allgeier2014).
+For example, phosphorus excretion and piscivory are higher in communities that include large-bodied fishes or occupy high trophic levels (Fig. 2; @Allgeier2014).  
 In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
-Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportional contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
+Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
 Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
@@
 
-Secondly, alongside features of community structure, functions may also be influenced by specific high-performing taxa.
-Certain species tend to contribute more or less to a particular function, relative to their contribution to biomass (Fig. 3a; Fig. S3,S4).
-Further, abundant species impact rates of functioning at the community level [@Topor2019].
-We show that functions consistently hinge on a few dominant species (Fig.
+Secondly, alongside community structure, functions may also be influenced by specific high-performing taxa (Fig.
+3a; Fig.
+S3,S4), which may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
+At the local scale, we show that functions consistently hinge on a few dominant species (Fig.
 3b).
-Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
-However, the identity of these species varies dramatically between reefs (Fig. 3c).
+Specifically, on average, more than 50% of a given function is upheld by only 12% of the species present within a local community.
+However, the identity of these species varies dramatically among reefs (Fig. 3c).
 While few high-performing taxa dominate functioning in each location, there are no species that are dominant across their entire range.
@@
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
-Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations.
+Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across locations [@Lefcheck2019].
 
@@
 When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g.
-@Morais2020glob], while negatively impacting phosphorus excretion herbivory, and piscivory (Fig.
+@Morais2020glob] but negatively impact phosphorus excretion, herbivory, and piscivory (Fig.
 2).
-On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006].
-However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
-Thus, considering multiple functions paints a more nuanced picture of how human-induced shifts in reef fish community structure impact coral reef ecosystems.
+On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
+However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
+Thus, considering multiple functions paints a more nuanced picture of how human-induced shifts in reef fish community structure may impact coral reef ecosystems.
 
@@
 Conversely, the loss of individuals due to climate change and consequent coral mortality may disproportionally reduce phosphorus excretion, nitrogen excretion, and biomass production.
-Fishing and the loss of live coral impact species important for phosphorus excretion.
+Combined, fishing and the loss of live coral impact species important for phosphorus excretion.
 Surprisingly, although fishing pressure can negatively impact large herbivores such as parrotfishes [@Bellwood2011], herbivory is the least vulnerable function.
 This may be due to the high variability in ecosystem roles within the comparatively large pool of herbivorous fish species.
-While small herbivores are abundant and not particularly vulnerable to fishing, larger herbivorous species are frequently targeted and prone to functional extinction in areas with high fishing pressure [@Bellwood2012].
-While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are strongly complementary, and it is important to recognize the specific functional roles performed by small subsets of herbivorous species (e.g.
-bioerosion [@Bellwood2011; @Green2009]).
-Thus, our results reflect the overall vulnerability of functions; yet, this does not consider the distinct roles played by small groups of species nested within a broad function such as herbivory.
+While small herbivores are abundant and not particularly vulnerable to fishing, larger herbivores are frequently targeted and prone to functional extinction in areas with high fishing pressure [@Bellwood2012].
+While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are strongly complementary and, thus, potentially more vulnerable.
 
-Conserving biomass, diversity, and ecosystem functions are important objectives of most current conservation initiatives [@Cinner2020].
-Even though safeguarding fish biomass enhances functioning, the trade-offs between key functions reveal a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
+Conserving biomass, diversity, and ecosystem functions are important objectives of most conservation initiatives [@Cinner2020].
+While safeguarding fish biomass enhances functioning, the trade-offs between key functions reveal a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
 For example, the establishment of marine protected areas, which are one of the primary conservation tactics for coral reefs [@Graham2020], may protect herbivorous species and thus provide benefits for herbivory.
-However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards domination of herbivores may result in the decline of phosphorus excretion.
+However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards herbivore domination may result in the decline of phosphorus excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
 It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], as well as making informed decisions on local needs and stressors.
-Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010], we highlight the importance of community structure and the identity of dominant species at the local scale.
-While, maintaining the diversity of fishes is critical, at local scales, species richness only has a minor impact on individual functions.
-Rather, dissimilarity between local communities may be critical in maintaining functioning across the seascape since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
+While there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010], we highlight the importance of community structure and the identity of dominant species at the local scale.
+Maintaining the diversity of fishes is critical, yet, at local scales, species richness has a minor impact on individual functions.
+Importantly, dissimilarity between local communities may be critical to maintain functioning across seascapes since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
 
-Overall, through coral reef fishes, we demonstrate that the variability in processes that govern the cycling of elements presents an unrecognized challenge for protecting ecosystem functioning.
-Management strategies that call for the enhancement of coral reef functioning via an economic mindset, where higher functioning is better, are not feasible.
+Overall, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning.
+Management strategies that call for the enhancement of coral reef functioning via an economic mindset (i.e.
+where higher functioning is better) are not feasible.
 Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to variable, local trade-offs, drivers, and anthropogenic threats.
@@
 
-![Figure 1: Spatial variation in five key, biomass-corrected ecosystem functions.
+![Fig.
+1: Spatial variation in five key, biomass-corrected ecosystem functions.
 Dots indicate locations of field surveys, with dot sizes representing the ranked values of biomass-corrected function, and color scales showing categorical assignments (black = lower 25%, grey = 25-75%, color = >75%).
@@
 
-![Figure 2: Fixed effect values from Bayesian linear regressions that examine the effects of community variables on five functions.
-Community variables include species richness, and descriptors of the trophic level, size, and immaturity of fishes.
+![Fig.
+2.
+Effects of ecological community variables on five functions.
+Fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes.
 To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables.
@@
 
-![Figure 3: a) The median family-level contributions to each function relative to their contribution to standing stock biomass.
+![Fig.
+3.
+Family and species-level contributions to five ecosystem functions on coral reefs.
+a) The median family-level contributions to each function relative to their contribution to standing stock biomass.
 The twelve included families are ordered by their median contribution to biomass.
@@
 
-![Figure 4: Vulnerability of five critical functions to fishing, climate change-induced coral loss, and both stressors combined.
+![Fig.
+4.
+Vulnerability of five critical functions to fishing, climate change-induced coral loss, and both stressors combined.
 Vulnerability is presented as the proportion of communities (filled bars) in which functional vulnerability is higher than vulnerability based on fish biomass (i.e. not accounting for species contributions to each function).](../output/plots/figure_4_vuln_com.png)

### 2021-07-27 text/suppl_tables_figures.Rmd
post defense back to work

@@
 ```{r, echo = FALSE}
-  list <- readd(commodels_real)
-  table <- rbind(
-    tidy(list[[1]], par_type = "non-varying") %>%
+  tab <- tidy(readd(mod_mvfun_com))
+test <- summary(tab)$summary %>% 
+  as.data.frame() %>%
+  tibble::rownames_to_column("name") %>%
+  tidyr::separate(name, into = c("dep", "var", "extra"), sep = "_") %>%
+  dplyr::mutate(var = paste0(var, extra)) %>%
+  table <- 
+    tidy(tab) %>%
     mutate_if(is.numeric, round, 4) %>%
@@
                     )) %>%
-    mutate(response = "log(N excretion)"),
-    tidy(list[[2]], par_type = "non-varying") %>%
-    mutate_if(is.numeric, round, 4) %>%
-    mutate(term = c("intercept",
-                    "sst",
-                    "log(biomass)",
-                    "richness",
-                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
-                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
-                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
-                    )) %>%
-    mutate(response = "log(P excretion)"),
-    tidy(list[[3]], par_type = "non-varying") %>%
-    mutate_if(is.numeric, round, 4) %>%
-    mutate(term = c("intercept",
-                    "sst",
-                    "log(biomass)",
-                    "richness",
-                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
-                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
-                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
-                    )) %>%
-    mutate(response = "log(Production)"),
-    tidy(list[[4]], par_type = "non-varying") %>%
-    mutate_if(is.numeric, round, 4) %>%
-    mutate(term = c("intercept",
-                    "sst",
-                    "log(biomass)",
-                    "richness",
-                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
-                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
-                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
-                    )) %>%
-    mutate(response = "log(Herbivory)"),
-    tidy(list[[5]], par_type = "non-varying") %>%
-    mutate_if(is.numeric, round, 4) %>%
-    mutate(term = c("intercept",
-                    "sst",
-                    "log(biomass)",
-                    "richness",
-                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
-                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
-                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
-                    )) %>%
-    mutate(response = "log(Piscivory)")) %>%
-    select(response, term, estimate, std.error, lower, upper)
-
+    mutate(response = "log(N excretion)")
   flextable(table) %>%

### 2021-07-27 R/functions_analysis.R

@@ -96,14 +96,10 @@ get_residuals <- function(summary_transect_complete, procmodels){
   return(res)
 }
 
-get_location_effect <- function(procmodels, summary_transect){
-  result <- lapply(procmodels, function(x){
-      x %>%
-      spread_draws(r_locality[locality, Intercept]) %>%
-      median_qi() %>%
-      select(locality, effect = r_locality)
-  }) %>% purrr::reduce(dplyr::left_join, by = "locality")
-  
+get_location_effect <- function(model, summary_transect){
+  result <- ranef(model)$locality[,1,] %>% as.data.frame() %>%
+    rownames_to_column("locality")
+
   colnames(result) <- c("locality", "r_loc_Fn", "r_loc_Fp", "r_loc_Gc", 
                         "r_loc_I_herb", "r_loc_I_pisc")
   
@@ -119,7 +115,24 @@ get_location_effect <- function(procmodels, summary_transect){
     
 }
 
-
+get_location_effect2 <- function(model, summary_transect){
+  result <- ranef(model)$locality %>% as.data.frame() %>%
+    rownames_to_column("locality") %>%
+    select(1:2)
+  
+  colnames(result) <- c("locality", "r_loc_multi")
+  
+  # add coordinates
+  coord <- select(summary_transect, bioregion, locality, lat, lon) %>%
+    unique() %>%
+    group_by(bioregion, locality) %>%
+    summarize_all(mean)
+  
+  result <- coord %>% left_join(result) %>% ungroup()
+  
+  return(result)
+  
+}
 
 ####### community models ######
 run_commodels <- function(summary_transect_complete){
@@ -414,7 +427,7 @@ impute <- function(summary_transect_complete){
                  data = summary_transect_complete[summary_transect_complete$I_herb>0,],
                  cores = 4,
                  backend = "cmdstanr",
-                 threads = threading(20))
+                 threads = threading(10))
   
   imp1 <- fitted(fitimp1,
                  newdata = summary_transect_complete[summary_transect_complete$I_herb==0,],
@@ -431,7 +444,7 @@ impute <- function(summary_transect_complete){
                  data = summary_transect_complete[summary_transect_complete$I_pisc>0,],
                  cores = 4,
                  backend = "cmdstanr",
-                 threads = threading(20))
[…]

### 2021-07-27 R/functions_plots.R

@@ -1248,5 +1248,283 @@ alt_diet <- function(tfish, cnpflux){
 }
 
 
+###### absolute functions map 
+make_maps_supp <- function(location_effect){
+  
+  library("rnaturalearth")
+  library("rnaturalearthdata")
+  library(rgeos)
+  library(sf)
+  world <- ne_countries(scale = "medium", returnclass = "sf")
+  class(world)
+  
+  
+  
+  theme_worldmap <- function(){
+    theme_bw()+
+      theme(legend.position = "none", 
+            panel.grid = element_blank(),
+            panel.border = element_rect(fill = NA, color = "grey", size = 1),
+            axis.title = element_blank(),
+            axis.text.x = element_text(size = 6),
+            axis.text.y = element_text(size = 6),
+            plot.title = element_text(size = 6, hjust = 0, face = "bold"), 
+            plot.margin = unit(c(0.002,0.002,0.002,0.002), units = , "cm"),
+            panel.spacing = unit(0, "cm")
+      ) 
+  }
+  
+  col <- fish(n = 5, option = "Callanthias_australis")
+  
+  get_scale <- function(f){
+    quant <- quantile(f, c(0,0.25,0.75,1), na.rm = TRUE)
+    quant[1] <- quant[1] - 0.5   # adjust lower bound
+    factor(cut(f, breaks = quant), labels = c( "low", "medium", "high"))
+  }
+  
+  get_scores <- function(proc){
+    probs <- seq(0,1,0.01)
+    quantiles <- quantile(proc, prob = probs, na.rm = TRUE)
+    quant <- as.numeric(factor(findInterval(proc, quantiles)))/100
+    return(quant)
+  }
+  
+  
+  getcol <- colorRampPalette(c("white", col[1]))
+  pal2 <- getcol(n = 3)
+  getcol <- colorRampPalette(c("black","white"))
+  pal1 <- getcol(n = 3)
+  pal <- c(pal1[1], pal2[2:3])
+  pal <- c("black", "grey50", col[1])
+  
+  
+  
+  a <-
+    ggplot(location_effect) + 
+    geom_sf(data = world, color = NA, fill = "lightgrey") +
+    geom_point(aes(x = lon, y = lat, color = get_scale(r_loc_Fn), 
+                   size = get_scores(r_loc_Fn)),  alpha = 0.8,
+               position = position_jitter(0,0), shape = 16) +
[…]

### 2021-07-27 R/functions_tables.R

@@ -1,0 +1,255 @@
+make_table_mod_mvfun_bm <- function(brmsfit) {
+  
+  sum <- summary(brmsfit)
+  tab_fixed <- sum$fixed %>%
+    as.data.frame() %>%
+    tibble::rownames_to_column("name") %>%
+    tidyr::separate(name, into = c("response", "term", "extra"), sep = "_") %>%
+    dplyr::mutate(term = paste0(term, extra)) %>%
+    dplyr::mutate(term = str_replace_all(term, "NA", "")) %>%
+    dplyr::mutate(response = case_when(response == "logFn" ~ "log(N excretion)",
+                                       response == "logFp" ~ "log(P excretion)",
+                                       response == "logGc" ~ "log(production)",
+                                       response == "logIherb" ~ "log(herbivory)",
+                                       response == "logIpisc" ~ "log(piscivory)"),
+                  term = case_when(term == "logbiomasstot" ~ "log(biomass)",
+                                   term == "mean" ~ "sst",
+                                   TRUE ~ term)) %>%
+    dplyr::select(-extra) %>%
+    dplyr::select(-7, -8, -9) %>%
+    dplyr::mutate(type = "fixed")
+  
+  tab_sigma <- sum$spec_pars %>%
+    as.data.frame() %>%
+    tibble::rownames_to_column("name") %>%
+    tidyr::separate(name, into = c("term", "response"), sep = "_") %>%
+    dplyr::mutate(response = case_when(response == "logFn" ~ "log(N excretion)",
+                                       response == "logFp" ~ "log(P excretion)",
+                                       response == "logGc" ~ "log(production)",
+                                       response == "logIherb" ~ "log(herbivory)",
+                                       response == "logIpisc" ~ "log(piscivory)")) %>%
+    dplyr::select(-7, -8, -9)
+  
+  tab_rescor<- sum$rescor_pars %>%
+    as.data.frame() %>%
+    tibble::rownames_to_column("term") %>%
+    dplyr::select(-6, -7, -8) 
+  
+  tab_cor_loc <- sum$random$locality %>%
+    as.data.frame() %>%
+    tibble::rownames_to_column("term") %>%
[…]

### 2021-07-27 R/functions_wrangling.R

@@ -8,7 +8,7 @@ load("data/fishtree_glob.RData")
 get_sptl <- function(x){
   sptl <- read.csv("data/species_list_tl.csv")
   sptl$Species <- gsub("_", " ", sptl$species)
-  tax <- rfishbase::load_taxa()
+  tax <- dplyr::collect(rfishbase::load_taxa())
   sptl <- right_join(dplyr::select(tax, Species, Family), sptl)
   sptl[sptl$species == "Rhinesomus_triqueter", "Family"] <- "Ostraciidae"
   sptl[sptl$species == "Abudefduf_luridus", "Family"] <- "Pomacentridae"
@@ -108,33 +108,9 @@ get_kmax <- function(){
   return(kmax)
 }
 
-##### find lw #####
+##### get lw #####
 get_lw <- function(sptl){
-lwl <- map(as.list(sptl$Species), possibly(fishflux::find_lw, otherwise =  NA_real_))
-lwl2 <- lapply(lwl, function(x){
-   if (is.na(x)){
-     res <- data.frame(
-       species = NA, lwa_m = NA, lwa_sd = NA, lwb_m = NA, lwb_sd = NA
-     )
-     return(res)
-   } else{
-     return(x)
-   }
- }) 
-
- lwd <- plyr::ldply(lwl2) %>% drop_na()
- lwd$species <- gsub(" ", "_", lwd$species)
- traits <-left_join(select(sptl, species), lwd) %>% dplyr::select( species, lwa_m, lwb_m, lwa_sd, lwb_sd) %>% ungroup()
- treesp <- 
-   data.frame(species = fishtree[[1]]$tip.label)
- traits <- dplyr::left_join(treesp, traits)
- 
- test <- phylopars(traits, fishtree[[1]])
- recon <- test$anc_recon %>% as.data.frame()
- recon$species <- rownames(recon)
- recon <- recon[1:1110,]
- lw_glob <- recon
- return(lw_glob)
+  readr::read_csv("data/length_weight_fishbase.csv")
 }
 
 ##### ar and troph #####

### 2021-07-27 R/packages.R

@@ -13,7 +13,7 @@ library(patchwork)
 library(fishualize)
 library(ggnewscale)
 library(tidytree)
-library(ggtree)
+#library(ggtree)
 library(forcats)
 library(ggrepel)
 library(tidyr)
@@ -25,5 +25,7 @@ library(officer)
 library(rnaturalearth)
 library(rnaturalearthdata)
 library(cmdstanr)
+library(stringr)
+library(tibble)
 
 Sys.setlocale("LC_MESSAGES", "en_US.utf8")

### 2021-07-27 R/plan.R

@@ -45,9 +45,12 @@ plan <- drake_plan(
   # combine summary data, sst 
   summary_transect_complete = combine_summary(summary_transect, herb_pisc),
   
+  # subset 
+  summary_transect_sub = dplyr::filter(summary_transect_complete, I_herb > 0, I_pisc > 0),
+  
   # imputation 
   imp = impute(summary_transect_complete),
-  summary_transect_imp = imp,
+  summary_transect_imp = imp[[1]],
   
   ##### models #####
   # run models only with biomass ans sst
@@ -63,58 +66,72 @@ plan <- drake_plan(
   # commodels_real = run_commodels_abs(summary_transect_complete),
   
   # site loc
-  mod_mv_siteloc = fit_mvfun_siteloc(summary_tranect_imp),
+  mod_mv_siteloc = fit_mvfun_siteloc(summary_transect_imp),
   mod_mf_siteloc = fit_mf_siteloc(summary_transect_imp),
   
   # add biomass sst
   mod_mvfun_bm = fit_mvfun_bm(summary_transect_imp),
+  mod_mf_bm = fit_mf_bm(summary_transect_imp),
   
   # community analysis
-  mod_mvfun_bm = fit_mvfun_com(summary_transect_imp),
-  mod_mf_com = fit_mf_com(summary_transect_imp),
+  mod_mvfun_com = fit_mvfun_com(summary_transect_imp),
+  mod_mvfun_com2 = fit_mvfun_com2(summary_transect_imp), #get absolute slopes
+  mod_mf_com = fit_mf_com(summary_transect_imp), 
+  
+  # Same model with data subset
+  mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
+  
+  # output tables 
+  tab_mod_mv_siteloc = make_table_mod_mv_siteloc(mod_mv_siteloc),
+  tab_mod_mf_siteloc = make_table_mod_mf_siteloc(mod_mf_siteloc), 
+  tab_mod_mvfun_bm = make_table_mod_mvfun_bm(mod_mvfun_bm),
+  tab_mod_mvfun_com = make_table_mod_mvfun_com(mod_mvfun_com),
+  tab_mod_mf_com = make_table_mod_mf_com(mod_mf_com),
+  tab_mod_mvfun_com_sub = make_table_mod_mvfun_com(mod_mvfun_com_sub),
+  tab_mod_mvfun_com2 = make_table_mod_mvfun_com(mod_mvfun_com2),
   
   ##### contribution analysis #####
[…]

### 2021-07-27 _drake.R

@@ -2,6 +2,7 @@ source("R/packages.R")  # loads packages
 source("R/functions_wrangling.R") # defines the create_plot() function
 source("R/functions_analysis.R") # defines the create_plot() function
 source("R/functions_plots.R") # defines the create_plot() function
+source("R/functions_tables.R") # defines the create_plot() function
 source("R/plan.R")      # creates the drake plan
 
 

### 2021-07-27 text/suppl_methods.Rmd
edits methods from thesis

@@
 
+The developed bioenergetic model `fishflux` uses the Von Bertalanffy growth function to calculate daily growth.
+This growth function relies on three parameters: $l_{\infty}$, $\kappa$, and $t_0$.
+For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e., $k_{max}$, @Morais2018].
+For simplicity, we kept $t0$ constant at 0 for all species.
+
 ### 1.1 Data compilation
-We first compiled maximum lengths for all species with Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$ .
-For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e.
-$k_{max}$, @Morais2018].
-$t0$ was kept constant at 0 for all species.
+We first compiled maximum lengths for all species using Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$.
+Then, we extracted the available data for $k_{max}$ from Morais & Bellwood (2018), which are essentially $\kappa$ values from Fishbase, standardized to the maximum length [@Morais2018].
+We filtered out the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
+In total, this selection process resulted in 439 observations of kmax for varying species and temperatures. \par
 
-We extracted the data for $k_{max}$ from Morais et al.
-(2018) [@Morais2018] and filtered out only the species of our species list.
-As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method.
-In total, this selection process resulted in 439 observations of kmax for different species and temperatures.
+Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands, and to which we contributed through data collection and analysis [@Morat2020].
+This dataset includes total length measurements to the nearest millimeter and fish weights to the nearest 0.1 grams.
+Further, it includes distances between annual growth increments, measured by two independent researchers to prevent biases induced by a single observer.
+These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve (see REF FISHGROWBOT).
+\par
 
-Further, we collected additional otolith data, including measurements of fishes from five Polynesian islands. 
-We collected data across four archipelagos, including six distinct islands: Mo'orea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018.
-All fishes were collected in the lagoon and/or outer slope, depending on the accessibility of the respective habitats.
+Specifically, we used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish lengths at previous ages.
+We adapted the traditional model to also estimate the uncertainty around the obtained length estimates and allow for the inclusion of missing values using a Bayesian approach (see ref fishgrowbot for details).
+Then, we fitted the Von Bertalanffy growth model to all species at each location for which there were at least 3 individuals, using Bayesian hierarchical regression models.
+Both steps of this procedure were carried out using the developed R package 'fishgrowbot' (ref).
+The package also automatically estimates the parameter $k_{max}$.
+\par
 
-For each species, otoliths were cut transversely, using a diamond disc saw (Presi Mecatome T210) to obtain a section of 500 μm.
-Sections were then fixed on a glass side with thermoplastic glue (Crystalbond TM).
-Small otoliths were directly embedded in the thermoplastic glue and polished until obtaining a transversal section.
-Otoliths were sanded with abrasive discs of decreasing grain size (2,400 and 1,200 grains cm- 130 2) and polished with a 0.25 μm diamond suspension in order to be closest to the nucleus.
-All sections were photographed under a Leica DM750 light microscope with a Leica ICC50 HD microscope camera and LAS software (Leica Microsystems).
-
-A standardized transect across the otoliths (from the nucleus to the edge) was chosen for each species, and distances between annual growth increments were measured using the software ImageJ.
-This procedure was performed twice by two independent researchers to prevent biases induced by a single observer.
-When the coefficient of variation between the two observers was greater than 5%, a common reading was reached by averaging the measurements for each section.
-
-We then used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).
-
-Finally, we fitted the Von Bertalanffy growth models to all species at each location for which there were at least 3 individuals.
-We fitted the models using Bayesian hierarchical regression models provided by the R package fishgrowbot (ref).
-
-After combining the two data sources, we obtained 496 estimates of $k_{max}$ for 181 species.
+After combining the two data sources, we obtained 496 estimates of $k_{max}$ for 181 species across varying temperatures.
 
@@
 ### 2.1 Data collection    
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea, the Caribbean, and Palmyra.
-Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
-$Q_\textrm{k}$ (\%) were then measured in the lab using standard methods.
-Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974].
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea (Parravicini, unpub.), the Caribbean [@Allgeier2020sci], and Palmyra (Bukepile unpub.).
+Their gut contents were removed and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
+Whole body elemental proportions ($Q_\textrm{k}$) were then measured in the lab using standard methods.
+Specifically, ground samples were analyzed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500), and for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974].
 Elemental content was calculated based on dry mass.
@@
 After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder.
-Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry.
+Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry described above.
 
 ### 3.2 Data analysis and extrapolation  
-\noindent We used trophic guilds defined by @Parravicini2020.
-We fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level.
+\noindent Using trophic guilds defined by @Parravicini2020, we fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level.
 This model had a median Bayesian R2 of 0.62, 0.62, and 0.48 for C, N and P respectively.
-Next, we extracted 1000 draws of the predicted the CNP\% per trophic guild.
+Next, we extracted 1000 draws of the predicted CNP\% per trophic guild.
 Parravicini et al.
@@
 animal material and primary producers is likely to be higher than regional differences within trophic categorizations.
-Further, as the used trophic guild classification includes probabilities to belong to each group, variation is included when the trophic categorization is not well known.
+Further, since the used trophic guild classification includes probabilities to belong to each group, variation is included when the trophic categorization is not well known.
 For example, if a species has a 50% probability to be a herbivore and a 50% probability to be a sessile invertivore this uncertainty will be reflected the estimation of the diet CNP\%.
@@
 ## 4 Metabolic parameters    
-### 4.1 Data collection    
-In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species.
-Individuals were collected using handnets and clove oil by scuba divers.
-
-### 4.2 Metabolic rate
-To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we conducted intermittent-closed respirometry experiments at 28°C [@Steffensen1989; @Clark2013].
-After an acclimatization and fasting period of 48 h in aquaria, the fish were individually transferred to a water-filled tub at 28°C and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
+### 4.1 Data collection and lab experiments    
+To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we carried out intermittent-closed respirometry experiments [@Steffensen1989; @Clark2013].
+In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species using hand nets and clove oil (Parravicini, Brandl, and Mercière, unpub.).
+After an acclimatization and fasting period of 48 h in aquaria, the fishes were individually transferred to a water-filled tub at 28°C (ambient sea water temperature) and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
 Then, they were placed in respirometry chambers submersed in an ambient and temperature-controlled tank, where they were left for ~23 h.
@@
 The cycles consisted of a measurement (sealed) period followed by a flush period during which the respirometry chambers were flushed with fully aerated water from the ambient tank.
-Because fish were exhausted right before entering the respirometry chambers, it is possible to measure the approximate MMR.
+Because fishes were exhausted right before entering the respirometry chambers, it was possible to measure the approximate MMR.
 Depending on fish size, 8 respirometry chambers ranging in volume (including tubes and pumps) from 0.4 to 4.4 L were run in parallel, and measurement and flush periods lasted between 3 to 15 min and 3 to 5 min, respectively.
-SMR was calculated as the average of the 10 % lowest  values measured during the entire period, after the removal of outliers [@Chabot2016].
+SMR was calculated as the average of the 10 \% lowest values measured during the entire period, after the removal of outliers [@Chabot2016].
 MMR was calculated from the slope of the first measurement period.
+\par
 
 ### 4.3 Data analysis and extrapolation
-To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$) and $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a Bayesian mixed effect model predicting the log10-transformed metabolic rate with the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the intercept and the species.
-We ran the model for 4000 iterations, with a warm-up of 2000 iterations.
+To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the species and family intercept effect using brms [@Burkner2017].
+We ran the model for 4000 iterations, with a warm-up of 2000 iterations, and four chains.
 Further, we used an informative prior for the slope ($\alpha \sim normal(0.8, 0.5)$.
 The model had a Bayesian R2 of 0.973 (95\%CI: 0.972-0.974).
-We then extracted the family-level $\alpha$ by summing the slope of the model with the effects of the family on the slope of the SMR.
-We did this for 1000 iterations and then took the mean and standard deviation.
-In a similar way we extracted the family-level intercept for SMR, and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of 1000 iterations of the intercept.
-Finally, $\theta$ was quantified as followed, based on the assumption that fishes rest 12h a day and they on average spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
+We then predicted the family-level $\alpha$ by summing the slope of the model with the effects of the family on the slope of the SMR.
+We did this for all iterations and then took the mean and standard deviation.
+In a similar way, we extracted the family-level intercept for SMR and MMR (figure \@ref(fig:c4f4)), and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of all iterations of the intercept (i.e., the intercept for SMR).
+Finally, we estimated $\theta$ as followed, based on the assumption that fishes rest 12h a day and they on average spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
 <!-- \begin{equation} -->
@@
 <!-- \end{equation} -->
-where 1000 iterations of the back-transformed family-level intercepts were used for SMR and MMR. We then summarized these predictions by taking the mean and standard deviation. 
-We used the family-level estimates for these three parameters for all species in our database.
-For families that were not represented in our respirometry dataset, we used an average across all families.
+where all iterations of the back-transformed family-level intercepts were used for SMR and MMR. We then summarized these predictions by taking the mean and standard deviation.
+We used the family-level estimates for these parameters for all species in our database.
+For families that were not represented in our respirometry dataset, we used the average across all families.
+The parameter $f0$ was adjusted for each temperature in the varying locations of the underwater visual census database, following @Barneche2014:
+
+$$f0_{adjusted} = f0(T_{ref}) e^{E_r(\frac{1}{\kappa T_ref} - \frac{1}{\kappa T})},$$
+where $\kappa$ is the Boltsmann's constant ($8.62 * 10^{-5} eV K^{-1}$), $E_r$ is the activation energy (0.59 eV, extracted from @Barneche2014), $f0(T_{ref})$ is the value of the metabolic normalization at a fixed reference temperature (301.15 K = 28 + 273.15K), $T$ is the temperature of interest (K).
 

### 2021-07-30 text/main.Rmd
text edits rev minor

@@
 We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes.
-We show that functions exhibit critical trade-offs driven by diverging community structures, such that no reef can holistically maximize functioning.
+We show that functions exhibit critical trade-offs driven by varying community structures, such that no reef can holistically maximize functioning.
 Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; 70% of the 1,110 species in our dataset are functionally dominant.
@@
 @Cinner2020].
-Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to mefficient anagement [@Brandl2019front].
+Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to efficient management [@Brandl2019front].
 
@@
 
-The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
+The five key ecosystem functions performed by fishes across the world's coral reefs exhibit high variability (Fig. 1).
 Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we observed a predictably strong relationship between fish biomass and all five functions (Fig.

### 2021-08-04 text/methods.Rmd
update methods and added priors

@@
 \noindent We used a published global database of reef fish abundance and sizes collected along belt transects [@Barneche2019].
-This database encompasses 9118 transects across 585 sites (98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic.
-The database only includes sites at the outer reef slope and with a hard reef bottom.
+This database encompasses 9118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic.
+Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019].
+The database only includes transects at the outer reef slope and with a hard reef bottom.
 Transects were carried out at a constant depth, parallel to the reef crest.
@@
 The dataset then included 1110 species that belong to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration of the USA (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).
+Further, for each transect (fish community), we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
 
-## 2. Bioenergetic modeling
-\noindent Here, we focused on 5 key processes mediated by fish: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e.
+## 2. Quantification of functions
+\noindent For each transect, we estimated five key process-based functions mediated by fishes: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e.
 ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e.
-ingestion rate of fishes (g/day/m^2^).
-These 5 processes were estimated in each transect using individual-based bioenergetic models that predicts elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
+ingestion rate of fishes (g/day/m^2^) [@Brandl2019front].
+These five functions were estimated in each transect using individual-based bioenergetic models that predict elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
 The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
 We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
-We ran the model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the cumulated estimates for the fish community per surface area.
-Each process is thus expressed in dry mass per day per square meter.
+We ran an individual bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the summed estimates on the fish community level per surface area (m^2^).
+Each function is thus expressed in dry mass (of C, N, or P) per day per square meter.
 We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
@@
 Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.
+Finally, we estimated multifunction, i.e. one measure that combines all five functions by taking the geometric average.
 
-## 3. Relationship between functions and biomass
-
-The standing stock biomass of communities is inevitably related to all functions because of the additive nature of the quantification and general metabolic theory.
-Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, all functions are also positively correlated with temperature.
-To model the effect of biomass and sea surface temperature (sst), independent of other factors, we performed a Bayesian mixed effect regression of each log-transformed function for community-level observations ($y_j$):
-<!-- \begin{equation} -->
-	$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
-<!-- 	\label{modbiom1} -->
-<!-- \end{equation}      -->
-
-<!-- \begin{equation} -->
-$$\mu_{\textrm{j}} = \beta_0 +{\beta_1} {x_{log(biomass),j}} + {\beta_2} {x_{sst,j}}$$
-<!-- 	\label{modbiom2} -->
-<!-- \end{equation} -->
-
-\noindent We then assessed the covariation between functions, independent of biomass and sst.
-To do so, we first extracted the median residuals for each function per transect.
-In some transects, there were no piscivores or herbivores observed.
-In those cases, we did not include these transects in the analysis.
-We then quantified the correlations that exist among the different functions using these median residuals.
-Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
-We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
-
-## 4. Effect of community structure on ecosystem functions 
-\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community.
+## 3. Community structure variables
+We quantified a set of variables that characterize the fish community structure.
 These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
@@
 Finally, the trophic level was extracted from fishbase [@Froese2018].
-Additionally, we quantified the transect-level species richness.
+
+## 5. Imputation of herbivory and piscivory
+
+## 4. Regression models
+The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and general metabolic theory.
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, functions are expected to be positively correlated with temperature.
+To model the effect of biomass and sea surface temperature (sst), while simultaneously investigating the correlations between the the five functions, we performed a multivariate Bayesian mixed effect regression the log-transformed functions for transect-level observations ($i$) including site and location effects:
+
+$$\begin{bmatrix}Y_{ExN,i} \\ Y_{ExP,i} \\ Y_{Prod,i} \\ Y_{Herb,i} \\ Y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+$$S = \begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\ 
+0 & \sigma_{ExP} & 0 & 0 & 0 \\ 
+0 & 0 & \sigma_{Prod,i} & 0 & 0\\ 
+0 & 0 & 0 & \sigma_{Herb} & 0\\ 
+0 & 0 & 0 & 0 & \sigma_{Pisc} \end{bmatrix} 
+R 
+\begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\ 
+0 & \sigma_{ExP} & 0 & 0 & 0 \\ 
+0 & 0 & \sigma_{Prod,i} & 0 & 0\\ 
+0 & 0 & 0 & \sigma_{Herb} & 0\\ 
+0 & 0 & 0 & 0 & \sigma_{Pisc} \end{bmatrix}$$
+
+$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} $$
+$$\beta0_{ExN} \sim  student( 3, -3.9, 2.5)\\
+\beta0_{ExP} \sim  student( 3, -6.6, 2.5)\\
+\beta0_{Prod} \sim  student( 3, -4.3, 2.5)\\
+\beta0_{Herb} \sim  student( 3, -2.4, 2.5)\\
+\beta0_{Pisc} \sim  student( 3, -4.6, 2.5)\\
+R \sim lkj\_corr(1)
+$$
+
+\noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+To further optimize convergence of the model, we sampled from the cholesky decomposed triangular matrix L such that $R = LL^T$.
+We used flat priors for the model slopes $\beta1, \beta2$.
+
+The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples  were used to estimate posterior distributions.
+We used Bayesian R2 to estimate the amount of explained variation of each model.
+Posterior predictive checks for are provided in Supporting Informationxxxxx.
+
+\noindent The multivariate  and mixed structure of the above-mentioned model allowed us to extract the correlations between the five functions on the location, site, and  We then assessed the covariation between functions, independent of biomass and sst.
+To do so, we first extracted the median residuals for each function per transect.
+In some transects, there were no piscivores or herbivores observed.
+In those cases, we did not include these transects in the analysis.
+We then quantified the correlations that exist among the different functions using these median residuals.
+Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
+We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
+
+## 4. Effect of community structure on ecosystem functions 
+\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, Additionally, we quantified the transect-level species richness.
 For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).

### 2021-08-04 R/functions_analysis.R

@@ -521,22 +521,44 @@ fit_mf_siteloc <- function(data){
       threads = threading(10))
 }
 
-fit_mf_bm <- function(data){
-  brm(log(multi) ~ log(biomass_tot) + mean + (1|s|sites) + (1|p|locality),
-      data = data, cores = 4,
-      backend = "cmdstanr",
-      threads = threading(10))
-}
 
 
 ##### 2) add biomass and sst
 fit_mvfun_bm <- function(data){
-  brm(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc)) ~ 
-        log(biomass_tot) + mean + (1|s|sites) + (1|p|locality),
+  prior <- 
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logFn") +
+    set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logFn") +
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logFp") +
+    set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logFp") +
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logGc") +
+    set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logGc") +
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logIherb") +
+    set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logIherb") +
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logIpisc") +
+    set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logIpisc") 
+  
+  brm(bf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc)) ~ 
+        log(biomass_tot) + mean + (1|s|sites) + (1|p|locality)) + 
+        set_rescor(rescor = TRUE),
       data = data, cores = 4,
       backend = "cmdstanr",
-      threads = threading(10))
+      threads = threading(10),
+      prior = prior)
 }
+
+fit_mf_bm <- function(data){
+  
+  prior <- 
+    set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", ) +
[…]

### 2021-08-04 R/functions_plots.R

@@ -1,5 +1,47 @@
 
-make_fig1 <- function(location_effect){
+make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, mod_mf_siteloc, mod_mf_bm, coords){
+  
+  re <- ranef(mod_mvfun_bm)
+  re_loc <- re$locality[,1,] %>%
+    as.data.frame()
+  colnames(re_loc) <- c("r_loc_Fn", "r_loc_Fp", "r_loc_Gc", "r_loc_Iherb", "r_loc_Ipisc")
+  
+  re1 <- ranef(mod_mv_siteloc)
+  re_loc1 <- re1$locality[,1,] %>%
+    as.data.frame()
+  colnames(re_loc1) <- c("r1_loc_Fn", "r1_loc_Fp", "r1_loc_Gc", "r1_loc_Iherb", "r1_loc_Ipisc")
+  re_loc1 <- re_loc1 %>%
+    rownames_to_column("locality") 
+  
+  re2 <- ranef(mod_mf_siteloc)
+  re_loc2 <- re2$locality[,1,1] %>%
+    as.data.frame()
+  colnames(re_loc2) <- c("r1_loc_mf")
+  re_loc2 <- re_loc2 %>%
+    rownames_to_column("locality") 
+  
+  re3 <- ranef(mod_mf_bm)
+  re_loc3 <- re3$locality[,1,1] %>%
+    as.data.frame()
+  colnames(re_loc3) <- c("r_loc_mf")
+  re_loc3 <- re_loc3 %>%
+    rownames_to_column("locality") 
+
+  
+  coords <- coords %>%
+    select(- sites, -lat, -lon, -mean) %>%
+    unique()
+  
+  data <- re_loc %>%
+    rownames_to_column("locality") %>%
+    left_join(coords) %>%
+    left_join(re_loc1) %>%
+    unique()
+  
+  
+  data2 <- left_join(re_loc2, re_loc3) %>%
+    left_join(coords) %>%
+    unique()
   
   library("rnaturalearth")
   library("rnaturalearthdata")
@@ -11,7 +53,7 @@ make_fig1 <- function(location_effect){
   
   
   theme_worldmap <- function(){
-    theme_bw()+
+    theme_bw() +
       theme(legend.position = "none", 
             panel.grid = element_blank(),
             panel.border = element_rect(fill = NA, color = "grey", size = 1),
[…]

### 2021-08-04 R/functions_wrangling.R

@@ -471,5 +471,13 @@ combine_summary <- function(summary_transect, herb_pisc){
   
 }
 
-
+##### coordinates per location and site #####
+get_coords_siteloc <- function(data) {
+  data %>%
+    group_by(bioregion, locality, sites) %>%
+    summarize_at(vars(lat, lon, mean), median) %>%
+    group_by(locality) %>%
+    mutate(lon_loc = median(lon), lat_loc = median(lat)) 
+    
+}
 

### 2021-08-04 R/plan.R

@@ -79,7 +79,7 @@ plan <- drake_plan(
   mod_mf_com = fit_mf_com(summary_transect_imp), 
   
   # Same model with data subset
-  mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
+  #mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
   
   # output tables 
   tab_mod_mv_siteloc = make_table_mod_mv_siteloc(mod_mv_siteloc),
@@ -87,7 +87,7 @@ plan <- drake_plan(
   tab_mod_mvfun_bm = make_table_mod_mvfun_bm(mod_mvfun_bm),
   tab_mod_mvfun_com = make_table_mod_mvfun_com(mod_mvfun_com),
   tab_mod_mf_com = make_table_mod_mf_com(mod_mf_com),
-  tab_mod_mvfun_com_sub = make_table_mod_mvfun_com(mod_mvfun_com_sub),
+  #tab_mod_mvfun_com_sub = make_table_mod_mvfun_com(mod_mvfun_com_sub),
   tab_mod_mvfun_com2 = make_table_mod_mvfun_com(mod_mvfun_com2),
   
   ##### contribution analysis #####
@@ -97,10 +97,11 @@ plan <- drake_plan(
   freq_dominance = get_fd(sp_importance),
 
   ##### Species vulnerability #####
-  vulnerability = get_vuln(sptl),
-  spi_vuln = get_spi_vuln(sp_importance, vulnerability)#,
+  #vulnerability = get_vuln(sptl),
+  #spi_vuln = get_spi_vuln(sp_importance, vulnerability)#,
   # 
   # ##### FIGURES #####
+  coords = get_coords_siteloc(summary_transect_imp)
   # # main
   # fig1 = make_fig1(location_effect),
   # fig2 = make_fig2(commodels),

### 2021-08-06 text/methods.Rmd
imputation text

@@
 
-## 5. Imputation of herbivory and piscivory
+## 4. Regression models
 
-## 4. Regression models
+### 4.1 Imputation of herbivory and piscivory
+In the underwater visual transect database, xx transects contained no herbivores and xx transects contained no piscivores yielding false zeros for herbivory and piscivory, respectively.
+We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores.
+In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all.
+To avoid removing all transects with missing values for herbivory or piscivory (n = xx) from our database, we imputed the missing values by fitting two models using the observed herbivory and piscivory rates and then imputing the missing values by taking the means of posterior predictions.
+In other words, we used the predictor values corresponding to missing responses to predict herbivory and piscivory rates.
+As predictor variables, we used all community structure variables described above and sea surface temperature.
+Additionally, we used .
+
+Specifically, we fitted a Bayesian regression
+
 The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and general metabolic theory.

### 2021-08-06 R/functions_analysis.R

@@ -422,7 +422,6 @@ impute <- function(summary_transect_complete){
                    standard(nspec) + standard(size_m) + standard(troph_m) + standard(imm_m) +
                    standard(size_q3) + standard(troph_q3) + standard(imm_q1) +
                    standard(imm_q3) + standard(troph_q1) + standard(size_q1) +
-                   standard(Gc) + standard(Fp) + standard(Fn) +
                    (1|s|sites) + (1|p|locality),
                  data = summary_transect_complete[summary_transect_complete$I_herb>0,],
                  cores = 4,
@@ -439,7 +438,6 @@ impute <- function(summary_transect_complete){
                    standard(nspec) + standard(size_m) + standard(troph_m) + standard(imm_m) +
                    standard(size_q3) + standard(troph_q3) + standard(imm_q1) +
                    standard(imm_q3) + standard(troph_q1) + standard(size_q1) +
-                   standard(Gc) + standard(Fp) + standard(Fn) +
                    (1|s|sites) + (1|p|locality),
                  data = summary_transect_complete[summary_transect_complete$I_pisc>0,],
                  cores = 4,
@@ -470,6 +468,21 @@ impute <- function(summary_transect_complete){
   
   return(list(summary_transect_imp = result, 
               models = list(fitimp1, fitimp2)))
+}
+
+subset_data <- function(data) {
+  data %>%
+    dplyr::filter(I_herb > 0, I_pisc > 0) %>%
+    mutate(Fn_st = stand(Fn),
+           Fp_st = stand(Fp),
+           Gc_st = stand(Gc),
+           I_herb_st = stand(I_herb),
+           I_pisc_st = stand(I_pisc)) %>%
+    rowwise() %>%
+    mutate(multi = geomean(Fn_st, Fp_st, Gc_st, I_herb_st, I_pisc_st)) %>%
+    ungroup() %>%
+    mutate(multi = stand(multi))
+  
 }
 
 

### 2021-08-06 R/plan.R

@@ -46,7 +46,7 @@ plan <- drake_plan(
   summary_transect_complete = combine_summary(summary_transect, herb_pisc),
   
   # subset 
-  summary_transect_sub = dplyr::filter(summary_transect_complete, I_herb > 0, I_pisc > 0),
+  summary_transect_sub = subset_data(summary_transect_complete),
   
   # imputation 
   imp = impute(summary_transect_complete),
@@ -78,8 +78,13 @@ plan <- drake_plan(
   mod_mvfun_com2 = fit_mvfun_com2(summary_transect_imp), #get absolute slopes
   mod_mf_com = fit_mf_com(summary_transect_imp), 
   
-  # Same model with data subset
-  #mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
+  # Same models with data subset
+  mod_mv_siteloc_sub = fit_mvfun_siteloc(summary_transect_sub),
+  mod_mf_siteloc_sub = fit_mf_siteloc(summary_transect_sub),
+  mod_mvfun_bm_sub = fit_mvfun_bm(summary_transect_sub),
+  mod_mf_bm_sub = fit_mf_bm(summary_transect_sub),
+  mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
+  mod_mf_com_sub = fit_mf_com(summary_transect_sub), 
   
   # output tables 
   tab_mod_mv_siteloc = make_table_mod_mv_siteloc(mod_mv_siteloc),
@@ -87,8 +92,8 @@ plan <- drake_plan(
   tab_mod_mvfun_bm = make_table_mod_mvfun_bm(mod_mvfun_bm),
   tab_mod_mvfun_com = make_table_mod_mvfun_com(mod_mvfun_com),
   tab_mod_mf_com = make_table_mod_mf_com(mod_mf_com),
-  #tab_mod_mvfun_com_sub = make_table_mod_mvfun_com(mod_mvfun_com_sub),
-  tab_mod_mvfun_com2 = make_table_mod_mvfun_com(mod_mvfun_com2),
+  tab_mod_mvfun_com_sub = make_table_mod_mvfun_com(mod_mvfun_com_sub),
+  #tab_mod_mvfun_com2 = make_table_mod_mvfun_com(mod_mvfun_com2),
   
   ##### contribution analysis #####
   contr_family = get_cf(contributions, herb_pisc),

### 2021-08-06 text/methods.Rmd
methods model formulas

--- 2021-08-04 text/methods.Rmd
@@
 Further, for each transect (fish community), we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
+All data wrangling and analyses were performed in the software program R (version 4.0.2; R core team 2020).
 
@@
 
-## 5. Imputation of herbivory and piscivory
+## 4. Regression models
 
-## 4. Regression models
-The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and general metabolic theory.
-Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, functions are expected to be positively correlated with temperature.
-To model the effect of biomass and sea surface temperature (sst), while simultaneously investigating the correlations between the the five functions, we performed a multivariate Bayesian mixed effect regression the log-transformed functions for transect-level observations ($i$) including site and location effects:
+### 4.1 Imputation of herbivory and piscivory
+In the underwater visual transect database, xx transects did not contain herbivores and xx transects did not contain piscivores, yielding false zeros for herbivory and piscivory, respectively.
+We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores.
+In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all.
+To avoid removing all transects with missing values for herbivory or piscivory (n = xx) from our database, we imputed the missing values by fitting two Bayesian regression models using the observed herbivory and piscivory rates and then imputing the missing values by taking the means of posterior predictions.
+In other words, we used the median predictor values corresponding to missing responses to impute herbivory and piscivory rates.
+As predictor variables, we used the community structure variables described above and sea surface temperature, all standardized.
+Additionally, we included random effects of sites and localities on the intercepts.
+Both models thus had the following model structure:
+$$ y_i \sim normal(\mu_i, \sigma) $$
+$$\begin{array}{c}
+\mu_{i} = (\beta0 + \delta_{loc} +  \delta_{site}) + \beta_1 x_{log(biomass),i} + \beta_2 x_{sst,i}  + \beta_3 x_{richness,i}  + \beta_4 x_{size_m,i}  + \beta_5 x_{size_{2.5\%},i} +  \beta_6 x_{size_{97.5\%},i} + \\
+\beta_7 x_{troph_m,i}  + \beta_8 x_{troph_{2.5\%},i} +  \beta_9 x_{troph_{97.5\%},i} + \beta_{10} x_{imm_m,i}  + \beta_{11} x_{imm_{2.5\%},i} +  \beta_{12} x_{imm_{97.5\%},i} \end{array}$$,
 
-$$\begin{bmatrix}Y_{ExN,i} \\ Y_{ExP,i} \\ Y_{Prod,i} \\ Y_{Herb,i} \\ Y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+where $i$ represents the transects, $\beta_0$ is the intercept, $\beta_1$ to $\beta_{12}$ are the fixed effect parameters, $\delta_{loc}$ is the random effect of the locality, $\delta_{site}$ is the random effect of the site, biomass represents the total standing stock biomass of the community, sst the sea surface temperature, richness is the species richness, size is the total length, troph is the trophic level, imm is the immaturity, and $m$, $2.5\%$, and $97.5\%$ respectively represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community.
+For these models, we used uninformative priors for the fixed effect parameters ($\beta_{1-12}$) and weakly informative priors for the standard deviations of residuals and random effects (ADD THE PRIOR).
+To insure that the performed Imputationdidn't change main results of the downstream regression models, we repeated all below-mentioned models on a subset of the transect data, excluding the original missing values.
+Results of models are shown in the supplementary information xxxxxxx.
+
+### 4.2 Regressions with biomass and SST, and estimates of correlation
+
+The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification.
+The relationships between functions and biomass are likely to be allometric following metabolic theory.
+Therefore, we log-transformed each function and biomass in all regression analyses.
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration [@Morais2018; refMETABOLIC], functions are hypothesised to be affected by  temperature.
+To model the effect of biomass and SST, while simultaneously investigating the correlations between the the five functions (independent of biomass and SST), we performed a multivariate Bayesian mixed effect regression model:
+
+$$\begin{bmatrix}log(Y_{ExN,i}) \\ log(Y_{ExP,i}) \\ log(Y_{Prod,i}) \\ log(Y_{Herb,i}) \\ log(Y_{Pisc,i}) \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
 $$S = \begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\
@@
 \begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\
-0 & \sigma_{ExP} & 0 & 0 & 0 \\ 
+0 & \sigma_{ExP} & 0 & 0 & 0 \\with the exclusion of
 0 & 0 & \sigma_{Prod,i} & 0 & 0\\
@@
 $$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} $$
-$$\beta0_{ExN} \sim  student( 3, -3.9, 2.5)\\
-\beta0_{ExP} \sim  student( 3, -6.6, 2.5)\\
-\beta0_{Prod} \sim  student( 3, -4.3, 2.5)\\
-\beta0_{Herb} \sim  student( 3, -2.4, 2.5)\\
-\beta0_{Pisc} \sim  student( 3, -4.6, 2.5)\\
-R \sim lkj\_corr(1)
-$$
+$$\mu_{\textrm{ExP,i}} = (\beta0_{ExP} +  \delta_{ExP, loc} +  \delta_{ExP, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExP}} {x_{sst,i}} $$
+$$\mu_{\textrm{Prod,i}} = (\beta0_{Prod} +  \delta_{Prod, loc} +  \delta_{Prod, site}) +{\beta1_{Prod}} {x_{log(biomass),i}} + {\beta2_{Prod}} {x_{sst,i}} $$
+$$\mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) +{\beta1_{Herb}} {x_{log(biomass),i}} + {\beta2_{Herb}} {x_{sst,i}} $$
+$$\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) +{\beta1_{Pisc}} {x_{log(biomass),i}} + {\beta2_{Pisc}} {x_{sst,i}} $$,
+
+where i is the transect, Y_{ExN,i} is N excretion, Y_{ExP,i} is P excretion, Y_{Prod,i} is biomass production, Y_{Herb,i} is herbivory, Y_{ExN,i} is piscivory, \sigma represents the residual error of each function (ExN, ExP, Prod, Herb, and Pisc), R is the correlation matrix of the residuals.
+Locality- and site-level effects are also structured including covariation among functions.
+There are thus three correlation matrices in total, or in other words the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality-level, site-level, and transect-level.
 
 \noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
-To further optimize convergence of the model, we sampled from the cholesky decomposed triangular matrix L such that $R = LL^T$.
-We used flat priors for the model slopes $\beta1, \beta2$.
+We used a lkj_corr prior for each of the three correlation matrices ($R \sim lkj\_corr(1)$) (ADD REF).
+We used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
 
-The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples  were used to estimate posterior distributions.
-We used Bayesian R2 to estimate the amount of explained variation of each model.
-Posterior predictive checks for are provided in Supporting Informationxxxxx.
+### 4.3 Intercepts-only models
+Additionally, we performed a multivariate intercept-only model to estimate the functions per locality, and a univariate intercept-only model to estimate the multifunction per locality.
+The model structures were similar as the above-mentioned models, the only difference being the exclusion of the predictor variables (sst and biomass).
+Further, we fitted a similar univariate model to predict the multifunction per locality:
+$$\mu_{\textrm{multi,i}} = \beta0_{multi} +  \delta_{multi, loc} +  \delta_{multi, site} $$
 
-\noindent The multivariate  and mixed structure of the above-mentioned model allowed us to extract the correlations between the five functions on the location, site, and  We then assessed the covariation between functions, independent of biomass and sst.
-To do so, we first extracted the median residuals for each function per transect.
-In some transects, there were no piscivores or herbivores observed.
-In those cases, we did not include these transects in the analysis.
-We then quantified the correlations that exist among the different functions using these median residuals.
-Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
-We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
-
-## 4. Effect of community structure on ecosystem functions 
+### 4.4 Effect of community structure on ecosystem functions
 \noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, Additionally, we quantified the transect-level species richness.
@@
 
-<!-- \begin{equation} -->
 $$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
-<!-- 	\label{modcom1} -->
-<!-- \end{equation}      -->
 
-<!-- \begin{equation} -->
 $\begin{array}{c} \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \\ \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} \end{array}$
-<!-- 	\label{modcom2} -->
-<!-- \end{equation} -->
 
-To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
-We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations, and used weakly-informative priors [@Burkner2017].
+### 4.5 Model specifications
+We ran all Bayesian reggression models using the R package *brms* which uses the stan algorithm.
+The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
+For all models we inspected the MCMC chains and the Rhat for convergence and peformed posterior predictive checks (Appendix xxxx).
+We used Bayesian R2 to estimate the amount of explained variation of each model.
 

### 2021-08-12 text/methods.Rmd
methods

--- 2021-08-04 text/methods.Rmd
@@
 Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.
-Finally, we estimated multifunction, i.e. one measure that combines all five functions by taking the geometric average.
+Finally, we estimated multifunction, i.e.
+one measure that combines all five functions by taking the geometric average of the five standardized functions.
+Using the geometric mean rather than the arithmetic mean because functions are dependent on each other and may vary considerably.
 
@@
 
-## 5. Imputation of herbivory and piscivory
+## 4. Data analysis
 
-## 4. Regression models
-The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and general metabolic theory.
-Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, functions are expected to be positively correlated with temperature.
-To model the effect of biomass and sea surface temperature (sst), while simultaneously investigating the correlations between the the five functions, we performed a multivariate Bayesian mixed effect regression the log-transformed functions for transect-level observations ($i$) including site and location effects:
+### 4.1 Imputation of herbivory and piscivory
+In the underwater visual transect database, 291 transects (3%) did not contained herbivores and 4467 transects (49%) did not contain piscivores yielding false zeros for herbivory and piscivory, respectively.
+We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores.
+In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all.
+To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by fitting two models using the observed herbivory and piscivory rates and then imputing the missing values by taking the means of posterior predictions.
+In other words, we used the predictor values corresponding to missing responses to predict herbivory and piscivory rates.
+As predictor variables, we used all community structure variables described above and sea surface temperature.
+Additionally, we added random effects for localities and sites.
 
-$$\begin{bmatrix}Y_{ExN,i} \\ Y_{ExP,i} \\ Y_{Prod,i} \\ Y_{Herb,i} \\ Y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+First, we simultaneously investigated the effects of biomass and sst on all functions and the correlations among functions (independent of biomass and sst). 
+The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
+Further, because of the known relationship between temperature and parameters related to growth and respiration (see suppl.
+methods), functions are expected to be affected by temperature.
+To model the effects of biomass and sst while simultaneously investigating the correlations between the five functions, we fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
+
+$$\begin{bmatrix}y_{ExN,i} \\ y_{ExP,i} \\ y_{Prod,i} \\ y_{Herb,i} \\ y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+
 $$S = \begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\ 
@@
 
-$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} $$
-$$\beta0_{ExN} \sim  student( 3, -3.9, 2.5)\\
-\beta0_{ExP} \sim  student( 3, -6.6, 2.5)\\
-\beta0_{Prod} \sim  student( 3, -4.3, 2.5)\\
-\beta0_{Herb} \sim  student( 3, -2.4, 2.5)\\
-\beta0_{Pisc} \sim  student( 3, -4.6, 2.5)\\
-R \sim lkj\_corr(1)
+$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
+\mu_{\textrm{ExP,i}} = (\beta0_{ExP} +  \delta_{ExP, loc} +  \delta_{ExP, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExP}} {x_{sst,i}} \\
+\mu_{\textrm{Prod,i}} = (\beta0_{Prod} +  \delta_{Prod, loc} +  \delta_{Prod, site}) +{\beta1_{Prod}} {x_{log(biomass),i}} + {\beta2_{Prod}} {x_{sst,i}} \\
+\mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) +{\beta1_{Herb}} {x_{log(biomass),i}} + {\beta2_{Herb}} {x_{sst,i}} \\
+\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) +{\beta1_{Pisc}} {x_{log(biomass),i}} + {\beta2_{Pisc}} {x_{sst,i}} 
 $$
 
-\noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
-To further optimize convergence of the model, we sampled from the cholesky decomposed triangular matrix L such that $R = LL^T$.
-We used flat priors for the model slopes $\beta1, \beta2$.
+\noindent All parameters $\beta$ were given weakly-informative priors ($\beta1 \sim  normal(1, 1), \beta2 \sim  normal(0, 1)$).
+We applied non-centered parametrisation for site and location effects ($\delta_{loc}, \delta_{site}$) which also included the correlation between site and locality effects across functions.
+The model thus included a total of three correlation matrices that each had the same prior ($R \sim lkj\_corr(1)$).
+All standard deviations had a general weakly-informative prior: $\sigma \sim student(3, 0, 2.5)$.
 
 The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
-We used Bayesian R2 to estimate the amount of explained variation of each model.
-Posterior predictive checks for are provided in Supporting Informationxxxxx.
+The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots.
+Posterior predictive checks for are provided in Supporting Information xxxx.
 

### 2021-08-12 R/functions_plots.R

@@ -1,14 +1,22 @@
 
-make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, mod_mf_siteloc, mod_mf_bm, coords){
+make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
   
-  re <- ranef(mod_mvfun_bm)
-  re_loc <- re$locality[,1,] %>%
-    as.data.frame()
-  colnames(re_loc) <- c("r_loc_Fn", "r_loc_Fp", "r_loc_Gc", "r_loc_Iherb", "r_loc_Ipisc")
+  nsiteloc <- summary_transect %>%
+    group_by(locality) %>%
+    mutate(nsite = length(unique(sites))) %>%
+    select(locality, sites, nsite) %>%
+    unique() 
+  
+  ls1 <- nsiteloc[nsiteloc$nsite==1, ]$locality
+  ls2 <- nsiteloc[nsiteloc$nsite==1, ]$sites
   
   re1 <- ranef(mod_mv_siteloc)
   re_loc1 <- re1$locality[,1,] %>%
     as.data.frame()
+  re_site1 <- re1$sites[,1,] %>%
+    as.data.frame()
+  re_loc1[ls1,] <- re_loc1[ls1,] + re_site1[ls2,]
+  
   colnames(re_loc1) <- c("r1_loc_Fn", "r1_loc_Fp", "r1_loc_Gc", "r1_loc_Iherb", "r1_loc_Ipisc")
   re_loc1 <- re_loc1 %>%
     rownames_to_column("locality") 
@@ -16,30 +24,25 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, mod_mf_siteloc, mod_mf_bm, c
   re2 <- ranef(mod_mf_siteloc)
   re_loc2 <- re2$locality[,1,1] %>%
     as.data.frame()
+  re_site2 <- re1$sites[,1,1] %>%
+    as.data.frame()
+  re_loc2[ls1,] <- re_loc2[ls1,] + re_site2[ls2,]
   colnames(re_loc2) <- c("r1_loc_mf")
   re_loc2 <- re_loc2 %>%
     rownames_to_column("locality") 
-  
-  re3 <- ranef(mod_mf_bm)
-  re_loc3 <- re3$locality[,1,1] %>%
-    as.data.frame()
-  colnames(re_loc3) <- c("r_loc_mf")
-  re_loc3 <- re_loc3 %>%
[…]

### 2021-08-12 R/test.R

@@ -1,0 +1,560 @@
+
+
+loadd(vulnerability)
+loadd(contributions)
+loadd(herb_pisc)
+loadd(summary_transect_imp)
+
+con <- left_join(contributions, vulnerability) %>%
+  left_join(herb_pisc$contributions_herb_pisc) %>%
+  group_by(transect_id) %>%
+  dplyr::summarize(
+    vuln_bm_fi = sum(biomass_p * vuln_fi, na.rm = TRUE),
+    vuln_Fn_fi = sum(Fn_p * vuln_fi, na.rm = TRUE),
+    vuln_Fp_fi = sum(Fp_p * vuln_fi, na.rm = TRUE),
+    vuln_Gc_fi = sum(Gc_p * vuln_fi, na.rm = TRUE),
+    vuln_Iherb_fi = sum(I_herb_p[I_herb_p > 0] * vuln_fi[I_herb_p > 0], na.rm = TRUE),
+    vuln_Ipisc_fi = sum(I_pisc_p[I_pisc_p > 0] * vuln_fi[I_pisc_p > 0], na.rm = TRUE),
+    vuln_bm_cl = sum(biomass_p * vuln_climate, na.rm = TRUE),
+    vuln_Fn_cl = sum(Fn_p * vuln_climate, na.rm = TRUE),
+    vuln_Fp_cl = sum(Fp_p * vuln_climate, na.rm = TRUE),
+    vuln_Gc_cl = sum(Gc_p * vuln_climate, na.rm = TRUE),
+    vuln_Iherb_cl = sum(I_herb_p[I_herb_p > 0] * vuln_climate[I_herb_p > 0], na.rm = TRUE),
+    vuln_Ipisc_cl = sum(I_pisc_p[I_pisc_p > 0] * vuln_climate[I_pisc_p > 0], na.rm = TRUE)) %>%
+  filter(vuln_Ipisc_cl > 0, vuln_Iherb_cl > 0) %>%
+  left_join(summary_transect_imp)
+
+long <- con %>% 
+  pivot_longer(cols = starts_with('vuln'), 
+               names_to = c("null", "fun","type"), names_sep = "_") %>%
+  pivot_wider(names_from = type, values_from = value)
+
+
+rescor <- sum$rescor_pars
+sum$random$locality
+
+test <- left_join(degree_dominance, summary_transect_imp)
+
+library(hitandrun)
+te <- (simplex.sample(20, 100, sort=FALSE))[[1]]
+rowSums(te)
+
+
+ks_area <- function(data){
[…]

### 2021-08-12 text/methods.Rmd

@@
 one measure that combines all five functions by taking the geometric average of the five standardized functions.
-Using the geometric mean rather than the arithmetic mean because functions are dependent on each other and may vary considerably.
+We used the geometric mean because functions are dependent on each other and may vary considerably.
 
@@
 
+where i is the transect, Y_{ExN,i} is N excretion, Y_{ExP,i} is P excretion, Y_{Prod,i} is biomass production, Y_{Herb,i} is herbivory, Y_{ExN,i} is piscivory, \sigma represents the residual error of each function (ExN, ExP, Prod, Herb, and Pisc), R is the correlation matrix of the residuals.
+Locality- and site-level effects are also structured including covariation among functions.
+There are thus three correlation matrices in total, or in other words the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality-level, site-level, and transect-level.
+
+\noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+We used a lkj_corr prior for each of the three correlation matrices ($R \sim lkj\_corr(1)$) (ADD REF).
+We used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
+
 \noindent All parameters $\beta$ were given weakly-informative priors ($\beta1 \sim  normal(1, 1), \beta2 \sim  normal(0, 1)$).
@@
 
-## 4. Effect of community structure on ecosystem functions 
+### 4.3 Intercepts-only models
+Additionally, we performed a multivariate intercept-only model to estimate the functions per locality, and a univariate intercept-only model to estimate the multifunction per locality.
+The model structures were similar as the above-mentioned models, the only difference being the exclusion of the predictor variables (sst and biomass).
+Further, we fitted a similar univariate model to predict the multifunction per locality:
+$$\mu_{\textrm{multi,i}} = \beta0_{multi} +  \delta_{multi, loc} +  \delta_{multi, site} $$
+
+### 4.4 Effect of community structure on ecosystem functions
 \noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, Additionally, we quantified the transect-level species richness.
@@
 
-<!-- \begin{equation} -->
 $$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
-<!-- 	\label{modcom1} -->
-<!-- \end{equation}      -->
 
-<!-- \begin{equation} -->
 $\begin{array}{c} \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \\ \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} \end{array}$
-<!-- 	\label{modcom2} -->
-<!-- \end{equation} -->
 
-To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
-We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations, and used weakly-informative priors [@Burkner2017].
+where $i$ represents the transects, $\beta_0$ is the intercept, $\beta_1$ to $\beta_{12}$ are the fixed effect parameters, $\delta_{loc}$ is the random effect of the locality, $\delta_{site}$ is the random effect of the site, biomass represents the total standing stock biomass of the community, sst the sea surface temperature, richness is the species richness, size is the total length, troph is the trophic level, imm is the immaturity, and $m$, $2.5\%$, and $97.5\%$ respectively represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community.
+For these models, we used uninformative priors for the fixed effect parameters ($\beta_{1-12}$) and weakly informative priors for the standard deviations of residuals and random effects (ADD THE PRIOR).
+To insure that the performed Imputationdidn't change main results of the downstream regression models, we repeated all below-mentioned models on a subset of the transect data, excluding the original missing values.
+Results of models are shown in the supplementary information xxxxxxx.
+
+### 4.5 Model specifications
+We ran all Bayesian reggression models using the R package *brms* which uses the stan algorithm.
+The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
+For all models we inspected the MCMC chains and the Rhat for convergence and peformed posterior predictive checks (Appendix xxxx).
+We used Bayesian R2 to estimate the amount of explained variation of each model.
 

### 2021-08-13 R/functions_analysis.R
multi function change

@@ -520,11 +520,12 @@ validate_model <- function(fit, save_plots = TRUE, name = "Title", pars = NULL){
 ##### Models #####
 ##### 1) only site and location 
 fit_mvfun_siteloc <- function(data){
-  brm(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc)) ~ 
-        (1|s|sites) + (1|p|locality),
+  brm(mf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc))|mi() ~ 
+        (1|s|sites) + (1|p|locality)) + 
+        set_rescor(rescor = TRUE),
       data = data, cores = 4,
       backend = "cmdstanr",
-      threads = threading(10))
+      threads = threading(12))
   
 }
 fit_mf_siteloc <- function(data){
@@ -550,7 +551,7 @@ fit_mvfun_bm <- function(data){
     set_prior(prior = "normal(1,1)", class = "b", coef = "logbiomass_tot", resp = "logIpisc") +
     set_prior(prior = "normal(0,1)", class = "b", coef = "mean", resp = "logIpisc") 
   
-  brm(bf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc)) ~ 
+  brm(bf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc))|mi() ~ 
         log(biomass_tot) + mean + (1|s|sites) + (1|p|locality)) + 
         set_rescor(rescor = TRUE),
       data = data, cores = 4,
@@ -579,8 +580,7 @@ fit_mvfun_com <- function(data){
                   Fp_st = standard(log(Fp)),
                   Gc_st = standard(log(Gc)),
                   I_herb_st = standard(log(I_herb)),
-                  I_pisc_st = standard(log(I_pisc)),
-                  multi_st = standard(log(multi)))
+                  I_pisc_st = standard(log(I_pisc)))
   
   prior <- 
     set_prior(prior = "normal(1,1)", class = "b", coef = "standardlogbiomass_tot", resp = "Fnst") +
@@ -594,63 +594,63 @@ fit_mvfun_com <- function(data){
     set_prior(prior = "normal(1,1)", class = "b", coef = "standardlogbiomass_tot", resp = "Ipiscst") +
     set_prior(prior = "normal(0,1)", class = "b", coef = "standardmean", resp = "Ipiscst") +
     
[…]

### 2021-08-13 R/functions_plots.R

@@ -21,15 +21,25 @@ make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
   re_loc1 <- re_loc1 %>%
     rownames_to_column("locality") 
   
-  re2 <- ranef(mod_mf_siteloc)
-  re_loc2 <- re2$locality[,1,1] %>%
-    as.data.frame()
-  re_site2 <- re1$sites[,1,1] %>%
-    as.data.frame()
-  re_loc2[ls1,] <- re_loc2[ls1,] + re_site2[ls2,]
-  colnames(re_loc2) <- c("r1_loc_mf")
-  re_loc2 <- re_loc2 %>%
-    rownames_to_column("locality") 
+  re_loc1 <- re_loc1 %>%
+    group_by() %>%
+    mutate(r1 = normalize(r1_loc_Fn),
+           r2 = normalize(r1_loc_Fp),
+           r3 = normalize(r1_loc_Gc),
+           r4 = normalize(r1_loc_Iherb),
+           r5 = normalize(r1_loc_Ipisc)) %>%
+    rowwise() %>%
+    mutate(r_multi = geomean(r1, r2, r3, r4, r5))
+  
+  # re2 <- ranef(mod_mf_siteloc)
+  # re_loc2 <- re2$locality[,1,1] %>%
+  #   as.data.frame()
+  # re_site2 <- re1$sites[,1,1] %>%
+  #   as.data.frame()
+  # re_loc2[ls1,] <- re_loc2[ls1,] + re_site2[ls2,]
+  # colnames(re_loc2) <- c("r1_loc_mf")
+  # re_loc2 <- re_loc2 %>%
+  #   rownames_to_column("locality") 
  
 
   
@@ -41,10 +51,10 @@ make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
     left_join(coords) %>%
     unique()
   
-  
-  data2 <- (re_loc2) %>%
-    left_join(coords) %>%
-    unique()
+  # 
+  # data2 <- (re_loc2) %>%
+  #   left_join(coords) %>%
+  #   unique()
   
   library("rnaturalearth")
   library("rnaturalearthdata")
@@ -249,14 +259,14 @@ make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
   pal <- c("black", "grey60", "deepskyblue1")
   
   f <-
-    ggplot(data2) + 
+    ggplot(data) + 
[…]

### 2021-08-13 R/functions_wrangling.R

@@ -330,7 +330,8 @@ comm <-
   }) %>% plyr::ldply()
 
 ## combine all variables per transect
-tfs <- left_join(tfs, comm)
+tfs <- left_join(tfs, comm) 
+
 
 return(tfs)
 }
@@ -436,7 +437,11 @@ tfs <- dplyr::group_by(tfish, region, locality, sites, area, transect_id) %>%
   dplyr::summarise(
     I_herb = sum(I[herb == TRUE], na.rm = TRUE),
     I_pisc = sum(I[pisc == TRUE], na.rm = TRUE),
-  ) %>% ungroup() 
+  ) %>% ungroup() %>%
+  mutate(I_herb = case_when(I_herb == 0 ~ NA_real_,
+                            TRUE ~ I_herb),
+         I_pisc = case_when(I_pisc == 0 ~ NA_real_,
+                            TRUE ~ I_pisc))
 
 
 contr <- dplyr::group_by(tfish, region, locality, sites, area, transect_id) %>% 

### 2021-08-13 R/plan.R

@@ -46,11 +46,11 @@ plan <- drake_plan(
   summary_transect_complete = combine_summary(summary_transect, herb_pisc),
   
   # subset 
-  summary_transect_sub = subset_data(summary_transect_complete),
+  #summary_transect_sub = subset_data(summary_transect_complete),
   
   # imputation 
-  imp = impute(summary_transect_complete),
-  summary_transect_imp = imp[[1]],
+  #imp = impute(summary_transect_complete),
+  #summary_transect_imp = imp[[1]],
   
   ##### models #####
   # run models only with biomass ans sst
@@ -66,33 +66,33 @@ plan <- drake_plan(
   # commodels_real = run_commodels_abs(summary_transect_complete),
   
   # site loc
-  mod_mv_siteloc = fit_mvfun_siteloc(summary_transect_imp),
-  mod_mf_siteloc = fit_mf_siteloc(summary_transect_imp),
+  mod_mv_siteloc = fit_mvfun_siteloc(summary_transect_complete),
+  #mod_mf_siteloc = fit_mf_siteloc(summary_transect_imp),
   
   # add biomass sst
-  mod_mvfun_bm = fit_mvfun_bm(summary_transect_imp),
-  mod_mf_bm = fit_mf_bm(summary_transect_imp),
+  mod_mvfun_bm = fit_mvfun_bm(summary_transect_complete),
+  #mod_mf_bm = fit_mf_bm(summary_transect_imp),
   
   # community analysis
-  mod_mvfun_com = fit_mvfun_com(summary_transect_imp),
-  mod_mvfun_com2 = fit_mvfun_com2(summary_transect_imp), #get absolute slopes
-  mod_mf_com = fit_mf_com(summary_transect_imp), 
+  mod_mvfun_com = fit_mvfun_com(summary_transect_complete),
+  mod_mvfun_com2 = fit_mvfun_com2(summary_transect_complete), #get absolute slopes
+  #mod_mf_com = fit_mf_com(summary_transect_imp), 
   
   # Same models with data subset
-  mod_mv_siteloc_sub = fit_mvfun_siteloc(summary_transect_sub),
-  mod_mf_siteloc_sub = fit_mf_siteloc(summary_transect_sub),
[…]

### 2021-08-13 R/test.R

@@ -558,3 +558,50 @@ mod_mf_siteloc %>%
             rtot_ub = quantile(r_tot, 0.975),
             )
 ran
+
+
+
+loadd(mod_mvfun_bm)
+
+nd <- data.frame(biomass_tot = seq(50,500, 4), mean = 26, locality = NA, sites = NA)
+
+fit <- predict(mod_mvfun_bm, newdata = nd, summary = F, nsamples = 1000)
+ef <- fit
+
+ef[,,1] <- normalize(exp(ef[,,1]))
+ef[,,2] <- normalize(exp(ef[,,2])) 
+ef[,,3] <- normalize(exp(ef[,,3])) 
+ef[,,4] <- normalize(exp(ef[,,4])) 
+ef[,,5] <- normalize(exp(ef[,,5])) 
+
+mf <- apply(ef, 1:2, geomean)
+mf[,] <- normalize(mf[,])
+
+f1_m <- apply(ef[,,1], 2, mean) 
+mf_m <- apply(mf, 2, mean) 
+mf_lb <- apply(mf, 2, quantile, 0.025) 
+mf_ub <- apply(mf, 2, quantile, 0.975) 
+
+ggplot() +
+  geom_ribbon(aes(x = nd$biomass_tot, ymin = mf_lb, ymax = mf_ub), alpha = 0.5)+
+  geom_line(aes(x = nd$biomass_tot, y= (mf_m))) 
+
+lm(log(mf_m)~log(nd$biomass_tot))
+lm(log(f1_m)~log(nd$biomass_tot))
+
+sub <- ef[,1,]
+hist(sub[,1])
+
+test <- apply(sub, 1, geomean)
+
+summary(test)
+
+sub <- ef[,100,]
+hist(sub[,1])
+
+test <- apply(sub, 1, geomean)
+
+summary(test)
+
+
+

### 2021-08-13 R/functions_analysis.R
fix bug

@@ -520,7 +520,7 @@ validate_model <- function(fit, save_plots = TRUE, name = "Title", pars = NULL){
 ##### Models #####
 ##### 1) only site and location 
 fit_mvfun_siteloc <- function(data){
-  brm(mf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc))|mi() ~ 
+  brm(bf(mvbind(log(Fn), log(Fp), log(Gc), log(I_herb), log(I_pisc))|mi() ~ 
         (1|s|sites) + (1|p|locality)) + 
         set_rescor(rescor = TRUE),
       data = data, cores = 4,

### 2021-08-14 R/functions_plots.R
update figure code

@@ -1,5 +1,5 @@
 
-make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
+make_fig1 <- function(mod_mv_siteloc, coords, summary_transect){
   
   nsiteloc <- summary_transect %>%
     group_by(locality) %>%
@@ -374,7 +374,7 @@ make_fig1 <- function(mod_mv_siteloc, mod_mf_siteloc, coords, summary_transect){
 
 
 
-make_fig2 <- function(commodels){
+make_fig2 <- function(mod_mvfun_com){
   
   fe <- brms::fixef(mod_mvfun_com) %>%
     as.data.frame() %>%
@@ -422,7 +422,7 @@ make_fig2 <- function(commodels){
                    position = position_dodge(.7), size = 1, linetype = 1) +
     geom_point(aes(x = var, y = Estimate, color = dep), position = position_dodge(.7), size = 3) +
     coord_flip() +
-    scale_y_continuous(lim = c(-0.22, 0.22)) +
+   # scale_y_continuous(lim = c(-0.22, 0.22)) +
     theme_minimal() +
     scale_color_fish_d(option = "Callanthias_australis",
                        labels = c("N excretion", "P excretion", "Production", "Herbivory", "Piscivory"),
@@ -443,55 +443,6 @@ make_fig2 <- function(commodels){
     )  
   slopes
   ggsave("output/plots/fig2_com_slopes.png", slopes, width = 8, height = 9)
-  
-  
-  fe2 <-
-    brms::fixef(mod_mf_com) %>%
-    as.data.frame() %>%
-    tibble::rownames_to_column("name") %>%
-    dplyr::filter(!name == "Intercept") %>%
-    filter(!name == "standardlogbiomass_tot") %>%
-    filter(!name == "standardmean") %>%
-    mutate(name = fct_relevel(name,
-                              "standardimm_q1",
-                              "standardimm_m",
-                              "standardimm_q3",
-                              "standardsize_q1",
-                              "standardsize_m",
-                              "standardsize_q3",
-                              "standardtroph_q1",
-                              "standardtroph_m",
-                              "standardtroph_q3",
-                              "standardnspec"
-    ))
-  
-  slopes2 <-
-    ggplot(fe2) +
-    geom_vline(xintercept = seq(1, 10 ,1) + .5, color = "lightgrey",
-               size = 0.5, linetype = 1, alpha = 0.7) +
[…]

### 2021-08-16 text/methods.Rmd
methods of mv models updated

--- 2021-08-12 text/methods.Rmd
@@
 ## 1. Underwater visual census database
-\noindent We used a published global database of reef fish abundance and sizes collected along belt transects [@Barneche2019].
+\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019].
 This database encompasses 9118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic.
@@
 Transects were carried out at a constant depth, parallel to the reef crest.
-We selected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize the bias related to the identification of small individuals, and finally we discarded rare species, for which less than 20 individuals were ever recorded across all transects.
-The dataset then included 1110 species that belong to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm to minimize the bias related to the identification of small individuals, and rare species for which less than 20 individuals were ever recorded across all transects.
+The dataset then included 1110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
 Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration of the USA (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).
-Further, for each transect (fish community), we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
+Further, for each transect, we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
+All data wrangling and analyses were performed in the software program R (version 4.0.2; R core team 2020).
 
 ## 2. Quantification of functions
-\noindent For each transect, we estimated five key process-based functions mediated by fishes: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e.
+\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN/day/m^2^), phosphorus excretion rate (gP/day/m^2^), production of biomass through growth (gC/day/m^2^), herbivory, i.e.
 ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e.
 ingestion rate of fishes (g/day/m^2^) [@Brandl2019front].
-These five functions were estimated in each transect using individual-based bioenergetic models that predict elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
-The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
+These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g.
+daily C intake rates, N and P excretion rates, growth rates) [@Schiettekatte2020].
+This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
 We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
-We ran an individual bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the summed estimates on the fish community level per surface area (m^2^).
-Each function is thus expressed in dry mass (of C, N, or P) per day per square meter.
-We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020].
+We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each function in each transect.
+Finally, we summarized functions on the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area.
+Each function is thus expressed as dry mass (of C, N, or P) per day per square meter.
+We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020.
 To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
@@
 
-## 4. Data analysis
+## 4. Multivariate regression models
 
-### 4.1 Imputation of herbivory and piscivory
+We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level, (2) investigate the effects of bioimass and sst, and the correlations among functions independent of biomass and sst, and (3) estimate the effects of the community structure on each function.
+\par
+
 In the underwater visual transect database, 291 transects (3%) did not contained herbivores and 4467 transects (49%) did not contain piscivores yielding false zeros for herbivory and piscivory, respectively.
@@
 In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all.
-To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by fitting two models using the observed herbivory and piscivory rates and then imputing the missing values by taking the means of posterior predictions.
-In other words, we used the predictor values corresponding to missing responses to predict herbivory and piscivory rates.
-As predictor variables, we used all community structure variables described above and sea surface temperature.
-Additionally, we added random effects for localities and sites.
+To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by adding these observations as parameters in the multivariate models.
+\par
 
-First, we simultaneously investigated the effects of biomass and sst on all functions and the correlations among functions (independent of biomass and sst). 
+First, we performed a multivariate intercept-only regression model with the five -log-transformed functions to estimate the functions per locality.
+The model structure includes intercepts and random effects for localities and sites:
+
+$$\begin{bmatrix}y_{ExN,i} \\ y_{ExP,i} \\ y_{Prod,i} \\ y_{Herb,i} \\ y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+
+$$
+\mu_{\textrm{ExN,i}}  = (\beta0_{ExN}  +  \delta_{ExN, loc}  +  \delta_{ExN, site}) \\
+\mu_{\textrm{ExP,i}}  = (\beta0_{ExP}  +  \delta_{ExP, loc}  +  \delta_{ExP, site})  \\
+\mu_{\textrm{Prod,i}} = (\beta0_{Prod} +  \delta_{Prod, loc} +  \delta_{Prod, site}) \\
+\mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) \\
+\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) ,
+$$
+
+$$
+S = \begin{bmatrix}
+\sigma_{ExN} & 0 & 0 & 0 & 0\\
+0 & \sigma_{ExP} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{Prod,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{Herb} & 0\\
+0 & 0 & 0 & 0 & \sigma_{Pisc}
+\end{bmatrix}
+R
+\begin{bmatrix}
+\sigma_{ExN} & 0 & 0 & 0 & 0\\
+0 & \sigma_{ExP} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{Prod,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{Herb} & 0\\
+0 & 0 & 0 & 0 & \sigma_{Pisc}
+\end{bmatrix},
+$$
+
+where i is the index of the transect, y_{ExN,i} is the N excretion rate of transect i, y_{ExP,i} is the P excretion rate, y_{Prod,i} is the biomass production rate, y_{Herb,i} is the herbivory rate, y_{ExN,i} is the piscivory rate, \sigma represents the residual error of each function (ExN, ExP, Prod, Herb, and Pisc), R is the correlation matrix of the residuals.
+Locality- and site-level effects are also structured including covariation among functions.
+There are thus three correlation matrices in total, or in other words the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality-level, site-level, and transect-level.
+
+\noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+We used a lkj_corr prior for each of the three correlation matrices ($R \sim lkj\_corr(1)$).
+
+Second, we ran a mixed-effect model to simultaneously investigate the effects of biomass and sst on all functions and the correlations among functions (independent of biomass and sst).
 The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
@@
 methods), functions are expected to be affected by temperature.
-To model the effects of biomass and sst while simultaneously investigating the correlations between the five functions, we fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
+We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
 
@@
 
-$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
+$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
 \mu_{\textrm{ExP,i}} = (\beta0_{ExP} +  \delta_{ExP, loc} +  \delta_{ExP, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExP}} {x_{sst,i}} \\
@@
 
-\noindent All parameters $\beta$ were given weakly-informative priors ($\beta1 \sim  normal(1, 1), \beta2 \sim  normal(0, 1)$).
-We applied non-centered parametrisation for site and location effects ($\delta_{loc}, \delta_{site}$) which also included the correlation between site and locality effects across functions.
-The model thus included a total of three correlation matrices that each had the same prior ($R \sim lkj\_corr(1)$).
-All standard deviations had a general weakly-informative prior: $\sigma \sim student(3, 0, 2.5)$.
+where $\beta1_{ExN}, \beta1_{ExP}, \beta1_{Prod}, \beta1_{Herb}, \beta1_{Pisc}$ are the fixed effects of the log-transformed biomass, and $\beta2_{ExN}, \beta2_{ExP}, \beta2_{Prod}, \beta2_{Herb}, \beta2_{Pisc}$ are the fixed effects of sst.
+Locality- and site-level effects are now thus structured including covariation among functions, independent of biomassand sst.
+Similarly, the residual variation of functions incorporates the correlations between functions, without the effect of biomass and sst.
+We used similar priors as describved above, and we used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
 
+\noindent Finally, to investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
+
+$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} x_{log(biomass),i} + \beta2_{function} x_{sst,i}  + \beta3_{function} x_{richness,i}  + \beta4_{function} x_{size_m,i}  + \beta5_{function} x_{size_{2.5\%},i} +  \beta6_{function} x_{size_{97.5\%},i} + \\ \beta7_{function} x_{troph_m,i}  + \beta8_{function} x_{troph_{2.5\%},i} +  \beta9_{function} x_{troph_{97.5\%},i} + \beta10_{function} x_{imm_m,i}  + \beta11_{function} x_{imm_{2.5\%},i} +  \beta12_{function} x_{imm_{97.5\%},i} $$
+
+where richness is the species richness, $size$ is the total length, $troph$ is the trophic level, $imm$ is the immaturity, and $m$, $2.5\%$, and $97.5\%$ respectively represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community.
+For these models, we used weakly informative priors for the fixed effect parameters ($\beta3-\beta12 \sim normal(0,1)$) and the same priors as described above for other parameters. par
+
+All models were fitted using brms (ref).
 The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
@@
 Posterior predictive checks for are provided in Supporting Information xxxx.
-
-\noindent The multivariate and mixed structure of the above-mentioned model allowed us to extract the correlations between the five functions on the location, site, and  We then assessed the covariation between functions, independent of biomass and sst.
-To do so, we first extracted the median residuals for each function per transect.
-In some transects, there were no piscivores or herbivores observed.
-In those cases, we did not include these transects in the analysis.
-We then quantified the correlations that exist among the different functions using these median residuals.
-Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality.
-We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.
-
-## 4. Effect of community structure on ecosystem functions 
-\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, Additionally, we quantified the transect-level species richness.
-For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).
-
-<!-- \begin{equation} -->
-$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
-<!-- 	\label{modcom1} -->
-<!-- \end{equation}      -->
-
-<!-- \begin{equation} -->
-$\begin{array}{c} \mu_{j} = \beta_0 + \beta_1 x_{log(biomass),j} + \beta_2 x_{sst,j}  + \beta_3 x_{richness,j}  + \beta_4 x_{size_m,j}  + \beta_5 x_{size_{2.5\%},j} +  \beta_6 x_{size_{97.5\%},j} + \\ \beta_7 x_{troph_m,j}  + \beta_8 x_{troph_{2.5\%},j} +  \beta_9 x_{troph_{97.5\%},j} + \beta_{10} x_{imm_m,j}  + \beta_{11} x_{imm_{2.5\%},j} +  \beta_{12} x_{imm_{97.5\%},j} \end{array}$
-<!-- 	\label{modcom2} -->
-<!-- \end{equation} -->
-
-To compare effects across functions and assess the relative importance of each variable, we standardized all variables prior to model fitting.
-We fitted all 5 models by using 4 cores, that each had 2000 iterations with a warm-up of 1000 iterations, and used weakly-informative priors [@Burkner2017].
+We ran all Bayesian reggression models using the R package *brms* which uses the stan algorithm.
+The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
 

### 2021-08-17 varia/NEE/Response_to_reviewers.Rmd
methods almost done

---
output:
  word_document:
    fig_caption: yes
    reference_docx: ../text/word_template.docx
---
# Response to reviewers

## Reviewer #1 (Remarks to the Author):

Nature Ecology and Evolution review:
Global Drivers and vulnerabilities of coral reef fish functions

My overall opinion of this manuscript is positive. The global distribution of these fish functions on coral reefs has not been previously assessed, nor has their overlap or vulnerability. There’s clear novelty, broad interest, compelling results, the manuscript is generally well written and well-structured, and the authors use multiple extensive datasets and a wide array of sound laboratory and statistical methods. Therefore, my overall recommendation is that this article will ultimately be publishable in Nature Ecology and Evolution. However, I am recommending a major revision because this manuscript needs to be substantially improved. While there is little to criticize regarding most of the data, methods, and results, the paper is severely lacking in sufficient detail and information. In many instances, not nearly enough information is provided for the reader to fully comprehend what is being presented, and in some instances key data or methods elements are not provided. There
are also too many bold and unnecessary statements that are not properly backed up by the given citations. The authors should also check for grammar errors, as I encountered many throughout the paper. Lastly, there are two instances where I believe the methods are not optimal and should be improved (calculating correlations between functions and estimating species’ length infinity). I will go through the paper line by line and provide my comments and suggestions:

*Thank ypou for your constructive and detailed review. We have now clarified and detailed methods throughout. Further, we updated the approach to estimating correlations by applying multivariate models as suggested. We also thoroughly checked for grammar errors and modified the main text substantially. Overall, we incorporated all comments with exception of the suggested approach to estimating species length infinity. We provide more details of the modifications below.*

Line 3: why not just say “Preserving ecosystem functioning is a critical challenge…”
*We now state "Preserving the functioning of coral reefs is a critical challenge of the 21st century."*

Line 10: what is meant here by “diverging,” perhaps a better word choice is needed.
*Changed to "varying"*

Line 20: these first two statements are overly bold and not well-focused. The authors would do better to precisely outline the issues they fill with this research article, and to do succinctly, with concise, information-driven, factual sentences. Have people really been managing coral reef fisheries with a surplus-production model for thousands of years? Even if true, does this information help place your reader in the context of your study? The citation given referencing millennia of production-based management schemes is not an article about historical ecosystem impacts, but a modern, long-term plant biodiversity experiment. The authors should improve these aspects throughout the paper and ensure proper citations are given.

Line 32: Coral reef ecosystem services are crucial for people throughout the tropics, but not necessarily all of humanity. You might want to replace humanity with something more focused. The sentence that follows about cycling elements to thrive in nutrient-poor waters is out of place and breaks the flow. What you want is to connect the importance of reef ecosystem services to their threats, so this sentence should be removed.
*We removed "to humanity" and the sentence about efficient cycling of elements.*

Line 54: this should say coral reefs, not just reefs, since you do not include other types of reefs, e.g., rocky reefs from temperate locations.
*Done.*

A general comment for the entire results section: very few of the actual results are presented - there is little to no information on the analyses used, there are no numbers/data/statistics provided, and the main results are very quickly glossed over. While the format of NEE dictates that much information be provided in the supplementary material, sufficient information must still be given for the reader to understand how you achieved your conclusions. A good example comes on line 126, where the authors state that by “combining vulnerability scores and species contributions,” they demonstrate how fishing and coral loss will impact fish functions, then a figure reference is provided. The reader has no idea how these things were combined or what analyses were done to reach these conclusions. In the paragraph beginning on line 54, when the authors state that fish functions vary substantially, as a reader I am expecting to find out how they vary, which ones covary, which areas of
the world have high or low functions or high or low multifunctionality, yet all that is stated is that herbivory is negatively correlated with phosphorus excretion. So, while the authors state that they demonstrate clear tradeoffs in services and that biomass alone is insufficient, I must take them for the word and rely only on a figure to provide any detail.

*We now wrote a new, seperate results section.*

Paragraph beginning on line 86: no information is given here as to how these contributions were calculated. The reader will have to constantly reference the supplementary methods to understand the results of the paper.

Coming back to line 126: no information is provided as to how this analysis was done or what was quantified, and no actual quantitative results are given. As a reader it’s hard to believe that anything has been truly demonstrated when the only information given is a figure.

Concluding paragraph: I suggest the authors spend some time reflecting about the management implications of this work. Are there certain high or low functioning areas that should be prioritized? If we have limited resources but need to prioritize some functions, or combinations of functions, to preserve, which should they be?

Figure 3: I am a bit confused on how to interpret the x axis. Negative coefficients indicate higher contribution to function while positive indicate higher contribution to biomass? So, Lethrinids contribute highly to biomass but not piscivory? Please try to make this clearer for the reader.
*The x-axis was showing the difference between the contribution to function and the contribution to biomass. This means that higher values indicate that a certain family tends to contribute more than a certain function compared to its biomass. We now removed this figure, because it seemed to be more confusing than informative.*

Methods: something critical has been missed here despite the extensive use of Bayesian mixed effects models in this paper. These data have an important, intrinsic hierarchical structure that has not been accounted for nor mentioned. In these data, transects are nested in sites, which are nested in localities. This needs to be stated upfront for the reader to understand the structure of the data and its implications. Furthermore, some models may need to be adjusted to account for this hierarchy. Observations from the same spatial units are non-independent and likely exhibit some degree of autocorrelation, so the statistical methods must account for this non-independence. Hence, the models used should be adjusted to include varying intercept random effects for site and locality.

*We adapted all models to include random effects for site and locality and we modeled all five functions simultaneously in a multivariate model structure. Further, we now explicitly discuss the hierarchical structure of the uvc dataset at the start of the method section.*

Line 8: when you selected families for which you have data, was there a minimum in terms of the number of species in this family for which you had data? For instance, did you select an entire family even if you only had data on one species within the family?

*To check.*

Line 26/27: here I am getting a bit lost. You say you ran “the model” yet no model has been presented. You then say you ran this model for every combination of body sizes and sea surface temperatures, yet as a reader I don’t know anything about body sizes or sea surface temperatures at this point in the methods/data, so it’s impossible for me to gauge what exactly you are doing. Furthermore, there has been no mention of what environmental data were used or where they came from. You mention sea surface temperatures, but not whether these were measured in-situ during fish transects or came from satellite sources or a climate model. For all instances of environmental data in the paper, the source and resolution of these data must be provided.
*The model mentioned here is talking about the bioenergetic model 'fishflux' that estimates fluxes of carbon, nitrogen, and phosphorus. We now reworded this section to clarify this. We also added mentions of body size and sea surface temperature in the first section of the methods.*

Line 45: a reference should be given for temperature.
*We added the reference for sea surface temperature in the first section of the methods.*

Line 47-50: you’ve stated that a mixed effect model was performed but the equation given clearly shows a simple linear model with no random effects, so this isn’t actually a mixed effects model. However, it should be. If I am clearly understanding this section the authors have performed, for each function, a simple liner regression of function ~ log(biomass) + SST, and they have extracted the transect-level residuals. Then, they’ve tested the raw Pearson correlations between the residuals for the different pairs of functions. There are multiple issues here. 1) this approach does not account for the spatial hierarchy of the data, so it ignores spatial non-independence as well as uneven sampling effort. Locations with the highest sampling intensity will thus drive the resulting patterns. This needs to be a mixed effects model with random effects for site and locality. Curiously, the authors state just afterwards that they did run a mixed effects model of this nature, but no
further information is given. 2) Running a correlation on the residuals of a linear model instead of running a multiple regression is an inappropriate analysis. Please see Freckleton, R.P. (2002), On the misuse of residuals in ecology: regression of residuals vs. multiple regression. Journal of Animal Ecology, 71: 542-545 for a thorough review of this issue. Please also see McElreath, Richard. Statistical rethinking: A Bayesian course with examples in R and Stan. CRC press, 2020, particularly Chapter 5 page 137, which states:

“Residuals are parameters, not data. There is a tradition, especially in parts of biology, of using residuals from one model as data in another model. For example, a biologist might regress brain size on body size and then use the brain size residuals as data in another model. This procedure is always a mistake. Residuals are not known. They are parameters, variables with unobserved values. Treating them as known values throws away uncertainty. The right way to adjust for body size is to include it in the same model, preferably a model designed in light of an explicit causal model.”

If all parameters are standardized, regression coefficients are equivalent to correlation coefficients. Thus, in the simplest sense, if you wanted to know the correlation strength between, for example, herbivory and phosphate excretion while accounting for the spatial hierarchy of your data and controlling for biomass and SST, you could run a Bayesian mixed effects model of herbivory ~ phosphate + biomass + SST, or phosphate ~ herbivory + biomass + SST (both of which would provide the same correlation strength). However, the most appropriate way to do this analysis is probably to perform a multivariate mixed effects model (like others performed in this paper), with [herbivory, piscivory, phosphate excretion, nitrate excretion, production] ~ biomass + SST, and to extract the correlation coefficients between the functions from this model. This will provide equivalent results to what several sets of mixed effects regressions between each pair of standardized functions would provide,
but in one holistic analysis.

*We agree with the reviewer on both arguments made. We now included random effects of localities and sites. Further, to estimate correlation coefficients we opted for the most elegant option - multivariate mixed-effects models. This enabled us to estimate correlations on the site, locality, and residual level, as is now shown in figure 2. The only obstacle for using multivariate models was that some transects have false zeros for herbivory or piscivory. We solved this issue by including these observations as missing values, essentially handling them as parameters in the model. This is now explained in the methods section as followed:*
*"In the underwater visual transect database, 291 transects (3%) did not contained herbivores and 4467 transects (49%) did not contain piscivores yielding false zeros for herbivory and piscivory, respectively. We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores. In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all. To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by adding these observations as parameters in the multivariate models."*

Line 48: does community-level refer to transect? If so, state that.
*Indeed, we now stated this.*

Line 58: because the structure of the data has not yet been presented, the reader is not aware of what a “locality” is, so make sure to sufficiently introduce the data in the beginning of the methods.
*We now introduce the structure of the data in the beginning of the methods.*

Line 72: You should state why each function was log-transformed.
*Functions were log-transformed to ensure a normal distribution of residual errors and to incorporate the allometric relationship with biomass of most functions due to metabolic theory. We now state is in the methods.*

Line 76: again, this appears to be a simple linear model with no random effects, and therefore not a mixed effects model. Perhaps I am missing something? In either case, this model should also be a mixed effects model that accounts for the data structure: transects nested in sites nested in localities, otherwise your data could be highly biased by uneven sampling effort between localities and by autocorrelation within localities.
*As stated earlier, we now included random effects.*

Line 82: What were these weakly informative priors? Standard practice is to provide this as part of the model equation/formula to be completely transparent with the model. Secondly, no information has been given as to how the models were evaluated? There must have been some assessment of model quality? Minimally R hat, chain convergence, posterior predictive checks, etc.
*We now provide the priors we used, and specified how we assessed the model quality. Specifically, we checked, the R hat, trace plots, and posterior prediction plots.*

Line 104: I’d encourage the authors to read carefully over their manuscript. This sentence is an example where the phrase is ambiguous and not clear. “To know how often species are contributing more than average” to me means: in how many transects is there a species that dominates the function. However, what the authors mean is for each species, how often does it dominate a function. So, it is a species-by-species analysis and not a transect-level analysis, and this needs to be clear.
*We now modified the wording to: "Finally, we quantified the frequency of dominance per species, i.e. the number of transects in which a species is dominant for a given function divided by the total number of transects in which that species is observed."*

Line 117: It’s unclear to me whether the authors developed their own model based on the scores from Graham et al, or if they used a model already produced by Graham et al.
*We used the scores from Graham et al. to create a new model and used the model to predict the scores for species that are not provided in that paper.*

Line 120: why are model formulas/equations provided for other Bayesian models but not here?
*We now added the equations.*

Line 121: Reference the supplementary figure otherwise the reader has no basis on which to believe there was a good model fit.
*to do*

Line 127-130: this information is passed over very quickly without enough detail. Please expand this section to better explain exactly how this analysis was done and make it clearer for the reader as to how it should be interpreted.
*We now removed this sentence and calculation because we now opt to show the vulnerability scores per community, rather than proportions.*

Line 10: Here the authors have extracted max lengths from FishBase and substituted them for length infinity. Max length and length infinity, while similar values, are not interchangeable. Froese & Binohlan (2005) specifically published methods on how to estimate length infinity from FishBase max length and provided the formula to do so on the FishBase downloads page. The authors could easily convert these raw max length values to estimated length infinity values using this approach. The authors should either make this adjustment or specify why this was not done.

Froese, R. and Binohlan, C. (2000), Empirical relationships to estimate asymptotic length, length at first maturity and length at maximum yield per recruit in fishes, with a simple method to evaluate length frequency data. Journal of Fish Biology, 56: 758-773.

*to do*

Line 11: what is this standardized coefficient? Is there a reference?

Line 14: Be careful to reword this sentence, you’ve filtered out all other species than the species in your species list, not the other way around.

Line 15: I am a bit lost here, what is the “length-frequency method” is this also from Morais?

Line 17: again, what temperatures are you referring to? No information has been given about temperature to this point in the manuscript.

Line 18: “additional” otolith data implies that there were otolith date previously referenced in the manuscript. If this is not the case be sure not to confuse the reader.

Line 19: “All fishes” - there is no information given on how many species were collected or how many families these species represented. You should also mention how these fishes were collected – what method and were they euthanized, etc.?

Line 41: Here you state that you fitted Bayesian Hierarchical models, but no information is given about these models? How are they hierarchical? Why are they hierarchical? What likelihood functions were used? What priors were used? This information should be presented for each of the Bayesian models you conduct in the paper.

Line 43: It is not clear how many species and individuals actually had otolith data? 496 estimates yes, but how many species?

Line 52: natural log transformed.

Line 53: what were these priors? Put them with the model formula.

Line 59: Is this value considered high? Low? Medium? It would be good to give some context for the reader.

Line 69: Here you say, “for all 100 trees.” Again, you really have to consider the information you have given to the reader at this point. The reader hasn’t heard anything about any phylogenetic trees, but now you are saying you’ve got 100 of them. Why 100? Where did they come from? This information is really the basic necessities that need to presented before you rush into describing the analyses.

Comment for phylogenetic extrapolation: overall I’m quite impressed with the work you’ve done, and I do believe your phylogenetic analyses are properly executed. However, is it possible to perform some form of cross validation to ensure the accuracy of these extrapolations given that you’ve extrapolated a huge number of species? For instance, image that all the hard data you collected came from closely related species and families, this might produce unreliable “out-of-sample” predictions.

Line 110: It could be good to say how many families and how many species per family since you use these data for extrapolation.
Line 123: combined how?

Line 135: The level of detail given here is really insufficient. Where were these individuals caught? What habitat type? As a reader I don’t know what part of the world they came from or whether they were caught in a lagoon or on a reef crest.

Line 153: how did you define what an outlier is?

Line 161: If you used an informative prior you must give the reasoning as to why and to how you chose the prior.

Extended Data Figure 2: it might be easier to read if you put the names of the functions as figure titles.

Extended Data Figure 5: just a small thing, but some figures have capital letters for the panel labels, and some have lower case.

Final comment: I want to reiterate that although my review is detailed and critical, I tried to be constructive because this paper has clear potential to be published in NEE, and you need to tie up any loose ends in this manuscript before it can be published in a top tier journal. Overall, I remain positive about the manuscript. The main substance in terms of data and results is undeniable and I will ultimately support the publication of this manuscript.

I am signing my review for transparency and I invite the authors to contact me if they have any questions.

Sincerely,
Matthew McLean

Reviewer #2 (Remarks to the Author):

This manuscript offers a summary of how coral reef fish communities affect ecosystem functions across the globe by analyzing a database of reef fish species abundance in reefs around the world. The authors then calculated five ecosystem functions using multiple, complex methodologies and analyze the role of fish community structure (i.e., richness, body size, trophic level, and immaturity) in individual functions. As presented, no one individual aspect of community structure is revealed to explain ecosystem functioning across global reefs, but the authors suggest that the variation among communities and between regions means that there is no clear objective for protecting coral reef function and that there are no global keystone species to target.

Overall, this manuscript needs to be rewritten, line by line, in order to improve its clarity. Sentences are imprecise throughout, which muddies the take home messages of the discussion and confuses the main objectives of the study. This is an impressive piece of work that has used multiple data sources and synthesized them in unique, groundbreaking ways. When a manuscript involves big data like this, the authors absolutely have to be fully precise with their explanations of why things were done in the way they were. This manuscript unfortunately is not there, from both an ecological and methodological standpoint. Clearer gaps in knowledge need to be addressed in the introduction, more precise language on how these gaps will be addressed needs to be added/changed, and the big picture and small scale implications of what we have learned from this global analyses needs to be outlined better.

One major point of confusion for me was the lack of any attempt to combine the ecosystem functions mentioned into a multifunctionality framework. The authors even specifically state that it is necessary to examine multiple functions at once in order to understand how reefs may be changing with different fish communities (line 154-6). Well, the data exist in this paper for this to happen! Even a simple average geometric mean of multifunctionality could be informative, especially for identifying hotspots in fish-driven reef function.

Also, based on the title and abstract of this paper, I expected a discussion of how fish community structure as a whole, and not just species diversity, need to be explicitly considered when estimating how fish affect functioning in coral reefs. There are a couple of places where this topic is briefly touched upon, but this should be directly addressed in both the introduction and discussion. This would also allow the authors to discuss a key finding, that biomass is the key predictor for ecosystem functioning across reefs. I know that, and agree with, the biomass-corrected variables used in the paper. But I don’t see why the authors couldn’t use and discuss both biomass effects, and then biomass independent effects. That seems like a huge part of this story, and that there actually IS a global pattern in how fish communities affect ecosystem functions in reefs. The authors mention that their work reveals that there is no clear objective for protecting coral reef functioning,
and there are no global keystone species to target. It is unclear how exactly the authors evaluated those statements, and is surprising that the authors have no recommendations that would help address those clear conservation goals from their global analyses.

---
Section/Line comments
Abstract:
This section is very strong. The authors should use the focus of each of these sentences to guide the topic sentences of the manuscript sections. Clear and concise!

Introduction:
The introduction could use a rewrite with clarity and concision in mind. Between lines 25-42, I counted way too many uses of words and phrases that contradict the statement made before (e.g., “However, ….” , “…but simultaneously quantifying”, “Yet, the integrity of reefs” etc.). This is indicative of an unfocused introduction. The central message is simple enough that the authors should be more specific and precise with their wording and sentences.

3- “integrity” of ecosystems is vague, especially when the authors actually mean “functioning.” Could actually just remove this opener and start with the next sentence, which is pretty good. In that sentence, and throughout, be careful with informal language. “The world’s coral reefs” can be replaced with “Coral reefs” (I don’t think any readers are going to be thinking of any coral reefs on other worlds!) and “today’s coral reef conservation efforts” to “current coral reef conservation efforts”.

21- “integrity” repeated here again. Still unsure what the integrity of an ecosystem means.

22- careful with switching tenses here. This sentence could probably be removed.

23-25 why does sustaining multiple functions require both high richness and a variety of species assemblages? Also, what does “a variety of species assemblages” mean? Are the authors trying to say that community structure as a whole, and not just biodiversity, is key to a multifunctional ecosystem? If so, that is a fantastic point to make and represents a huge gap in ecology today!

31-42 I was surprised that this paragraph doesn’t fully focus on the role of fishes in nutrient cycling/ecosystem functioning in coral reefs.

33- “integrity” repeated again. Do you mean function?
34- An example of an edit to be more concise: the authors wrote “a plethora of stressors” and then added “such as….”. Pick one of the two of these. I would suggest getting rid of “a plethora of”.
37 Generally it is better to write out exactly why a topic is “at the forefront of scientific discourse” as opposed to just stating that it is. Because the reader is left to ask, why?

40-2 These two sentences are a good example of where this introduction goes astray. First, the sentence starts with “Conversely, …” but the sentence does not offer information that is counter to the previous sentence (not to mention that the previous sentence began with an “However” further obscuring the main point. I suppose “additionally” would be more appropriate, but it’s still unclear. I’m not sure that it is true that we know little about elemental fluxes and their drivers, as claimed. Are you talking about the role of reef fish in elemental fluxes? Be precise. Next, the Allgeier paper cited here as a “but see” example examines exactly what the authors claim that we know comparatively little about. That citation seems like a very good jumping off point for this paper, considering the differences in scale in this paper (global) vs that one (multi-site). Finally, the ending sentence offers no reasoning. Why does “this” (again even the “this” is
unclear, is it that we have only proxies of functioning, or that we know little about elemental fluxes? Or both?) constitute a severe limitation.

Paragraph on line 86 This paragraph talks a lot about “species” roles, but the figure shows taxa groups in families. This gets confusing when claims like “functions consistently hinge [upon] a few dominant species” (line 92-3) are made. Do you mean, “a few dominant families”? Or are there key species that provide high functioning?

97-100 These results seem like a very interesting implication of this research, but I don’t know where in the figures the reader can see this. Without a visual, this is difficult to interpret. Determine how important this finding is, and decide how to get this across in a more clear way. Also, please make sure that this isnt directly repetitive from the introduction.

102-105 See below comment on line 122. This reads like a topic sentence. Readers are going to be very interested in the details behind the claim that both species richness and functionally dominant key species are important to maximize the functions provided by reef fish. Regardless, this sentence doesn’t quite mesh with the opening sentence of this paragraph, so please edit for clarity here.

108 I’m not sure what a “severe change” is, especially in a broad term like community structure.
112 “effect” used twice in one sentence.
114 is this what Fig 2 shows? Do you mean Fig 4? Unclear
114-116 “On the other hand” and “However” open back to back sentences. This is a clear indication that whatever points are trying to be made, are unfocused.

122 This closing sentence for this paragraph is a great example of something that happens a lot in this paper. The paragraph above it is wavering, with an unclear main theme. This last sentence is actually quite good and brings up a fantastic point. It reads much more like a topic sentence. Considering the topic sentence of this paragraph is pretty vague (i.e., “shines new light on” doesn’t tell us anything specific), the authors should consider a reordering of the logic flow here, in above paragraphs, and in the discussion section as a whole.
122-4 I’m not sure that something can be both nuanced and holistic. Rephrase.

125 “Similarly…” It is unclear what is similar here. Rephrase
134 What does this sentence mean? How do herbivores fishes have a high variability in species roles? Should you have grouped the species roles differently then, into categories like “grazers of macroalgae” “bioeroders” “grazers of microalgae”? You defined what an herbivore is, so it’s strange to see that high variability is explained by your too-broad definition of herbivore.
135,137 Back to back sentences beginning with “While”.

137 …But can you not do this, with the data you have collected? The whole end of this paragraph is confusing and needs to be revisited.

Figure Comments:

Fig 1- This figure encapsulates the scale and scope of these analyses in a really nice way. There isnt a lot of specific information that can be gathered from this figure, besides that there were a lot of sites all throughout the world (which is a great thing!). Do the authors want to highlight that there are hotspots of function in different places, for different functions? If so, probably just include the colored points. Also, would there be any value in a figure that shows the highest multifunctional sites, i.e., where multiple processes are occurring at high rates? Identifying the global multifunctional hotspots of coral reef fish communities could be of value to conservation and management.

Fig 2. In the caption (181), do you mean “effect size” or “average effect size estimate” as opposed to “fixed effect values”? Regardless, the community variables besides richness mapped out in this figure are unclear. What is the difference between the 97.5% size line and the 2.5% size line? Is 97.5% size mean that the fish community is mostly made up of large fish? Maybe come up with more descriptive variable names than this? I definitely do not know what the immaturity variables are supposed to represent, and how they are different to size. This is further unclear when looking back at the ms text in line 78 that implies that small/immature fish are the same.

Fig 3. The axis on 3a needs to be explained better. Dots to the right of the 0 line indicate that this family contributes more to this function than as predicted by biomass? Actually, all axes need to be explained better

Fig 4. I understand what the authors are trying to do here, but I’m not sure that this figure is necessary. Which functions are vulnerable to climate change and overfishing can be discussed in words without too much confusion. This figure, and the paragraph in the main text surrounding it, seem out of place.

Methods:
Section 3 Did I miss a mention of the priors used here? I see uninformative priors are used in section 4
80 “fitted” should be “fit” ?

Supp Methods
A strength of this manuscript is the synthesis of multiple data sources and analytical techniques. However, this creates a lot of methods and thus, requires that even the supplementary methods need to be extra clear. It would be helpful to add a topic sentence to each relevant section of the Supp Methods so that the reader knows why each method is being used and explained. For example, line 3 should say exactly what parameters are going to be explained in this Supp Methods section, instead of “a number of parameters are required.” Carry this clarity throughout this Supp Methods section. For example, start section 1 (or 1.1) with something along the lines of, “To estimate the growth parameters of fish species (or families?) in our database, we used maximum length from fishbase and collected otolith data…”. Without this, it is difficult to tell why techniques like the Bayesian phylogenetic regression model are necessary.

14 is kmax defined? k is defined as a growth rate parameter in the Methods line 68, but each Methods section should be able to stand alone.

Reviewer #3 (Remarks to the Author):

Review of Global drivers and vulnerabilities of coral reef fish functions

I enjoyed reading this paper. Using coral reef fishes as a model system, it contains a simple but important message: a given ecosystem function can exist on a coral reef due to a relatively small number of species being present (and the identify of these species contributing to this particular function varies across geographies). The paper also contains an important applied message: that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem function on coral reefs. The paper is well written, although I think some statements could be clarified in places (see minor comments below).

My only major comment is the need to better justify the five key ecosystem functions that you focus on for the reader. I understand these are taken from the Brandl et al. paper, but many readers may not realise. Also, why 5 and not the 8 presented by Brandl et al.? This needs to come early on so the reader feels comfortable with your focused choice – your paper hinges on this to some extent. I suggest building this out in paragraph three (lines 43-53). You can do this in 2-3 strong sentences.

Minor comments

Lines13-16. Link between these two sentences is not clear for the reader: “Furthermore, functions are locally dominated by few species, but worldwide, 70% of the 1110 species in our dataset contribute disproportionally to functioning in at least one local community. This leads to disparate vulnerabilities of functions to anthropogenic stressors”

Lines 18-19 – are you suggesting here that conservation strategies to maximize function will always need to be context dependent – I think you are. If so, I would state this more clearly, as this is an important message from the data.

Line 32-33. Not just efficient recycling of nutrients that’s key to their persistence in oligotrophic waters, it’s also about the feedbacks that raise primary production levels around coral reefs (Gove et al. 2016 Nature Comms 7: 10581) and the flexible trophic ecology of corals to exploit these resources (Fox et al. 2018 Current Biology 28: 3355-3363).

Line 37. Suggest adding Williams & Graham (2019) Funct Ecol 33: 942-947 to references here also as this editorial captures the messages from a suite of studies talking about functional changes to coral reefs in the Anthropocene.

Line 41 – “but see 18”. Please tell us what Allgeier et al. found – annoying for reader to have to go and read another paper to understand this statement.

Line 41-42. How exactly is this hindering effective management of reefs? You leave the reader guessing here – poor style.

Line 69. Suggest avoid the term “holistic”, nothing can ever truly be holistic, without mentioning the connotations of unscientific holistic medicines.

Line 78. “and/or” is poor style. You can just write “and”. If a mechanic was advertising that their garage fixes exhausts “and” steering systems, you could take your car there to have both fixed, or just one….they are not implying it has to be both at the same time!

Line 93. I think this is meant to read “consistently hinge on”.

Line 107. Contributions to what?

Line 108-109. The Hughes et al. reference is not appropriate here as it does not address “reef fish”.

Line 119-120. Why does a shift in algal symbiont dominance matter? I think you need to make it clearer to reader here why this (and algal growth) are considered bad (if that is what you are implying).

Line 123. Same comment about use of “holistic”.

Line 125. Poor style to start a new paragraph with “similarly”. Too much connection/reliance on previous sentence that sits in a different paragraph.

Line 132-133. Can impact smaller browsers also, see Heenan et al. (2016) Proc B 283: 1843 (Fig. 3).

Line 164. Suggest replace “through” with “using”.

Figure 1. Why is there no key for the bubble values? The size differences between bubbles is also not that clear – can this be emphasized? Also not clear what the “categorical assignments” are from the figure legend alone – please expand the explanation.

Figures 2-4. Don’t take this the wrong way, but I find the choice of primary colours in your figures rather off-putting (in particular Fig 4). Also, the choice of some color combinations could be more inclusive (e.g. your use of red/green to denote different groups). There are plenty of color-blind friendly palettes out there now.

Figure 2 seems unnecessarily large – this could be a single column figure.

Figure 4 – Suggest proportion values radiating out run to 1 so piscivory falls within the axis bounds.

All Figures – there are some inconsistencies in font use/size across your figures. This might seem picky, but important for consistency.

Did you synthesize this data set yourself or did you use an existing database that has been previously published from? Please make this clear in the main manuscript.

### 2021-08-17 text/methods.Rmd
methods almost done

@@
 We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level, (2) investigate the effects of bioimass and sst, and the correlations among functions independent of biomass and sst, and (3) estimate the effects of the community structure on each function.
-\par
+For each model, functions were log-transformed to ensure the normal distribution of residuals and to allow the allometric relationship with biomass, hypothesized by metabolic theory [@Brown2004].\par
 
@@
 
-First, we performed a multivariate intercept-only regression model with the five -log-transformed functions to estimate the functions per locality.
+First, we performed a multivariate intercept-only regression model with the five log-transformed functions to estimate the functions per locality.
 The model structure includes intercepts and random effects for localities and sites:
@@
 
-All models were fitted using brms (ref).
+All Bayesian models were fitted using the R package *brms* (ref) which uses Stan, a C++ package for performing full Bayesian inference.
 The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
@@
 Posterior predictive checks for are provided in Supporting Information xxxx.
-We ran all Bayesian reggression models using the R package *brms* which uses the stan algorithm.
-The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by  using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
 
@@
 <!-- \begin{equation} -->
-$$	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},$$
+$$	\textrm{contribution}_{f,i,j} = \frac{F_{f,i,j}}{\sum F_{f,j}},$$
 <!-- 	\label{con} -->
@@
 
-Finally, to know how often species are contributing more than average for a certain function, we quantified the frequency of dominance, i.e.
-the number of times a species is dominant divided by the total number of transects in which that species is observed.
+Finally, we quantified the frequency of dominance per species, i.e.
+the number of transects in which a species is dominant for a given function divided by the total number of transects in which that species is observed.
 A species is considered dominant for a certain function in a given transect if their contribution is higher than 1/R, i.e.
@@
 ## 6. Vulnerability to fishing and climate change
-For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
+First, we estimated or extracted two measures of vulnerability per species: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
 For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals.
-Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral and body size [@Graham2011].
-Graham et al.
-(2011) [@Graham2011] developed a score for climate change vulnerability for 134 species.
-We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
+Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral, and body size [@Graham2011].
+Specifically, we used a score for climate change vulnerability for 134 species found in Graham et al.
+(2011) [@Graham2011] and fitted a Bayesian mixed effect predictive model that relates these vulnerability scores with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
 not dependent) [@Coker2014; @Cole2008].
-We also included a random effect for family.
+We also included a random effect for family:
+$$ y_i \sim normal(\mu_i, \sigma)$$
+$$
+\mu_i = (\beta0 +  \delta_{family}) + \beta1 log(sizemax) + \beta2 HD + \beta3 FD  ,
+$$
+with $y_i$ the vulnerability score of species i, $\mu_i$ the average predicted vulnerability score, sizemax the maximum length of the species, HD de dependence for habitat, and FD the depedendence for food.
 To verify the fit of the model we inspected the posterior predictive plot, which indicated a good fit.
 Further, the model had a Bayesian R2 of 0.97.
-We thus used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
-For species' vulnerability to fishing, we extracted the index from Cheung et al.
+We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
+We provide the model parameters in supplementary table xx.
+\par For species' vulnerability to fishing, we extracted the index from Cheung et al.
 (2005) [@Cheung2005].
 Next, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
-We also calculated community-level vulnerability scores based on biomass contributions as a comparison.
-Finally, we calculated the proportions of communities that had a higher vulnerability score of functions, compared to the vulnerability score based on biomass alone.
-In other words, we quantified the proportions of communities that have an increased functional vulnerability.
+Finally, we fitted a mixed model to predict the average vulnerability to climate change and fishing for each function.
 

### 2021-08-27 text/main.Rmd
text updates

@@
 Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
-However, our capacity to evaluate reef functioning typically relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
+Our capacity to evaluate reef functioning typically relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
 @Cinner2020].
-Conversely, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to efficient management [@Brandl2019front].
+However, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to efficient management [@Brandl2019front].
+How can we protect functions if we can not quantify them?
 
@@
 
-The five key ecosystem functions performed by fishes across the world's coral reefs exhibit high variability (Fig. 1).
+## Results
+By combining individual-level bioenergetic models and global underwater visual transect data, we quantified five key ecosystem functions across the globe.
+By running a multivariate Bayesian model with, we estimated the average functions per locality as well as a combined measure of multifunction (Fig. 1).
+Functions across localities show similar spatial patterns, yet a high level of function does not nescessarily ensure a high level of another function. For example, xxxx.
+
 Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we observed a predictably strong relationship between fish biomass and all five functions (Fig.
-S1a-e, Fig.
-S2).
-However, our analyses demonstrate striking variability after accounting for biomass: in communities with similar biomass, functions may differ by two orders of magnitude or more (Fig. S1a-f).
-Thus, using biomass as a proxy for functioning masks fundamental differences in critical community-level functions.
-Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Fig. S1g).
-For example, high herbivory rates and nitrogen excretion negatively correlate with rates of phosphorus excretion.
+1).
+We ran a multivariate mixed effect Bayesian model to assess the relationship between all five functions and biomass.
+We also incorporated sea surface temperature (sst) because it affects the metabolic and groth rates of fishes, which scales up to the community [@Barneche2019].
+We found positive slopes xxx for biomass and xxx for sst.
+
+The above-mentioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and sst.
+Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2).
+The correlations mostly overlapped across the three levels for a given pair of functions.
+We found consistently negative trade-offs between P excretion and N excretion, P excretion and biomass production.
+Further, there were slightly weaker negative correlations between piscivory and N excretion and between piscivory and herbivory.
+As a consequence of the negative correlations, there are no transects that can have a high value of production and P excretion simultaneously for example.
+
+To explore what drives the residual variation and trade-offs of functions beyond the effects of biomass and sst, we conducted a multivariate Bayesian mixed effect model by adding ten variables that describe the community structure: species richness and the median, lower, and upper 95% quantiles of size, immaturity, and trophic level of the individuals inside a community.
+We found that the community structure drives the observed trade-offs (Fig.
+3).
+
+We also questioned if functions tend to be driven by specific species.
+We quantified the degree of dominance inside each community and found that functions are on average charachterized by a high level of dominance, i.e.
+in most communities, a small proportion of species perform most of a function (Fig.
+4a).
+As a comparison, we simulated random communities ranging from 5 to 50 species which yielded an average XX.
+The predicted average of the degree of dominance was x, x, x, x, and x for each function respectively.
+We also calculated the proportion of species that is dominant in at least one transect (i.e.
+species that contribute more than a community in which each species contributes equally).
+We found that most species play a dominant role, and 70% of all species contributed disproportionally to a function in at least one community (Fig.
+4b).
+We finally investigate how often species are dominant across their range and found that very few species are dominant throughout their range (Fig.
+4c).
+Together, this means that functions inside communities tend to be driven by few dominant species, but that the identity of these dominant species varies highly across communities.
+
+## Discussion
+
+By quantifying five key functions mediated by coral reef fishes, we demonstrate that ecosystem-wide functioning is driven by both fish biomass and community structure due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Schramski2015].
+While biomass is one of the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], our analyses suggests that biomass alone does not sufficiently characterize functioning and using biomass as a proxy for functioning masks fundamental differences in critical community-level functions.
+Further, we demonstrate strong trade-offs among the five functions, independent of biomass.
 Consequently, for a given value of biomass, no reef can yield above average values across all five functions.
-While many reefs may stand out as hotspots for one function, none can holistically maximize functioning (Fig. 1).
+While many reefs may stand out as hotspots for one function, none can holistically maximize functioning.
 
-Community structure and species-specific traits clearly impact rates of functioning.
-First, using community-level ecological predictors known to affect elemental fluxes (body size, trophic level, species richness, biomass, temperature, and age structure [@Schiettekatte2020]; Fig.
-2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig.
-2; Table S2; Fig.
-S2).
+Due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure significantly impacts ecosystem-wide functioning [@Schramski2015].
 For example, phosphorus excretion and piscivory are higher in communities that include large-bodied fishes or occupy high trophic levels (Fig. 2; @Allgeier2014).
@@
 Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
-Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure significantly impacts ecosystem-wide functioning [@Schramski2015].
 
@@
 
-The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in our changing world.
+Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems.
 Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Hughes2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
@@
 However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
-Thus, considering multiple functions paints a more nuanced picture of how human-induced shifts in reef fish community structure may impact coral reef ecosystems.
 

### 2021-09-06 R/functions_analysis.R
streamline code

@@ -319,6 +319,79 @@ get_dd <- function(contributions, herb_pisc){
   return(key)
 }
 
+get_dd_site <- function(contributions, herb_pisc){
+  
+  # combine data
+  
+  
+  nspec <- left_join(contributions, herb_pisc$contributions_herb_pisc) %>%
+    ungroup() %>% group_by(sites) %>%
+    dplyr::summarise(nspec = length(unique(species)),
+                     nspec_h = length(unique(species[I_herb_p>0])),
+                     nspec_p = length(unique(species[I_pisc_p>0])))
+  
+  
+  ### function to calculate area of ranked function contribution !! 
+  # data has to be ordered
+  # y = cumsum!!
+  rank_area <- function(y) {
+    n <- length(y)
+    a <- y[2:n]
+    b <- y[1:(n-1)]
+    area <- sum(a + b)/2
+    return(area)
+  }
+  
+  # dominance function
+  ks_area <- function(data, var){
+    
+    if (var %in% c("I_herb_p", "I_pisc_p")){
+      data <- data %>%
+        filter(.data[[var]] > 0)
+    }
+    
+    if (nrow(data) == 0){
+      return(NA)
+    }else if (nrow(data) == 1){
+      return(1)
+    }else{
+      drank <- data %>% 
+        mutate(rank = dplyr::dense_rank(desc(.data[[var]]))) %>%
+        dplyr::arrange(rank) %>%
+        mutate(cumsum = cumsum(.data[[var]]))
+      
+      A <- rank_area(drank$cumsum)
+      
+      r <- nrow(data) # species richness
+      A_max <- 1 * (r - 1) # maximum if first species performs 100% (rectangle)
+      A_min <- (r^2-1)/(2*r) # minimum if all sp contribute equally (trapezium)
+      
+      dd <- (A - A_min)/(A_max - A_min)
+      
+      return(dd)
+    }
+  }
+  
+  con <- ungroup(tfs)
+  
+  key <- parallel::mclapply(unique(con$sites), function(x){
+    
+    t <- dplyr::filter(con, sites == x)
+    
+    result <- data.frame(
+      sites = x,
+      dd_Fn = ks_area(t, "Fn_p"),
+      dd_Fp = ks_area(t, "Fp_p"),
+      dd_Gc = ks_area(t, "Gc_p"),
[…]

### 2021-09-06 R/functions_plots.R

@@ -1,5 +1,5 @@
 
-make_fig1 <- function(mod_mv_siteloc, coords, summary_transect){
+make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
   
   nsiteloc <- summary_transect %>%
     group_by(locality) %>%
@@ -30,17 +30,6 @@ make_fig1 <- function(mod_mv_siteloc, coords, summary_transect){
            r5 = normalize(r1_loc_Ipisc)) %>%
     rowwise() %>%
     mutate(r_multi = geomean(r1, r2, r3, r4, r5))
-  
-  # re2 <- ranef(mod_mf_siteloc)
-  # re_loc2 <- re2$locality[,1,1] %>%
-  #   as.data.frame()
-  # re_site2 <- re1$sites[,1,1] %>%
-  #   as.data.frame()
-  # re_loc2[ls1,] <- re_loc2[ls1,] + re_site2[ls2,]
-  # colnames(re_loc2) <- c("r1_loc_mf")
-  # re_loc2 <- re_loc2 %>%
-  #   rownames_to_column("locality") 
- 
 
   
   coords <- coords %>%
@@ -50,11 +39,6 @@ make_fig1 <- function(mod_mv_siteloc, coords, summary_transect){
   data <- re_loc1 %>%
     left_join(coords) %>%
     unique()
-  
-  # 
-  # data2 <- (re_loc2) %>%
-  #   left_join(coords) %>%
-  #   unique()
   
   library("rnaturalearth")
   library("rnaturalearthdata")
@@ -270,7 +254,7 @@ make_fig1 <- function(mod_mv_siteloc, coords, summary_transect){
     scale_color_manual(values = pal, name = "",
                        drop = TRUE, na.translate = F) +
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
-    geom_text(aes(x = -175, y = 30, label = "Multifunction"), size = 3, hjust = 0) +
+    geom_text(aes(x = -175, y = 30, label = "Multifunctionality"), size = 3, hjust = 0) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.8))) +
     scale_size_continuous(range = c(0.5, 4), guide = FALSE) +
     theme_worldmap()+ 
@@ -1713,84 +1697,206 @@ make_map_multi_supp <- function(model, coords){
 ##### correlations #####
 
[…]

### 2021-09-06 R/functions_wrangling.R

@@ -6,13 +6,7 @@ load("data/fishtree_glob.RData")
 
 ##### sptl #####
 get_sptl <- function(x){
-  sptl <- read.csv("data/species_list_tl.csv")
-  sptl$Species <- gsub("_", " ", sptl$species)
-  tax <- dplyr::collect(rfishbase::load_taxa())
-  sptl <- right_join(dplyr::select(tax, Species, Family), sptl)
-  sptl[sptl$species == "Rhinesomus_triqueter", "Family"] <- "Ostraciidae"
-  sptl[sptl$species == "Abudefduf_luridus", "Family"] <- "Pomacentridae"
-  sptl[sptl$Family == "Scaridae", "Family"] <- "Labridae"
+  sptl <- read_csv("data/species_list_tl.csv")
   return(sptl)
 }
 
@@ -407,6 +401,61 @@ get_contributions <- function(tfish, cnpflux, params, summary_transect){
     filter(!is.na(nspec))
   
   return(tfss)
+}
+
+get_contributions_site <- function(tfish, cnpflux, params, summary_transect){
+  
+  diet <- read.csv("data/extrapolation_trophic_guilds.csv") 
+  
+  diets <- diet %>%
+    select(species, p2_m, p4_m, trophic_guild_predicted = trophic_guild_predicted) %>% 
+    mutate(herb = trophic_guild_predicted == 2 & p2_m > 0.5,
+           pisc = trophic_guild_predicted == 4 & p4_m > 0.5) %>%
+    select(species, herb, pisc)
+  
+  tfish <- left_join(tfish, cnpflux) %>% 
+    left_join(select(params, Species, lwa_m, lwb_m, trophic_guild_predicted)) %>% 
+    mutate(
+      Fc = Fc_median * abun,
+      Fn = Fn_median * abun,
+      Fp = Fp_median * abun,
+      Ic = Ic_median * abun,
+      In = In_median * abun,
+      Ip = Ip_median * abun,
+      Gc = Gc_median * abun,
+      Gn = Gn_median * abun,
+      Gp = Gp_median * abun,
+      Wc = Wc_median * abun,
+      Wn = Wn_median * abun,
+      Wp = Wp_median * abun,
+      biomass = abun * lwa_m * size_cm^lwb_m) %>%
[…]

### 2021-09-06 R/plan.R

@@ -45,25 +45,7 @@ plan <- drake_plan(
   # combine summary data, sst 
   summary_transect_complete = combine_summary(summary_transect, herb_pisc),
   
-  # subset 
-  #summary_transect_sub = subset_data(summary_transect_complete),
-  
-  # imputation 
-  #imp = impute(summary_transect_complete),
-  #summary_transect_imp = imp[[1]],
-  
   ##### models #####
-  # run models only with biomass ans sst
-  # bmmodels = run_bmmodels(summary_transect_complete),
-  # residuals = get_residuals(summary_transect_complete, procmodels),
-  
-  # run models proc ~ biomass et al
-  # procmodels = run_procmodels(summary_transect_complete),
-  # location_effect = get_location_effect(procmodels, summary_transect),
-  
-  # run models proc ~ community vars
-  # commodels = run_commodels(summary_transect_complete),
-  # commodels_real = run_commodels_abs(summary_transect_complete),
   
   # site loc
   mod_mv_siteloc = fit_mvfun_siteloc(summary_transect_complete),
@@ -71,35 +53,22 @@ plan <- drake_plan(
   
   # add biomass sst
   mod_mvfun_bm = fit_mvfun_bm(summary_transect_complete),
-  #mod_mf_bm = fit_mf_bm(summary_transect_imp),
-  
+
   # community analysis
   mod_mvfun_com = fit_mvfun_com(summary_transect_complete),
   mod_mvfun_com2 = fit_mvfun_com2(summary_transect_complete), #get absolute slopes
-  #mod_mf_com = fit_mf_com(summary_transect_imp), 
-  
-  # Same models with data subset
-  # mod_mv_siteloc_sub = fit_mvfun_siteloc(summary_transect_sub),
-  # mod_mf_siteloc_sub = fit_mf_siteloc(summary_transect_sub),
-  # mod_mvfun_bm_sub = fit_mvfun_bm(summary_transect_sub),
-  # mod_mf_bm_sub = fit_mf_bm(summary_transect_sub),
-  # mod_mvfun_com_sub = fit_mvfun_com(summary_transect_sub),
-  #mod_mf_com_sub = fit_mf_com(summary_transect_sub), 
-  
+
   # output tables 
   tab_mod_mv_siteloc = make_table_mod_mv_siteloc(mod_mv_siteloc),
[…]

### 2021-09-06 R/test.R

@@ -74,17 +74,19 @@ rank_area <- function(y) {
   return(area)
 }
 
-list <- parallel::mclapply(21, function(j){
-  te <- (simplex.sample(j, 1000, sort=FALSE))[[1]]
+list <- parallel::mclapply(2:277, function(j){
+  te <- (simplex.sample(j, 500, sort=FALSE))[[1]]
    dd <- (apply(te, 1, ks_area))
    data.frame(nspec = j, dd = dd)
 }, mc.cores = 50)
 
-vec <- plyr::ldply(list)
+vec <- plyr::ldply(list) %>%
+  group_by(nspec) %>%
+  dplyr::summarize(dd = mean(dd))
 
 summary(vec$dd)
 
-plot(5:100, vec)
+plot(vec$nspec, vec$dd)
 
 hist(vec$dd)
 
@@ -310,6 +312,7 @@ predsim <- fitted(fit_sim)
  
   
    ####### vuln ######
+  loadd(contributions, vulnerability, herb_pisc)
   
   con <- left_join(contributions, vulnerability) %>%
     left_join(herb_pisc$contributions_herb_pisc) %>%
@@ -336,7 +339,7 @@ predsim <- fitted(fit_sim)
     filter(!fun == "bm")
   
   ggplot(con) +
-    geom_point(aes(x = vuln_Fp_cl, y = vuln_Fp_fi)) +
+    geom_point(aes(x = vuln_Fp_cl, y = vuln_Fp_fi), alpha = 0.2) +
     geom_smooth(aes(x = vuln_Fp_cl, y = vuln_Fp_fi))
   
   con <- left_join(con, summary_transect_imp)
@@ -347,7 +350,7 @@ predsim <- fitted(fit_sim)
   con_long <- left_join(con_long, select(summary_transect_imp, sites, locality, transect_id, nspec, biomass_tot))
   
   
-  fit_v <- brm(mvbind(fi, cl) ~ fun + fun:log(nspec) + fun:log(biomass_tot),#+ (1|sites) + (1|locality),
+  fit_v <- brm(mvbind(fi, cl) ~ fun + fun:nspec + fun:log(biomass_tot) + (fun|sites) + (fun|locality),
   data = con_long, cores = 4,
   backend = "cmdstanr",
   threads = threading(15))
@@ -360,9 +363,9 @@ predsim <- fitted(fit_sim)
   
   v1 <-
   ggplot(fe1) +
-    geom_line(aes(x = log(effect1__), y = estimate__, color = effect2__)) +
[…]

### 2021-09-06 text/main.Rmd
restructure main text

@@
 **Main Text:**
-The flow of elements through biological communities fuels all life on Earth [@Welti2017].
-Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
-For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of biomass [@Weisser2017].
-Sustaining multiple functions requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
-However, there can be trade-offs between functions, and efforts to maximize one function can negatively impact another [@Zavaleta2010].
-A deeper understanding of such trade-offs is required to make informed management decisions, but simultaneously quantifying multiple ecosystem functions is challenging.
-Therefore, trade-offs between functions, their drivers, and their vulnerability remain poorly understood in many ecosystems [@Brandl2019front].
-
+The flow of elements through biological communities fuels all ecosystems on Earth [@Welti2017].
+Contemporary ecosystems and their functioning are threatened by the harmful dominance of humans.
+our modern society has initiated a mass extinction episode, unprecedented in human history and threatening the functioning of the planet’s ecosystems [@Ceballos2015].
+Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats including warming, and intensive fishing pressure [@Hughes2017; ref fishing].
 Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services [@Teh2013].
-Yet, their integrity is threatened by a plethora of anthropogenic stressors [@Hughes2017].
 Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
@@
 How can we protect functions if we can not quantify them?
+
+Therefore, trade-offs between functions, their drivers, and their vulnerability remain poorly understood in many ecosystems [@Brandl2019front].
 
@@
 
-Secondly, alongside community structure, functions may also be influenced by specific high-performing taxa (Fig.
-3a; Fig.
-S3,S4), which may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
-At the local scale, we show that functions consistently hinge on a few dominant species (Fig.
-3b).
+Further, our results reveal that functions consistently hinge on a few dominant species, but the identity of local, dominant species vary strongly across locations [@Lefcheck2019].
+Locally, specific high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
 Specifically, on average, more than 50% of a given function is upheld by only 12% of the species present within a local community.
-However, the identity of these species varies dramatically among reefs (Fig. 3c).
-While few high-performing taxa dominate functioning in each location, there are no species that are dominant across their entire range.
+Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
+While few high-performing taxa dominate functioning in each site, there are no species that are dominant across their entire range.
 In addition, 70% of all species contributed disproportionally to a specific function in at least one community.
-Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
 Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across locations [@Lefcheck2019].
 
-Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems.
+Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
 Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Hughes2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.

### 2021-09-08 text/main.Rmd
edits intro, discussion and finnished results

@@
 The flow of elements through biological communities fuels all ecosystems on Earth [@Welti2017].
-Contemporary ecosystems and their functioning are threatened by the harmful dominance of humans.
-our modern society has initiated a mass extinction episode, unprecedented in human history and threatening the functioning of the planet’s ecosystems [@Ceballos2015].
-Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats including warming, and intensive fishing pressure [@Hughes2017; ref fishing].
-Coral reefs are among the most diverse and productive ecosystems on Earth and provide essential ecosystem services [@Teh2013].
-Severe declines in habitat quality and fish biomass have brought coral reef functioning to the forefront of scientific discourse [@Bellwood2019; @Brandl2019front].
-Our capacity to evaluate reef functioning typically relies on static proxies of functions, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
+Contemporary ecosystems and their functioning are threatened by the harmful dominance of humans [@Ceballos2015].
+Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats including warming, and intensive fishing pressure [@Hughes2017; @Pauly2002].
+Drastic declines in habitat quality and fish biomass coral reefs have evoked serious concerns about the persistence of coral reef functioning [@Bellwood2019; @Williams2019; @Brandl2019front).
+However, our knowledge on process-based functions - fluxes of elements and energy - is still in its infancy and evaluations of coral reef functioning typically relies on static proxies, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
 @Cinner2020].
-However, we know comparatively little about actual functions - fluxes of elements and energy - and their drivers (but see [@Allgeier2016]), which constitutes a severe limitation to efficient management [@Brandl2019front].
-How can we protect functions if we can not quantify them?
+The sparsity of quantification of functions constitutes a severe limitation to efficient management [@Brandl2019front]: How can we conserve functions if we can not quantify them?
 
-Therefore, trade-offs between functions, their drivers, and their vulnerability remain poorly understood in many ecosystems [@Brandl2019front].
+Coral reef fishes play an essential role in coral reef functioning, because coral reef fishes contribute to a high proportion of consumer biomass and therefore represent essential vectors of fluxes of carbon, nitrogen and phosphorus through storage and recycling (McIntyre et al.
+2008; All-
+geier et al.
+2014; Barneche et al.
+2014).
+Broad ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory , and piscivory (secondary consumption) (Brandl et al.
+2019front).
+While the high diversity of coral reef fishes has inspired many studies with a focus on ecosystem functioning, only a handful of studies have attempted to quantify functions as continuous fluxes (Brandl et al.
+2019a).
+Rather, most studies define fish-mediated ecosystem functioning with proxies such as trait diversity or total biomass (e.g.
+Mora& Sale 2011; e.g., Mouillot et al.
+2014).
+Further, studies that do quantify functions are mostly focused on biomass production (e.g., @Morais2019; @Morais2020glob) or fish excretion (e.g., @Allgeier2014).
+An assessment of multiple functions on a large scale is currently lacking.
+Therefore, trade-offs between functions, their drivers, and their vulnerability to global stressors remain poorly understood in coral reef ecosystems [@Brandl2019front].
 
@@
 ## Results
-By combining individual-level bioenergetic models and global underwater visual transect data, we quantified five key ecosystem functions across the globe.
-By running a multivariate Bayesian model with, we estimated the average functions per locality as well as a combined measure of multifunction (Fig. 1).
-Functions across localities show similar spatial patterns, yet a high level of function does not nescessarily ensure a high level of another function. For example, xxxx.
+By combining individual-level bioenergetic models and global underwater visual transect data, we quantified five key ecosystem functions mediated by coral reef fishes across the globe.
+We estimated the average functions per locality as well as a combined measure of multifunctionality by running a multivariate Bayesian regression model (Fig.
+1).
+Functions across localities show similar spatial patterns, yet a high level of function does not nescessarily ensure a high level of another function.
+For example, Trindade in the South Atlantic Ocean has high values for N excretion, P excretion, and piscivory, but average values for biomass production.
+A measure of multifunctionality thus does not appropriately represent the state of all functions.
 
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we observed a predictably strong relationship between fish biomass and all five functions (Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we demonstrate a predictably strong relationship between fish biomass and all five functions by running multivariate mixed effect Bayesian model (Fig.
 1).
-We ran a multivariate mixed effect Bayesian model to assess the relationship between all five functions and biomass.
-We also incorporated sea surface temperature (sst) because it affects the metabolic and groth rates of fishes, which scales up to the community [@Barneche2019].
-We found positive slopes xxx for biomass and xxx for sst.
+Specifically, the effects of the log-transformed biomass on log-transformed functions were 0.932 (95\%CI: 0.929; 0.934), 1.051 (1.047; 1.056), 0.771 (0.764; 0.780), 0.940 (0.923; 0.957), and 0.668 (0.635; 0.702) for N excretion, P excretion, production, herbivory, and piscivory, respectively.
+We also incorporated sea surface temperature (sst) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019].
+We found positive effects of temperature on N excretion, production, and herbivory, and negligible effects of sst on P excretion and piscivory (suppl table).
 
 The above-mentioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and sst.
-Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2).
+Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2, suppl. fig x).
 The correlations mostly overlapped across the three levels for a given pair of functions.
@@
 Further, there were slightly weaker negative correlations between piscivory and N excretion and between piscivory and herbivory.
-As a consequence of the negative correlations, there are no transects that can have a high value of production and P excretion simultaneously for example.
+As a consequence of the negative correlations, a fish community cannot have high values for all functions simultaneously.
 
@@
 We found that the community structure drives the observed trade-offs (Fig.
-3).
+3; table x).
 
-We also questioned if functions tend to be driven by specific species.
-We quantified the degree of dominance inside each community and found that functions are on average charachterized by a high level of dominance, i.e.
+We then questioned if functions tend to be driven by specific species across sites.
+We quantified the degree of dominance inside each community on the site-level and found that functions are on average charachterized by a high level of dominance, i.e.
 in most communities, a small proportion of species perform most of a function (Fig.
@@
 species that contribute more than a community in which each species contributes equally).
-We found that most species play a dominant role, and 70% of all species contributed disproportionally to a function in at least one community (Fig.
+We found that most species play a dominant role, and 70\% of all species contributed disproportionally to a function in at least one community (Fig.
 4b).
@@
 
-By quantifying five key functions mediated by coral reef fishes, we demonstrate that ecosystem-wide functioning is driven by both fish biomass and community structure due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Schramski2015].
+By quantifying five key functions mediated by coral reef fishes, we demonstrate that ecosystem-wide functioning is mainly driven by fish biomass, yet biomass alone does not fully capture functional variability across communities.
 While biomass is one of the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], our analyses suggests that biomass alone does not sufficiently characterize functioning and using biomass as a proxy for functioning masks fundamental differences in critical community-level functions.
-Further, we demonstrate strong trade-offs among the five functions, independent of biomass.
+We demonstrate strong trade-offs among the five functions, independent of biomass.
 Consequently, for a given value of biomass, no reef can yield above average values across all five functions.
-While many reefs may stand out as hotspots for one function, none can holistically maximize functioning.
+While many reefs may stand out as hotspots for one function, none can maximize all functions.
 
-Due to variations in organismal physiology and life-history traits [@Schiettekatte2020], fish community structure significantly impacts ecosystem-wide functioning [@Schramski2015].
-For example, phosphorus excretion and piscivory are higher in communities that include large-bodied fishes or occupy high trophic levels (Fig. 2; @Allgeier2014).
-In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
-Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
-Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion.
+Fish community structure drives the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
+For example, we observed a clear trade-off between P excretion and biomass production which is largely driven by the age and trophic community structure.
+Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet (@Allgeier2014).
+In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
+Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; ref], while communities dominated by immature fishes logically maximize biomass production.
+Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].
 
-Further, our results reveal that functions consistently hinge on a few dominant species, but the identity of local, dominant species vary strongly across locations [@Lefcheck2019].
+Further, our results reveal that functions consistently hinge on a few dominant species, but the identity of local, dominant species vary strongly across sites [@Lefcheck2019].
 Locally, specific high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
@@
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
-While few high-performing taxa dominate functioning in each site, there are no species that are dominant across their entire range.
-In addition, 70% of all species contributed disproportionally to a specific function in at least one community.
-Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across locations [@Lefcheck2019].
+While few high-performing taxa indeed dominate functioning in each site, there are no species that are dominant across their entire range.
+In addition, more than half of all species contributed disproportionally to a specific function in at least one site inside their range.
 
 Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
-Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Hughes2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
-For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017].
-When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g.
-@Morais2020glob] but negatively impact phosphorus excretion, herbivory, and piscivory (Fig.
-2).
-On the other hand, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
-However, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
-
-Similarly, the species-specific vulnerability of functionally-dominant species heavily affects the vulnerability of functions.
-By combining species-level vulnerability scores to fishing and climate change induced coral loss [@Graham2011] and the contributions of each species to each function, we illustrate that the loss of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by phosphorus excretion (Fig.
-4).
-Conversely, the loss of individuals due to climate change and consequent coral mortality may disproportionally reduce phosphorus excretion, nitrogen excretion, and biomass production.
-Combined, fishing and the loss of live coral impact species important for phosphorus excretion.
-Surprisingly, although fishing pressure can negatively impact large herbivores such as parrotfishes [@Bellwood2011], herbivory is the least vulnerable function.
-This may be due to the high variability in ecosystem roles within the comparatively large pool of herbivorous fish species.
-While small herbivores are abundant and not particularly vulnerable to fishing, larger herbivores are frequently targeted and prone to functional extinction in areas with high fishing pressure [@Bellwood2012].
-While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are strongly complementary and, thus, potentially more vulnerable.
+Fishing and climate-induced coral loss have caused severe changes in reef fish biomass and community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
+Intensive fishing and associated reductions in biomass of large fishes alters the size, age, and trophic structure of fish communities [@Graham2017].
+When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g. @Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
+Futher, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
+However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
 
@@
 For example, the establishment of marine protected areas, which are one of the primary conservation tactics for coral reefs [@Graham2020], may protect herbivorous species and thus provide benefits for herbivory.
-However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards herbivore domination may result in the decline of phosphorus excretion.
+However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards herbivore domination may result in the decline of P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
-It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], as well as making informed decisions on local needs and stressors.
-While there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010], we highlight the importance of community structure and the identity of dominant species at the local scale.
-Maintaining the diversity of fishes is critical, yet, at local scales, species richness has a minor impact on individual functions.
-Importantly, dissimilarity between local communities may be critical to maintain functioning across seascapes since no species consistently provides high contributions for all functions or across its range [@Zavaleta2010].
+It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
+process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy [@Brandl2019front].
+To appropriately manage coral reef functioning with local needs and stressors, future research should seek to establish functional baselines for global coral reefs.
+Until then, our study suggests that coral reef fish functions can be managed by maximizing standing stock biomass, protecting local key species, and promoting a balanced community structure.
 
@@
 ![Fig.
-1: Spatial variation in five key, biomass-corrected ecosystem functions.
-Dots indicate locations of field surveys, with dot sizes representing the ranked values of biomass-corrected function, and color scales showing categorical assignments (black = lower 25%, grey = 25-75%, color = >75%).
-Black circular outlines highlight the five locations with the highest values of each biomass-corrected function.](../output/plots/fig1_multimap.png)
+1: Maps of five key ecosystem functions and multifunction, and their relationships with biomass.
+Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = lower 25\%, grey = 25-75\%, color = >75\%).
+Black circular outlines highlight the five localities with the highest values of each function.
+Multifunction represents the weighted average of the five standardized functions.
+Right: The predicted values for functions and multifunction with increasing biomass.
+The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.](../output/plots/fig1_multimap.png)
 
 ![Fig.
-2.
+2: Correlations among five functions while accounting for biomass and sea surface temperature.
+a: Modeled correlation coefficients of residual errors.
+Dots represent the average and lines represent the 95%CI.
+b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.](../output/plots/fig1_multimap.png)
+
+![Fig.
+3.
 Effects of ecological community variables on five functions.
-Fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes.
+Dots indicate fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes.
 To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables.
@@
 ![Fig.
-3.
-Family and species-level contributions to five ecosystem functions on coral reefs.
-a) The median family-level contributions to each function relative to their contribution to standing stock biomass.
-The twelve included families are ordered by their median contribution to biomass.
-b) The distribution of the degree of dominance of communities for each function.
+4: Local dominance in species contributions for five ecosystem functions on coral reefs.
+a: The degree of dominance of communities for each function on the site-level.
+Colored dots represent the raw values and the black dots and lines display the mean and 95\% credible intervals of the average degree of dominance, respectively.
 Degrees of dominance range between zero (all species contribute equally) and one (a single species is the sole contributor to a given function).
-c) Species-specific frequencies of dominance in each function across all communities, ranging from zero (species are never dominant) to one (dominant wherever present).
-A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).
-Shaded areas show the distribution of the values.
-Dots represent the median value, and lines indicate the interquartile range.](../output/plots/fig3_contributions.png)
+The vertical dashed line shows the average of the degree of dominance of 1,000 randomly simulated communities.
+b: Bar plot showing the proportion of species that are dominant in at least one site relative to the total number of species.
+In the case of herbivory and piscivory, the total number of herbivores and piscivores, respectively, is used.
+c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present).
+A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).](../output/plots/fig3_contributions.png)
 
 ![Fig.
-4.
-Vulnerability of five critical functions to fishing, climate change-induced coral loss, and both stressors combined.
-Vulnerability is presented as the proportion of communities (filled bars) in which functional vulnerability is higher than vulnerability based on fish biomass (i.e. not accounting for species contributions to each function).](../output/plots/figure_4_vuln_com.png)
+5.
+Vulnerability of five critical functions to fishing and climate change-induced coral loss.
+Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.](../output/plots/figure_4_vuln_com.png)
 

### 2021-09-09 text/main.Rmd
methods edits

@@
 bibliography: ../text/global_proc.bib
-csl: science.csl
+csl: nature.csl
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(drake)
-loadd(fig1)
-loadd(fig2)
-loadd(fig3)
-loadd(fig4)
-```
 
@@
 **Abstract:**
-Preserving the functioning of coral reefs is a critical challenge of the 21st century.
+Preserving coral reef functioning is a critical challenge of the 21st century.
 However, a lack of quantitative assessments of multiple functions across large spatial scales has hindered local and regional conservation efforts.
 We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes.
-We show that functions exhibit critical trade-offs driven by varying community structures, such that no reef can holistically maximize functioning.
-Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; 70% of the 1,110 species in our dataset are functionally dominant.
+We show that functions exhibit critical trade-offs driven by varying community structures, such that no community can maximize all functions.
+Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
 Our results underline the need for a nuanced approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.
@@
 **Main Text:**
-The flow of elements through biological communities fuels all ecosystems on Earth [@Welti2017].
-Contemporary ecosystems and their functioning are threatened by the harmful dominance of humans [@Ceballos2015].
-Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats including warming, and intensive fishing pressure [@Hughes2017; @Pauly2002].
-Drastic declines in habitat quality and fish biomass coral reefs have evoked serious concerns about the persistence of coral reef functioning [@Bellwood2019; @Williams2019; @Brandl2019front).
-However, our knowledge on process-based functions - fluxes of elements and energy - is still in its infancy and evaluations of coral reef functioning typically relies on static proxies, such as live coral cover, standing stock biomass of reef fishes, or the diversity of qualitative traits [e.g.
-@Cinner2020].
-The sparsity of quantification of functions constitutes a severe limitation to efficient management [@Brandl2019front]: How can we conserve functions if we can not quantify them?
+The flow of elements through biological communities fuels all ecosystems on earth [@Welti2017]. Harmful human dominance disrupts the natural functioning in contemperory ecosystems [@Ceballos2015].
+Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats such as warming, and intensive fishing pressure [@Hughes2017; @Pauly2002].
+Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reef functioning [@Bellwood2019; @Williams2019; @Brandl2019front).
+However, our knowledge on process-based functions - fluxes of elements and energy - is still in its infancy and evaluations of coral reef functioning typically rely on static proxies, such as live coral cover, standing stock biomass of reef fishes, or measures of diversity [e.g.
+@Cinner2020; @Mouillot2014; @Mora2011].
+This sparsity of quantification of functions constitutes a severe limitation to efficient management of coral reef ecosystem functioning [@Brandl2019front].
 
-Coral reef fishes play an essential role in coral reef functioning, because coral reef fishes contribute to a high proportion of consumer biomass and therefore represent essential vectors of fluxes of carbon, nitrogen and phosphorus through storage and recycling (McIntyre et al.
-2008; All-
-geier et al.
-2014; Barneche et al.
-2014).
-Broad ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory , and piscivory (secondary consumption) (Brandl et al.
-2019front).
-While the high diversity of coral reef fishes has inspired many studies with a focus on ecosystem functioning, only a handful of studies have attempted to quantify functions as continuous fluxes (Brandl et al.
-2019a).
-Rather, most studies define fish-mediated ecosystem functioning with proxies such as trait diversity or total biomass (e.g.
-Mora& Sale 2011; e.g., Mouillot et al.
-2014).
-Further, studies that do quantify functions are mostly focused on biomass production (e.g., @Morais2019; @Morais2020glob) or fish excretion (e.g., @Allgeier2014).
+Coral reef fishes play an essential role in coral reef functioning, because they contribute to a high proportion of consumer biomass and therefore represent essential vectors of fluxes of carbon (C), nitrogen (N) and phosphorus (P) through storage and recycling [@McIntyre2008; @Allgeier2014; @Barneche2014].
+Ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory , and piscivory (secondary consumption) (@Brandl2019front).
+While the high diversity of coral reef fishes has inspired many studies with a focus on ecosystem functioning, only a handful of studies have attempted to quantify functions as continuous fluxes [@Brandl2019front].
+Further, studies that do quantify functions mostly focused on biomass production (e.g., @Morais2019; @Morais2020glob) or fish excretion (e.g., @Allgeier2014), and suggest that functions rely on community structure.
 An assessment of multiple functions on a large scale is currently lacking.
-Therefore, trade-offs between functions, their drivers, and their vulnerability to global stressors remain poorly understood in coral reef ecosystems [@Brandl2019front].
+Consequently, trade-offs amongs functions, their drivers, and their vulnerability to global stressors remain poorly understood in coral reef ecosystems [@Brandl2019front].
 
 Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
-Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory, and piscivory.
-We apply these bioenergetic models to 9,118 reef fish communities across 585 sites worldwide (Table S1) to:
+Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: N excretion, P excretion, biomass production, herbivory, and piscivory.
+We apply these bioenergetic models to 9,118 reef fish transects across 585 sites worldwide (Table S1) to:
 (1) quantify community-level reef fish functions and their trade-offs,
@@
 We also incorporated sea surface temperature (sst) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019].
-We found positive effects of temperature on N excretion, production, and herbivory, and negligible effects of sst on P excretion and piscivory (suppl table).
+We found positive effects of sst on N excretion, production, and herbivory, and negligible effects of sst on P excretion and piscivory (table Sx).
 
 The above-mentioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and sst.
-Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2, suppl. fig x).
+Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2, fig. Sx.
 The correlations mostly overlapped across the three levels for a given pair of functions.
@@
 4b).
-We finally investigate how often species are dominant across their range and found that very few species are dominant throughout their range (Fig.
+Finally, we investigated how often species are dominant across their range and found that very few species are dominant throughout their range (Fig.
 4c).
@@
 By quantifying five key functions mediated by coral reef fishes, we demonstrate that ecosystem-wide functioning is mainly driven by fish biomass, yet biomass alone does not fully capture functional variability across communities.
-While biomass is one of the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], our analyses suggests that biomass alone does not sufficiently characterize functioning and using biomass as a proxy for functioning masks fundamental differences in critical community-level functions.
+While biomass is one of the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], our analyses suggests that biomass alone does not sufficiently characterize functioning.
 We demonstrate strong trade-offs among the five functions, independent of biomass.
-Consequently, for a given value of biomass, no reef can yield above average values across all five functions.
-While many reefs may stand out as hotspots for one function, none can maximize all functions.
+Using biomass as a proxy for functioning can therefore mask fundamental differences in critical community-level functions.
+Furthermore, for a given value of biomass, no reef can yield above average values across all five functions.
+While many reefs may stand out as hotspots for one function, none can maximize all functions simultaneously.
 
-Fish community structure drives the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
+Fish community structures drive the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
 For example, we observed a clear trade-off between P excretion and biomass production which is largely driven by the age and trophic community structure.
@@
 In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
-Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; ref], while communities dominated by immature fishes logically maximize biomass production.
+Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood], while communities dominated by immature fishes maximize biomass production.
 Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].
 
-Further, our results reveal that functions consistently hinge on a few dominant species, but the identity of local, dominant species vary strongly across sites [@Lefcheck2019].
+Our results also reveal that functions consistently hinge on a few dominant species, but the identities of local, dominant species vary strongly across sites [@Lefcheck2019].
 Locally, specific high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
-Specifically, on average, more than 50% of a given function is upheld by only 12% of the species present within a local community.
 Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
@@
 In addition, more than half of all species contributed disproportionally to a specific function in at least one site inside their range.
+There are thus no widespread key species to target for conservation, rather, the functional role and conservation priority of species should be investigated at a local scale.
 
@@
 process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy [@Brandl2019front].
-To appropriately manage coral reef functioning with local needs and stressors, future research should seek to establish functional baselines for global coral reefs.
-Until then, our study suggests that coral reef fish functions can be managed by maximizing standing stock biomass, protecting local key species, and promoting a balanced community structure.
+To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
+Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure.
 
@@
 
-# Figures
+<br>
+
+**References**
+<div id="refs"></div>
+
+**Acknowledgements:**
+We thank the staff at CRIOBE, Moorea for field support.
+We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Sophie Schiettekatte for proof-reading the manuscript, and Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analyis.
+This research was funded by the BNP Paribas Foundation (Reef Services Project) and the French National Agency for Scientific Research (ANR; REEFLUX Project; ANR‐17‐CE32‐0006).
+This research is product of the SCORE-REEF group funded by the Centre de Synthèse et d’Analyse sur la Biodiversité (CESAB) of the Foundation pour la Recherche sur la Biodiversité (FRB) and the Agence Nationale de la Biodiversité (AFB).
+VP was supported by the Institut Universitaire de France (IUF) and JMC was supported by a Make Our Planet Great Again Postdoctoral Grant (mopga‐pdf‐0000000144).
+**Author contributions:**
+NMDS and VP conceived the idea and NMDS, VP, SJB, and JMC designed methodology; NMDS, JMC, SJB, AM, FM, VP, KSM, JEA and DEB collected the data; All authors shared existing data.
+NMDS analyzed the data and led the writing of the manuscript.
+All authors contributed significantly to the drafts and approved the final version for publication.
+**Competing interests:** None declared.
+**Data and materials availability:**
+All data and code to reproduce figures are available online through GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9).
+All data on individual fish traits are available from the corresponding author on reasonable request.
+
+**Figure legends**
 
@@
 Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.](../output/plots/figure_4_vuln_com.png)
-
-<br>
-
-**References and Notes:**
-<div id="refs"></div>
-
-**Acknowledgements:**
-We thank the staff at CRIOBE, Moorea for field support.
-We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Sophie Schiettekatte for proof-reading the manuscript, and Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analyis.
-**Funding:**
-This research was funded by the BNP Paribas Foundation (Reef Services Project) and the French National Agency for Scientific Research (ANR; REEFLUX Project; ANR‐17‐CE32‐0006).
-This research is product of the SCORE-REEF group funded by the Centre de Synthèse et d’Analyse sur la Biodiversité (CESAB) of the Foundation pour la Recherche sur la Biodiversité (FRB) and the Agence Nationale de la Biodiversité (AFB).
-VP was supported by the Institut Universitaire de France (IUF) and JMC was supported by a Make Our Planet Great Again Postdoctoral Grant (mopga‐pdf‐0000000144).
-**Author contributions:**
-NMDS and VP conceived the idea and NMDS, VP, SJB, and JMC designed methodology; NMDS, JMC, SJB, AM, FM, VP, KSM, JEA and DEB collected the data; All authors shared existing data.
-NMDS analyzed the data and led the writing of the manuscript.
-All authors contributed significantly to the drafts and approved the final version for publication.
-**Competing interests:** None declared.
-**Data and materials availability:**
-All data and code to reproduce figures are available online through GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9).
-All data on individual fish traits are available from the corresponding author on reasonable request.
-
-**Supplementary Materials:**
-Materials and Methods
-Figures S1-S5
-Table S1
-Supplementary methods
-References (##-##)

### 2021-09-09 text/methods.Rmd
methods edits

@@
 Finally, we estimated multifunction, i.e.
-one measure that combines all five functions by taking the geometric average of the five standardized functions.
+one measure that combines all five functions by taking the geometric average of the five functions ( nomalized to range between zero and 100).
 We used the geometric mean because functions are dependent on each other and may vary considerably.
@@
 
-\noindent Finally, to investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
+\noindent Finally, to investigate the effect of the community structure while still accounting for the effects of standing biomass and sst, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
 
@@
 
-All Bayesian models were fitted using the R package *brms* (ref) which uses Stan, a C++ package for performing full Bayesian inference.
+All Bayesian models were fitted using the R package *brms* [@Burkner2017] which uses Stan, a C++ package for performing full Bayesian inference [@Carpenter2017].
 The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
-The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots.
-Posterior predictive checks for are provided in Supporting Information xxxx.
+The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig Sx).
 
 ## 5. Species dominance and contributions to functions
-We quantified the relative contribution of each species to each function for all transects as followed:
+We quantified the relative contribution of each species to each function for all sites as followed:
 <!-- \begin{equation} -->
@@
 <!-- \end{equation} -->
-where i is a certain species, j is a transect, F is the value of function f.
+where i is a certain species, j is a site, F is the value of function f.
 
-Then, we quantified the degree of species dominance per function for each transect.
+Then, we quantified the degree of species dominance per function for each site.
 We did this by first ranking species according to their contribution to function, followed by quantifying the cumulative contributions of species to functions.
@@
 Finally, we quantified the frequency of dominance per species, i.e.
-the number of transects in which a species is dominant for a given function divided by the total number of transects in which that species is observed.
-A species is considered dominant for a certain function in a given transect if their contribution is higher than 1/R, i.e.
+the number of sites in which a species is dominant for a given function divided by the total number of sites in which that species is observed.
+A species is considered dominant for a certain function in a given site if their contribution is higher than 1/R, i.e.
 they contribute more than the situation in which each species contributes equally to a certain function.
 
-## 6. Vulnerability to fishing and climate change
-First, we estimated or extracted two measures of vulnerability per species: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011].
-For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals.
-Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral, and body size [@Graham2011].
-Specifically, we used a score for climate change vulnerability for 134 species found in Graham et al.
-(2011) [@Graham2011] and fitted a Bayesian mixed effect predictive model that relates these vulnerability scores with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs.
-not dependent) [@Coker2014; @Cole2008].
-We also included a random effect for family:
-$$ y_i \sim normal(\mu_i, \sigma)$$
-$$
-\mu_i = (\beta0 +  \delta_{family}) + \beta1 log(sizemax) + \beta2 HD + \beta3 FD  ,
-$$
-with $y_i$ the vulnerability score of species i, $\mu_i$ the average predicted vulnerability score, sizemax the maximum length of the species, HD de dependence for habitat, and FD the depedendence for food.
-To verify the fit of the model we inspected the posterior predictive plot, which indicated a good fit.
-Further, the model had a Bayesian R2 of 0.97.
-We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset.
-We provide the model parameters in supplementary table xx.
-\par For species' vulnerability to fishing, we extracted the index from Cheung et al.
-(2005) [@Cheung2005].
-Next, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species.
-Finally, we fitted a mixed model to predict the average vulnerability to climate change and fishing for each function.
-
 ## References

### 2021-09-09 text/suppl_methods.Rmd
methods edits

@@
 
-To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required [see @Schiettekatte2020].
-Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models.
+We used individual-based bioenergetic models to estimate key fish-mediated functions in global coral reefs.
+We first assembled a global species list based on an openly accessible database of reef fish abundances and sizes collected during belt transects by divers [@Barneche2019].
+We used a subset of available data (see methods) and included 1110 species that belong to 25 families: Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae.
+To apply bioenergetic models and estimate fluxes of carbon (C), nitrogen (N), and phosphorus (P) for all species in the underwater visual census database across their entire temperature range, a number of parameters are required [Table 1; @Schiettekatte2020].
+Here, we describe how these parameters were quantified for all 1110 species through a combination of literature, empirical measures, and Bayesian models.
+
 All protocols related to the capture and handling of fish complied to the ethical standards of CRIOBE and EPHE, and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019).
@@
 
+Table 1.
+Overview of model parameters and variables, including input parameters, to be specified by the user of the model, which are indicated with \(\times\).
+Main output variables, predicted by the model are indicated with \(\star\).
+VBGC = von Bertalanffy growth curve.
+| **Symbol**                    | **Description**                                           | **Unit**                                              |
+|-------------------------------|-----------------------------------------------------------|-------------------------------------------------------|
+| \(k\)                         | Index for element C, N or P                               | \(\_\)                                                |
+| \(S_\textrm{k}\) \(\star\)    | Element-specific minimal supply rate                      | \(\textrm{g d}^{-1}\)                                 |
+| \(G_\textrm{k}\) \(\star\)    | Element-specific growth                                   | \(\textrm{g d}^{-1}\)                                 |
+| \(F_\textrm{0k}\) \(\star\)   | Element-specific minimal inorganic flux                   | \(\textrm{g d}^{-1}\)                                 |
+| \(a_\textrm{k}\) \(\times\)   | Element-specific assimilation efficiency                  | \(\_\)                                                |
+| \(l_\textrm{t}\) \(\times\)   | Total length of individual at time t                      | cm                                                    |
+| \(t\)                         | Age                                                       | yr                                                    |
+| \(l_{\infty}\) \(\times\)     | Asymptotic adult length (VBGC)                            | cm                                                    |
+| \(\kappa\) \(\times\)         | Growth rate parameter (VBGC)                              | \(\textrm{yr}^{-1}\)                                  |
+| \(t_0\) \(\times\)            | Age at settlement (VBGC)                                  | \(\textrm{yr}\)                                       |
+| \(lw_a\) \(\times\)           | Parameter length-weight relationship                      | \(\textrm{g cm}^{-1}\)                                |
+| \(lw_b\) \(\times\)           | Parameter length-weight relationship                      | \(\_\)                                                |
+| \(Q_\textrm{k}\) \(\times\)   | Element-specific body content percentage of dry mass      | \(\%\)                                                |
+| \(m_\textrm{w}\)              | Wet body mass                                             | g                                                     |
+| \(F_\textrm{0Cr}\)            | Resting metabolic rate                                    | \(\textrm{g d}^{-1}\)                                 |
+| \(F_\textrm{0Cz}\)            | Mass-specific turnover rate of C                          | \(\textrm{g C} \textrm{g}^{-1} \textrm{d}^{-1}\)      |
+| \(F_\textrm{0Cs}\)            | Rate of C spent in body mass growth                       | \(\textrm{g d}^{-1}\)                                 |
+| \(f_\textrm{0}\) \(\times\)   | Metabolic normalisation constant independent of body mass | \(\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}\) |
+| \(\alpha\) \(\times\)         | Mass-scaling exponent                                     | \(\_\)                                                |
+| \(m_{w\infty}\)               | Asymptotic wet mass of an adult individual                | g                                                     |
+| \(\phi\)                      | Cost of growth                                            | \(\textrm{g C g}^{-1}\)                               |
+| \(\theta\) \(\times\)         | Activity scope                                            | \(\_\)                                                |
+| \(v\) \(\times\)              | Environmental temperature                                 | \(\textdegree C\)                                     |
+| \(h\) \(\times\)              | trophic level                                             | \(\_\)                                                |
+| \(r\) \(\times\)              | Aspect ratio of caudal fin                                | \(\_\)                                                |
+| \(F_\textrm{0Nz}\) \(\times\) | Mass-specific turnover rate of N                          | \(\textrm{g N} \textrm{g}^{-1} \textrm{d}^{-1}\)      |
+| \(F_\textrm{0Pz}\) \(\times\) | Mass-specific turnover rate of P                          | \(\textrm{g P} \textrm{g}^{-1} \textrm{d}^{-1}\)      |
+| \(m_\textrm{dw}\)             | Ratio of dry mass and wet mass of fish                    | \(\_\)                                                |
+| \(m_\textrm{d}\)              | Dry body mass                                             | g                                                     |
+| \(D_\textrm{k}\) \(\times\)   | Element-specific diet content percentage of dry mass      | \(\%\)                                                |
+| \(I_\textrm{k}\) \(\star\)    | Element-specific ingestion rate                           | \(\textrm{g d}^{-1}\)                                 |
+| \(W_\textrm{k}\) \(\star\)    | Element-specific egestion rate                            | \(\textrm{g d}^{-1}\)                                 |
+| \(F_\textrm{rk}\) \(\star\)   | Element-specific residual inorganic flux                  | \(\textrm{g d}^{-1}\)                                 |
+| \(F_\textrm{k}\) \(\star\)    | Element-specific total inorganic flux                     | \(\textrm{g d}^{-1}\)                                 |
+
 ## 1. Growth parameters
 
-The developed bioenergetic model `fishflux` uses the Von Bertalanffy growth function to calculate daily growth.
+The used bioenergetic model uses the Von Bertalanffy growth function to calculate daily growth.
 This growth function relies on three parameters: $l_{\infty}$, $\kappa$, and $t_0$.
@@
 Then, we extracted the available data for $k_{max}$ from Morais & Bellwood (2018), which are essentially $\kappa$ values from Fishbase, standardized to the maximum length [@Morais2018].
-We filtered out the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
+We selected the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
 In total, this selection process resulted in 439 observations of kmax for varying species and temperatures. \par
 
-Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands, and to which we contributed through data collection and analysis [@Morat2020].
+Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands [@Morat2020].
 This dataset includes total length measurements to the nearest millimeter and fish weights to the nearest 0.1 grams.
 Further, it includes distances between annual growth increments, measured by two independent researchers to prevent biases induced by a single observer.
-These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve (see REF FISHGROWBOT).
+These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve [@Morat2020].
 \par
@@
 Then, we fitted the Von Bertalanffy growth model to all species at each location for which there were at least 3 individuals, using Bayesian hierarchical regression models.
-Both steps of this procedure were carried out using the developed R package 'fishgrowbot' (ref).
+Both steps of this procedure were carried out using the developed R package 'fishgrowbot'.
 The package also automatically estimates the parameter $k_{max}$.
@@
 
-\noindent Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
+Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
+I therefore aimed to predict $k_{max}$ based on body size, temperature, and phylogeny by using a phylogenetic regression model.
+\par
 
-We applied a Bayesian hierarchical model to predict the growth rate of fishes as a function of body size, temperature and phylogeny:
+I extracted the phylogenetic position of all species included through the Fish Tree of Life [@Rabosky2018].
+I retrieved 100 synthetic stochastically resolved phylogenies where missing taxa were placed according to the highest level of taxonomy using the function `fishtree_complete_phylogeny()` in the R package fishtree [@Chang2019].
+For each tree, I calculated the correlation matrix and then averaged each element across the 100 matrices to get one correlation matrix that could be used in the regression model.
+\par
 
+I then fitted a Bayesian phylogenetic regression to predict the growth rate parameter of fishes depending on body size, temperature, and phylogeny with the R package brms [@Burkner2017]:
 <!-- \begin{equation} -->
-$$\textrm{ln}kmax = (\beta_{\textrm{0}} + \gamma_{\textrm{0phy}}) +  \beta_{\textrm{1}} \textrm{ln}sizemax +  \beta_{\textrm{2}} sst + \epsilon,$$
+$$\textrm{ln}k_{max} \sim normal(mu, sigma)$$
+$$mu = (\beta_{\textrm{0}} + \gamma_{\textrm{0phy}}) +  \beta_{\textrm{1}} \textrm{ln}sizemax +  \beta_{\textrm{2}} sst ,$$
 <!-- \label{kmax} -->
 <!-- \end{equation} -->
+where $\textrm{ln}k_{max}$ represents the natural log-transformed $k_{max}$ value, mu is the predicted average, and sigma is the standard deviation, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature.
+I used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. \par
 
-\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
-\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
-\noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature.
+The model fit confirmed a negative relationship of $\textrm{ln}k_{max}$ with maximum body size, and a positive relationship with sea surface temperature (figure \@ref(fig:c4f1)).
+I verified model convergence and fit by checking the posterior predictive plot, inspecting parameter trace plots, and checking the R statistic.
 The Bayesian R2 of the model was 0.738 (95\%CI: 0.702-0.769).
-\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects, attributable to the phylogeny(i.e.
-$\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
+\par
+
+The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects attributable to the phylogeny (i.e., $\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
 This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).
+This means that most of the variation is ecplained by phylogeny.
 
@@
 
-\noindent The CNP\% content of organisms is known to be highly conserved within families [@Allgeier2020sci].
+\noindent The CNP\% content of organisms is known to be highly conserved within taxa [@Allgeier2020sci].
 We therefore use phylogeny to extrapolate these values.
@@
 By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database.
+Essentially, we performed a weighted average od CNP content across diet groups for each species, where the weights represent the probability of being in a certain trophic guild.
 We then took the average and standard deviation across all 1000 draws.
@@
 To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we carried out intermittent-closed respirometry experiments [@Steffensen1989; @Clark2013].
-In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species using hand nets and clove oil (Parravicini, Brandl, and Mercière, unpub.).
+In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species in Moorea, French Polynesia.
+Fishes were capturedby scuba divers using hand nets and clove oil and immidiately transported to the laboratory in coolers with ambient seawater and oxygen stones.
+MORE INFO TO ADD??
 After an acclimatization and fasting period of 48 h in aquaria, the fishes were individually transferred to a water-filled tub at 28°C (ambient sea water temperature) and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
@@
 
-### 4.3 Data analysis and extrapolation
-To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the species and family intercept effect using brms [@Burkner2017].
+### 4.2 Data analysis and extrapolation
+To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the species and family intercept effect using brms [@Burkner2017]:
+$$
+log(mr) \sim normal(\mu, \sigma),\\
+\mu = f_\textrm{0} + \alpha log(biomass)
+$$
+
 We ran the model for 4000 iterations, with a warm-up of 2000 iterations, and four chains.
@@
 where all iterations of the back-transformed family-level intercepts were used for SMR and MMR. We then summarized these predictions by taking the mean and standard deviation.
-We used the family-level estimates for these parameters for all species in our database.
-For families that were not represented in our respirometry dataset, we used the average across all families.
+We used the family-level estimates for these parameters for all species in our database. For families that were not represented in our respirometry dataset, we used the average across all families.
 The parameter $f0$ was adjusted for each temperature in the varying locations of the underwater visual census database, following @Barneche2014:

### 2021-09-23 varia/NEE/Response_to_reviewers.Rmd
supp methods

@@
 output:
-  word_document:
-    fig_caption: yes
-    reference_docx: ../text/word_template.docx
+  word_document
 ---
@@
 In many instances, not nearly enough information is provided for the reader to fully comprehend what is being presented, and in some instances key data or methods elements are not provided.
-There
-are also too many bold and unnecessary statements that are not properly backed up by the given citations.
+There are also too many bold and unnecessary statements that are not properly backed up by the given citations.
 The authors should also check for grammar errors, as I encountered many throughout the paper.
@@
 
-*Thank ypou for your constructive and detailed review.
-We have now clarified and detailed methods throughout.
+*Thank you for your constructive and detailed review.
+We have now provide more details in methods and supplementary methods.
 Further, we updated the approach to estimating correlations by applying multivariate models as suggested.
@@
 Line 3: why not just say “Preserving ecosystem functioning is a critical challenge…”
-*We now state "Preserving the functioning of coral reefs is a critical challenge of the 21st century."*
+*We now state "Preserving coral reef functioning is a critical challenge of the 21st century."*
 
@@
 The authors should improve these aspects throughout the paper and ensure proper citations are given.
+*We have now substantially changed the first paragraph of the introduction to quickly place the reader in the context of coral reef functioning.*
 
@@
 
-*We now wrote a new, seperate results section.*
+*We now wrote a new, seperate results section.
+Further, following the recommendation of another reviewer, we now removed this part of analysis entirely.
+Functional vulnerability is now discussed by combining our results with the known effects of human stressors on fish community structure.*
 
@@
 The reader will have to constantly reference the supplementary methods to understand the results of the paper.
+*We now provide more information in the results section.*
 
@@
 As a reader it’s hard to believe that anything has been truly demonstrated when the only information given is a figure.
+*This paragraph is now removed entirely because as we removed this part of the analysis as mentioned above.*
 
@@
 If we have limited resources but need to prioritize some functions, or combinations of functions, to preserve, which should they be?
+*This paper aims to demonstrate existing trade-offs among functions and what drives them.
+In order to have applicable management recommendations, we first need to find out how much of a certain function is 'good'.
+We are currently still lacking understanding of what a healthy reef really looks like in terms of process-based functions.
+We added the following sentences: "It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
+process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy.
+To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
+Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure."*
 
@@
 Please try to make this clearer for the reader.
+
 *The x-axis was showing the difference between the contribution to function and the contribution to biomass.
@@
 
-*To check.*
+*To add in supp methods.*
 
@@
 For all instances of environmental data in the paper, the source and resolution of these data must be provided.
-*The model mentioned here is talking about the bioenergetic model 'fishflux' that estimates fluxes of carbon, nitrogen, and phosphorus.
-We now reworded this section to clarify this.
+*The model mentioned here is talking about the bioenergetic model provided in the R package 'fishflux' that estimates fluxes of carbon, nitrogen, and phosphorus.
+We now reworded this section to clarify.
 We also added mentions of body size and sea surface temperature in the first section of the methods.*
@@
 This needs to be a mixed effects model with random effects for site and locality.
-Curiously, the authors state just afterwards that they did run a mixed effects model of this nature, but no
-further information is given.
+Curiously, the authors state just afterwards that they did run a mixed effects model of this nature, but no further information is given.
 2) Running a correlation on the residuals of a linear model instead of running a multiple regression is an inappropriate analysis.
@@
 This enabled us to estimate correlations on the site, locality, and residual level, as is now shown in figure 2.
-The only obstacle for using multivariate models was that some transects have false zeros for herbivory or piscivory.
-We solved this issue by including these observations as missing values, essentially handling them as parameters in the model.
+The only obstacle for using multivariate models was that some transects have missing values (false zeros) for herbivory or piscivory.
+We tackled this issue by including these observations as missing values, essentially handling them as parameters in the model.
 This is now explained in the methods section as followed:*
@@
 Line 117: It’s unclear to me whether the authors developed their own model based on the scores from Graham et al, or if they used a model already produced by Graham et al.
-*We used the scores from Graham et al. to create a new model and used the model to predict the scores for species that are not provided in that paper.*
+*We used the scores from Graham et al.
+to create a new model and used the model to predict the scores for species that are not provided in that paper.
+Graham et al.
+only used three families, so we are aware that this is a big extrapolation.
+Following reviewer's recommendation, we now removed this analysis from the paper.*
 
 Line 120: why are model formulas/equations provided for other Bayesian models but not here?
-*We now added the equations.*
+*This part was removed.*
 
 Line 121: Reference the supplementary figure otherwise the reader has no basis on which to believe there was a good model fit.
-*to do*
+*Same*
 
@@
 Please expand this section to better explain exactly how this analysis was done and make it clearer for the reader as to how it should be interpreted.
-*We now removed this sentence and calculation because we now opt to show the vulnerability scores per community, rather than proportions.*
+*Same.*
 
@@
 
-*to do*
+*Thank you for the suggestion.
+This is the only comment that we decided not to include.
+The paper by Froese and Binohlan is over twenty years old and the data they used does not include reef fishes.
+Moreover, asymptotic length can vary significantly across locations depending on temperature and other environmental variables.
+We therefore opted for a method proposed and applied by Renato Morais and colleagues.
+They standardize asymptotic lenth to maximum length to avoid underestimating growth.
+In this method, the parameter k, is adapted to kmax in order to represent a realistic growth curve.
+Doing this may underestimate growth of juvenile fishes, while the potential overestimation of adult fishes would be very minimal.
+As visual census data often does not accurately record juveniles and we removed small fishes from this specific analysis, we argue that our method minimizes potential bias considering the data available.
+The risk of using a general conversion factor would be too big as we would estimate a growth equal to zero for a lot of individuals and potentially dramatically underestimate biomass production.*
 
 Line 11: what is this standardized coefficient? Is there a reference?
+*We added the definition and reference.
+"For k, we used a standardized coefficient that describes the potential growth trajectory of an individual if linf were to be equal to its maximum length (i.e., kmax; Morais & Bellwood, 2018)."*
 
 Line 14: Be careful to reword this sentence, you’ve filtered out all other species than the species in your species list, not the other way around.
+*We changed it to "We selected the species of our species list"*
 
 Line 15: I am a bit lost here, what is the “length-frequency method” is this also from Morais?
+*The length-frequency method is another, arguably unreliable way to estimate growth trajectories, that is used for some of the data provided on fishbase.
+We opted to only use growth curve parameters that were estimated from otolith data.
+We clarified this by saying: "We selected the species of our species list and only included the k estimates coming from otolith studies."*
 
 Line 17: again, what temperatures are you referring to? No information has been given about temperature to this point in the manuscript.
+*As mentioned above, we now added text on temperature at the start of the methods section.*
 
 Line 18: “additional” otolith data implies that there were otolith date previously referenced in the manuscript. If this is not the case be sure not to confuse the reader.
+*We now clarified this by mentioning otolith data in the previous paragraph.*
 
@@
 You should also mention how these fishes were collected – what method and were they euthanized, etc.?
+*Since initial submission, this data was published under the form of a data paper. We now added this reference.*
 
@@
 This information should be presented for each of the Bayesian models you conduct in the paper.
+*We added more details on the model.*
 
 Line 43: It is not clear how many species and individuals actually had otolith data? 496 estimates yes, but how many species?
+*"After combining the two data sources, we obtained 496 estimates of kmax for 181 species across varying temperatures."*
 
 Line 52: natural log transformed.
+*Done.*
 
 Line 53: what were these priors? Put them with the model formula.
+*To do!*
 
 Line 59: Is this value considered high? Low? Medium? It would be good to give some context for the reader.
+*It means that most of the variation (independent of size and sst) is explained by phylogeny. This value is thus considered quite high. We now specify this.*
 
@@
 This information is really the basic necessities that need to presented before you rush into describing the analyses.
+*We added a paragraph on the phylogenetic trees.*
 
@@
 For instance, image that all the hard data you collected came from closely related species and families, this might produce unreliable “out-of-sample” predictions.
+*To do.*
 
 Line 110: It could be good to say how many families and how many species per family since you use these data for extrapolation.
+*To do.*
 Line 123: combined how?
+*Essentially by taking a weighted average of nutrient contents across trophic groups where the weights represent the probability of being in a diet group.*
 
@@
 As a reader I don’t know what part of the world they came from or whether they were caught in a lagoon or on a reef crest.
+*To add.*
 
 Line 153: how did you define what an outlier is?
+*To add.*
 
 Line 161: If you used an informative prior you must give the reasoning as to why and to how you chose the prior.
+*To add.*
 
 Extended Data Figure 2: it might be easier to read if you put the names of the functions as figure titles.
+*We added the function names.*
 
 Extended Data Figure 5: just a small thing, but some figures have capital letters for the panel labels, and some have lower case.
+*Fixed.*
 
@@
 
+*Thank you. We have now rewritten the manuscript substantially. We focused on imroving clarity, we added a results section, and provided much more details in the methods.*
+
 One major point of confusion for me was the lack of any attempt to combine the ecosystem functions mentioned into a multifunctionality framework.
@@
 Even a simple average geometric mean of multifunctionality could be informative, especially for identifying hotspots in fish-driven reef function.
+
+*We now added estimates of multifunctionality per locality and and biomass based on a geometric mean as suggested.
+We agree that suh a measure can be infomative, but we argue that multifunctionality should be interpreted with care as this summarizing measure may obscure the trade-offs between individual functions.*
 
@@
 That seems like a huge part of this story, and that there actually IS a global pattern in how fish communities affect ecosystem functions in reefs.
-The authors mention that their work reveals that there is no clear objective for protecting coral reef functioning,
-and there are no global keystone species to target.
+The authors mention that their work reveals that there is no clear objective for protecting coral reef functioning, and there are no global keystone species to target.
 It is unclear how exactly the authors evaluated those statements, and is surprising that the authors have no recommendations that would help address those clear conservation goals from their global analyses.
+*We now mention the role of community structure in the introduction.
+In the discussion, we both discuss the effect of biomass and community structure as a whole.
+We also modified the discussion on conservation.
+We now say: "It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
+process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy.
+To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
+Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure."*
 
@@
 This section is very strong. The authors should use the focus of each of these sentences to guide the topic sentences of the manuscript sections. Clear and concise!
+*Thank you. We aimed to clarify all topical sentences.*
 
@@
 The central message is simple enough that the authors should be more specific and precise with their wording and sentences.
+*We rewrote the introduction and avoided using many contradicting words. We believe the introduction is now more focused.*
 
@@
 “The world’s coral reefs” can be replaced with “Coral reefs” (I don’t think any readers are going to be thinking of any coral reefs on other worlds!) and “today’s coral reef conservation efforts” to “current coral reef conservation efforts”.
+*We removed the word 'integrity' throughout the manuscript. We also avoided using informal language and removed the given examples.*
 
 21- “integrity” repeated here again. Still unsure what the integrity of an ecosystem means.
+*Agreed, it is a rather confusing and vague term. We removed it.*
 
 22- careful with switching tenses here. This sentence could probably be removed.
+*Done.*
 
@@
 If so, that is a fantastic point to make and represents a huge gap in ecology today!
+*This section has been changed entirely.*
 
 31-42 I was surprised that this paragraph doesn’t fully focus on the role of fishes in nutrient cycling/ecosystem functioning in coral reefs.
+*The second paragraph of the introduction now focuses on fishes.*
 
 33- “integrity” repeated again. Do you mean function?
+*No more integrity in this manuscript.*
+
 34- An example of an edit to be more concise: the authors wrote “a plethora of stressors” and then added “such as….”. Pick one of the two of these. I would suggest getting rid of “a plethora of”.
+*Done as suggested.*
+
 37 Generally it is better to write out exactly why a topic is “at the forefront of scientific discourse” as opposed to just stating that it is. Because the reader is left to ask, why?
+*We removed this sentence and now say: "Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reef functioning."*
 
@@
 unclear, is it that we have only proxies of functioning, or that we know little about elemental fluxes? Or both?) constitute a severe limitation.
+*As mentioned above, we rewrote the introduction entirely, and hope you will find it has improved in clarity.*
 
@@
 Or are there key species that provide high functioning?
+*We understand the confusion, and now removed the part of the figure shhowing the contribution of fish families as it was not a main result and distracts the reader from the main point which is indeed that on a local scale a few key species provide high functioning while the identity of these key species vary across sites.*
 
@@
 Also, please make sure that this isnt directly repetitive from the introduction.
+*We now have a seperate results paragraph accompagning figure 4. We hope this clarifies these findings.*
 
@@
 Regardless, this sentence doesn’t quite mesh with the opening sentence of this paragraph, so please edit for clarity here.
+*The topical sentence of this paragraph is now: "Our results also reveal that functions consistently hinge on a few dominant species, but the identities of local, dominant species vary strongly across sites."*
 
 108 I’m not sure what a “severe change” is, especially in a broad term like community structure.
+*We modified the sentence as followed: "Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure."*
+
 112 “effect” used twice in one sentence.
+*Changed to: "When accounting for the effect of biomass, these community shifts can..."*
+
 114 is this what Fig 2 shows? Do you mean Fig 4? Unclear
+*We removed the mention of the figure in this discussion paragraph as we now have a seperate results section.*
+
 114-116 “On the other hand” and “However” open back to back sentences. This is a clear indication that whatever points are trying to be made, are unfocused.
+*We edited the section and replaced 'on the other hand' to 'further', and 'However' to 'Simultaneously'.*
 
@@
 The paragraph above it is wavering, with an unclear main theme.
-This last sentence is actually quite good and brings up a fantastic point.
+This last sentence is actually quite good and brings up a fantasticthough point.
 It reads much more like a topic sentence.
 Considering the topic sentence of this paragraph is pretty vague (i.e., “shines new light on” doesn’t tell us anything specific), the authors should consider a reordering of the logic flow here, in above paragraphs, and in the discussion section as a whole.
+*The topical sentence of this paragraph now reads: "Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems."*
+
 122-4 I’m not sure that something can be both nuanced and holistic. Rephrase.
+*We removed the sentence.*
 
 125 “Similarly…” It is unclear what is similar here. Rephrase
+*We removed this paragraph as suggested below.*
+
 134 What does this sentence mean?
@@
 137 …But can you not do this, with the data you have collected? The whole end of this paragraph is confusing and needs to be revisited.
+*We removed this paragraph altogether.*
 
@@
 Identifying the global multifunctional hotspots of coral reef fish communities could be of value to conservation and management.
+*We now edited this first figure to show the actual function estimates per location, as well as a measure of multifunctionality.*
 
@@
 This is further unclear when looking back at the ms text in line 78 that implies that small/immature fish are the same.
+*This is now figure 3.
+We modified the x-axis label to "standardized effect size" and the percentages to lower and upper.
+We provided extra information in the legend.
+An individual fish can both be small and mature, so both variables are quite different.
+Immaturity is a measure that represents the position in the growth curve.
+We now also added a definition in the legend.
 
@@
 Actually, all axes need to be explained better
+*We removed figure 3a.*
 
@@
 This figure, and the paragraph in the main text surrounding it, seem out of place.
+*As suggested, we removed this figure and the paragraph surrounding it. Instead, we now provide a conceptual figure that supports this part of the discussion.*
 
@@
 80 “fitted” should be “fit” ?
+
+*We added more information on the priors everywhere.*
 
@@
 Without this, it is difficult to tell why techniques like the Bayesian phylogenetic regression model are necessary.
+*We now added much more information and introductory sentences in the supplementary methods.*
 
 14 is kmax defined? k is defined as a growth rate parameter in the Methods line 68, but each Methods section should be able to stand alone.
+
+*We added the definition.*
 
@@
 
+*Thank you, we are delighted that you enjoyed reading our paper. We clarified the text as specified below.*
+
 My only major comment is the need to better justify the five key ecosystem functions that you focus on for the reader.
@@
 You can do this in 2-3 strong sentences.
+*We substantially modified the introduction and added a paragraph on fish-mediated functions specifically.
+We agree that quantifying all functions proposed by Brandl et al.
+would have been even better.
+However, we did not have access to data to do so.
+For example, CaCO3 production by corals requires on detailed data on coral cover including the community composition and the sizes of corals.
+We did not have any data on benthic cover for this specific project.
+We thus only analyzed the functions that are related to fishes based on the data available and the confidence in methodology.*
 
@@
 This leads to disparate vulnerabilities of functions to anthropogenic stressors”
+*We removed the second sentence.*
 
@@
 If so, I would state this more clearly, as this is an important message from the data.
+*We now say: "Our results underline the need for a nuanced, local, and context-dependent approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass."*
 
@@
 2018 Current Biology 28: 3355-3363).
+*Agreed. However, we now removed this sentence following the suggestion of reviewer 1. MAYBE I SHOULD INCLUDE THIS??*
 
@@
 Suggest adding Williams & Graham (2019) Funct Ecol 33: 942-947 to references here also as this editorial captures the messages from a suite of studies talking about functional changes to coral reefs in the Anthropocene.
+*Done.*
 
 Line 41 – “but see 18”. Please tell us what Allgeier et al. found – annoying for reader to have to go and read another paper to understand this statement.
+*Done. We now state this explicitely.*
 
 Line 41-42. How exactly is this hindering effective management of reefs? You leave the reader guessing here – poor style.
+*We now say: "This sparsity of quantification of functions constitutes a severe limitation to efficient management of coral reef ecosystem functioning." I AM NOT SURE THAT THIS SUFFICES.
+ANY SUGGESTIONS?*
 
 Line 69. Suggest avoid the term “holistic”, nothing can ever truly be holistic, without mentioning the connotations of unscientific holistic medicines.
+*We removed the word 'holistic'.*
 
@@
 If a mechanic was advertising that their garage fixes exhausts “and” steering systems, you could take your car there to have both fixed, or just one….they are not implying it has to be both at the same time!
+*Good point, we changed it to 'and'.*
 
 Line 93. I think this is meant to read “consistently hinge on”.
+*Modified as suggestes.*
 
 Line 107. Contributions to what?
+*Contributions to functions. We removed this specific sentence though.*
 
 Line 108-109. The Hughes et al. reference is not appropriate here as it does not address “reef fish”.
+*Agreed. We removed the reference here.*
 
 Line 119-120. Why does a shift in algal symbiont dominance matter? I think you need to make it clearer to reader here why this (and algal growth) are considered bad (if that is what you are implying).
+*We simplified this section and now say: ...
+so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth in comparison with corals.*
 
 Line 123. Same comment about use of “holistic”.
+*We removed the word holistic.*
 
 Line 125. Poor style to start a new paragraph with “similarly”. Too much connection/reliance on previous sentence that sits in a different paragraph.
+*We removed this entire paragraph.*
 
 Line 132-133. Can impact smaller browsers also, see Heenan et al. (2016) Proc B 283: 1843 (Fig. 3).
+*Same.*
 
 Line 164. Suggest replace “through” with “using”.
+*Done as suggested.*
 
@@
 Also not clear what the “categorical assignments” are from the figure legend alone – please expand the explanation.
+*We added extra details in the legend.*
 
@@
 There are plenty of color-blind friendly palettes out there now.
+*The color palette was created based on the natural colors of a coral reef fish species: Callanthias australis.
+We regret that the reviewer found the colors off-putting.
+We tested the color combination by simulating color-blindness using the website https://coolors.co/ and the red green combination seem to be distinguishable due to differences in clarity.
+Moreover, as functions are kept in the same order throughout the paper, the results could be interpreted even if there were no colors at all.
+Therefore, we decided to keep the colors for now, but if this is a big issue for the reviewer or the editor agrees with the reviewer, we will change the color palette.*
 
 Figure 2 seems unnecessarily large – this could be a single column figure.
+*Agreed. We decreased the size.*
 
 Figure 4 – Suggest proportion values radiating out run to 1 so piscivory falls within the axis bounds.
+*This is a great point, thanks for noticing. However, following a recommendation of reviewer 2, we now actually removed this figure.*
 
 All Figures – there are some inconsistencies in font use/size across your figures. This might seem picky, but important for consistency.
+*We standardized sizes and fonts as much as possible.*
 
 Did you synthesize this data set yourself or did you use an existing database that has been previously published from? Please make this clear in the main manuscript.
+*We used an existing underwater visual census database that has been previously published from. We collected extra data ourselves to parametrize bioenergetic models. We stated this more clearly now.*

### 2021-09-23 text/main.Rmd
supp methods

@@
     fig_caption: yes
-    reference_docx: ../text/word_template_science.docx
+    reference_docx: ../text/word_template.docx
 bibliography: ../text/global_proc.bib
@@
 Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
-Our results underline the need for a nuanced approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.
+Our results underline the need for a nuanced, local, and context-dependent approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.
 
@@
 In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
-Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood], while communities dominated by immature fishes maximize biomass production.
+Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood2005], while communities dominated by immature fishes maximize biomass production.
 Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].
@@
 
-Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
-Fishing and climate-induced coral loss have caused severe changes in reef fish biomass and community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
+Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
+Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have effects on ecosystem functioning.
 Intensive fishing and associated reductions in biomass of large fishes alters the size, age, and trophic structure of fish communities [@Graham2017].
-When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g. @Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
+When accounting for the effect of biomass, these community shifts can enhance nitrogen excretion and production [e.g.
+@Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
 Futher, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
-However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].
+Simultaneously, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth in comparison with corals [@Burkepile2013].
 
@@
 
-Overall, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning.
+Overall, using coral reef fishes, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning.
 Management strategies that call for the enhancement of coral reef functioning via an economic mindset (i.e.
@@
 
-![Fig.
+Fig.
 1: Maps of five key ecosystem functions and multifunction, and their relationships with biomass.
@@
 Right: The predicted values for functions and multifunction with increasing biomass.
-The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.](../output/plots/fig1_multimap.png)
+The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.
 
-![Fig.
+Fig.
 2: Correlations among five functions while accounting for biomass and sea surface temperature.
@@
 Dots represent the average and lines represent the 95%CI.
-b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.](../output/plots/fig1_multimap.png)
+b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.
 
-![Fig.
+Fig.
 3.
@@
 All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data).
-Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)
+Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.
+Immaturity is defined as the derivative of the Von Bertalanffy growth model for a given size, and the higher this value, the younger the individual.
 
-![Fig.
+Fig.
 4: Local dominance in species contributions for five ecosystem functions on coral reefs.
@@
 c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present).
-A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).](../output/plots/fig3_contributions.png)
+A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).
 
-![Fig.
+Fig.
 5.
 Vulnerability of five critical functions to fishing and climate change-induced coral loss.
-Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.](../output/plots/figure_4_vuln_com.png)
+Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.

### 2021-09-23 text/methods.Rmd
supp methods

@@
 Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration of the USA (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).
-Further, for each transect, we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
+Further, for each transect, we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014].
 All data wrangling and analyses were performed in the software program R (version 4.0.2; R core team 2020).
@@
 $$
-\mu_{\textrm{ExN,i}}  = (\beta0_{ExN}  +  \delta_{ExN, loc}  +  \delta_{ExN, site}) \\
+\begin{array}{c} \mu_{\textrm{ExN,i}}  = (\beta0_{ExN}  +  \delta_{ExN, loc}  +  \delta_{ExN, site}) \\
 \mu_{\textrm{ExP,i}}  = (\beta0_{ExP}  +  \delta_{ExP, loc}  +  \delta_{ExP, site})  \\
@@
 \mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) \\
-\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) ,
+\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) , \end{array}
 $$
@@
 
-$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
+$$\begin{array}{c} \mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
 \mu_{\textrm{ExP,i}} = (\beta0_{ExP} +  \delta_{ExP, loc} +  \delta_{ExP, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExP}} {x_{sst,i}} \\
@@
 \mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) +{\beta1_{Herb}} {x_{log(biomass),i}} + {\beta2_{Herb}} {x_{sst,i}} \\
-\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) +{\beta1_{Pisc}} {x_{log(biomass),i}} + {\beta2_{Pisc}} {x_{sst,i}}
+\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) +{\beta1_{Pisc}} {x_{log(biomass),i}} + {\beta2_{Pisc}} {x_{sst,i}} \end{array}
 $$
@@
 
-$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} x_{log(biomass),i} + \beta2_{function} x_{sst,i}  + \beta3_{function} x_{richness,i}  + \beta4_{function} x_{size_m,i}  + \beta5_{function} x_{size_{2.5\%},i} +  \beta6_{function} x_{size_{97.5\%},i} + \\ \beta7_{function} x_{troph_m,i}  + \beta8_{function} x_{troph_{2.5\%},i} +  \beta9_{function} x_{troph_{97.5\%},i} + \beta10_{function} x_{imm_m,i}  + \beta11_{function} x_{imm_{2.5\%},i} +  \beta12_{function} x_{imm_{97.5\%},i} $$
+$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} x_{log(biomass),i} + \beta2_{function} x_{sst,i}  + \beta3_{function} x_{richness,i}  + \beta4_{function} x_{size_m,i}  + \beta5_{function} x_{size_{2.5\%},i} +  \beta6_{function} x_{size_{97.5\%},i} + \\
+\beta7_{function} x_{troph_m,i}  + \beta8_{function} x_{troph_{2.5\%},i} +  \beta9_{function} x_{troph_{97.5\%},i} + \beta10_{function} x_{imm_m,i}  + \beta11_{function} x_{imm_{2.5\%},i} +  \beta12_{function} x_{imm_{97.5\%},i} \end{array}$$
 

### 2021-09-23 text/suppl_methods.Rmd
supp methods

--- 2021-07-27 text/suppl_methods.Rmd
@@
 
-# Supplementary methods
+# Supplementary methods of “Biological trade-offs underlie coral reef ecosystem functioning”
 
-To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required [see @Schiettekatte2020].
-Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models.
+We used individual-based bioenergetic models to estimate key fish-mediated functions in global coral reefs.
+We first assembled a global species list based on an openly accessible database of reef fish abundances and sizes collected during belt transects by divers [@Barneche2019].
+We used a subset of available data (see methods) and included 1110 species that belong to 25 families: Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae.
+To apply bioenergetic models and estimate fluxes of carbon (C), nitrogen (N), and phosphorus (P) for all species in the underwater visual census database across their entire temperature range, a number of parameters are required [Table 1; @Schiettekatte2020].
+Here, we describe how these parameters were quantified for all 1110 species through a combination of literature, empirical measures, and Bayesian models.
+
 All protocols related to the capture and handling of fish complied to the ethical standards of CRIOBE and EPHE, and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019).
@@
 
+Table 1. Overview of model input parameters, adopted from Schiettekatte et al. (2020). VBGC = von Bertalanffy growth curve.
+
+**ADD TABLE**
+
 ## 1. Growth parameters
 
-The developed bioenergetic model `fishflux` uses the Von Bertalanffy growth function to calculate daily growth.
-This growth function relies on three parameters: $l_{\infty}$, $\kappa$, and $t_0$.
+The bioenergetic model uses the Von Bertalanffy growth function to estimate daily growth [@Schiettekatte2020].
+This growth function relies on three parameters: $l_{\infty}$ (i.e.
+the population asymptotic body length of a fish), $\kappa$ (i.e.
+the rate at which fish in a population, on average, approaches its population asymptotic body size), and $t_0$ (i.e.
+the theoretical age at which length is zero).
 For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e., $k_{max}$, @Morais2018].
@@
 We first compiled maximum lengths for all species using Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$.
-Then, we extracted the available data for $k_{max}$ from Morais & Bellwood (2018), which are essentially $\kappa$ values from Fishbase, standardized to the maximum length [@Morais2018].
-We filtered out the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
-In total, this selection process resulted in 439 observations of kmax for varying species and temperatures. \par
+Then, we extracted the available data for $k_{max}$ from Morais & Bellwood (2018), which are estimated using growth curve parameters from Fishbase, standardized to the maximum length [@Morais2018].
+We selected the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
+In total, this selection process resulted in 439 observations of $k_{max}$ for varying species and temperatures. \par
 
-Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands, and to which we contributed through data collection and analysis [@Morat2020].
+Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands [@Morat2020].
 This dataset includes total length measurements to the nearest millimeter and fish weights to the nearest 0.1 grams.
 Further, it includes distances between annual growth increments, measured by two independent researchers to prevent biases induced by a single observer.
-These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve (see REF FISHGROWBOT).
+These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve [@Morat2020].
 \par
@@
 Specifically, we used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish lengths at previous ages.
-We adapted the traditional model to also estimate the uncertainty around the obtained length estimates and allow for the inclusion of missing values using a Bayesian approach (see ref fishgrowbot for details).
+We adapted the traditional model to also estimate the uncertainty around the obtained length estimates and allow for the inclusion of missing values using a Bayesian approach (see R package fishgrowbot).
 Then, we fitted the Von Bertalanffy growth model to all species at each location for which there were at least 3 individuals, using Bayesian hierarchical regression models.
-Both steps of this procedure were carried out using the developed R package 'fishgrowbot' (ref).
+Both steps of this procedure were carried out using the developed R package 'fishgrowbot'.
 The package also automatically estimates the parameter $k_{max}$.
@@
 
-\noindent Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
+Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
+We therefore aimed to predict $k_{max}$ based on body size, temperature, and phylogeny by using a phylogenetic regression model.
+\par
 
-We applied a Bayesian hierarchical model to predict the growth rate of fishes as a function of body size, temperature and phylogeny:
+We extracted the phylogenetic position of all species included through the Fish Tree of Life [@Rabosky2018].
+We retrieved 100 synthetic stochastically resolved phylogenies where missing taxa were placed according to the highest level of taxonomy using the function `fishtree_complete_phylogeny()` in the R package fishtree [@Chang2019].
+For each tree, we then calculated the correlation matrix and averaged each element across the 100 matrices to get one correlation matrix that could be used in the regression model.
+\par
 
+We then fitted the Bayesian phylogenetic regression to predict the growth rate parameter of fishes depending on body size, temperature, and phylogeny using the R package brms [@Burkner2017]:
 <!-- \begin{equation} -->
-$$\textrm{ln}kmax = (\beta_{\textrm{0}} + \gamma_{\textrm{0phy}}) +  \beta_{\textrm{1}} \textrm{ln}sizemax +  \beta_{\textrm{2}} sst + \epsilon,$$
+$$\textrm{ln}k_{max} \sim normal(\mu, \sigma)$$
+$$mu = (\beta_{\textrm{0}} + \gamma_{\textrm{0phy}}) +  \beta_{\textrm{1}} \textrm{ln}sizemax +  \beta_{\textrm{2}} sst ,$$
 <!-- \label{kmax} -->
 <!-- \end{equation} -->
+where $\textrm{ln}k_{max}$ represents the natural log-transformed $k_{max}$ value, $\mu$ is the predicted average, and $\sigma$ is the standard deviation, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the random-effect coefficient that accounts for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature.
+We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. \par
 
-\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
-\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
-\noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature.
-The Bayesian R2 of the model was 0.738 (95\%CI: 0.702-0.769).
-\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects, attributable to the phylogeny(i.e.
-$\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
+The model fit confirmed a negative relationship of $\textrm{ln}k_{max}$ with maximum body size ($\beta_\textrm{1}$ = -0.76, 95\%CI: -0.96,-0.57 ), and a positive relationship with sea surface temperature ($\beta_\textrm{2}$ = 0.02, 95\%CI: 0.00,0.05 ).
+We verified model convergence and fit by checking the posterior predictive plot, inspecting parameter trace plots, and checking the R statistic.
+The Bayesian R2 of the model was 0.738 (95\%CI: 0.702,0.769).
+\par
+
+The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects attributable to the phylogeny (i.e., $\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
 This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).
+This means that most of the variation, independent of the effect of body size and SST, is explained by phylogeny.
 
-\noindent We extrapolated $kmax$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.
+\noindent We extrapolated $k_{max}$ for all species across the full SST range in which those species occur in the database, with SST rounded to the °C, which results in 4712 unique SST and species combinations.
 There is currently no streamlined method to make predictions for new species from a phylogenetic regression model.
@@
 Per draw, we averaged the extrapolated values per species for the hundred trees.
-Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa$ for each species.
+Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa_{max}$ for each species.
 We only use one chain in order to keep computational time reasonable.
-Finally, we summarised all $\kappa$ predictions per sst per species by taking the mean and standard deviation across the 1000 draws.
+Finally, we summarized all $\kappa_{max}$ predictions per SST per species by taking the mean and standard deviation across the 1000 draws.
+
+Finally, we tested our phylogenetic extrapolation approach by performing a leave-one-out cross validation.
+Specifically, we conducted the above-described approach 496 times, each time removing one species from the analysis and extrapolating to that species.
+We then compared the extrapolated values for $\kappa_{max}$ to the predicted $\kappa_{max}$ values based on the full model.
+These values were positively correlated with a correlation coefficient of 0.88.
 
@@
 ### 2.1 Data collection
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea (Parravicini, unpub.), the Caribbean [@Allgeier2020sci], and Palmyra (Bukepile unpub.).
+\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea [@Allgeier2021; Parravicini unpub.], the Caribbean [@Allgeier2020sci], and Palmyra (Burkepile unpub.) (table 2).
 Their gut contents were removed and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
@@
 
+Table 2. Overview number of species and individuals per fish family, used for body stoichiometry analysis. Per species, there was a minimal replication of 4.
+
+**ADD TABLE**
+
 ### 2.2 Data analysis and extrapolation
 
-\noindent The CNP\% content of organisms is known to be highly conserved within families [@Allgeier2020sci].
+\noindent The CNP\% content of organisms is known to be highly conserved within taxa [@Allgeier2020sci; @Allgeier2021].
 We therefore use phylogeny to extrapolate these values.
@@
 
-$$mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},$$
+$$mu_{\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},$$
 <!-- 	\label{cnp2} -->
@@
 
-\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$ respectively, $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the intercept variation, based on the relatedness as described by the phylogeny per element k, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the residual species-level intercept variation per element k.
+\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$ respectively, $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $S$ is the covariance matrix of the residual errors of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the random-effect coefficient that account for the intercept variation, based on the relatedness as described by the phylogeny per element $k$, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the random-effect coefficient that account for the residual species-level intercept variation per element k.
 
@@
 Specifically, we used the phylopars function from the Rphylopars package [@Bruggeman2009].
-This function uses ancectral state reconstruction and brownian motion, and takes the correlation between C, N and P into account.
+This function uses ancestral state reconstruction and Brownian motion, and takes the correlation between C, N and P into account.
 
@@
 By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database.
+Essentially, we performed a weighted average of CNP content across diet groups for each species, where the weights represent the probability of being in a certain trophic guild.
 We then took the average and standard deviation across all 1000 draws.
@@
 To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we carried out intermittent-closed respirometry experiments [@Steffensen1989; @Clark2013].
-In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species using hand nets and clove oil (Parravicini, Brandl, and Mercière, unpub.).
+In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species in Moorea, French Polynesia.
+Fishes were captured by scuba divers using hand nets and clove oil and immediately transported to the laboratory in coolers with ambient seawater and oxygen stones.
 After an acclimatization and fasting period of 48 h in aquaria, the fishes were individually transferred to a water-filled tub at 28°C (ambient sea water temperature) and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
@@
 
-### 4.3 Data analysis and extrapolation
-To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and mr type (SMR or MMR) on both the species and family intercept effect using brms [@Burkner2017].
+### 4.2 Data analysis and extrapolation
+To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and metabolic rate type (SMR or MMR) on both the intercept and slopes using brms [@Burkner2017]:
+$$
+\begin{array}{c} log(MR) \sim normal(\mu, \sigma),\\
+\mu = f_\textrm{0} + \alpha log(biomass) \\ \end{array}
+$$
 We ran the model for 4000 iterations, with a warm-up of 2000 iterations, and four chains.
-Further, we used an informative prior for the slope ($\alpha \sim normal(0.8, 0.5)$.
+Further, we used an informative prior, for the slope ($\alpha \sim normal(0.8, 0.5)$), based on previous work [@Barneche2014].
 The model had a Bayesian R2 of 0.973 (95\%CI: 0.972-0.974).
@@
 We did this for all iterations and then took the mean and standard deviation.
-In a similar way, we extracted the family-level intercept for SMR and MMR (figure \@ref(fig:c4f4)), and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of all iterations of the intercept (i.e., the intercept for SMR).
+In a similar way, we extracted the family-level intercept for SMR and MMR, and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of all iterations of the intercept (i.e., the intercept for SMR).
 Finally, we estimated $\theta$ as followed, based on the assumption that fishes rest 12h a day and they on average spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
@@
 We used the family-level estimates for these parameters for all species in our database.
-For families that were not represented in our respirometry dataset, we used the average across all families.
+We used the average across all families for families that were not represented in our respirometry dataset, (Bothidae, Chaetodontidae, Fistulariidae, Haemulidae, Kyphosidae, Lethrinidae, Lutjanidae, Mugilidae, Ostraciidae, Pempheridae, Sciaenidae, Siganidae).
 The parameter $f0$ was adjusted for each temperature in the varying locations of the underwater visual census database, following @Barneche2014:

### 2021-10-05 text/main.Rmd
updates comments Vale, Jordan, Simon, Seb, Diego before resubmission

@@
 We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes.
-We show that functions exhibit critical trade-offs driven by varying community structures, such that no community can maximize all functions.
-Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
-Our results underline the need for a nuanced, local, and context-dependent approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.
+We show that functions exhibit critical trade-offs driven by varying community structures such that no community can maximize all functions.
+Further, functions are locally dominated by few species, but the identity of dominant species substantially varies at the global scale.
+In fact, more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
+Our results reinforce the need for a nuanced, locally tailored approach to coral reef conservation that considers multiple ecological functions beyond the effect of standing stock biomass.
 
 **Main Text:**
-The flow of elements through biological communities fuels all ecosystems on earth [@Welti2017]. Harmful human dominance disrupts the natural functioning in contemperory ecosystems [@Ceballos2015].
-Coral reefs represent a prime example of an ecosystem that is severely impacted by anthropogenic threats such as warming, and intensive fishing pressure [@Hughes2017; @Pauly2002].
-Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reef functioning [@Bellwood2019; @Williams2019; @Brandl2019front).
-However, our knowledge on process-based functions - fluxes of elements and energy - is still in its infancy and evaluations of coral reef functioning typically rely on static proxies, such as live coral cover, standing stock biomass of reef fishes, or measures of diversity [e.g.
-@Cinner2020; @Mouillot2014; @Mora2011].
-This sparsity of quantification of functions constitutes a severe limitation to efficient management of coral reef ecosystem functioning [@Brandl2019front].
+The flow of elements through biological communities fuels all ecosystems on earth [@Welti2017]. Humans increasingly threaten biodiversity and ecosystem functioning [@Ceballos2015].
+Coral reefs are a prime example of an ecosystem severely impacted by anthropogenic activities.
+Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reefs [@Hughes2017; @Pauly2002].
+Maintaining ecosystem functions, defined as fluxes of elements, is a major goal for conservation of coral reefs [@Bellwood2019; @Williams2019; @Brandl2019front].
+However, past evaluations of functions on coral reefs have mostly relied on static proxies such as live coral cover, standing stock biomass of reef fishes, or measures of diversity [@Cinner2020; @Mouillot2014; @Mora2011].
+These simplified proxies, although useful, may not properly represent ecological functions because the fluxes of elements can scale non-linearly with variables such as biomass [@Barneche2014].
+Therefore, improving the quantification of ecological functions constitutes an important step towards the efficient management of coral reef ecosystem functioning [@Brandl2019front].
 
-Coral reef fishes play an essential role in coral reef functioning, because they contribute to a high proportion of consumer biomass and therefore represent essential vectors of fluxes of carbon (C), nitrogen (N) and phosphorus (P) through storage and recycling [@McIntyre2008; @Allgeier2014; @Barneche2014].
-Ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory , and piscivory (secondary consumption) (@Brandl2019front).
-While the high diversity of coral reef fishes has inspired many studies with a focus on ecosystem functioning, only a handful of studies have attempted to quantify functions as continuous fluxes [@Brandl2019front].
-Further, studies that do quantify functions mostly focused on biomass production (e.g., @Morais2019; @Morais2020glob) or fish excretion (e.g., @Allgeier2014), and suggest that functions rely on community structure.
-An assessment of multiple functions on a large scale is currently lacking.
-Consequently, trade-offs amongs functions, their drivers, and their vulnerability to global stressors remain poorly understood in coral reef ecosystems [@Brandl2019front].
+As a dominant group of consumers, coral reef fishes are essential vectors of carbon (C), nitrogen (N) and phosphorus (P) [@McIntyre2008; @Allgeier2014; @Barneche2014].
+Ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory, and piscivory (secondary consumption) (@Brandl2019front).
+While the high diversity of coral reef fishes has inspired many studies that focus on ecosystem functioning, only a handful of studies have attempted to actually quantify functions as continuous fluxes [@Brandl2019front].
+Further, studies that quantify functions as a flow of matter mostly focus on single functions (e.g.
+biomass production [@Morais2019; @Morais2020glob] or fish excretion [ @Allgeier2014]) and are restricted to a small number of species and local scales.
+Consequently, trade-offs amongs multiple functions, their drivers, and their vulnerability to anthropogenic stressors remain poorly understood in coral reef ecosystems across large spatial scales [@Brandl2019front].
 
 Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
-Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: N excretion, P excretion, biomass production, herbivory, and piscivory.
+Using empirical species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: N excretion, P excretion, biomass production, herbivory, and piscivory for 1,100 species.
 We apply these bioenergetic models to 9,118 reef fish transects across 585 sites worldwide (Table S1) to:
@@
 ## Results
-By combining individual-level bioenergetic models and global underwater visual transect data, we quantified five key ecosystem functions mediated by coral reef fishes across the globe.
-We estimated the average functions per locality as well as a combined measure of multifunctionality by running a multivariate Bayesian regression model (Fig.
+We quantified five key ecosystem functions mediated by coral reef fishes across the globe (Fig.
 1).
-Functions across localities show similar spatial patterns, yet a high level of function does not nescessarily ensure a high level of another function.
-For example, Trindade in the South Atlantic Ocean has high values for N excretion, P excretion, and piscivory, but average values for biomass production.
+Functions across localities show a similar geographocal pattern.
+However, at the global scale we could not find a single location with high levels of functioning across all functions.
 A measure of multifunctionality thus does not appropriately represent the state of all functions.
 
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we demonstrate a predictably strong relationship between fish biomass and all five functions by running multivariate mixed effect Bayesian model (Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we demonstrate a predictably strong relationship between fish biomass and all five functions (Fig.
 1).
-Specifically, the effects of the log-transformed biomass on log-transformed functions were 0.932 (95\%CI: 0.929; 0.934), 1.051 (1.047; 1.056), 0.771 (0.764; 0.780), 0.940 (0.923; 0.957), and 0.668 (0.635; 0.702) for N excretion, P excretion, production, herbivory, and piscivory, respectively.
-We also incorporated sea surface temperature (sst) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019].
-We found positive effects of sst on N excretion, production, and herbivory, and negligible effects of sst on P excretion and piscivory (table Sx).
+Specifically, in a multivariate mixed effects Bayesian model, the slopes of the log-transformed biomass were 0.932 (95\%CI: 0.929, 0.934) for N excretion, 1.051 (1.047, 1.056) for P excretion, 0.771 (0.764, 0.780) for production, 0.940 (0.923, 0.957) for herbivory, and 0.668 (0.635, 0.702) for piscivory.
+These slopes indicate that the relationships between biomass and functions are all non-linear, which demonstrates that biomass is not an appropriate proxy for function.
+We also incorporated sea surface temperature (SST) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019].
+We found positive effects of SST on N excretion, production, and herbivory, and no effects of SST on P excretion and piscivory (table S3).
 
-The above-mentioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and sst.
-Specifically, we estimated correlations between functions on three levels: the locality effects, the site effects, and the residual variations (Fig. 2, fig. Sx.
-The correlations mostly overlapped across the three levels for a given pair of functions.
-We found consistently negative trade-offs between P excretion and N excretion, P excretion and biomass production.
-Further, there were slightly weaker negative correlations between piscivory and N excretion and between piscivory and herbivory.
-As a consequence of the negative correlations, a fish community cannot have high values for all functions simultaneously.
+The forementioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and SST.
+In particular, we estimated correlations between functions on three levels: the locality effects, site effects, and residual variations (Fig. 2, Fig. S1).
+The correlations displayed comparable patterns on each level.
+We found strong negative trade-offs between P excretion and N excretion as well as P excretion and biomass production.
+Further, we found slightly weaker negative correlations between piscivory and N excretion as well as piscivory and herbivory.
+Thus, a reef fish community does not simultaneously display high values of functioning across all investigated functions.
 
-To explore what drives the residual variation and trade-offs of functions beyond the effects of biomass and sst, we conducted a multivariate Bayesian mixed effect model by adding ten variables that describe the community structure: species richness and the median, lower, and upper 95% quantiles of size, immaturity, and trophic level of the individuals inside a community.
-We found that the community structure drives the observed trade-offs (Fig.
-3; table x).
+To explore what drives the variation and trade-offs of functions beyond the effects of biomass and SST, we ran a multivariate Bayesian mixed effects model by adding ten variables that describe the structure of each fish assemblage: species richness and the median, lower, and upper 95% quantiles of size, immaturity, and trophic level of individuals inside a community.
+Each of these components have non-zero effects on at least one of the five functions, suggesting that the observed trade-offs may be, at least in part, rooted in the structure of the focal community (Fig.
+3; Table S4).
 
-We then questioned if functions tend to be driven by specific species across sites.
-We quantified the degree of dominance inside each community on the site-level and found that functions are on average charachterized by a high level of dominance, i.e.
-in most communities, a small proportion of species perform most of a function (Fig.
+Beyond community structure, we examined whether functions are driven by specific species across sites.
+We quantified the degree of dominance inside each community at the site-level and found that, on average, functions are dominated by a small fraction of the species in each community (Fig.
 4a).
-As a comparison, we simulated random communities ranging from 5 to 50 species which yielded an average XX.
-The predicted average of the degree of dominance was x, x, x, x, and x for each function respectively.
 We also calculated the proportion of species that is dominant in at least one transect (i.e.
-species that contribute more than a community in which each species contributes equally).
-We found that most species play a dominant role, and 70\% of all species contributed disproportionally to a function in at least one community (Fig.
+species with a disproportionally high contribution as compared to a community in which all species contribute equally).
+However, we also found that at a global scale many species play a dominant role.
+In particular, 70\% of all species contributed disproportionally to a function in at least one community (Fig.
 4b).
-Finally, we investigated how often species are dominant across their range and found that very few species are dominant throughout their range (Fig.
+Yet, very few species are dominant throughout their range (Fig.
 4c).
-Together, this means that functions inside communities tend to be driven by few dominant species, but that the identity of these dominant species varies highly across communities.
+Thus, functions within communities tend to be driven by few dominant species, but the identity of those dominant species varies across sites.
 
@@
 
-By quantifying five key functions mediated by coral reef fishes, we demonstrate that ecosystem-wide functioning is mainly driven by fish biomass, yet biomass alone does not fully capture functional variability across communities.
-While biomass is one of the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], our analyses suggests that biomass alone does not sufficiently characterize functioning.
-We demonstrate strong trade-offs among the five functions, independent of biomass.
-Using biomass as a proxy for functioning can therefore mask fundamental differences in critical community-level functions.
+By quantifying five key processes mediated by coral reef fishes, we demonstrate that coral reef ecosystem functioning is shaped by biological trade-offs, local community structure, and species identity.
+Standing biomass is one of the most commonly employed indicators of coral reef functioning [@Cinner2020; @Brandl2019front], and our analyses confirm the pervasive influence of biomass on all other processes.
+Yet, our results also show non-linear relationships between functions and biomass and suggest that biomass alone does not sufficiently characterize functioning, as we found strong trade-offs among the five functions independent of biomass.
+Using biomass as a proxy might, therefore, mask fundamental differences in community-level functioning.
 Furthermore, for a given value of biomass, no reef can yield above average values across all five functions.
-While many reefs may stand out as hotspots for one function, none can maximize all functions simultaneously.
+While a reef may stand out as a hotspot for one function, no reef can maximize all functions simultaneously.
 
-Fish community structures drive the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
-For example, we observed a clear trade-off between P excretion and biomass production which is largely driven by the age and trophic community structure.
-Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet (@Allgeier2014).
-In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
-Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood2005], while communities dominated by immature fishes maximize biomass production.
+The observed trade-offs among functions are driven by fish community structure and the organismal physiology and life-history traits of its consituents [@Schiettekatte2020; @Schramski2015].
+For example, we observed a clear trade-off between P excretion and biomass production which is mostly driven by the age and trophic structure.
+Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet [@Allgeier2014].
+In contrast, biomass production is high in communities dominated by fishes that occupy low trophic levels because herbivores tend to exhibit higher growth rates [@Morais2018].
+Moreover, P is retained for skeletal growth in young fishes, thus limiting P excretion rates [@Schiettekatte2020; @Hood2005].
 Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].
 
-Our results also reveal that functions consistently hinge on a few dominant species, but the identities of local, dominant species vary strongly across sites [@Lefcheck2019].
-Locally, specific high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019].
-Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
-While few high-performing taxa indeed dominate functioning in each site, there are no species that are dominant across their entire range.
-In addition, more than half of all species contributed disproportionally to a specific function in at least one site inside their range.
-There are thus no widespread key species to target for conservation, rather, the functional role and conservation priority of species should be investigated at a local scale.
+Our results also reveal that functions consistently rely on a few dominant species, but the identities of local, dominant species strongly vary across sites [@Lefcheck2019].
+Locally, a small number of high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019], which may have led to their designation as functionally-dominant “key species” in various locations [@Bellwood2006].
+However, our results revealed that no species dominated throughout their geographical range, and more than half of all species contributed disproportionally to a specific function at a at least one site.
+Thus, there are no widespread key species to target for coral reef conservation; rather, local species dominance across functions can guide local conservation efforts, and the preservation of regional reef fish biodiversity should be prioritized in broad-scale policy.
 
 Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
-Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have effects on ecosystem functioning.
-Intensive fishing and associated reductions in biomass of large fishes alters the size, age, and trophic structure of fish communities [@Graham2017].
-When accounting for the effect of biomass, these community shifts can enhance nitrogen excretion and production [e.g.
-@Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
-Futher, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
-Simultaneously, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth in comparison with corals [@Burkepile2013].
+Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017], and we suggest that these changes will differentially affect ecosystem functioning.
+Intensive fishing and associated reductions in the biomass of large fishes, for example, alters the size, age, and trophic structure of fish communities [@Graham2017].
+When accounting for the effect of biomass, these community shifts can enhance N excretion and production [e.g. @Morais2020glob], but they will negatively impact P excretion, herbivory, and piscivory.
+Further, declines in coral cover related to climate change are often associated with shifts toward herbivores [@Graham2006].
+Herbivores generally contribute little to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth over corals [@Burkepile2013].
 
-Conserving biomass, diversity, and ecosystem functions are important objectives of most conservation initiatives [@Cinner2020].
+Sustaining biomass, diversity, and ecosystem functioning are important objectives of most conservation initiatives [@Cinner2020].
 While safeguarding fish biomass enhances functioning, the trade-offs between key functions reveal a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
-For example, the establishment of marine protected areas, which are one of the primary conservation tactics for coral reefs [@Graham2020], may protect herbivorous species and thus provide benefits for herbivory.
+For example, the establishment of marine protected areas, which are one of the primary conservation stratigies for coral reefs [@Graham2020], may protect herbivorous species.
 However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards herbivore domination may result in the decline of P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
-It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
-process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy [@Brandl2019front].
-To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
-Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure.
+It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions.
+Yet, our comprehension of process-based functioning or the definition a “functional” coral reef is still poorly understood [@Brandl2019front].
+Establishing functional baselines for global coral reefs is a critical challenge for future studies.
+Until then, our results suggest that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species and vulnerable consituents of the community (e.g.
+large carnivores), and promoting regional biodiversity.
 
-Overall, using coral reef fishes, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning.
-Management strategies that call for the enhancement of coral reef functioning via an economic mindset (i.e.
+We demonstrate that the variability in processes that govern the elemental cycling in complex ecosystems such as tropical coral reefs represents an unrecognized challenge for protecting ecosystem functioning.
+Management strategies that call for the enhancement of ecosystem functioning via an economic mindset (i.e.
 where higher functioning is better) are not feasible.
-Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to variable, local trade-offs, drivers, and anthropogenic threats.
+Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to local trade-offs, drivers, and anthropogenic threats.
 
@@
 We thank the staff at CRIOBE, Moorea for field support.
-We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Sophie Schiettekatte for proof-reading the manuscript, and Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analyis.
+We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analysis, and Sophie Schiettekatte for proof-reading the manuscript.
+.
 This research was funded by the BNP Paribas Foundation (Reef Services Project) and the French National Agency for Scientific Research (ANR; REEFLUX Project; ANR‐17‐CE32‐0006).
@@
 **Data and materials availability:**
-All data and code to reproduce figures are available online through GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9).
-All data on individual fish traits are available from the corresponding author on reasonable request.
+All data and code to reproduce the figures are available on GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9).
+All data on individual empirical measurements are available from the corresponding author upon request.
 
@@
 Fig.
-1: Maps of five key ecosystem functions and multifunction, and their relationships with biomass.
-Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = lower 25\%, grey = 25-75\%, color = >75\%).
-Black circular outlines highlight the five localities with the highest values of each function.
-Multifunction represents the weighted average of the five standardized functions.
-Right: The predicted values for functions and multifunction with increasing biomass.
-The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.
+1: Maps of the five key ecosystem functions, multifunctionality, and the relationships between the functions and biomass.
+Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = < 25\%, grey = 25-75\%, color = >75\%).
+Black outlines highlight the five localities with the highest values of each function.
+Multifunctionality represents the weighted average of the five standardized functions.
+Right: The predicted values for functions and multifunctionality with increasing biomass.
+The lines represent the average modeled relationship and the shaded areas show the 95\% credible intervals of the predictions.
 
 Fig.
-2: Correlations among five functions while accounting for biomass and sea surface temperature.
+2: Correlations of the five functions, accounting for biomass and sea surface temperature.
 a: Modeled correlation coefficients of residual errors.
 Dots represent the average and lines represent the 95%CI.
-b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.
+b-k: Scatter plots of the mean residual errors of the functions.
 
@@
 3.
-Effects of ecological community variables on five functions.
-Dots indicate fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes.
-To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables.
+Effects of ecological community variables on the five functions.
+Dots indicate fixed effect values from Bayesian linear regressions that examine the effects of species richness, trophic level, size, and immaturity of fishes.
+To represent both the median and spread of trophic level, size, and immaturity across individuals within a community, we included lower and upper 95% quantile values of these three traits as community variables.
 All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data).
 Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.
-Immaturity is defined as the derivative of the Von Bertalanffy growth model for a given size, and the higher this value, the younger the individual.
+Immaturity is defined as the derivative of the von Bertalanffy growth model for a given size; thus, the higher this value, the younger the individual.
 
 Fig.
-4: Local dominance in species contributions for five ecosystem functions on coral reefs.
-a: The degree of dominance of communities for each function on the site-level.
-Colored dots represent the raw values and the black dots and lines display the mean and 95\% credible intervals of the average degree of dominance, respectively.
-Degrees of dominance range between zero (all species contribute equally) and one (a single species is the sole contributor to a given function).
-The vertical dashed line shows the average of the degree of dominance of 1,000 randomly simulated communities.
-b: Bar plot showing the proportion of species that are dominant in at least one site relative to the total number of species.
-In the case of herbivory and piscivory, the total number of herbivores and piscivores, respectively, is used.
+4: Local dominance in species contributions to five ecosystem functions on coral reefs.
+a: The degree of dominance for each function at the site level.
+The degree of dominance of a community ranges between zero (all species contribute equally to the function) and one (a single species is the sole contributor to a given function).
+Colored dots represent the raw values, and the black dots and lines display the mean and 95\% credible intervals of degree of dominance among all sites.
+In some cases, the credible interval was too small to be visible.
+The vertical dashed line shows the average degree of dominance of 1,000 randomly simulated communities.
+b: Bar plot of the proportion of species that are dominant in at least one site relative to the total number of species, or, for herbivory and piscivory, the total number of herbivores and piscivores, respectively.
 c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present).
@@
 5.
-Vulnerability of five critical functions to fishing and climate change-induced coral loss.
-Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.
+Vulnerability of the five functions to fishing and climate change-induced coral loss.
+Conceptual scheme of the potential ways in which fishing and climate change can affect functions through their known effects on biomass and community structure.

### 2021-10-05 text/methods.Rmd
updates comments Vale, Jordan, Simon, Seb, Diego before resubmission

--- 2021-09-09 text/methods.Rmd
@@
 \noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019].
-This database encompasses 9118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic.
+This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans.
 Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019].
-The database only includes transects at the outer reef slope and with a hard reef bottom.
+The database only includes transects on the outer reef slope and with a hard reef bottom.
 Transects were carried out at a constant depth, parallel to the reef crest.
-We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm to minimize the bias related to the identification of small individuals, and rare species for which less than 20 individuals were ever recorded across all transects.
-The dataset then included 1110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
-Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration of the USA (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).
-Further, for each transect, we calculated the species richness and estimated the total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2013].
-All data wrangling and analyses were performed in the software program R (version 4.0.2; R core team 2020).
+We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm (to minimize the bias related to the identification of small individuals), and rare species for which less than 20 individuals were recorded across all transects.
+The dataset then included 1,110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html).
+Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014].
+All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).
 
 ## 2. Quantification of functions
-\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN/day/m^2^), phosphorus excretion rate (gP/day/m^2^), production of biomass through growth (gC/day/m^2^), herbivory, i.e.
-ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e.
-ingestion rate of fishes (g/day/m^2^) [@Brandl2019front].
+\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN m^-2^ day^-1^), phosphorus excretion rate (gP m^-2^ day^-1^), production of biomass through growth (gC m^-2^ day^-1^), herbivory, (i.e.
+ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e.
+ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front].
 These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g.
-daily C intake rates, N and P excretion rates, growth rates) [@Schiettekatte2020].
+daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020].
 This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
-We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods).
-We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each function in each transect.
-Finally, we summarized functions on the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area.
-Each function is thus expressed as dry mass (of C, N, or P) per day per square meter.
+We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods).
+We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to obtain the contribution of each individual to each function in each transect.
+Finally, we summarized functions at the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area.
+Each function is thus E_{textrm{P}}ressed as dry mass (of C, N, or P) per day per square meter.
 We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020.
-To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].
-Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Fig.
+To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al.
+(2020) [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on E_{textrm{P}}ert opinion [@Mouillot2014; @Parravicini2020] (Fig.
 S5).
-Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.
+Both the herbivory and piscivory rates match the E_{textrm{P}}ert opinion trophic guild classifications.
 Finally, we estimated multifunction, i.e.
-one measure that combines all five functions by taking the geometric average of the five functions ( nomalized to range between zero and 100).
-We used the geometric mean because functions are dependent on each other and may vary considerably.
+one measure that combines all five functions by taking the geometric average of the five functions (normalized to a range between zero and 100).
+We used the geometric mean because functions are dependent on each other and vary by several orders of magnitude.
 
 ## 3. Community structure variables
-We quantified a set of variables that characterize the fish community structure.
+We quantified a set of variables that characterize fish community structure.
 These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
-Specifically, we calculated the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
-The total length is based on the visual estimation by divers.
+Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
+The total length is based on visual estimations by divers.
 The immaturity is quantified using the following formula:
@@
 Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual.
-Finally, the trophic level was extracted from fishbase [@Froese2018].
+Finally, trophic level was extracted from Fishbase [@Froese2018].
 
@@
 
-We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level, (2) investigate the effects of bioimass and sst, and the correlations among functions independent of biomass and sst, and (3) estimate the effects of the community structure on each function.
-For each model, functions were log-transformed to ensure the normal distribution of residuals and to allow the allometric relationship with biomass, hypothesized by metabolic theory [@Brown2004].\par
+We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function.
+For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004].\par
 
-In the underwater visual transect database, 291 transects (3%) did not contained herbivores and 4467 transects (49%) did not contain piscivores yielding false zeros for herbivory and piscivory, respectively.
-We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores.
-In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all.
-To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by adding these observations as parameters in the multivariate models.
+In the underwater visual transect database, 291 transects (3%) did not contain herbivores and 4467 transects (49%) did not contain piscivores yielding zeros for herbivory and piscivory, respectively.
+We considered that these absence of herbivores or piscivores are likely an underestimation of their actual abundance at the surveyed reef site, as all reefs typically host a few herbivores and piscivores (i.e.
+they are likely false-zeros).
+To avoid removing all transects with missing values for herbivory or piscivory (n = 4,620) from our database when running multivariate analyses, we imputed these zeros as missing values, and they were eventually set as parameters in the multivariate models.
 \par
@@
 
-$$\begin{bmatrix}y_{ExN,i} \\ y_{ExP,i} \\ y_{Prod,i} \\ y_{Herb,i} \\ y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+$$\begin{bmatrix}y_{E_{textrm{N}},i} \\ y_{E_{textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{textrm{N}},i} \\ \mu_{E_{textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
 
 $$
-\mu_{\textrm{ExN,i}}  = (\beta0_{ExN}  +  \delta_{ExN, loc}  +  \delta_{ExN, site}) \\
-\mu_{\textrm{ExP,i}}  = (\beta0_{ExP}  +  \delta_{ExP, loc}  +  \delta_{ExP, site})  \\
-\mu_{\textrm{Prod,i}} = (\beta0_{Prod} +  \delta_{Prod, loc} +  \delta_{Prod, site}) \\
-\mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) \\
-\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) ,
+\begin{array}{c} \mu_{\textrm{E_{textrm{N}},i}}  = (\beta0_{E_{textrm{N}}}  +  \delta_{E_{textrm{N}}, loc}  +  \delta_{E_{textrm{N}}, site}) \\
+\mu_{\textrm{E_{textrm{P}},i}}  = (\beta0_{E_{textrm{P}}}  +  \delta_{E_{textrm{P}}, loc}  +  \delta_{E_{textrm{P}}, site})  \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) , \end{array}
 $$
@@
 S = \begin{bmatrix}
-\sigma_{ExN} & 0 & 0 & 0 & 0\\
-0 & \sigma_{ExP} & 0 & 0 & 0 \\
-0 & 0 & \sigma_{Prod,i} & 0 & 0\\
-0 & 0 & 0 & \sigma_{Herb} & 0\\
-0 & 0 & 0 & 0 & \sigma_{Pisc}
+\sigma_{E_{textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
 \end{bmatrix}
@@
 \begin{bmatrix}
-\sigma_{ExN} & 0 & 0 & 0 & 0\\
-0 & \sigma_{ExP} & 0 & 0 & 0 \\
-0 & 0 & \sigma_{Prod,i} & 0 & 0\\
-0 & 0 & 0 & \sigma_{Herb} & 0\\
-0 & 0 & 0 & 0 & \sigma_{Pisc}
+\sigma_{E_{textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
 \end{bmatrix},
@@
 
-where i is the index of the transect, y_{ExN,i} is the N excretion rate of transect i, y_{ExP,i} is the P excretion rate, y_{Prod,i} is the biomass production rate, y_{Herb,i} is the herbivory rate, y_{ExN,i} is the piscivory rate, \sigma represents the residual error of each function (ExN, ExP, Prod, Herb, and Pisc), R is the correlation matrix of the residuals.
+where $i$ is the index of the transect, $y_{E_{textrm{N}},i}$ is the N excretion rate of transect i, $y_{E_{textrm{P}},i}$ is the P excretion rate, $y_{B,i}$ is the biomass production rate, $y_{H,i}$ is the herbivory rate, $y_{E_{textrm{N}},i}$ is the piscivory rate, $\sigma$ represents the residual error of each function ($E_{textrm{N}}$, $E_{textrm{P}}$, $B$, $H$, and $P$), R is the correlation matrix of the residuals.
 Locality- and site-level effects are also structured including covariation among functions.
-There are thus three correlation matrices in total, or in other words the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality-level, site-level, and transect-level.
+There are thus three correlation matrices in total, meaning that the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality, site, and transect.
 
-\noindent We used non-centered parametrisation for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
-We used a lkj_corr prior for each of the three correlation matrices ($R \sim lkj\_corr(1)$).
+\noindent We used non-centered parameterization for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+We used a prior (lkj_{corr}) for each of the three correlation matrices ($R \sim lkj\_corr(1)$).
 
-Second, we ran a mixed-effect model to simultaneously investigate the effects of biomass and sst on all functions and the correlations among functions (independent of biomass and sst).
-The standing stock biomass of communities is inevitably positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
-Further, because of the known relationship between temperature and parameters related to growth and respiration (see suppl.
-methods), functions are expected to be affected by temperature.
+Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
+The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature.
 We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
 
-$$\begin{bmatrix}y_{ExN,i} \\ y_{ExP,i} \\ y_{Prod,i} \\ y_{Herb,i} \\ y_{Pisc,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{ExN,i} \\ \mu_{ExP,i} \\ \mu_{Prod,i} \\ \mu_{Herb,i} \\ \mu_{Pisc,i}\end{bmatrix}, S \right),$$
+$$\begin{bmatrix}y_{E_{textrm{N}},i} \\ y_{E_{textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{textrm{N}},i} \\ \mu_{E_{textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
 
-$$S = \begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\
-0 & \sigma_{ExP} & 0 & 0 & 0 \\
-0 & 0 & \sigma_{Prod,i} & 0 & 0\\
-0 & 0 & 0 & \sigma_{Herb} & 0\\
-0 & 0 & 0 & 0 & \sigma_{Pisc} \end{bmatrix}
+$$S = \begin{bmatrix}\sigma_{E_{textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}
 R
-\begin{bmatrix}\sigma_{ExN} & 0 & 0 & 0 & 0\\
-0 & \sigma_{ExP} & 0 & 0 & 0 \\
-0 & 0 & \sigma_{Prod,i} & 0 & 0\\
-0 & 0 & 0 & \sigma_{Herb} & 0\\
-0 & 0 & 0 & 0 & \sigma_{Pisc} \end{bmatrix}$$
+\begin{bmatrix}\sigma_{E_{textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}$$
 
-$$\mu_{\textrm{ExN,i}} = (\beta0_{ExN} +  \delta_{ExN, loc} +  \delta_{ExN, site}) +{\beta1_{ExN}} {x_{log(biomass),i}} + {\beta2_{ExN}} {x_{sst,i}} \\
-\mu_{\textrm{ExP,i}} = (\beta0_{ExP} +  \delta_{ExP, loc} +  \delta_{ExP, site}) +{\beta1_{ExP}} {x_{log(biomass),i}} + {\beta2_{ExP}} {x_{sst,i}} \\
-\mu_{\textrm{Prod,i}} = (\beta0_{Prod} +  \delta_{Prod, loc} +  \delta_{Prod, site}) +{\beta1_{Prod}} {x_{log(biomass),i}} + {\beta2_{Prod}} {x_{sst,i}} \\
-\mu_{\textrm{Herb,i}} = (\beta0_{Herb} +  \delta_{Herb, loc} +  \delta_{Herb, site}) +{\beta1_{Herb}} {x_{log(biomass),i}} + {\beta2_{Herb}} {x_{sst,i}} \\
-\mu_{\textrm{Pisc,i}} = (\beta0_{Pisc} +  \delta_{Pisc, loc} +  \delta_{Pisc, site}) +{\beta1_{Pisc}} {x_{log(biomass),i}} + {\beta2_{Pisc}} {x_{sst,i}}
+$$\begin{array}{c} \mu_{\textrm{E_{textrm{N}},i}} = (\beta0_{E_{textrm{N}}} +  \delta_{E_{textrm{N}}, loc} +  \delta_{E_{textrm{N}}, site}) +{\beta1_{E_{textrm{N}}}} {{log(biomass),i}} + {\beta2_{E_{textrm{N}}}} {{SST,i}} \\
+\mu_{\textrm{E_{textrm{P}},i}} = (\beta0_{E_{textrm{P}}} +  \delta_{E_{textrm{P}}, loc} +  \delta_{E_{textrm{P}}, site}) +{\beta1_{E_{textrm{P}}}} {{log(biomass),i}} + {\beta2_{E_{textrm{P}}}} {{SST,i}} \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) +{\beta1_{B}} {{log(biomass),i}} + {\beta2_{B}} {{SST,i}} \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) +{\beta1_{H}} {{log(biomass),i}} + {\beta2_{H}} {{SST,i}} \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) +{\beta1_{P}} {{log(biomass),i}} + {\beta2_{P}} {{SST,i}} \end{array}
 $$
 
-where $\beta1_{ExN}, \beta1_{ExP}, \beta1_{Prod}, \beta1_{Herb}, \beta1_{Pisc}$ are the fixed effects of the log-transformed biomass, and $\beta2_{ExN}, \beta2_{ExP}, \beta2_{Prod}, \beta2_{Herb}, \beta2_{Pisc}$ are the fixed effects of sst.
-Locality- and site-level effects are now thus structured including covariation among functions, independent of biomassand sst.
-Similarly, the residual variation of functions incorporates the correlations between functions, without the effect of biomass and sst.
-We used similar priors as describved above, and we used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
+where $\beta1_{E_{textrm{N}}}, \beta1_{E_{textrm{P}}}, \beta1_{B}, \beta1_{H}, \beta1_{P}$ are the fixed effects of the log-transformed biomass, and $\beta2_{E_{textrm{N}}}, \beta2_{E_{textrm{P}}}, \beta2_{B}, \beta2_{H}, \beta2_{P}$ are the fixed effects of SST.
+Locality- and site-level effects are thus structured including covariation among functions, independent of biomassand SST.
+Similarly, the residual variation of functions incorporates the correlations between functions, without the effect of biomass and SST.
+We used similar priors as described above, and we used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
 
-\noindent Finally, to investigate the effect of the community structure while still accounting for the effects of standing biomass and sst, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
+\noindent Finally, to investigate the effect of community structure while still accounting for the effects of standing biomass and SST, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
 
-$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} x_{log(biomass),i} + \beta2_{function} x_{sst,i}  + \beta3_{function} x_{richness,i}  + \beta4_{function} x_{size_m,i}  + \beta5_{function} x_{size_{2.5\%},i} +  \beta6_{function} x_{size_{97.5\%},i} + \\ \beta7_{function} x_{troph_m,i}  + \beta8_{function} x_{troph_{2.5\%},i} +  \beta9_{function} x_{troph_{97.5\%},i} + \beta10_{function} x_{imm_m,i}  + \beta11_{function} x_{imm_{2.5\%},i} +  \beta12_{function} x_{imm_{97.5\%},i} $$
+$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} {log(biomass),i} + \beta2_{function} {SST,i}  + \beta3_{function} {richness,i}  + \beta4_{function} {size_m,i}  + \beta5_{function} {size_{2.5\%},i} +  \beta6_{function} {size_{97.5\%},i} + \\
+\beta7_{function} {troph_m,i}  + \beta8_{function} {troph_{2.5\%},i} +  \beta9_{function} {troph_{97.5\%},i} + \beta10_{function} {imm_m,i}  + \beta11_{function} {imm_{2.5\%},i} +  \beta12_{function} {imm_{97.5\%},i} \end{array}$$
 
-where richness is the species richness, $size$ is the total length, $troph$ is the trophic level, $imm$ is the immaturity, and $m$, $2.5\%$, and $97.5\%$ respectively represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community.
+where $richness$ is the species richness, $size$ is the total length, $troph$ is the trophic level, $imm$ is the immaturity, and $m$, $2.5\%$, and $97.5\%$ represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community, respectively.
 For these models, we used weakly informative priors for the fixed effect parameters ($\beta3-\beta12 \sim normal(0,1)$) and the same priors as described above for other parameters. par
 
-All Bayesian models were fitted using the R package *brms* [@Burkner2017] which uses Stan, a C++ package for performing full Bayesian inference [@Carpenter2017].
-The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up, meaning that a total of 4,000 samples were used to estimate posterior distributions.
-The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig Sx).
+All Bayesian models were fitted using the R package *brms* [@Burkner2017], which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017].
+The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up.
+Thus, a total of 4,000 draws were used to estimate posterior distributions.
+The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig S2).
 
 ## 5. Species dominance and contributions to functions
-We quantified the relative contribution of each species to each function for all sites as followed:
+We quantified the relative contribution of each species to each function for all sites as follows:
 <!-- \begin{equation} -->
@@
 Then, we quantified the degree of species dominance per function for each site.
-We did this by first ranking species according to their contribution to function, followed by quantifying the cumulative contributions of species to functions.
-Then, we used the area under the species accumulation curve as a measure for the degree of dominance.
-Specifically, the degree of dominance (DD) was calculated as followed:
+We first ranked species according to their contribution to function, then we quantified the cumulative contributions of species to functions.
+Finally, we used the area under the species accumulation curve as a measure for the degree of dominance.
+Specifically, the degree of dominance (DD) for a function performed by R species was calculated as follows:
+
 <!-- \begin{equation} -->
@@
 <!-- \end{equation} -->
-where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, $A_max$ is the theoretical area under the curve where one species performs the entire function.
+where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, and $A_max$ is the theoretical area under the curve where one species performs the entire function.
 They are quantified as:
@@
 
-where $C_i$ is the contribution of a certain species and R is the number of species contributing to a certain function.
+where $C_i$ is the contribution of a certain species and R R equals the species richness in the case of N excretion, P excretion, and production.
+For herbivory and piscivory, R represents the number of herbivores and piscivores, respectively.
 The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that a single species performs the entire function.
-In the case of N excretion, P excretion, and production, R equals the species richness, while for herbivory and piscivory R represents the number of herbivores and piscivores, respectively.
 
-Finally, we quantified the frequency of dominance per species, i.e.
-the number of sites in which a species is dominant for a given function divided by the total number of sites in which that species is observed.
-A species is considered dominant for a certain function in a given site if their contribution is higher than 1/R, i.e.
-they contribute more than the situation in which each species contributes equally to a certain function.
+Finally, we quantified the frequency of dominance per species (i.e.
+the number of sites in which a species is dominant for a given function divided by the total number of sites in which that species is observed).
+A species is considered dominant for a certain function in a given site if their contribution is higher than 1/R (i.e.
+they contribute more than the situation in which each species contributes equally to a certain function).
 

### 2021-10-05 text/suppl_methods.Rmd
updates comments Vale, Jordan, Simon, Seb, Diego before resubmission

@@
 
-We used individual-based bioenergetic models to estimate key fish-mediated functions in global coral reefs.
-We first assembled a global species list based on an openly accessible database of reef fish abundances and sizes collected during belt transects by divers [@Barneche2019].
-We used a subset of available data (see methods) and included 1110 species that belong to 25 families: Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae.
-To apply bioenergetic models and estimate fluxes of carbon (C), nitrogen (N), and phosphorus (P) for all species in the underwater visual census database across their entire temperature range, a number of parameters are required [Table 1; @Schiettekatte2020].
-Here, we describe how these parameters were quantified for all 1110 species through a combination of literature, empirical measures, and Bayesian models.
+We first assembled a global species list based on an openly accessible database of reef fish abundances and sizes; all data were collected via belt transects on SCUBA [@Barneche2019] .
+We then used individual-based bioenergetic models to estimate key fish-mediated functions in each transect.
+We used a subset of data (see methods) and included 1,110 species that belong to 25 families: Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae.
+To apply bioenergetic models and estimate fluxes of carbon (C), nitrogen (N), and phosphorus (P) for all species in the database across their entire temperature range, a number of parameters are required [Table 1; @Schiettekatte2020] .
+Here, we describe how these parameters were quantified for all 1,110 species through a combination of primary literature, empirical measures, and Bayesian models.
 
-All protocols related to the capture and handling of fish complied to the ethical standards of CRIOBE and EPHE, and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019).
-Extraction and transport of samples were approved by the government of French Polynesia.
-All analyzes were carried out in R v.3.6.3 and Bayesian modes were run using Stan [@Carpenter2017] and the R package brms [@Burkner2017].
+All protocols related to the capture and handling of fish complied to the ethical standards of the Centre for Island Research and Environmental Observatory (CRIOBE), and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019).
+Collection and transport of samples were approved by the government of French Polynesia.
+All analyses were carried out in R v.3.6.3, and Bayesian models were run using Stan [@Carpenter2017] and the R package *brms* [@Burkner2017] .
 
-Table 1. Overview of model input parameters, adopted from Schiettekatte et al. (2020). VBGC = von Bertalanffy growth curve.
+Table 1. Overview of input parameters required by *fishflux*, detailed in Schiettekatte et al. (2020) [@Schiettekatte2020] . VBGC = von Bertalanffy growth curve.
 
@@
 
-The bioenergetic model uses the Von Bertalanffy growth function to estimate daily growth [@Schiettekatte2020].
+The bioenergetic model uses the von Bertalanffy growth function to estimate daily growth [@Schiettekatte2020] .
 This growth function relies on three parameters: $l_{\infty}$ (i.e.
 the population asymptotic body length of a fish), $\kappa$ (i.e.
-the rate at which fish in a population, on average, approaches its population asymptotic body size), and $t_0$ (i.e.
+the rate at which a fish in a population, on average, approaches its population asymptotic body size), and $t_0$ (i.e.
 the theoretical age at which length is zero).
-For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e., $k_{max}$, @Morais2018].
-For simplicity, we kept $t0$ constant at 0 for all species.
+For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were equal to its maximum length [i.e., $k_{max}$, @Morais2018] .
+For simplicity, we kept $t_0$ constant at 0 for all species.
 
@@
 Then, we extracted the available data for $k_{max}$ from Morais & Bellwood (2018), which are estimated using growth curve parameters from Fishbase, standardized to the maximum length [@Morais2018].
-We selected the species of our species list and only included the $k_{max}$ estimates coming from otolith studies.
+We selected the species that occured in our species list and only included the $k_{max}$ estimates from otolith studies.
 In total, this selection process resulted in 439 observations of $k_{max}$ for varying species and temperatures. \par
 
-Further, we used an openly accessible otolith dataset, including measurements of fishes from five French Polynesian islands [@Morat2020].
+Further, we used an openly accessible otolith dataset, gathering 669 individuals belonging to 44 species, sampled around five French Polynesian islands [@Morat2020] .
 This dataset includes total length measurements to the nearest millimeter and fish weights to the nearest 0.1 grams.
 Further, it includes distances between annual growth increments, measured by two independent researchers to prevent biases induced by a single observer.
-These data can be used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the Von Bertalanffy growth curve [@Morat2020].
+These data were used to estimate growth rate parameters using a two-step approach: back-calculation to achieve individual-level size-at-age data and hierarchical regression to fit the von Bertalanffy growth curve [@Morat2020] .
 \par
@@
 Specifically, we used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish lengths at previous ages.
-We adapted the traditional model to also estimate the uncertainty around the obtained length estimates and allow for the inclusion of missing values using a Bayesian approach (see R package fishgrowbot).
-Then, we fitted the Von Bertalanffy growth model to all species at each location for which there were at least 3 individuals, using Bayesian hierarchical regression models.
-Both steps of this procedure were carried out using the developed R package 'fishgrowbot'.
+We adapted the traditional model to also estimate the uncertainty around the obtained length estimates and allow for the inclusion of missing values using a Bayesian approach.
+Then, we fitted the von Bertalanffy growth model to all species at each location for which there were at least 3 individuals, using Bayesian hierarchical regression models.
+Both steps of this procedure were carried out using the developed R package *fishgrowbot*.
 The package also automatically estimates the parameter $k_{max}$.
@@
 
-After combining the two data sources, we obtained 496 estimates of $k_{max}$ for 181 species across varying temperatures.
+After combining the two datasets, we obtained 496 estimates of $k_{max}$ for 181 species across varying temperatures.
 
@@
 
-Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018].
-We therefore aimed to predict $k_{max}$ based on body size, temperature, and phylogeny by using a phylogenetic regression model.
+Aside from phylogeny, $k_{max}$ is mostly determined by body size and temperature [@Morais2018] .
+We therefore fitted a Bayesian phylogenetic regression to predict $k_{max}$ based on body size, temperature, and phylogeny.
 \par
 
-We extracted the phylogenetic position of all species included through the Fish Tree of Life [@Rabosky2018].
-We retrieved 100 synthetic stochastically resolved phylogenies where missing taxa were placed according to the highest level of taxonomy using the function `fishtree_complete_phylogeny()` in the R package fishtree [@Chang2019].
-For each tree, we then calculated the correlation matrix and averaged each element across the 100 matrices to get one correlation matrix that could be used in the regression model.
+We extracted the phylogenetic position of all species included through the Fish Tree of Life [@Rabosky2018] .
+We retrieved 100 synthetic stochastically resolved phylogenies where missing taxa were placed according to the highest level of taxonomic resolution using the function *fishtree_complete_phylogeny()* in the R package *fishtree* [@Chang2019] .
+For each tree, we then calculated the correlation matrix and averaged each element across 100 matrices to obtain one correlation matrix for the regression model.
 \par
 
-We then fitted the Bayesian phylogenetic regression to predict the growth rate parameter of fishes depending on body size, temperature, and phylogeny using the R package brms [@Burkner2017]:
+We then fitted the Bayesian phylogenetic regression to predict the growth rate parameter of fishes depending on body size, temperature, and phylogeny using the R package *brms* [@Burkner2017] :
 <!-- \begin{equation} -->
@@
 <!-- \end{equation} -->
-where $\textrm{ln}k_{max}$ represents the natural log-transformed $k_{max}$ value, $\mu$ is the predicted average, and $\sigma$ is the standard deviation, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the random-effect coefficient that accounts for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature.
-We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. \par
+where $\textrm{ln}k_{max}$ represents the natural log-transformed $k_{max}$ value, $\mu$ is the predicted average, $\sigma$ is the standard deviation, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the random-effect coefficient that accounts for the residual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, and $\beta_\textrm{2}$ is the slope for SST.
+We used uninformative priors and ran the model for 2,000 iterations with a warm-up of 1,000 iteration for 4 chains. \par
 
-The model fit confirmed a negative relationship of $\textrm{ln}k_{max}$ with maximum body size ($\beta_\textrm{1}$ = -0.76, 95\%CI: -0.96,-0.57 ), and a positive relationship with sea surface temperature ($\beta_\textrm{2}$ = 0.02, 95\%CI: 0.00,0.05 ).
+The model fit confirmed a negative relationship of $\textrm{ln}k_{max}$ with maximum body size ($\beta_\textrm{1}$ = -0.76, 95\%CI: -0.96;-0.57 ), and a positive relationship with sea surface temperature ($\beta_\textrm{2}$ = 0.02, 95\%CI: 0.00;0.05 ).
 We verified model convergence and fit by checking the posterior predictive plot, inspecting parameter trace plots, and checking the R statistic.
-The Bayesian R2 of the model was 0.738 (95\%CI: 0.702,0.769).
+The Bayesian R2 of the model was 0.738 (95\%CI: 0.702;0.769).
 \par
 
-The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects attributable to the phylogeny (i.e., $\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
-This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).
+The phylogenetic heritability (equivalent to Pagel’s$\lambda$) was estimated as the proportion of total variance, conditioned on the effects attributable to the phylogeny (i.e., $\lambda = \frac{{\textrm{sd}(\gamma_{\textrm{0phy}})}^2} {{\textrm{sd}(\gamma_\textrm{0phy})}^2 + \epsilon^2}$).
+This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70;0.77).
 This means that most of the variation, independent of the effect of body size and SST, is explained by phylogeny.
 
-\noindent We extrapolated $k_{max}$ for all species across the full SST range in which those species occur in the database, with SST rounded to the °C, which results in 4712 unique SST and species combinations.
+\noindent We extrapolated $k_{max}$ for all species across the full SST range for species that occur in the database, with SST rounded to the degree (°C), which results in 4,712 unique SST and species combinations.
 There is currently no streamlined method to make predictions for new species from a phylogenetic regression model.
-We circumvented the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model.
-We subsequently predicted these phylogenetic effects for missing species with the help of the function phyEstimate in the picante package for R [@Kembel2010].
-This function uses phylogenetic ancestral state estimation to infer trait values for new species on a phylogenetic tree by rerooting the tree to the parent edge for the node to be predicted [@Kembel2012].
-We repeated this for all 100 trees and 1000 draws.
-Per draw, we averaged the extrapolated values per species for the hundred trees.
+We circumvented this issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$, for each species included in the model.
+We subsequently predicted these phylogenetic effects for missing species with the help of the function *phyEstimate* in the R package *picante* [@Kembel2010] .
+This function uses phylogenetic ancestral state estimation to infer continuous trait values for new species on a phylogenetic tree by rerooting the tree to the parent edge for the node to be predicted [@Kembel2012] .
+We repeated this for all 100 trees and 1,000 draws.
+For each draw, we averaged the extrapolated values per species for the 100 trees.
 Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa_{max}$ for each species.
-We only use one chain in order to keep computational time reasonable.
+We only used one chain in order to keep computational time within reason.
 Finally, we summarized all $\kappa_{max}$ predictions per SST per species by taking the mean and standard deviation across the 1000 draws.
@@
 ### 2.1 Data collection
-\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea [@Allgeier2021; Parravicini unpub.], the Caribbean [@Allgeier2020sci], and Palmyra (Burkepile unpub.) (table 2).
+\noindent We collected 1633 individuals of 108 species and 25 families between 2015 and 2017 in Mo'orea [@Allgeier2021] , the Caribbean [@Allgeier2020sci] , and Palmyra (Table 2).
 Their gut contents were removed and the whole body was freeze-dried and ground to powder with a Precellys homogenizer.
-Whole body elemental proportions ($Q_\textrm{k}$) were then measured in the lab using standard methods.
-Specifically, ground samples were analyzed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500), and for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974].
+Whole body elemental proportions ($Q_\textrm{k}$) were measured in the lab using standard methods.
+Specifically, ground samples were analyzed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500); samples were analyzed for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974] .
 Elemental content was calculated based on dry mass.
 
-Table 2. Overview number of species and individuals per fish family, used for body stoichiometry analysis. Per species, there was a minimal replication of 4.
+Table 2. Overview number of species and individuals per fish family used for body stoichiometry analysis. For each species, there was a minimum sample size of 4.
 
@@
 
-\noindent The CNP\% content of organisms is known to be highly conserved within taxa [@Allgeier2020sci; @Allgeier2021].
-We therefore use phylogeny to extrapolate these values.
+\noindent The CNP content of organisms is highly conserved within taxa [@Allgeier2020sci; @Allgeier2021] .
+We therefore used phylogeny to extrapolate these values to species with unknown body stoichiometry.
 We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.
@@
 
-\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$ respectively, $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $S$ is the covariance matrix of the residual errors of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the random-effect coefficient that account for the intercept variation, based on the relatedness as described by the phylogeny per element $k$, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the random-effect coefficient that account for the residual species-level intercept variation per element k.
+\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$, respectively, $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $S$ is the covariance matrix of the residual errors of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the random-effect coefficient that accounts for the intercept variation, based on the relatedness as described by the phylogeny per element $k$, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the random-effect coefficient that accounts for the residual species-level intercept variation per element k.
 
-\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains.
-\noindent The Bayesian R2 of the model was 0.39 (95\%CI: 0.36-0.42), 0.50 (95\%CI: 0.48-0.53), and 0.43 (95\%CI: 0.40-0.46) for C, N and P respectively.
-\noindent The phylogenetic heritability was 0.41 (95\%CI: 0.28-0.55), 0.58 (95\%CI: 0.4-0.66), and 0.57 (95\%CI: 0.46-0.69) for C, N, and P respectively.
+\noindent We used uninformative priors and ran the model for 2,000 iterations with a warm-up of 1,000 iteration using 4 chains (i.e., a total of 4,000 posterior draws).
+\noindent The Bayesian R^2^ of the model was 0.39 (95\%CI: 0.36-0.42), 0.50 (95\%CI: 0.48-0.53), and 0.43 (95\%CI: 0.40-0.46) for C, N, and P respectively.
+\noindent The phylogenetic heritability was 0.41 (95\%CI: 0.28-0.55), 0.58 (95\%CI: 0.4-0.66), and 0.57 (95\%CI: 0.46-0.69) for C, N, and P, respectively.
 
-\noindent As before, we used 1000 fitted draws for each species, and 100 phylogenetic trees to extrapolate to all species with unknown body stoichiometry.
-Specifically, we used the phylopars function from the Rphylopars package [@Bruggeman2009].
-This function uses ancestral state reconstruction and Brownian motion, and takes the correlation between C, N and P into account.
+\noindent We used 1,000 fitted draws for each species, and 100 phylogenetic trees to extrapolate to all species with unknown body stoichiometry, similar to the above methods.
+Specifically, we used the *phylopars* function from the *Rphylopars* package [@Bruggeman2009] .
+This function uses ancestral state reconstruction and Brownian motion, and takes the correlation among C, N, and P into account.
+
+Finally, we tested the phylogenetic extrapolation approach by performing a leave-one-out cross validation, similar to the methods described in section 1.2.
+The extrapolated species-level estimates were correlated with the mean species-level estimates from the full model with correlations of 0.61, 0.67, and 0.67 for C, N, and P, respectively.
 
@@
 ### 3.1 Data collection
-\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian islands.
+\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea, Tetiaroa, and Mangareva, three French Polynesian islands.
 We extracted the stomach content and stored it in a 2ml tube.
-After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder.
-Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry described above.
+After freezing the samples, we dry-froze all samples for at least 24 hours, then we ground them to powder.
+Samples were sent to the lab for CNP content analysis using similar methods as described above for the fish body stoichiometry.
 
 ### 3.2 Data analysis and extrapolation
-\noindent Using trophic guilds defined by @Parravicini2020, we fitted a multivariate Bayesian regression model to summarize CNP\% content data per trophic guild with random effects at the species level.
-This model had a median Bayesian R2 of 0.62, 0.62, and 0.48 for C, N and P respectively.
-Next, we extracted 1000 draws of the predicted CNP\% per trophic guild.
+\noindent Using trophic guilds defined by Parravicini et al.
+(2020) [@Parravicini2020] , we fitted a multivariate Bayesian regression model to summarize CNP content data per trophic guild with random effects at the species level.
+This model had a median Bayesian R^2^ of 0.62, 0.62, and 0.48 for C, N, and P, respectively.
+Next, we extracted 1,000 draws of the predicted CNP content per trophic guild.
 Parravicini et al.
-2020 [@Parravicini2020] provides the probability of reef fish species to be assigned to each of the eight defined trophic guilds(i.e.
+(2020) [@Parravicini2020] provides the probabilities of reef fish species to be assigned to each of the eight defined trophic guilds(i.e.
 sessile invertivores; herbivores, microvores, and detrivores; corallivores; piscivores; microinvertivores; macroinvertivores; crustacivores; planktivores).
-By combining these probabilities with the predicted diet contents per trophic guild, we finally estimated the diet CNP\% for each species in our database.
+By combining these probabilities with the predicted CNP contents per trophic guild, we finally estimated the diet CNP content for each species in our database.
 Essentially, we performed a weighted average of CNP content across diet groups for each species, where the weights represent the probability of being in a certain trophic guild.
-We then took the average and standard deviation across all 1000 draws.
-While we recognize the bias of using diet CNP\% estimates of a dataset in one region, we argue that variability between food categories e.g.
-animal material and primary producers is likely to be higher than regional differences within trophic categorizations.
-Further, since the used trophic guild classification includes probabilities to belong to each group, variation is included when the trophic categorization is not well known.
-For example, if a species has a 50% probability to be a herbivore and a 50% probability to be a sessile invertivore this uncertainty will be reflected the estimation of the diet CNP\%.
+We then took the average and standard deviation across all 1,000 draws.
+While we recognize the bias of using diet CNP content estimates of a dataset from a single region, we argue that variability between food categories (e.g.
+animal versus plant material) is likely higher than regional differences within trophic categorizations.
+Further, the trophic guild classification includes probabilities that belong to each group, so variation is included when the trophic categorization is not well known.
+For example, if a species has a 50\% probability of being herbivore and a 50\% probability of being a sessile invertivore, this uncertainty will be reflected in the estimation of the CNP content of the diet.
 
@@
 ### 4.1 Data collection and lab experiments
-To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we carried out intermittent-closed respirometry experiments [@Steffensen1989; @Clark2013].
-In the period between 2018 and 2019, we collected 1393 individuals of 61 species and 18 families with a minimum of 3 replicates per species in Moorea, French Polynesia.
-Fishes were captured by scuba divers using hand nets and clove oil and immediately transported to the laboratory in coolers with ambient seawater and oxygen stones.
-After an acclimatization and fasting period of 48 h in aquaria, the fishes were individually transferred to a water-filled tub at 28°C (ambient sea water temperature) and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012].
-Then, they were placed in respirometry chambers submersed in an ambient and temperature-controlled tank, where they were left for ~23 h.
+To quantify standard metabolic rate (SMR) and maximum metabolic rate (MMR), we carried out intermittent-closed respirometry experiments [@Steffensen1989; @Clark2013] .
+Between 2018 and 2019, we collected 1,393 individuals across 61 species and 18 families with a minimum sample size of 3 individuals per species in Mo'orea, French Polynesia.
+Fishes were captured on SCUBA using hand nets and clove oil and immediately transported to the laboratory in coolers with ambient seawater and oxygen stones.
+After an acclimatization and a fasting period of 48 h in aquaria, the fishes were individually transferred to a water-filled tub at 28°C (ambient sea water temperature) and manually chased by the experimenter until exhausted [@Norin2011; @Clark2012] .
+Then, they were placed in respirometry chambers submersed in an ambient and temperature-controlled tank, where they were left for  approximately 23 h.
 The intermittent respirometry cycles started immediately after a fish was placed in its respirometry chamber.
 The cycles consisted of a measurement (sealed) period followed by a flush period during which the respirometry chambers were flushed with fully aerated water from the ambient tank.
-Because fishes were exhausted right before entering the respirometry chambers, it was possible to measure the approximate MMR.
-Depending on fish size, 8 respirometry chambers ranging in volume (including tubes and pumps) from 0.4 to 4.4 L were run in parallel, and measurement and flush periods lasted between 3 to 15 min and 3 to 5 min, respectively.
-SMR was calculated as the average of the 10 \% lowest values measured during the entire period, after the removal of outliers [@Chabot2016].
+Fishes were exhausted immidiately before entering the respirometry chambers, so we measured the approximate MMR.
+Depending on fish size, 8 respirometry chambers ranging in volume from 0.4 to 4.4 L  (including tubes and pumps) were run in parallel, and measurement and flush periods lasted between 3 to 15 min and 3 to 5 min, respectively.
+SMR was calculated as the average of the 10 \% lowest values measured during the entire period, after the removal of outliers [@Chabot2016] .
 MMR was calculated from the slope of the first measurement period.
@@
 ### 4.2 Data analysis and extrapolation
-To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effect model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and metabolic rate type (SMR or MMR) on both the intercept and slopes using brms [@Burkner2017]:
+To retrieve the parameters $f_\textrm{0}$ (Metabolic normalisation constant independent of body mass; $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$), $\alpha$ (mass-scaling exponent), and $\theta$ (factorial activity scope), we fitted a normal Bayesian mixed effects model predicting the log10-transformed metabolic rate using the log10-transformed biomass including random effects of family, species, and metabolic rate type (SMR or MMR) on both the intercept and slopes using *brms* [@Burkner2017] :
 $$
@@
 We ran the model for 4000 iterations, with a warm-up of 2000 iterations, and four chains.
-Further, we used an informative prior, for the slope ($\alpha \sim normal(0.8, 0.5)$), based on previous work [@Barneche2014].
+Further, we used an informative prior, for the slope ($\alpha \sim normal(0.8, 0.5)$), based on previous work [@Barneche2014] .
 The model had a Bayesian R2 of 0.973 (95\%CI: 0.972-0.974).
 We then predicted the family-level $\alpha$ by summing the slope of the model with the effects of the family on the slope of the SMR.
-We did this for all iterations and then took the mean and standard deviation.
-In a similar way, we extracted the family-level intercept for SMR and MMR, and then quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of all iterations of the intercept (i.e., the intercept for SMR).
-Finally, we estimated $\theta$ as followed, based on the assumption that fishes rest 12h a day and they on average spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
+We did this for all iterations, then we took the mean and standard deviation.
+Similarly, we extracted the family-level intercept for SMR and MMR, then we quantified mean and standard deviation of $f_\textrm{0}$ after the back-transformation of all iterations of the intercept (i.e., the intercept for SMR).
+
+Finally, we estimated $\theta$ as follows, based on the assumption that, on average, fishes rest 12h a day and they spend the remaining 12 hours at a metabolic rate that is the average of their SMR and MMR:
 <!-- \begin{equation} -->
@@
 where all iterations of the back-transformed family-level intercepts were used for SMR and MMR. We then summarized these predictions by taking the mean and standard deviation.
-We used the family-level estimates for these parameters for all species in our database.
-We used the average across all families for families that were not represented in our respirometry dataset, (Bothidae, Chaetodontidae, Fistulariidae, Haemulidae, Kyphosidae, Lethrinidae, Lutjanidae, Mugilidae, Ostraciidae, Pempheridae, Sciaenidae, Siganidae).
-The parameter $f0$ was adjusted for each temperature in the varying locations of the underwater visual census database, following @Barneche2014:
+We used the family-level estimates of these parameters for all species in our database.
+We used the average across all families for families that were not represented in our respirometry dataset, (Bothidae, Chaetodontidae, Fistulariidae, Haemulidae, Kyphosidae, Lethrinidae, Lutjanidae, Mugilidae, Ostraciidae, Pempheridae, Sciaenidae, and Siganidae).
+
+The parameter $f0$ was adjusted for each temperature in the varying locations in the database, following @Barneche2014 :
 
 $$f0_{adjusted} = f0(T_{ref}) e^{E_r(\frac{1}{\kappa T_ref} - \frac{1}{\kappa T})},$$
-where $\kappa$ is the Boltsmann's constant ($8.62 * 10^{-5} eV K^{-1}$), $E_r$ is the activation energy (0.59 eV, extracted from @Barneche2014), $f0(T_{ref})$ is the value of the metabolic normalization at a fixed reference temperature (301.15 K = 28 + 273.15K), $T$ is the temperature of interest (K).
+where $\kappa$ is the Boltzmann's constant ($8.62 * 10^{-5} eV K^{-1}$), $E_r$ is the activation energy (0.59 eV, extracted from Barneche et al.
+(2014) @Barneche2014 ), $f0(T_{ref})$ is the value of the metabolic normalization at a fixed reference temperature (301.15 K), and $T$ is the temperature of interest (K).
 
 ## 5. Additional parameters
-We retrieved the parameters $lw_a$, $lw_b$, $h$, and $r$ from fishbase [@Froese2018].
-For the mass-specific turnover rates for N and P($F_\textrm{0Nz}$; $F_\textrm{0Pz}$), we used the estimates provided in Schiettekatte et al.
+We retrieved the parameters $lw_a$, $lw_b$, $h$, and $r$ for each species from Fishbase [@Froese2018] .
+For the mass-specific turnover rates for N and P ($F_\textrm{0Nz}$; $F_\textrm{0Pz}$), we used the estimates provided in Schiettekatte et al.
 (2020)  [@Schiettekatte2020].

### 2021-10-06 text/suppl_tables_figures.Rmd
:fish:

@@
 
-loadd(SI_fig1)
-loadd(SI_fig2)
-loadd(SI_pp_plots)
-loadd(SI_rank_plots)
+# loadd(SI_fig1)
+# loadd(SI_fig2)
+# loadd(SI_pp_plots)
+# loadd(SI_rank_plots)
 ```
@@
     fontsize(size = 10, part = "header") %>%
-    set_caption("Extended Date table 2: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
+    set_caption("Extended Date table 1: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
     autofit()
@@
 ```{r, echo = FALSE}
-  tab <- tidy(readd(mod_mvfun_com))
-test <- summary(tab)$summary %>% 
-  as.data.frame() %>%
-  tibble::rownames_to_column("name") %>%
-  tidyr::separate(name, into = c("dep", "var", "extra"), sep = "_") %>%
-  dplyr::mutate(var = paste0(var, extra)) %>%
-  table <- 
-    tidy(tab) %>%
-    mutate_if(is.numeric, round, 4) %>%
-    mutate(term = c("intercept",
-                    "sst",
-                    "log(biomass)",
-                    "richness",
-                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
-                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
-                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
-                    )) %>%
-    mutate(response = "log(N excretion)")
+ table <- readd(tab_mod_mv_siteloc)
   flextable(table) %>%
@@
     border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
-    set_caption("Extended Date table 2: Overview of parameters of the regressions relating the five functions to the community structure variables") %>%
+    set_caption("Supplementary table 2: Overview of parameters of the multivariate regression predicting the five functions with intercepts only.") %>%
+    autofit()
+```
+
+```{r, echo = FALSE}
+ table <- readd(tab_mod_mvfun_bm)
+  flextable(table) %>%
+    fontsize(size = 8) %>%
+    fontsize(size = 10, part = "header") %>%
+    merge_v(j = 1) %>% 
+    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
+    set_caption("Supplementary table 3: Overview of parameters of the multivariate regression predicting the five functions with biomass and sst.") %>%
+    autofit()
+```
+
+```{r, echo = FALSE}
+ table <- readd(tab_mod_mvfun_com)
+  flextable(table) %>%
+    fontsize(size = 8) %>%
+    fontsize(size = 10, part = "header") %>%
+    merge_v(j = 1) %>% 
+    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
+    set_caption("Supplementary table 4: Overview of parameters of the multivariate regression predicting the five functions and community variables.") %>%
     autofit()
@@
 
-![Extended Data Figure 1: a-e) Relationship between biomass and the five functions.
-Lines and shaded areas show the average and 95% credible interval of the predicted functions respectively, for a constant sea surface temperature of 26°C (the average across all sites).
-Vertical lines show the range of the estimated functions across fish communities per biomass class of 100g/m2.
-f) Fold variation of each function per biomass class of 100g/m2 across fish communities.
-g) Correlation matrix of the residuals of the five functions after regression with biomass and sea surface temperature.
-Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig1.png)
+![Extended Data Figure 1: Correlations among functions, independent of biomass and sst, on the locality and site level.](../output/plots/figSx_corplot.png)
 

### 2021-10-06 R/functions_analysis.R

@@ -319,14 +319,13 @@ get_dd <- function(contributions, herb_pisc){
   return(key)
 }
 
-get_dd_site <- function(contributions, herb_pisc){
-  
-  # combine data
+get_dd_site <- function(contributions){
   
   
-  nspec <- left_join(contributions, herb_pisc$contributions_herb_pisc) %>%
+  
+  con <- contributions %>%
     ungroup() %>% group_by(sites) %>%
-    dplyr::summarise(nspec = length(unique(species)),
+    dplyr::mutate(nspec = length(unique(species)),
                      nspec_h = length(unique(species[I_herb_p>0])),
                      nspec_p = length(unique(species[I_pisc_p>0])))
   
@@ -372,8 +371,7 @@ get_dd_site <- function(contributions, herb_pisc){
     }
   }
   
-  con <- ungroup(tfs)
-  
+
   key <- parallel::mclapply(unique(con$sites), function(x){
     
     t <- dplyr::filter(con, sites == x)
@@ -436,9 +434,12 @@ get_importance <- function(contributions, herb_pisc){
   
 }
 
-get_importance_site <- function(con){
+get_importance_site <- function(contributions, herb_pisc){
   
   # if con > 1/N !!
+  
+  con <- contributions
+  
   
   imp <- parallel::mclapply(unique(con$sites), function(x){
     sub <- filter(con, sites == x)
@@ -507,6 +508,59 @@ get_spi_vuln <- function(sp_importance, vulnerability){
            n_prop = n/n_spec_tot) %>% # proportion of species in vuln category
     mutate(perc = 100 * ep_prop/n_prop)
   
+}
+
+fit_mod_dd <- function(dd) {
+  fit1 <- brm(dd_Fn ~ 1, data = dd,
+              cores = 4,
+              backend = "cmdstanr",
+              threads = threading(10))
+  fit2 <- brm(dd_Fp ~ 1, data = dd,
+              cores = 4,
+              backend = "cmdstanr",
+              threads = threading(10))
+  fit3 <- brm(dd_Gc ~ 1, data = dd,
+              cores = 4,
+              backend = "cmdstanr",
+              threads = threading(10))
+  fit4 <- brm(dd_I_herb ~ 1, 
+              cores = 4,
+              backend = "cmdstanr",
+              threads = threading(10),
+              data = filter(dd, dd_I_herb>0))
+  fit5 <- brm(dd_I_pisc ~ 1,
+              cores = 4,
[…]

### 2021-10-06 R/functions_plots.R

@@ -28,10 +28,16 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
            r3 = normalize(r1_loc_Gc),
            r4 = normalize(r1_loc_Iherb),
            r5 = normalize(r1_loc_Ipisc)) %>%
-    rowwise() %>%
-    mutate(r_multi = geomean(r1, r2, r3, r4, r5))
-
+    ungroup()
   
+  re_loc1$r_multi <- sapply(1:98, function(i){
+    re_loc1[i,] %>%
+      select(r1, r2, r3, r4, r5) %>%
+      simplify() %>%
+      geomean()
+  })
+
+
   coords <- coords %>%
     select(- sites, -lat, -lon, -mean) %>%
     unique()
@@ -99,7 +105,9 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
                data = filter(data, r1_loc_Fn > quantile(data$r1_loc_Fn, 0.95, na.rm = TRUE))) +
     scale_color_manual(values = pal, name = "") +
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
-    geom_text(aes(x = -175, y = 30, label = "N excretion (g N/m²day)"), size = 3, hjust = 0) +
+    geom_text(aes(x = -175, y = 30, 
+                  label = as.character(expression(paste("N excretion (gN ", m^{-2}, day^{-1}, ")")))), 
+              size = 3, hjust = 0, parse = T) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 1))) +
     scale_size_continuous(range = c(0.5, 4), guide = FALSE) +
     theme_worldmap() + 
@@ -129,7 +137,9 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
                data = filter(data, r1_loc_Fp > quantile(data$r1_loc_Fp, 0.95, na.rm = TRUE))) +
     scale_color_manual(values = pal, name = "") +
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
-    geom_text(aes(x = -175, y = 30, label = "P excretion (g P/m²day)"), size = 3, hjust = 0) +
+    geom_text(aes(x = -175, y = 30, 
+                  label = as.character(expression(paste("P excretion (gP ", m^{-2}, day^{-1}, ")")))), 
[…]

### 2021-10-06 R/functions_tables.R

@@ -55,6 +55,7 @@ make_table_mod_mvfun_bm <- function(brmsfit) {
     dplyr::select(-Est.Error) %>%
     dplyr::mutate_if(is.numeric, round, 4) 
   
+  write_csv(tab, here::here("output", "data", "model_output_mod_mvfun_bm.csv"))
   tab
 }
 
@@ -122,33 +123,54 @@ make_table_mod_mvfun_com <- function(brmsfit) {
     dplyr::mutate(across(c(3,4,5), as.numeric)) %>%
     dplyr::mutate_if(is.numeric, round, 4) 
   
+  write_csv(tab, here::here("output", "data", "model_output_mod_mvfun_com.csv"))
+  
   tab
   
 }
 
-
-make_table_mod_mf_com <- function(brmsfit) {
+make_table_mod_mvfun_com2 <- function(brmsfit) {
   
   sum <- summary(brmsfit)
   tab_fixed <- sum$fixed %>%
     as.data.frame() %>%
-    tibble::rownames_to_column("term") %>%
+    tibble::rownames_to_column("name") %>%
+    tidyr::separate(name, into = c("response", "term", "extra"), sep = "_") %>%
+    dplyr::mutate(term = paste0(term,"_", extra)) %>%
     dplyr::mutate(term = str_replace_all(term, "_NA", "")) %>%
     dplyr::mutate(term = str_replace_all(term, "standard", "")) %>%
-    dplyr::mutate(
+    dplyr::mutate(response = case_when(response == "logFn" ~ "log(N excretion)",
+                                       response == "logFp" ~ "log(P excretion)",
+                                       response == "logGc" ~ "log(production)",
+                                       response == "logIherb" ~ "log(herbivory)",
+                                       response == "logIpisc" ~ "log(piscivory)"),
                   term = case_when(term == "logbiomass_tot" ~ "log(biomass)",
                                    term == "mean" ~ "sst",
                                    TRUE ~ term)) %>%
     dplyr::mutate(term = str_replace_all(term, "_q1", "_lb")) %>%
     dplyr::mutate(term = str_replace_all(term, "_q3", "_ub")) %>%
     dplyr::mutate(term = str_replace_all(term, "_m", "_median")) %>%
[…]

### 2021-10-06 R/functions_wrangling.R

@@ -110,30 +110,7 @@ get_lw <- function(sptl){
 ##### ar and troph #####
 
 get_artr <- function(sptl){
- ar <- map(as.list(sptl$Species), possibly(fishflux::aspect_ratio, otherwise =  NA_real_))
- ar2 <- lapply(ar, function(x){
-   if(is.data.frame(x)){
-     return(x$aspect_ratio)
-   } else{return(NA)}
-   }) %>% unlist()
- tr <- map(as.list(sptl$Species), possibly(fishflux::trophic_level, otherwise =  NA_real_))
- tr2 <- lapply(tr, function(x){
-   if(is.data.frame(x)){
-     return(x$trophic_level)
-   } else{return(NA)}
- }) %>% unlist()
- res <- sptl %>% mutate(h_m = tr2, r_m = ar2)
-
- # Family level average for missing
- ar_fam <- group_by(res, Family) %>% 
-   summarize(ar_fam = mean(r_m, na.rm = TRUE), tr_fam = mean(h_m, na.rm = TRUE))
- res <- left_join(res, ar_fam)
-
- res[is.na(res$r_m), "r_m"] <- res[is.na(res$r_m), "ar_fam"]
- res[is.na(res$h_m), "h_m"] <- res[is.na(res$h_m), "tr_fam"]
-
- res <- dplyr::select(res, Species, Family, r_m, h_m)
- 
+ res <- read_csv("data/params_h_r.csv")
  # add weight prop
  wp <- lapply(res$Family, fishflux::wprop) %>% plyr::ldply()
  res$mdwm <- wp$ww

### 2021-10-06 R/plan.R

@@ -37,6 +37,7 @@ plan <- drake_plan(
   output_fluxsum = write.csv(summary_transect, "output/data/flux_summary_transect.csv", row.names = FALSE),
   
   contributions = get_contributions(tfish, cnpflux, params, summary_transect),
+  contributions_site = get_contributions_site(tfish, cnpflux, params, summary_transect),
   sp_loc = unique(select(ungroup(contributions), bioregion, species)),
   
   # herbivory, piscivory 
@@ -65,10 +66,13 @@ plan <- drake_plan(
   #tab_mod_mvfun_com2 = make_table_mod_mvfun_com(mod_mvfun_com2),
   
   ##### contribution analysis #####
-  contr_family = get_cf(contributions, herb_pisc),
-  degree_dominance = get_dd_site(contributions, herb_pisc),
-  sp_importance = get_importance_site(contributions, herb_pisc),
+  #contr_family = get_cf(contributions, herb_pisc),
+  degree_dominance = get_dd_site(contributions_site),
+  sp_importance = get_importance_site(contributions_site),
   freq_dominance = get_fd_site(sp_importance),
+  
+  mod_dd = fit_mod_dd(degree_dominance),
+  mod_fd = fit_mod_fd(freq_dominance),
 
   ##### Species vulnerability #####
   #vulnerability = get_vuln(sptl),

### 2021-10-06 R/test.R

@@ -947,6 +947,7 @@ get_fd <- function(sp_importance){
 
 fd <- get_fd(imp)
 
+key <- degree_dominance
 
 plot1 <-
   ggplot() + 
@@ -965,7 +966,7 @@ plot1 <-
   # geom_pointrange(aes(y = "c", x = pr3[1], xmin = pr3[3], xmax = pr3[4])) +
   # geom_pointrange(aes(y = "b", x = pr4[1], xmin = pr4[3], xmax = pr4[4])) +
   # geom_pointrange(aes(y = "a", x = pr5[1], xmin = pr5[3], xmax = pr5[4])) +
-  geom_vline(xintercept = mean(vec$dd), linetype = 2) +
+   #geom_vline(xintercept = mean(vec$dd), linetype = 2) +
   theme_bw() +
   theme(panel.grid = element_blank()) +
   scale_y_discrete(labels = c("Piscivory", 

### 2021-10-06 text/main.Rmd
almost ready :fish:

@@
 Further, functions are locally dominated by few species, but the identity of dominant species substantially varies at the global scale.
-In fact, more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
+In fact, roughly half of the 1,110 species in our dataset are functionally dominant on a local scale.
 Our results reinforce the need for a nuanced, locally tailored approach to coral reef conservation that considers multiple ecological functions beyond the effect of standing stock biomass.
@@
 However, we also found that at a global scale many species play a dominant role.
-In particular, 70\% of all species contributed disproportionally to a function in at least one community (Fig.
+In particular, 49\% of all species contributed disproportionally to a function in at least one community (Fig.
 4b).
@@
 Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to local trade-offs, drivers, and anthropogenic threats.
+
+## Methods
+
+### 1. Underwater visual census database
+\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019].
+This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans.
+Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019].
+The database only includes transects on the outer reef slope and with a hard reef bottom.
+Transects were carried out at a constant depth, parallel to the reef crest.
+We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm (to minimize the bias related to the identification of small individuals), and rare species for which less than 20 individuals were recorded across all transects.
+The dataset then included 1,110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html).
+Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014].
+All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).
+
+### 2. Quantification of functions
+\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN m^-2^ day^-1^), phosphorus excretion rate (gP m^-2^ day^-1^), production of biomass through growth (gC m^-2^ day^-1^), herbivory, (i.e.
+ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e.
+ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front].
+These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g.
+daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020].
+This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
+We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods).
+We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to obtain the contribution of each individual to each function in each transect.
+Finally, we summarized functions at the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area.
+Each function is thus Epressed as dry mass (of C, N, or P) per day per square meter.
+We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020.
+To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al.
+(2020) [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on Expert opinion [@Mouillot2014; @Parravicini2020] (Fig.
+S5).
+Both the herbivory and piscivory rates match the Expert opinion trophic guild classifications.
+Finally, we estimated multifunction, i.e.
+one measure that combines all five functions by taking the geometric average of the five functions (normalized to a range between zero and 100).
+We used the geometric mean because functions are dependent on each other and vary by several orders of magnitude.
+
+### 3. Community structure variables
+We quantified a set of variables that characterize fish community structure.
+These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
+Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
+The total length is based on visual estimations by divers.
+The immaturity is quantified using the following formula:
+<!-- \begin{equation} -->
+	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
+<!-- 	\label{imm} -->
+<!-- \end{equation} -->
+where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i.
+Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual.
+Finally, trophic level was extracted from Fishbase [@Froese2018].
+
+### 4. Multivariate regression models
+
+We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function.
+For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004].\par
+
+In the underwater visual transect database, 291 transects (3%) did not contain herbivores and 4467 transects (49%) did not contain piscivores yielding zeros for herbivory and piscivory, respectively.
+We considered that these absence of herbivores or piscivores are likely an underestimation of their actual abundance at the surveyed reef site, as all reefs typically host a few herbivores and piscivores (i.e.
+they are likely false-zeros).
+To avoid removing all transects with missing values for herbivory or piscivory (n = 4,620) from our database when running multivariate analyses, we imputed these zeros as missing values, and they were eventually set as parameters in the multivariate models.
+\par
+
+First, we performed a multivariate intercept-only regression model with the five log-transformed functions to estimate the functions per locality.
+The model structure includes intercepts and random effects for localities and sites:
+
+$$\begin{bmatrix}y_{E_{\textrm{N}},i} \\ y_{E_{\textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{\textrm{N}},i} \\ \mu_{E_{\textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
+
+$$\begin{array}{c} \mu_{E_{\textrm{N}},i}  = (\beta0_{E_{\textrm{N}}}  +  \delta_{E_{\textrm{N}}, loc}  +  \delta_{E_{\textrm{N}}, site}) \\
+\mu_{E_{\textrm{P},i}}  = (\beta0_{E_{\textrm{P}}}  +  \delta_{E_{\textrm{P}}, loc}  +  \delta_{E_{\textrm{P}}, site})  \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) , \end{array}$$
+
+$$
+S = \begin{bmatrix}
+\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
+\end{bmatrix}
+R
+\begin{bmatrix}
+\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
+\end{bmatrix},
+$$
+
+where $i$ is the index of the transect, $y_{E_{\textrm{N}},i}$ is the N excretion rate of transect i, $y_{E_{\textrm{P}},i}$ is the P excretion rate, $y_{B,i}$ is the biomass production rate, $y_{H,i}$ is the herbivory rate, $y_{E_{\textrm{N}},i}$ is the piscivory rate, $\sigma$ represents the residual error of each function ($E_{\textrm{N}}$, $E_{\textrm{P}}$, $B$, $H$, and $P$), R is the correlation matrix of the residuals.
+Locality- and site-level effects are also structured including covariation among functions.
+There are thus three correlation matrices in total, meaning that the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality, site, and transect.
+
+\noindent We used non-centered parameterization for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+We used a prior (lkj_{corr}) for each of the three correlation matrices ($R \sim lkj\_corr(1)$).
+
+Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
+The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature.
+We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
+
+$$\begin{bmatrix}y_{E_{\textrm{N}},i} \\ y_{E_{\textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{\textrm{N}},i} \\ \mu_{E_{\textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
+
+$$S = \begin{bmatrix}\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}
+R
+\begin{bmatrix}\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}$$
+
+$$\begin{array}{c} \mu_{E_{\textrm{N}},i} = (\beta0_{E_{\textrm{N}}} +  \delta_{E_{\textrm{N}}, loc} +  \delta_{E_{\textrm{N}}, site}) +{\beta1_{E_{\textrm{N}}}} {{log(biomass),i}} + {\beta2_{E_{\textrm{N}}}} {{SST,i}} \\
+\mu_{E_{\textrm{P}},i} = (\beta0_{E_{\textrm{P}}} +  \delta_{E_{\textrm{P}}, loc} +  \delta_{E_{\textrm{P}}, site}) +{\beta1_{E_{\textrm{P}}}} {{log(biomass),i}} + {\beta2_{E_{\textrm{P}}}} {{SST,i}} \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) +{\beta1_{B}} {{log(biomass),i}} + {\beta2_{B}} {{SST,i}} \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) +{\beta1_{H}} {{log(biomass),i}} + {\beta2_{H}} {{SST,i}} \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) +{\beta1_{P}} {{log(biomass),i}} + {\beta2_{P}} {{SST,i}} \end{array}
+$$
+
+where $\beta1_{E_{\textrm{N}}}, \beta1_{E_{\textrm{P}}}, \beta1_{B}, \beta1_{H}, \beta1_{P}$ are the fixed effects of the log-transformed biomass, and $\beta2_{E_{\textrm{N}}}, \beta2_{E_{\textrm{P}}}, \beta2_{B}, \beta2_{H}, \beta2_{P}$ are the fixed effects of SST.
+Locality- and site-level effects are thus structured including covariation among functions, independent of biomassand SST.
+Similarly, the residual variation of functions incorporates the correlations between functions, without the effect of biomass and SST.
+We used similar priors as described above, and we used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
+
+\noindent Finally, to investigate the effect of community structure while still accounting for the effects of standing biomass and SST, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
+
+$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} {log(biomass),i} + \beta2_{function} {SST,i}  + \beta3_{function} {richness,i}  + \beta4_{function} {size_m,i}  + \beta5_{function} {size_{2.5\%},i} +  \beta6_{function} {size_{97.5\%},i} + \\
+\beta7_{function} {troph_m,i}  + \beta8_{function} {troph_{2.5\%},i} +  \beta9_{function} {troph_{97.5\%},i} + \beta10_{function} {imm_m,i}  + \beta11_{function} {imm_{2.5\%},i} +  \beta12_{function} {imm_{97.5\%},i} \end{array}$$
+
+where $richness$ is the species richness, $size$ is the total length, $troph$ is the trophic level, $imm$ is the immaturity, and $m$, $2.5\%$, and $97.5\%$ represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community, respectively.
+For these models, we used weakly informative priors for the fixed effect parameters ($\beta3-\beta12 \sim normal(0,1)$) and the same priors as described above for other parameters. par
+
+All Bayesian models were fitted using the R package *brms* [@Burkner2017], which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017].
+The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up.
+Thus, a total of 4,000 draws were used to estimate posterior distributions.
+The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig S2).
+
+### 5. Species dominance and contributions to functions
+We quantified the relative contribution of each species to each function for all sites as follows:
+<!-- \begin{equation} -->
+$$	\textrm{contribution}_{f,i,j} = \frac{F_{f,i,j}}{\sum F_{f,j}},$$
+<!-- 	\label{con} -->
+<!-- \end{equation} -->
+where i is a certain species, j is a site, F is the value of function f.
+
+Then, we quantified the degree of species dominance per function for each site.
+We first ranked species according to their contribution to function, then we quantified the cumulative contributions of species to functions.
+Finally, we used the area under the species accumulation curve as a measure for the degree of dominance.
+Specifically, the degree of dominance (DD) for a function performed by R species was calculated as follows:
+
+<!-- \begin{equation} -->
+$$	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},$$
+<!-- 	\label{dd} -->
+<!-- \end{equation} -->
+where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, and $A_max$ is the theoretical area under the curve where one species performs the entire function.
+They are quantified as:
+<!-- \begin{equation} -->
+$$	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},$$
+<!-- 	\label{Amin} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A}_{max} = R - 1,$$
+<!-- 	\label{Amax} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},$$
+<!-- 	\label{A} -->
+<!-- \end{equation} -->
+
+where $C_i$ is the contribution of a certain species and R R equals the species richness in the case of N excretion, P excretion, and production.
+For herbivory and piscivory, R represents the number of herbivores and piscivores, respectively.
+The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that a single species performs the entire function.
+
+Finally, we quantified the frequency of dominance per species (i.e.
+the number of sites in which a species is dominant for a given function divided by the total number of sites in which that species is observed).
+A species is considered dominant for a certain function in a given site if their contribution is higher than 1/R (i.e.
+they contribute more than the situation in which each species contributes equally to a certain function).
 

### 2021-10-15 text/main.Rmd
start of conflict

--- 2021-10-05 text/main.Rmd
@@
 
-# **Title:** Biological trade-offs underlie coral reef ecosystem functioning
+# **Title:** Biological trade-offs underpinning coral reef ecosystem functioning
 
@@
 However, a lack of quantitative assessments of multiple functions across large spatial scales has hindered local and regional conservation efforts.
-We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes.
+We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions associated with elemental cycling mediated by coral reef fishes.
 We show that functions exhibit critical trade-offs driven by varying community structures such that no community can maximize all functions.
 Further, functions are locally dominated by few species, but the identity of dominant species substantially varies at the global scale.
-In fact, more than half of the 1,110 species in our dataset are functionally dominant on a local scale.
+In fact, more than half of the 1,110 species in our dataset are functionally dominant somewhere on a local scale.
 Our results reinforce the need for a nuanced, locally tailored approach to coral reef conservation that considers multiple ecological functions beyond the effect of standing stock biomass.
@@
 **Main Text:**
-The flow of elements through biological communities fuels all ecosystems on earth [@Welti2017]. Humans increasingly threaten biodiversity and ecosystem functioning [@Ceballos2015].
+The flow of elements through biological communities fuels all ecosystems on earth [@Welti2017] . Humans increasingly threaten biodiversity and ecosystem functioning [@Ceballos2015] .
 Coral reefs are a prime example of an ecosystem severely impacted by anthropogenic activities.
-Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reefs [@Hughes2017; @Pauly2002].
-Maintaining ecosystem functions, defined as fluxes of elements, is a major goal for conservation of coral reefs [@Bellwood2019; @Williams2019; @Brandl2019front].
-However, past evaluations of functions on coral reefs have mostly relied on static proxies such as live coral cover, standing stock biomass of reef fishes, or measures of diversity [@Cinner2020; @Mouillot2014; @Mora2011].
-These simplified proxies, although useful, may not properly represent ecological functions because the fluxes of elements can scale non-linearly with variables such as biomass [@Barneche2014].
-Therefore, improving the quantification of ecological functions constitutes an important step towards the efficient management of coral reef ecosystem functioning [@Brandl2019front].
+Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reefs [@Hughes2017; @Pauly2002] .
+Maintaining ecosystem functions, defined as fluxes of elements, is a major goal for conservation of coral reefs [@Bellwood2019; @Williams2019; @Brandl2019front] .
+However, past evaluations of functions on coral reefs have mostly relied on static proxies such as live coral cover, standing stock biomass of reef fishes, or measures of diversity [@Cinner2020; @Mouillot2014; @Mora2011] .
+These simplified proxies, although useful, may not properly represent ecological functions because the fluxes of elements can scale non-linearly with variables such as biomass [@Barneche2014] .
+Therefore, improving the quantification of ecological functions constitutes an important step towards the efficient management of coral reef ecosystem functioning [@Brandl2019front] .
 
-As a dominant group of consumers, coral reef fishes are essential vectors of carbon (C), nitrogen (N) and phosphorus (P) [@McIntyre2008; @Allgeier2014; @Barneche2014].
+As a dominant group of consumers, coral reef fishes are essential vectors of carbon (C), nitrogen (N) and phosphorus (P) [@McIntyre2008; @Allgeier2014; @Barneche2014] .
 Ecosystem functions mediated by coral reef fishes include nutrient cycling, biomass production, herbivory, and piscivory (secondary consumption) (@Brandl2019front).
-While the high diversity of coral reef fishes has inspired many studies that focus on ecosystem functioning, only a handful of studies have attempted to actually quantify functions as continuous fluxes [@Brandl2019front].
-Further, studies that quantify functions as a flow of matter mostly focus on single functions (e.g.
-biomass production [@Morais2019; @Morais2020glob] or fish excretion [ @Allgeier2014]) and are restricted to a small number of species and local scales.
-Consequently, trade-offs amongs multiple functions, their drivers, and their vulnerability to anthropogenic stressors remain poorly understood in coral reef ecosystems across large spatial scales [@Brandl2019front].
+While the high diversity of coral reef fishes has inspired many studies that focus on ecosystem functioning, only a handful of studies have attempted to quantify functions as continuous fluxes [@Brandl2019front] .
+Further, studies that have quantified functions as a flow of matter mostly focused on single functions (e.g.
+biomass production [@Morais2019; @Morais2020glob]  or fish excretion [@Allgeier2014] ) and covered only a small number of species at local scales.
+Consequently, trade-offs among multiple functions, their drivers, and their vulnerability to anthropogenic stressors remain poorly understood in coral reef ecosystems across large spatial scales [@Brandl2019front] .
 
@@
 Using empirical species-specific data on basic organismal processes and Bayesian phylogenetic models, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: N excretion, P excretion, biomass production, herbivory, and piscivory for 1,100 species.
-We apply these bioenergetic models to 9,118 reef fish transects across 585 sites worldwide (Table S1) to:
-(1) quantify community-level reef fish functions and their trade-offs,
-(2) extract the community- and species-level effects on these functions, and
-(3) gauge the vulnerability of reef fish functioning in the Anthropocene.
+We apply these bioenergetic models to 9,118 reef fish transects across 585 sites worldwide (Supplementrary Table 1) to:
+(1) quantify community-level reef fish functions 
+(2) investigate trade-offs among functions,
+(3) extract the community- and species-level effects on these functions.
 
@@
 1).
-Functions across localities show a similar geographocal pattern.
+Functions across localities show a similar geographical pattern.
 However, at the global scale we could not find a single location with high levels of functioning across all functions.
-A measure of multifunctionality thus does not appropriately represent the state of all functions.
+A measure of multifunctionality thus does not appropriately represent the state of all functions assessed independently.
 
-Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front], and we demonstrate a predictably strong relationship between fish biomass and all five functions (Fig.
+Biomass is the most commonly employed indicator of coral reef functioning [@Cinner2020; @Brandl2019front] , and we demonstrate a predictably strong relationship between fish biomass and all five functions (Fig.
 1).
 Specifically, in a multivariate mixed effects Bayesian model, the slopes of the log-transformed biomass were 0.932 (95\%CI: 0.929, 0.934) for N excretion, 1.051 (1.047, 1.056) for P excretion, 0.771 (0.764, 0.780) for production, 0.940 (0.923, 0.957) for herbivory, and 0.668 (0.635, 0.702) for piscivory.
-These slopes indicate that the relationships between biomass and functions are all non-linear, which demonstrates that biomass is not an appropriate proxy for function.
-We also incorporated sea surface temperature (SST) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019].
-We found positive effects of SST on N excretion, production, and herbivory, and no effects of SST on P excretion and piscivory (table S3).
+These slopes indicate that the relationships between biomass and functions are all allometric, which demonstrates that biomass is not an appropriate proxy for function.
+We also incorporated sea surface temperature (SST) because it affects the metabolic and growth rates of fishes, which scales up to the community [@Barneche2019] .
+We found positive effects of SST on N excretion, production, and herbivory, and no effects of SST on P excretion and piscivory (Supplementary Table 3).
 
-The forementioned multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and SST.
-In particular, we estimated correlations between functions on three levels: the locality effects, site effects, and residual variations (Fig. 2, Fig. S1).
+Our multivariate model also allowed us to estimate the correlations between functions, independent of the effects of biomass and SST.
+In particular, we estimated correlations between functions on three levels: the locality effects, site effects, and residual variations (Fig. 2, Extended Data Fig. 1).
 The correlations displayed comparable patterns on each level.
@@
 Each of these components have non-zero effects on at least one of the five functions, suggesting that the observed trade-offs may be, at least in part, rooted in the structure of the focal community (Fig.
-3; Table S4).
+3; Supplementary Table 4).
+Some associations such as the negative and positive effects of trophic level on herbivory and piscivory, respectively, are expected from first principles, whereas others, such as the negative effect of immaturity on P excretion, are not immediately obvious (Fig.
+3).
 
-Beyond community structure, we examined whether functions are driven by specific species across sites.
+Beyond community structure, we examined whether functions are driven by particular species across sites.
 We quantified the degree of dominance inside each community at the site-level and found that, on average, functions are dominated by a small fraction of the species in each community (Fig.
@@
 We also calculated the proportion of species that is dominant in at least one transect (i.e.
-species with a disproportionally high contribution as compared to a community in which all species contribute equally).
-However, we also found that at a global scale many species play a dominant role.
-In particular, 70\% of all species contributed disproportionally to a function in at least one community (Fig.
+species with a disproportionally high contribution as compared to a community in which all species contribute equally), and many species play a dominant role somewhere in the surveyed locations.
+In particular, 49\% of all species contributed disproportionally to a function in at least one surveyed site (Fig.
 4b).
@@
 4c).
-Thus, functions within communities tend to be driven by few dominant species, but the identity of those dominant species varies across sites.
+Thus, functions within communities tend to be driven by few dominant species, and the identity of those dominant species varies across sites.
 
@@
 By quantifying five key processes mediated by coral reef fishes, we demonstrate that coral reef ecosystem functioning is shaped by biological trade-offs, local community structure, and species identity.
-Standing biomass is one of the most commonly employed indicators of coral reef functioning [@Cinner2020; @Brandl2019front], and our analyses confirm the pervasive influence of biomass on all other processes.
-Yet, our results also show non-linear relationships between functions and biomass and suggest that biomass alone does not sufficiently characterize functioning, as we found strong trade-offs among the five functions independent of biomass.
+Standing biomass is one of the most commonly employed indicators of coral reef functioning [@Cinner2020; @Brandl2019front] , and our analyses confirm the pervasive influence of biomass on all other processes.
+Yet, our results also show non-linear relationships between functions and biomass and suggest that biomass alone does not sufficiently characterize functioning; strong trade-offs occurred among the five functions independent of biomass.
 Using biomass as a proxy might, therefore, mask fundamental differences in community-level functioning.
@@
 
-The observed trade-offs among functions are driven by fish community structure and the organismal physiology and life-history traits of its consituents [@Schiettekatte2020; @Schramski2015].
-For example, we observed a clear trade-off between P excretion and biomass production which is mostly driven by the age and trophic structure.
-Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet [@Allgeier2014].
-In contrast, biomass production is high in communities dominated by fishes that occupy low trophic levels because herbivores tend to exhibit higher growth rates [@Morais2018].
-Moreover, P is retained for skeletal growth in young fishes, thus limiting P excretion rates [@Schiettekatte2020; @Hood2005].
-Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].
+The observed trade-offs among functions are driven by fish community structure and the organismal physiology and life-history traits of its consituents [@Schiettekatte2020; @Schramski2015] .
+For example, we observed a clear trade-off between P excretion and biomass production which is mostly driven by the age and trophic structure (Fig. 3).
+Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet [@Allgeier2014] .
+In contrast, biomass production is high in communities dominated by fishes that occupy low trophic levels because herbivores tend to exhibit higher growth rates [@Morais2018] .
+Moreover, P is retained for skeletal growth in young fishes, thus limiting P excretion rates [@Schiettekatte2020; @Hood2005] .
+Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science] .
 
-Our results also reveal that functions consistently rely on a few dominant species, but the identities of local, dominant species strongly vary across sites [@Lefcheck2019].
-Locally, a small number of high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019], which may have led to their designation as functionally-dominant “key species” in various locations [@Bellwood2006].
+Our results also reveal that functions consistently rely on a few dominant species, but the identities of local, dominant species strongly vary across sites [@Lefcheck2019] .
+Locally, a small number of high-performing taxa may disproportionately impact rates of functioning at the community level due to high biomass or abundance [@Topor2019] , which may have led to their designation as functionally-dominant “key species” in various locations [@Bellwood2006] .
 However, our results revealed that no species dominated throughout their geographical range, and more than half of all species contributed disproportionally to a specific function at a at least one site.
-Thus, there are no widespread key species to target for coral reef conservation; rather, local species dominance across functions can guide local conservation efforts, and the preservation of regional reef fish biodiversity should be prioritized in broad-scale policy.
+Thus, there are no widespread key species to target for coral reef conservation aimed at preserving these five functions; rather, local species dominance across functions can guide local conservation efforts, and the preservation of regional reef fish biodiversity should be prioritized in broad-scale policy.
 
-Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
-Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017], and we suggest that these changes will differentially affect ecosystem functioning.
-Intensive fishing and associated reductions in the biomass of large fishes, for example, alters the size, age, and trophic structure of fish communities [@Graham2017].
-When accounting for the effect of biomass, these community shifts can enhance N excretion and production [e.g. @Morais2020glob], but they will negatively impact P excretion, herbivory, and piscivory.
-Further, declines in coral cover related to climate change are often associated with shifts toward herbivores [@Graham2006].
-Herbivores generally contribute little to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth over corals [@Burkepile2013].
+Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems.
+Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017] , and we suggest that these changes will differentially affect ecosystem functioning.
+Intensive fishing and associated reductions in the biomass of large fishes, for example, alters the size, age, and trophic structure of fish communities [@Graham2017] .
+When accounting for the effect of biomass, these community shifts can enhance N excretion and production [e.g. @Morais2020glob] , but they will negatively impact P excretion, herbivory, and piscivory.
+Further, declines in coral cover related to climate change and warming seas at higher latitude coral reefs are often associated with shifts toward herbivores [@Graham2006; @Stuart-Smith2018] .
+Herbivores generally contribute little to P excretion [@Allgeier2014; @Schiettekatte2020] , so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth over corals [@Burkepile2013] .
 
-Sustaining biomass, diversity, and ecosystem functioning are important objectives of most conservation initiatives [@Cinner2020].
+Sustaining biomass, diversity, and ecosystem functioning are important objectives of most conservation initiatives [@Cinner2020] .
 While safeguarding fish biomass enhances functioning, the trade-offs between key functions reveal a critical challenge for coral reef conservation, where actions to enhance one function may negatively impact another.
-For example, the establishment of marine protected areas, which are one of the primary conservation stratigies for coral reefs [@Graham2020], may protect herbivorous species.
-However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020], and community shifts towards herbivore domination may result in the decline of P excretion.
+For example, the establishment of marine protected areas, which are one of the primary conservation stratigies for coral reefs [@Graham2020] , may protect herbivorous species.
+However, marine protected areas do not protect reefs from the pervasive effects of climate change [@Graham2020] , and community shifts towards herbivore domination may result in the decline of P excretion.
 Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions.
 It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions.
-Yet, our comprehension of process-based functioning or the definition a “functional” coral reef is still poorly understood [@Brandl2019front].
+Yet, our comprehension of process-based functioning or the definition a “functional” coral reef is still poorly understood [@Brandl2019front] .
 Establishing functional baselines for global coral reefs is a critical challenge for future studies.
@@
 
-Fig.
-1: Maps of the five key ecosystem functions, multifunctionality, and the relationships between the functions and biomass.
-Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = < 25\%, grey = 25-75\%, color = >75\%).
+**Fig.
+1: Maps of the five key ecosystem functions, multifunctionality, and the relationships between the functions and biomass.** Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = < 25\%, grey = 25-75\%, color = >75\%).
 Black outlines highlight the five localities with the highest values of each function.
@@
 
-Fig.
-2: Correlations of the five functions, accounting for biomass and sea surface temperature.
-a: Modeled correlation coefficients of residual errors.
-Dots represent the average and lines represent the 95%CI.
-b-k: Scatter plots of the mean residual errors of the functions.
+**Fig.
+2: Correlations of the five functions, accounting for biomass and sea surface temperature.** **a**: Modeled correlation coefficients of residual errors.
+Dots represent the average and the 95%CI is too narrow to be shown.
+**b-k**: Scatter plots of the mean residual errors of the functions.
 
-Fig.
+**Fig.
 3.
-Effects of ecological community variables on the five functions.
-Dots indicate fixed effect values from Bayesian linear regressions that examine the effects of species richness, trophic level, size, and immaturity of fishes.
+Effects of ecological community variables on the five functions.** Dots indicate fixed effect values from Bayesian linear regressions that examine the effects of species richness, trophic level, size, and immaturity of fishes.
 To represent both the median and spread of trophic level, size, and immaturity across individuals within a community, we included lower and upper 95% quantile values of these three traits as community variables.
@@
 
-Fig.
-4: Local dominance in species contributions to five ecosystem functions on coral reefs.
-a: The degree of dominance for each function at the site level.
+**Fig.
+4: Local dominance in species contributions to five ecosystem functions on coral reefs.** **a**: The degree of dominance for each function at the site level.
 The degree of dominance of a community ranges between zero (all species contribute equally to the function) and one (a single species is the sole contributor to a given function).
@@
 The vertical dashed line shows the average degree of dominance of 1,000 randomly simulated communities.
-b: Bar plot of the proportion of species that are dominant in at least one site relative to the total number of species, or, for herbivory and piscivory, the total number of herbivores and piscivores, respectively.
-c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present).
+**b**: Bar plot of the proportion of species that are dominant in at least one site relative to the total number of species, or, for herbivory and piscivory, the total number of herbivores and piscivores, respectively.
+**c**: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present).
 A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).
-
-Fig.
-5.
-Vulnerability of the five functions to fishing and climate change-induced coral loss.
-Conceptual scheme of the potential ways in which fishing and climate change can affect functions through their known effects on biomass and community structure.

### 2021-10-15 text/main.Rmd

@@
 species with a disproportionally high contribution as compared to a community in which all species contribute equally), and many species play a dominant role somewhere in the surveyed locations.
-In particular, 49\% of all species contributed disproportionally to a function in at least one surveyed site (Fig.
+In particular, 49\% of all species contributed disproportionally to a function at least one surveyed site (Fig.
 4b).
@@
 Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to local trade-offs, drivers, and anthropogenic threats.
+
+## Methods
+
+### 1. Underwater visual census database
+\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019].
+This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans.
+Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019].
+The database only includes transects on the outer reef slope and with a hard reef bottom.
+Transects were carried out at a constant depth, parallel to the reef crest.
+We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm (to minimize the bias related to the identification of small individuals), and rare species for which less than 20 individuals were recorded across all transects.
+The dataset then included 1,110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
+Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html).
+Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014].
+All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).
+
+### 2. Quantification of functions
+\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN m^-2^ day^-1^), phosphorus excretion rate (gP m^-2^ day^-1^), production of biomass through growth (gC m^-2^ day^-1^), herbivory, (i.e.
+ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e.
+ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front].
+These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g.
+daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020].
+This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
+We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods).
+We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to obtain the contribution of each individual to each function in each transect.
+Finally, we summarized functions at the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area.
+Each function is thus exressed as dry mass (of C, N, or P) per day per square meter.
+We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020.
+To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al.
+(2020) [@Parravicini2020].
+Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on Expert opinion [@Mouillot2014; @Parravicini2020] (Fig.
+S5).
+Both the herbivory and piscivory rates match the Expert opinion trophic guild classifications.
+Finally, we estimated multifunction, i.e.
+one measure that combines all five functions by taking the geometric average of the five functions (normalized to a range between zero and 100).
+We used the geometric mean because functions are dependent on each other and vary by several orders of magnitude.
+
+### 3. Community structure variables
+We quantified a set of variables that characterize fish community structure.
+These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
+Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
+The total length is based on visual estimations by divers.
+The immaturity is quantified using the following formula:
+<!-- \begin{equation} -->
+	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
+<!-- 	\label{imm} -->
+<!-- \end{equation} -->
+where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i.
+Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual.
+Finally, trophic level was extracted from Fishbase [@Froese2018].
+
+### 4. Multivariate regression models
+
+We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function.
+For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004].\par
+
+In the underwater visual transect database, 291 transects (3%) did not contain herbivores and 4467 transects (49%) did not contain piscivores yielding zeros for herbivory and piscivory, respectively.
+We considered that these absence of herbivores or piscivores are likely an underestimation of their actual abundance at the surveyed reef site, as all reefs typically host a few herbivores and piscivores (i.e.
+they are likely false-zeros).
+To avoid removing all transects with missing values for herbivory or piscivory (n = 4,620) from our database when running multivariate analyses, we imputed these zeros as missing values, and they were eventually set as parameters in the multivariate models.
+\par
+
+First, we performed a multivariate intercept-only regression model with the five log-transformed functions to estimate the functions per locality.
+The model structure includes intercepts and random effects for localities and sites:
+
+$$\begin{bmatrix}y_{E_{\textrm{N}},i} \\ y_{E_{\textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{\textrm{N}},i} \\ \mu_{E_{\textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
+
+$$\begin{array}{c} \mu_{E_{\textrm{N}},i}  = (\beta0_{E_{\textrm{N}}}  +  \delta_{E_{\textrm{N}}, loc}  +  \delta_{E_{\textrm{N}}, site}) \\
+\mu_{E_{\textrm{P},i}}  = (\beta0_{E_{\textrm{P}}}  +  \delta_{E_{\textrm{P}}, loc}  +  \delta_{E_{\textrm{P}}, site})  \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) , \end{array}$$
+
+$$
+S = \begin{bmatrix}
+\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
+\end{bmatrix}
+R
+\begin{bmatrix}
+\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P}
+\end{bmatrix},
+$$
+
+where $i$ is the index of the transect, $y_{E_{\textrm{N}},i}$ is the N excretion rate of transect i, $y_{E_{\textrm{P}},i}$ is the P excretion rate, $y_{B,i}$ is the biomass production rate, $y_{H,i}$ is the herbivory rate, $y_{E_{\textrm{N}},i}$ is the piscivory rate, $\sigma$ represents the residual error of each function ($E_{\textrm{N}}$, $E_{\textrm{P}}$, $B$, $H$, and $P$), R is the correlation matrix of the residuals.
+Locality- and site-level effects are also structured including covariation among functions.
+There are thus three correlation matrices in total, meaning that the model will estimate the correlation between functions (independent of biomass and SST) on three levels: locality, site, and transect.
+
+\noindent We used non-centered parameterization for site and location effects and all standard deviations had the following prior: $\sigma \sim student(3, 0, 2.5)$.
+We used a prior (lkj_{corr}) for each of the three correlation matrices ($R \sim lkj\_corr(1)$).
+
+Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
+The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
+Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature.
+We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:
+
+$$\begin{bmatrix}y_{E_{\textrm{N}},i} \\ y_{E_{\textrm{P}},i} \\ y_{B,i} \\ y_{H,i} \\ y_{P,i} \end{bmatrix} \sim MVNormal\left(\begin{bmatrix} \mu_{E_{\textrm{N}},i} \\ \mu_{E_{\textrm{P}},i} \\ \mu_{B,i} \\ \mu_{H,i} \\ \mu_{P,i}\end{bmatrix}, S \right),$$
+
+$$S = \begin{bmatrix}\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}
+R
+\begin{bmatrix}\sigma_{E_{\textrm{N}}} & 0 & 0 & 0 & 0\\
+0 & \sigma_{E_{\textrm{P}}} & 0 & 0 & 0 \\
+0 & 0 & \sigma_{B,i} & 0 & 0\\
+0 & 0 & 0 & \sigma_{H} & 0\\
+0 & 0 & 0 & 0 & \sigma_{P} \end{bmatrix}$$
+
+$$\begin{array}{c} \mu_{E_{\textrm{N}},i} = (\beta0_{E_{\textrm{N}}} +  \delta_{E_{\textrm{N}}, loc} +  \delta_{E_{\textrm{N}}, site}) +{\beta1_{E_{\textrm{N}}}} {{log(biomass),i}} + {\beta2_{E_{\textrm{N}}}} {{SST,i}} \\
+\mu_{E_{\textrm{P}},i} = (\beta0_{E_{\textrm{P}}} +  \delta_{E_{\textrm{P}}, loc} +  \delta_{E_{\textrm{P}}, site}) +{\beta1_{E_{\textrm{P}}}} {{log(biomass),i}} + {\beta2_{E_{\textrm{P}}}} {{SST,i}} \\
+\mu_{\textrm{B,i}} = (\beta0_{B} +  \delta_{B, loc} +  \delta_{B, site}) +{\beta1_{B}} {{log(biomass),i}} + {\beta2_{B}} {{SST,i}} \\
+\mu_{\textrm{H,i}} = (\beta0_{H} +  \delta_{H, loc} +  \delta_{H, site}) +{\beta1_{H}} {{log(biomass),i}} + {\beta2_{H}} {{SST,i}} \\
+\mu_{\textrm{P,i}} = (\beta0_{P} +  \delta_{P, loc} +  \delta_{P, site}) +{\beta1_{P}} {{log(biomass),i}} + {\beta2_{P}} {{SST,i}} \end{array}
+$$
+
+where $\beta1_{E_{\textrm{N}}}, \beta1_{E_{\textrm{P}}}, \beta1_{B}, \beta1_{H}, \beta1_{P}$ are the fixed effects of the log-transformed biomass, and $\beta2_{E_{\textrm{N}}}, \beta2_{E_{\textrm{P}}}, \beta2_{B}, \beta2_{H}, \beta2_{P}$ are the fixed effects of SST.
+Locality- and site-level effects are thus structured including covariation among functions, independent of biomassand SST.
+Similarly, the residual variation of functions incorporates the correlations between functions, without the effect of biomass and SST.
+We used similar priors as described above, and we used weakly-informative normal priors for the model slopes ($\beta1 \sim normal(1,1)$, $\beta2 \sim normal(0,1)$).
+
+\noindent Finally, to investigate the effect of community structure while still accounting for the effects of standing biomass and SST, we fitted a mixed effect multivariate model similar to the model specified above, but adding all community structure variables:
+
+$$\begin{array}{c} \mu_{\textrm{function,i}}  = \beta0_{function} + \beta1_{function} {log(biomass),i} + \beta2_{function} {SST,i}  + \beta3_{function} {richness,i}  + \beta4_{function} {size_m,i}  + \beta5_{function} {size_{2.5\%},i} +  \beta6_{function} {size_{97.5\%},i} + \\
+\beta7_{function} {troph_m,i}  + \beta8_{function} {troph_{2.5\%},i} +  \beta9_{function} {troph_{97.5\%},i} + \beta10_{function} {imm_m,i}  + \beta11_{function} {imm_{2.5\%},i} +  \beta12_{function} {imm_{97.5\%},i} \end{array}$$
+
+where $richness$ is the species richness, $size$ is the total length, $troph$ is the trophic level, $imm$ is the immaturity, and $m$, $2.5\%$, and $97.5\%$ represent the 50\%, 2.5\%, and 97.5\% quantiles across the fish community, respectively.
+For these models, we used weakly informative priors for the fixed effect parameters ($\beta3-\beta12 \sim normal(0,1)$) and the same priors as described above for other parameters. par
+
+All Bayesian models were fitted using the R package *brms* [@Burkner2017], which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017].
+The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up.
+Thus, a total of 4,000 draws were used to estimate posterior distributions.
+The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig S2).
+
+### 5. Species dominance and contributions to functions
+We quantified the relative contribution of each species to each function for all sites as follows:
+<!-- \begin{equation} -->
+$$	\textrm{contribution}_{f,i,j} = \frac{F_{f,i,j}}{\sum F_{f,j}},$$
+<!-- 	\label{con} -->
+<!-- \end{equation} -->
+where i is a certain species, j is a site, F is the value of function f.
+
+Then, we quantified the degree of species dominance per function for each site.
+We first ranked species according to their contribution to function, then we quantified the cumulative contributions of species to functions.
+Finally, we used the area under the species accumulation curve as a measure for the degree of dominance.
+Specifically, the degree of dominance (DD) for a function performed by R species was calculated as follows:
+
+<!-- \begin{equation} -->
+$$	\textrm{DD} = \frac{A - A_{min}}{A_{max} - A_{min}},$$
+<!-- 	\label{dd} -->
+<!-- \end{equation} -->
+where $A$ is the area under the curve, $A_{min}$ is the theoretical area under the curve where each species has an equal contribution to a certain function, and $A_max$ is the theoretical area under the curve where one species performs the entire function.
+They are quantified as:
+<!-- \begin{equation} -->
+$$	\textrm{A}_{min} = \frac{R^2 - 1}{2 R},$$
+<!-- 	\label{Amin} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A}_{max} = R - 1,$$
+<!-- 	\label{Amax} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+$$	\textrm{A} = \sum_{i = 2}^R \frac{C_i + C_{i-1}}{2},$$
+<!-- 	\label{A} -->
+<!-- \end{equation} -->
+
+where $C_i$ is the contribution of a certain species and R R equals the species richness in the case of N excretion, P excretion, and production.
+For herbivory and piscivory, R represents the number of herbivores and piscivores, respectively.
+The degree of dominance thus ranges between 0 and 1, where 0 means that each species contributes equally and 1 means that a single species performs the entire function.
+
+Finally, we quantified the frequency of dominance per species (i.e.
+the number of sites in which a species is dominant for a given function divided by the total number of sites in which that species is observed).
+A species is considered dominant for a certain function in a given site if their contribution is higher than 1/R (i.e.
+they contribute more than the situation in which each species contributes equally to a certain function).
 

### 2022-02-01 text/main.Rmd
figure sizes

@@
 Intensive fishing and associated reductions in the biomass of large fishes, for example, alters the size, age, and trophic structure of fish communities [@Graham2017]  .
-When accounting for the effect of biomass, these community shifts can enhance N excretion and production [e.g. @Morais2020glob] , but they will negatively impact P excretion, herbivory, and piscivory.
+When accounting for the effect of biomass, these community shifts can enhance N excretion and production [e.g.
+@Morais2020glob]  , but they will negatively impact P excretion, herbivory, and piscivory.
 Further, declines in coral cover related to climate change and warming seas at higher latitude coral reefs are often associated with shifts toward herbivores [@Graham2006; @Stuart-Smith2018]  .
@@
 ### 1. Underwater visual census database
-\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019].
+\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019] .
 This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans.
-Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019].
+Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019] .
 The database only includes transects on the outer reef slope and with a hard reef bottom.
@@
 Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html).
-Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014].
+Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014] .
 All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).
@@
 ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e.
-ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front].
+ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front] .
 These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g.
-daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020].
-This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020].
+daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020] .
+This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020] .
 We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods).
@@
 To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al.
-(2020) [@Parravicini2020].
+(2020) [@Parravicini2020] .
 Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on Expert opinion [@Mouillot2014; @Parravicini2020]  (Fig.
@@
 We quantified a set of variables that characterize fish community structure.
-These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020].
+These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020] .
 Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect.
@@
 Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual.
-Finally, trophic level was extracted from Fishbase [@Froese2018].
+Finally, trophic level was extracted from Fishbase [@Froese2018] .
 
@@
 We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function.
-For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004].\par
+For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004] .\par
 
@@
 Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
-The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004].
+The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004] .
 Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature.
@@
 
-All Bayesian models were fitted using the R package *brms* [@Burkner2017], which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017].
+All Bayesian models were fitted using the R package *brms* [@Burkner2017] , which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017] .
 The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up.

### 2022-02-01 R/functions_plots.R

@@ -107,7 +107,7 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
     geom_text(aes(x = -175, y = 30, 
                   label = as.character(expression(paste("N excretion (gN ", m^{-2}, day^{-1}, ")")))), 
-              size = 3, hjust = 0, parse = T) +
+              size = 2, hjust = 0, parse = T) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 1))) +
     scale_size_continuous(range = c(0.5, 4), guide = FALSE) +
     theme_worldmap() + 
@@ -139,7 +139,7 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
     geom_text(aes(x = -175, y = 30, 
                   label = as.character(expression(paste("P excretion (gP ", m^{-2}, day^{-1}, ")")))), 
-              size = 3, hjust = 0, parse = T) +
+              size = 2, hjust = 0, parse = T) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.8))) +
     scale_size_continuous(range = c(0.5, 4), guide = FALSE) +
     theme_worldmap() + 
@@ -171,7 +171,7 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
     geom_text(aes(x = -175, y = 30, 
                   label = as.character(expression(paste("Production (gC ", m^{-2}, day^{-1}, ")")))), 
-              size = 3, hjust = 0, parse = T) +
+              size = 2, hjust = 0, parse = T) +
     guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9))) +
     scale_size_continuous(range = c(0.5, 4), guide = FALSE) +
     theme_worldmap() + 
@@ -208,7 +208,7 @@ make_fig1 <- function(mod_mv_siteloc, mod_mvfun_bm, coords, summary_transect){
     coord_sf(ylim = c(-35, 35), expand = FALSE) +
     geom_text(aes(x = -175, y = 30, label = 
                     as.character(expression(paste("Herbivory (gC ", m^{-2}, day^{-1}, ")")))), 
[…]
